### 2010-10-26 lics/ICont.tex
Init Repo

We begin by defining \ensuremath{\Conid{Cont}}:

\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\Keyword{data}\;\Conid{Cont}\;(\Conid{I}\;\mathbin{:}\;\Conid{Set})\;\mathbin{:}\;\Conid{Set1}\;\Keyword{where}{}\<[E]%
\\
\>[B]{}\hsindent{3}{}\<[3]%
\>[3]{}\_\lhd\_\;\mathbin{:}\;(\Conid{S}\;\mathbin{:}\;\Conid{Set})\;\to \;(\Conid{P}\;\mathbin{:}\;\Conid{S}\;\to \;\Conid{I}\;\to \;\Conid{Set})\;\to \;\Conid{Cont}\;\Conid{I}{}\<[E]%
\\[\blanklineskip]%
\>[B]{}\Varid{sh}\;\mathbin{:}\;\{\mskip1.5mu \Conid{I}\;\mathbin{:}\;\Conid{Set}\mskip1.5mu\}\;\to \;\Conid{Cont}\;\Conid{I}\;\to \;\Conid{Set}{}\<[E]%
\\
\>[B]{}\Varid{sh}\;(\Conid{S}\;\lhd\;\Conid{P})\;\mathrel{=}\;\Conid{S}{}\<[E]%
\\[\blanklineskip]%
\>[B]{}\Varid{po}\;\mathbin{:}\;\{\mskip1.5mu \Conid{I}\;\mathbin{:}\;\Conid{Set}\mskip1.5mu\}\;\to \;(\Conid{C}\;\mathbin{:}\;\Conid{Cont}\;\Conid{I})\;\to \;\Varid{sh}\;\Conid{C}\;\to \;\Conid{I}\;\to \;\Conid{Set}{}\<[E]%
\\
\>[B]{}\Varid{po}\;(\Conid{S}\;\lhd\;\Conid{P})\;\mathrel{=}\;\Conid{P}{}\<[E]%
\\[\blanklineskip]%
\>[B]{}\Conid{ICont}\;\mathbin{:}\;\Conid{Set}\;\to \;\Conid{Set}\;\to \;\Conid{Set1}{}\<[E]%
\\
\>[B]{}\Conid{ICont}\;\Conid{I}\;\Conid{O}\;\mathrel{=}\;\Conid{O}\;\to \;\Conid{Cont}\;\Conid{I}{}\<[E]%
\ColumnHook
\end{hscode}\resethooks

It will be useful to view \ensuremath{\Conid{ICont}}, as \ensuremath{\Conid{O}}-indexed shapes and positions, rather than being an \ensuremath{\Conid{O}}-indexed \ensuremath{\Conid{Cont}}:

\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\Keyword{data}\;\Conid{ICont*}\;(\Conid{I}\;\Conid{O}\;\mathbin{:}\;\Conid{Set})\;\mathbin{:}\;\Conid{Set1}\;\Keyword{where}{}\<[E]%
\\
\>[B]{}\hsindent{3}{}\<[3]%
\>[3]{}\_\lhd\_\;\mathbin{:}\;(\Conid{S}\;\mathbin{:}\;\Conid{O}\;\to \;\Conid{Set})\;\to \;(\Conid{P}\;\mathbin{:}\;(\Varid{o}\;\mathbin{:}\;\Conid{O})\;\to \;\Conid{S}\;\Varid{o}\;\to \;\Conid{I}\;\to \;\Conid{Set})\;\to \;\Conid{ICont*}\;\Conid{I}\;\Conid{O}{}\<[E]%
\\[\blanklineskip]%
\>[B]{}\Varid{ic*}\;\mathbin{:}\;\{\mskip1.5mu \Conid{I}\;\Conid{O}\;\mathbin{:}\;\Conid{Set}\mskip1.5mu\}\;\to \;\Conid{ICont}\;\Conid{I}\;\Conid{O}\;\to \;\Conid{ICont*}\;\Conid{I}\;\Conid{O}{}\<[E]%
\\
\>[B]{}\Varid{ic*}\;\Conid{C}\;\mathrel{=}\;(\lambda\;\Varid{o}\;\to \;\Varid{sh}\;(\Conid{C}\;\Varid{o}))\;\lhd\;\lambda\;\Varid{o}\;\to \;\Varid{po}\;(\Conid{C}\;\Varid{o}){}\<[E]%
\\[\blanklineskip]%
\>[B]{}\Varid{*ic}\;\mathbin{:}\;\{\mskip1.5mu \Conid{I}\;\Conid{O}\;\mathbin{:}\;\Conid{Set}\mskip1.5mu\}\;\to \;\Conid{ICont*}\;\Conid{I}\;\Conid{O}\;\to \;\Conid{ICont}\;\Conid{I}\;\Conid{O}{}\<[E]%
\\
\>[B]{}\Varid{*ic}\;(\Conid{S}\;\lhd\;\Conid{P})\;\Varid{o}\;\mathrel{=}\;\Conid{S}\;\Varid{o}\;\lhd\;\Conid{P}\;\Varid{o}{}\<[E]%
\ColumnHook
\end{hscode}\resethooks

Similarly we define this view which allows us to see a \ensuremath{\Conid{Cont}\;(\Conid{I}\;\Varid{+}\;\Conid{J})} as having 2 sets of positions:

\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
\column{24}{@{}>{\hspre}l<{\hspost}@{}}%
\column{29}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\Keyword{data}\;\Conid{Cont+}\;(\Conid{I}\;\Conid{J}\;\mathbin{:}\;\Conid{Set})\;\mathbin{:}\;\Conid{Set1}\;\Keyword{where}{}\<[E]%
\\
\>[B]{}\hsindent{3}{}\<[3]%
\>[3]{}\_\lhd\_,\anonymous \;\mathbin{:}\;(\Conid{S}\;\mathbin{:}\;\Conid{Set})\;\to \;(\Conid{P}\;\mathbin{:}\;\Conid{S}\;\to \;\Conid{I}\;\to \;\Conid{Set})\;\to \;{}\<[E]%
\\
\>[3]{}\hsindent{21}{}\<[24]%
\>[24]{}(\Conid{Q}\;\mathbin{:}\;\Conid{S}\;\to \;\Conid{J}\;\to \;\Conid{Set})\;\to \;\Conid{Cont+}\;\Conid{I}\;\Conid{J}{}\<[E]%
\\[\blanklineskip]%
\>[B]{}\Varid{sh}\;\mathbin{:}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\mathbin{:}\;\Conid{Set}\mskip1.5mu\}\;\to \;\Conid{Cont+}\;\Conid{I}\;\Conid{J}\;\to \;\Conid{Set}{}\<[E]%
\\
\>[B]{}\Varid{sh}\;(\Conid{S}\;\lhd\;\Conid{P},\Conid{Q})\;\mathrel{=}\;\Conid{S}{}\<[E]%
\\[\blanklineskip]%
\>[B]{}\Varid{po}^I\;\mathbin{:}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\mathbin{:}\;\Conid{Set}\mskip1.5mu\}\;\to \;(\Conid{C}\;\mathbin{:}\;\Conid{Cont+}\;\Conid{I}\;\Conid{J})\;\to \;(\Varid{sh}\;\Conid{C})\;\to \;\Conid{I}\;\to \;\Conid{Set}{}\<[E]%
\\
\>[B]{}\Varid{po}^I\;(\Conid{S}\;\lhd\;\Conid{P},\Conid{Q})\;\mathrel{=}\;\Conid{P}{}\<[E]%
\\[\blanklineskip]%
\>[B]{}\Varid{po}^J\;\mathbin{:}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\mathbin{:}\;\Conid{Set}\mskip1.5mu\}\;\to \;(\Conid{C}\;\mathbin{:}\;\Conid{Cont+}\;\Conid{I}\;\Conid{J})\;\to \;(\Varid{sh}\;\Conid{C})\;\to \;\Conid{J}\;\to \;\Conid{Set}{}\<[E]%
\\
\>[B]{}\Varid{po}^J\;(\Conid{S}\;\lhd\;\Conid{P},\Conid{Q})\;\mathrel{=}\;\Conid{Q}{}\<[E]%
\\[\blanklineskip]%
\>[B]{}\Varid{c+}\;\mathbin{:}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\mathbin{:}\;\Conid{Set}\mskip1.5mu\}\;\to \;\Conid{Cont}\;(\Conid{I}\;\Varid{+}\;\Conid{J})\;\to \;\Conid{Cont+}\;\Conid{I}\;\Conid{J}{}\<[E]%
\\
\>[B]{}\Varid{c+}\;(\Conid{S}\;\lhd\;\Conid{P})\;\mathrel{=}\;\Conid{S}\;\lhd\;(\lambda\;\Varid{s}\;\Varid{i}\;\to \;\Conid{P}\;\Varid{s}\;(\Varid{inl}\;\Varid{i})),(\lambda\;\Varid{s}\;\Varid{j}\;\to \;\Conid{P}\;\Varid{s}\;(\Varid{inr}\;\Varid{j})){}\<[E]%
\\[\blanklineskip]%
\>[B]{}\Conid{ICont+}\;\mathbin{:}\;\Conid{Set}\;\to \;\Conid{Set}\;\to \;\Conid{Set}\;\to \;\Conid{Set1}{}\<[E]%
\\
\>[B]{}\Conid{ICont+}\;\Conid{I}\;\Conid{J}\;\Conid{O}\;\mathrel{=}\;\Conid{O}\;\to \;\Conid{Cont+}\;\Conid{I}\;\Conid{J}{}\<[E]%
\\[\blanklineskip]%
\>[B]{}\Keyword{data}\;\Conid{ICont+*}\;(\Conid{I}\;\Conid{J}\;\Conid{O}\;\mathbin{:}\;\Conid{Set})\;\mathbin{:}\;\Conid{Set1}\;\Keyword{where}{}\<[E]%
\\
\>[B]{}\hsindent{3}{}\<[3]%
\>[3]{}\_\lhd\_,\anonymous \;\mathbin{:}\;(\Conid{S}\;\mathbin{:}\;\Conid{O}\;\to \;\Conid{Set})\;\to \;(\Conid{P}\;\mathbin{:}\;(\Varid{o}\;\mathbin{:}\;\Conid{O})\;\to \;\Conid{S}\;\Varid{o}\;\to \;\Conid{I}\;\to \;\Conid{Set})\;\to \;{}\<[E]%
\\
\>[3]{}\hsindent{26}{}\<[29]%
\>[29]{}(\Conid{Q}\;\mathbin{:}\;(\Varid{o}\;\mathbin{:}\;\Conid{O})\;\to \;\Conid{S}\;\Varid{o}\;\to \;\Conid{J}\;\to \;\Conid{Set})\;\to \;\Conid{ICont+*}\;\Conid{I}\;\Conid{J}\;\Conid{O}{}\<[E]%
\\[\blanklineskip]%
\>[B]{}\Varid{ic+*}\;\mathbin{:}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\Conid{O}\;\mathbin{:}\;\Conid{Set}\mskip1.5mu\}\;\to \;\Conid{ICont+}\;\Conid{I}\;\Conid{J}\;\Conid{O}\;\to \;\Conid{ICont+*}\;\Conid{I}\;\Conid{J}\;\Conid{O}{}\<[E]%
\\
\>[B]{}\Varid{ic+*}\;\Conid{C}\;\mathrel{=}\;(\Varid{\char92 o}\;\to \;\Varid{sh}\;(\Conid{C}\;\Varid{o}))\;\lhd\;(\lambda\;\Varid{o}\;\to \;\Varid{po}^I\;(\Conid{C}\;\Varid{o})),\lambda\;\Varid{o}\;\to \;\Varid{po}^J\;(\Conid{C}\;\Varid{o}){}\<[E]%
\ColumnHook
\end{hscode}\resethooks

\pagebreak

Morphisms in \ensuremath{\Conid{Cont}\;\Conid{I}}:

\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
\column{8}{@{}>{\hspre}l<{\hspost}@{}}%
\column{10}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\Keyword{data}\;\_\Rightarrow\_\;\{\mskip1.5mu \Conid{I}\;\mathbin{:}\;\Conid{Set}\mskip1.5mu\}\;(\Conid{C}\;\Conid{D}\;\mathbin{:}\;\Conid{Cont}\;\Conid{I})\;\mathbin{:}\;\Conid{Set}\;\Keyword{where}{}\<[E]%
\\
\>[B]{}\hsindent{3}{}\<[3]%
\>[3]{}\_\lhd\_\;\mathbin{:}\;{}\<[10]%
\>[10]{}(\Varid{f}\;\mathbin{:}\;\Varid{sh}\;\Conid{C}\;\to \;\Varid{sh}\;\Conid{D})\;\to \;{}\<[E]%
\\
\>[10]{}(\Varid{r}\;\mathbin{:}\;(\Varid{s}\;\mathbin{:}\;\Varid{sh}\;\Conid{C})\;\to \;(\Varid{i}\;\mathbin{:}\;\Conid{I})\;\to \;\Varid{po}\;\Conid{D}\;(\Varid{f}\;\Varid{s})\;\Varid{i}\;\to \;\Varid{po}\;\Conid{C}\;\Varid{s}\;\Varid{i})\;\to \;\Conid{C}\;\Rightarrow\;\Conid{D}{}\<[E]%
\\[\blanklineskip]%
\>[B]{}\Varid{shf}\;\mathbin{:}\;\{\mskip1.5mu \Conid{I}\;\mathbin{:}\;\Conid{Set}\mskip1.5mu\}\;\to \;\{\mskip1.5mu \Conid{C}\;\Conid{D}\;\mathbin{:}\;\Conid{Cont}\;\Conid{I}\mskip1.5mu\}\;\to \;\Conid{C}\;\Rightarrow\;\Conid{D}\;\to \;\Varid{sh}\;\Conid{C}\;\to \;\Varid{sh}\;\Conid{D}{}\<[E]%
\\
\>[B]{}\Varid{shf}\;(\Varid{f}\;\lhd\;\Varid{r})\;\mathrel{=}\;\Varid{f}{}\<[E]%
\\[\blanklineskip]%
\>[B]{}\Varid{pof}\;\mathbin{:}\;{}\<[8]%
\>[8]{}\{\mskip1.5mu \Conid{I}\;\mathbin{:}\;\Conid{Set}\mskip1.5mu\}\;\to \;\{\mskip1.5mu \Conid{C}\;\Conid{D}\;\mathbin{:}\;\Conid{Cont}\;\Conid{I}\mskip1.5mu\}\;\to \;(\Varid{m}\;\mathbin{:}\;\Conid{C}\;\Rightarrow\;\Conid{D})\;\to \;(\Varid{s}\;\mathbin{:}\;\Varid{sh}\;\Conid{C})\;\to \;(\Varid{i}\;\mathbin{:}\;\Conid{I})\;\to \;{}\<[E]%
\\
\>[8]{}(\Varid{po}\;\Conid{D})\;(\Varid{shf}\;\Varid{m}\;\Varid{s})\;\Varid{i}\;\to \;(\Varid{po}\;\Conid{C})\;\Varid{s}\;\Varid{i}{}\<[E]%
\\
\>[B]{}\Varid{pof}\;(\Varid{f}\;\lhd\;\Varid{r})\;\mathrel{=}\;\Varid{r}{}\<[E]%
\\[\blanklineskip]%
\>[B]{}\_\cdot\_\;\mathbin{:}\;\{\mskip1.5mu \Conid{I}\;\mathbin{:}\;\Conid{Set}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{C}\;\Conid{D}\;\Conid{E}\;\mathbin{:}\;\Conid{Cont}\;\Conid{I}\mskip1.5mu\}\;\to \;(\Varid{f}\;\mathbin{:}\;\Conid{D}\;\Rightarrow\;\Conid{E})\;\to \;(\Varid{g}\;\mathbin{:}\;\Conid{C}\;\Rightarrow\;\Conid{D})\;\to \;\Conid{C}\;\Rightarrow\;\Conid{E}{}\<[E]%
\\
\>[B]{}(\Varid{a}\;\lhd\;\Varid{c})\;\cdot\;(\Varid{b}\;\lhd\;\Varid{d})\;\mathrel{=}\;(\lambda\;\Varid{s}\;\to \;\Varid{a}\;(\Varid{b}\;\Varid{s}))\;\lhd\;\lambda\;\Varid{s}\;\Varid{i}\;\Varid{r}\;\to \;\Varid{d}\;\Varid{s}\;\Varid{i}\;(\Varid{c}\;(\Varid{b}\;\Varid{s})\;\Varid{i}\;\Varid{r}){}\<[E]%
\ColumnHook
\end{hscode}\resethooks

Morphisms in \ensuremath{\Conid{ICont}\;\Conid{I}\;\Conid{J}}:

\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
\column{6}{@{}>{\hspre}l<{\hspost}@{}}%
\column{7}{@{}>{\hspre}l<{\hspost}@{}}%
\column{10}{@{}>{\hspre}l<{\hspost}@{}}%
\column{16}{@{}>{\hspre}l<{\hspost}@{}}%
\column{23}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\Keyword{data}\;\_\Rightarrow^*\_\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\mathbin{:}\;\Conid{Set}\mskip1.5mu\}\;(\Conid{C}\;\Conid{D}\;\mathbin{:}\;\Conid{ICont}\;\Conid{I}\;\Conid{J})\;\mathbin{:}\;\Conid{Set}\;\Keyword{where}{}\<[E]%
\\
\>[B]{}\hsindent{3}{}\<[3]%
\>[3]{}\_\lhd\_\;\mathbin{:}\;{}\<[10]%
\>[10]{}(\Varid{f}\;\mathbin{:}\;(\Varid{j}\;\mathbin{:}\;\Conid{J})\;\to \;\Varid{sh}\;(\Conid{C}\;\Varid{j})\;\to \;\Varid{sh}\;(\Conid{D}\;\Varid{j}))\;\to \;{}\<[E]%
\\
\>[10]{}(\Varid{r}\;\mathbin{:}\;{}\<[16]%
\>[16]{}(\Varid{j}\;\mathbin{:}\;\Conid{J})\;(\Varid{s}\;\mathbin{:}\;\Varid{sh}\;(\Conid{C}\;\Varid{j}))\;\to \;{}\<[E]%
\\
\>[16]{}(\Varid{i}\;\mathbin{:}\;\Conid{I})\;\to \;\Varid{po}\;(\Conid{D}\;\Varid{j})\;(\Varid{f}\;\Varid{j}\;\Varid{s})\;\Varid{i}\;\to \;\Varid{po}\;(\Conid{C}\;\Varid{j})\;\Varid{s}\;\Varid{i})\;\to \;{}\<[E]%
\\
\>[10]{}\Conid{C}\;\Rightarrow^*\;\Conid{D}{}\<[E]%
\\[\blanklineskip]%
\>[B]{}\Varid{m*}\;\mathbin{:}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\mathbin{:}\;\Conid{Set}\mskip1.5mu\}\;\to \;\{\mskip1.5mu \Conid{C}\;\Conid{D}\;\mathbin{:}\;\Conid{ICont}\;\Conid{I}\;\Conid{J}\mskip1.5mu\}\;\to \;{}\<[E]%
\\
\>[B]{}\hsindent{6}{}\<[6]%
\>[6]{}((\Varid{j}\;\mathbin{:}\;\Conid{J})\;\to \;\Conid{C}\;\Varid{j}\;\Rightarrow\;\Conid{D}\;\Varid{j})\;\to \;\Conid{C}\;\Rightarrow^*\;\Conid{D}{}\<[E]%
\\
\>[B]{}\Varid{m*}\;\{\mskip1.5mu \anonymous \mskip1.5mu\}\;\{\mskip1.5mu \anonymous \mskip1.5mu\}\;\{\mskip1.5mu \Conid{C}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{D}\mskip1.5mu\}\;\Varid{m}\;{}\<[23]%
\>[23]{}\Keyword{with}\;\Varid{ic*}\;\Conid{C}\;\mid \;\Varid{ic*}\;\Conid{D}{}\<[E]%
\\
\>[B]{}\Varid{m*}\;\{\mskip1.5mu \anonymous \mskip1.5mu\}\;\{\mskip1.5mu \anonymous \mskip1.5mu\}\;\{\mskip1.5mu \Conid{C}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{D}\mskip1.5mu\}\;\Varid{m}\;\mid \;(\Conid{S}\;\lhd\;\Conid{P})\;\mid \;(\Conid{T}\;\lhd\;\Conid{Q})\;\mathrel{=}\;(\lambda\;\Varid{j}\;\to \;\Varid{shf}\;(\Varid{m}\;\Varid{j}))\;\lhd\;\lambda\;\Varid{j}\;\to \;\Varid{pof}\;(\Varid{m}\;\Varid{j}){}\<[E]%
\\[\blanklineskip]%
\>[B]{}\Varid{*m}\;\mathbin{:}\;{}\<[7]%
\>[7]{}\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\mathbin{:}\;\Conid{Set}\mskip1.5mu\}\;\to \;\{\mskip1.5mu \Conid{C}\;\Conid{D}\;\mathbin{:}\;\Conid{ICont}\;\Conid{I}\;\Conid{J}\mskip1.5mu\}\;\to \;{}\<[E]%
\\
\>[7]{}(\Conid{C}\;\Rightarrow^*\;\Conid{D})\;\to \;((\Varid{j}\;\mathbin{:}\;\Conid{J})\;\to \;\Conid{C}\;\Varid{j}\;\Rightarrow\;\Conid{D}\;\Varid{j}){}\<[E]%
\\
\>[B]{}\Varid{*m}\;\{\mskip1.5mu \anonymous \mskip1.5mu\}\;\{\mskip1.5mu \anonymous \mskip1.5mu\}\;\{\mskip1.5mu \Conid{C}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{D}\mskip1.5mu\}\;(\Varid{f}\;\lhd\;\Varid{r})\;\mathrel{=}\;(\lambda\;\Varid{j}\;\to \;\Varid{f}\;\Varid{j}\;\lhd\;\Varid{r}\;\Varid{j}){}\<[E]%
\ColumnHook
\end{hscode}\resethooks

Give rise to functors, we do not prove the laws here, because we do not need them:

\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{8}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\Varid{left\char95 right}\;\mathbin{:}\;\{\mskip1.5mu \Conid{I}\;\mathbin{:}\;\Conid{Set}\mskip1.5mu\}\;\to \;\Conid{Cont}\;\Conid{I}\;\to \;(\Conid{I}\;\to \;\Conid{Set})\;\to \;\Conid{Set}{}\<[E]%
\\
\>[B]{}\Varid{left\char95 right}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\Conid{C}\;\Conid{T}\;\mathrel{=}\;\Sigma\;(\Varid{sh}\;\Conid{C})\;(\lambda\;\Varid{s}\;\to \;(\Varid{i}\;\mathbin{:}\;\Conid{I})\;\to \;\Varid{po}\;\Conid{C}\;\Varid{s}\;\Varid{i}\;\to \;\Conid{T}\;\Varid{i}){}\<[E]%
\\[\blanklineskip]%
\>[B]{}\Varid{\char95 \$\char95 }\;\mathbin{:}\;{}\<[8]%
\>[8]{}\{\mskip1.5mu \Conid{I}\;\mathbin{:}\;\Conid{Set}\mskip1.5mu\}\;\to \;\{\mskip1.5mu \Conid{C}\;\Conid{D}\;\mathbin{:}\;\Conid{Cont}\;\Conid{I}\mskip1.5mu\}\;\to \;(\Varid{m}\;\mathbin{:}\;\Conid{C}\;\Rightarrow\;\Conid{D})\;\to \;\{\mskip1.5mu \Conid{X}\;\mathbin{:}\;\Conid{I}\;\to \;\Conid{Set}\mskip1.5mu\}\;\to \;{}\<[E]%
\\
\>[8]{}\llbracket\;\Conid{C}\;\rrbracket\;\Conid{X}\;\to \;\llbracket\;\Conid{D}\;\rrbracket\;\Conid{X}{}\<[E]%
\\
\>[B]{}\Varid{\char95 \$\char95 }\;\{\mskip1.5mu \anonymous \mskip1.5mu\}\;(\Varid{a}\;\lhd\;\Varid{b})\;(\Varid{s},\Varid{f})\;\mathrel{=}\;\Varid{a}\;\Varid{s},\lambda\;\Varid{i}\;\Varid{q}\;\to \;\Varid{f}\;\Varid{i}\;(\Varid{b}\;\Varid{s}\;\Varid{i}\;\Varid{q}){}\<[E]%
\ColumnHook
\end{hscode}\resethooks

Before we define the least fixed point we define partial application. We begin by defining the functor \ensuremath{\Conid{U}}:

\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{9}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\Conid{U}\;\mathbin{:}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\mathbin{:}\;\Conid{Set}\mskip1.5mu\}\;\to \;\Conid{Cont}\;(\Conid{I}\;\Varid{+}\;\Conid{J})\;\to \;(\Conid{J}\;\to \;\Conid{Set})\;\to \;\Conid{Set}{}\<[E]%
\\
\>[B]{}\Conid{U}\;\Conid{C}\;\Conid{T}\;\mathrel{=}\;\llbracket\;(\Varid{sh}\;\Conid{C})\;\lhd\;(\lambda\;\Varid{s}\;\Varid{j}\;\to \;\Varid{po}\;\Conid{C}\;\Varid{s}\;(\Varid{inr}\;\Varid{j}))\;\rrbracket\;\Conid{T}{}\<[E]%
\\[\blanklineskip]%
\>[B]{}\Varid{mapU}\;\mathbin{:}\;{}\<[9]%
\>[9]{}\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\mathbin{:}\;\Conid{Set}\mskip1.5mu\}\;\to \;(\Conid{C}\;\mathbin{:}\;\Conid{Cont}\;(\Conid{I}\;\Varid{+}\;\Conid{J}))\;\to \;\{\mskip1.5mu \Conid{T}\;\Conid{T'}\;\mathbin{:}\;\Conid{J}\;\to \;\Conid{Set}\mskip1.5mu\}\;\to \;{}\<[E]%
\\
\>[9]{}(\Varid{f}\;\mathbin{:}\;(\Varid{j}\;\mathbin{:}\;\Conid{J})\;\to \;\Conid{T}\;\Varid{j}\;\to \;\Conid{T'}\;\Varid{j})\;\to \;\Conid{U}\;\Conid{C}\;\Conid{T}\;\to \;\Conid{U}\;\Conid{C}\;\Conid{T'}{}\<[E]%
\\
\>[B]{}\Varid{mapU}\;\Conid{C}\;\Varid{f}\;(\Varid{s},\Varid{g})\;\mathrel{=}\;\Varid{s},\lambda\;\Varid{j}\;\Varid{p}\;\to \;\Varid{f}\;\Varid{j}\;(\Varid{g}\;\Varid{j}\;\Varid{p}){}\<[E]%
\ColumnHook
\end{hscode}\resethooks

\pagebreak

And the indexed functor \ensuremath{\Conid{R}}:

\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
\column{6}{@{}>{\hspre}l<{\hspost}@{}}%
\column{9}{@{}>{\hspre}l<{\hspost}@{}}%
\column{41}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\Conid{R}\;\mathbin{:}\;{}\<[6]%
\>[6]{}\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\mathbin{:}\;\Conid{Set}\mskip1.5mu\}\;\to \;(\Conid{C}\;\mathbin{:}\;\Conid{Cont}\;(\Conid{I}\;\Varid{+}\;\Conid{J}))\;\to \;\{\mskip1.5mu \Conid{T}\;\mathbin{:}\;\Conid{J}\;\to \;\Conid{Set}\mskip1.5mu\}\;\to \;{}\<[E]%
\\
\>[6]{}(\Conid{Q}\;\mathbin{:}\;(\Varid{j}\;\mathbin{:}\;\Conid{J})\;\to \;\Conid{T}\;\Varid{j}\;\to \;\Conid{I}\;\to \;\Conid{Set})\;\to \;\Conid{U}\;\Conid{C}\;\Conid{T}\;\to \;\Conid{I}\;\to \;\Conid{Set}{}\<[E]%
\\
\>[B]{}\Conid{R}\;\{\mskip1.5mu \anonymous \mskip1.5mu\}\;\{\mskip1.5mu \Conid{J}\mskip1.5mu\}\;\Conid{C}\;\Conid{Q}\;(\Varid{s},\Varid{f})\;\Varid{i}\;\mathrel{=}\;{}\<[E]%
\\
\>[B]{}\hsindent{6}{}\<[6]%
\>[6]{}\Varid{po}\;\Conid{C}\;\Varid{s}\;(\Varid{inl}\;\Varid{i})\;{}\<[E]%
\\
\>[B]{}\hsindent{3}{}\<[3]%
\>[3]{}\Varid{+}\;{}\<[6]%
\>[6]{}\Sigma\;\Conid{J}\;(\lambda\;\Varid{j}\;\to \;\Sigma\;(\Varid{po}\;\Conid{C}\;\Varid{s}\;(\Varid{inr}\;\Varid{j}))\;(\lambda\;\Varid{p}\;\to \;\Conid{Q}\;\Varid{j}\;(\Varid{f}\;\Varid{j}\;\Varid{p})\;\Varid{i})){}\<[E]%
\\[\blanklineskip]%
\>[B]{}\Varid{mapR}\;\mathbin{:}\;{}\<[9]%
\>[9]{}\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\mathbin{:}\;\Conid{Set}\mskip1.5mu\}\;\to \;(\Conid{C}\;\mathbin{:}\;\Conid{Cont}\;(\Conid{I}\;\Varid{+}\;\Conid{J}))\;\to \;\{\mskip1.5mu \Conid{T}\;\mathbin{:}\;\Conid{J}\;\to \;\Conid{Set}\mskip1.5mu\}\;\to \;{}\<[E]%
\\
\>[9]{}\{\mskip1.5mu \Conid{Q}\;\Conid{Q'}\;\mathbin{:}\;(\Varid{j}\;\mathbin{:}\;\Conid{J})\;\to \;\Conid{T}\;\Varid{j}\;\to \;\Conid{I}\;\to \;\Conid{Set}\mskip1.5mu\}\;{}\<[E]%
\\
\>[9]{}(\Varid{f}\;\mathbin{:}\;(\Varid{j}\;\mathbin{:}\;\Conid{J})\;(\Varid{t}\;\mathbin{:}\;\Conid{T}\;\Varid{j})\;(\Varid{i}\;\mathbin{:}\;\Conid{I})\;\to \;\Conid{Q}\;\Varid{j}\;\Varid{t}\;\Varid{i}\;\to \;\Conid{Q'}\;\Varid{j}\;\Varid{t}\;\Varid{i})\;\to \;{}\<[E]%
\\
\>[9]{}(\Varid{u}\;\mathbin{:}\;\Conid{U}\;\Conid{C}\;\Conid{T})\;(\Varid{i}\;\mathbin{:}\;\Conid{I})\;\to \;\Conid{R}\;\Conid{C}\;\Conid{Q}\;\Varid{u}\;\Varid{i}\;\to \;\Conid{R}\;\Conid{C}\;\Conid{Q'}\;\Varid{u}\;\Varid{i}{}\<[E]%
\\
\>[B]{}\Varid{mapR}\;\Conid{C}\;\Varid{f}\;(\Varid{s},\Varid{g})\;\Varid{i}\;(\Varid{inl}\;\Varid{p})\;{}\<[41]%
\>[41]{}\mathrel{=}\;\Varid{inl}\;\Varid{p}{}\<[E]%
\\
\>[B]{}\Varid{mapR}\;\Conid{C}\;\Varid{f}\;(\Varid{s},\Varid{g})\;\Varid{i}\;(\Varid{inr}\;(\Varid{j},(\Varid{p},\Varid{q})))\;{}\<[41]%
\>[41]{}\mathrel{=}\;\Varid{inr}\;(\Varid{j},(\Varid{p},\Varid{f}\;\Varid{j}\;(\Varid{g}\;\Varid{j}\;\Varid{p})\;\Varid{i}\;\Varid{q})){}\<[E]%
\ColumnHook
\end{hscode}\resethooks

Again, we do not need to prove the functor laws for \ensuremath{\Conid{U}} and \ensuremath{\Conid{R}} but it would be possible in an extensional style.

We will need this relationship between \ensuremath{\Conid{U}} and \ensuremath{\Conid{R}}:

\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{8}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\phi\;\mathbin{:}\;{}\<[8]%
\>[8]{}\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\mathbin{:}\;\Conid{Set}\mskip1.5mu\}\;(\Conid{C}\;\mathbin{:}\;\Conid{Cont}\;(\Conid{I}\;\Varid{+}\;\Conid{J}))\;\{\mskip1.5mu \Conid{T}\;\Conid{T'}\;\mathbin{:}\;\Conid{J}\;\to \;\Conid{Set}\mskip1.5mu\}\;{}\<[E]%
\\
\>[8]{}(\Varid{f}\;\mathbin{:}\;(\Varid{j}\;\mathbin{:}\;\Conid{J})\;\to \;\Conid{T}\;\Varid{j}\;\to \;\Conid{T'}\;\Varid{j})\;{}\<[E]%
\\
\>[8]{}(\Conid{Q'}\;\mathbin{:}\;(\Varid{j}\;\mathbin{:}\;\Conid{J})\;\to \;\Conid{T'}\;\Varid{j}\;\to \;\Conid{I}\;\to \;\Conid{Set})\;(\Varid{u}\;\mathbin{:}\;\Conid{U}\;\Conid{C}\;\Conid{T})\;(\Varid{i}\;\mathbin{:}\;\Conid{I})\;\to \;{}\<[E]%
\\
\>[8]{}\Conid{R}\;\Conid{C}\;\Conid{Q'}\;(\Varid{mapU}\;\Conid{C}\;\Varid{f}\;\Varid{u})\;\Varid{i}\;\to \;\Conid{R}\;\Conid{C}\;(\lambda\;\Varid{j'}\;\Varid{t}\;\Varid{i'}\;\to \;\Conid{Q'}\;\Varid{j'}\;(\Varid{f}\;\Varid{j'}\;\Varid{t})\;\Varid{i'})\;\Varid{u}\;\Varid{i}{}\<[E]%
\\
\>[B]{}\phi\;\Conid{C}\;\Varid{f}\;\Conid{Q'}\;(\Varid{a},\Varid{b})\;\Varid{i}\;\Varid{x}\;\mathrel{=}\;\Varid{x}{}\<[E]%
\ColumnHook
\end{hscode}\resethooks

We now define the partial application of a \ensuremath{\Conid{Cont}\;(\Conid{I}\;\Varid{+}\;\Conid{J})} to an \ensuremath{\Conid{ICont}\;\Conid{I}\;\Conid{J}}, which gives rise to a functor:

\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
\column{10}{@{}>{\hspre}l<{\hspost}@{}}%
\column{21}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\anonymous \;[\mskip1.5mu \anonymous \mskip1.5mu]\;\mathbin{:}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\mathbin{:}\;\Conid{Set}\mskip1.5mu\}\;\to \;(\Conid{C}\;\mathbin{:}\;\Conid{Cont}\;(\Conid{I}\;\Varid{+}\;\Conid{J}))\;\to \;(\Conid{D}\;\mathbin{:}\;\Conid{ICont}\;\Conid{I}\;\Conid{J})\;\to \;\Conid{Cont}\;\Conid{I}{}\<[E]%
\\
\>[B]{}\Conid{C}\;[\mskip1.5mu \Conid{D}\mskip1.5mu]\;{}\<[10]%
\>[10]{}\Keyword{with}\;\Varid{ic*}\;\Conid{D}{}\<[E]%
\\
\>[B]{}\Conid{C}\;[\mskip1.5mu \Conid{D}\mskip1.5mu]\;{}\<[10]%
\>[10]{}\mid \;(\Conid{T}\;\lhd\;\Conid{Q})\;\mathrel{=}\;\Conid{U}\;\Conid{C}\;\Conid{T}\;\lhd\;\Conid{R}\;\Conid{C}\;\Conid{Q}{}\<[E]%
\\[\blanklineskip]%
\>[B]{}\Varid{map}\;[\mskip1.5mu \mskip1.5mu]\;\mathbin{:}\;{}\<[10]%
\>[10]{}\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\mathbin{:}\;\Conid{Set}\mskip1.5mu\}\;(\Conid{C}\;\mathbin{:}\;\Conid{Cont}\;(\Conid{I}\;\Varid{+}\;\Conid{J}))\;\to \;\{\mskip1.5mu \Conid{D}\;\Conid{D'}\;\mathbin{:}\;\Conid{ICont}\;\Conid{I}\;\Conid{J}\mskip1.5mu\}\;\to \;{}\<[E]%
\\
\>[10]{}((\Varid{j}\;\mathbin{:}\;\Conid{J})\;\to \;\Conid{D}\;\Varid{j}\;\Rightarrow\;\Conid{D'}\;\Varid{j})\;\to \;\Conid{C}\;[\mskip1.5mu \Conid{D}\mskip1.5mu]\;\Rightarrow\;\Conid{C}\;[\mskip1.5mu \Conid{D'}\mskip1.5mu]{}\<[E]%
\\
\>[B]{}\Varid{map}\;[\mskip1.5mu \mskip1.5mu]\;\Conid{C}\;\{\mskip1.5mu \Conid{D}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{D'}\mskip1.5mu\}\;\Varid{m}\;{}\<[21]%
\>[21]{}\Keyword{with}\;\Varid{m*}\;\Varid{m}{}\<[E]%
\\
\>[B]{}\Varid{map}\;[\mskip1.5mu \mskip1.5mu]\;\Conid{C}\;\{\mskip1.5mu \Conid{D}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{D'}\mskip1.5mu\}\;\Varid{m}\;{}\<[21]%
\>[21]{}\mid \;(\Varid{f}\;\lhd\;\Varid{r})\;\mathrel{=}\;{}\<[E]%
\\
\>[B]{}\hsindent{3}{}\<[3]%
\>[3]{}\Varid{mapU}\;\Conid{C}\;\Varid{f}\;\lhd\;\lambda\;\Varid{u}\;\Varid{i}\;\Varid{x}\;\to \;\Varid{mapR}\;\Conid{C}\;\Varid{r}\;\Varid{u}\;\Varid{i}\;(\phi\;\Conid{C}\;\Varid{f}\;(\lambda\;\Varid{j}\;\to \;\Varid{po}\;(\Conid{D'}\;\Varid{j}))\;\Varid{u}\;\Varid{i}\;\Varid{x}){}\<[E]%
\ColumnHook
\end{hscode}\resethooks

We can begin the construction of the least fixed point. The shapes inductive containers will be given by \ensuremath{\Conid{W}}-Types, here the constructor \ensuremath{\Varid{sup}} takes advantage of the functor \ensuremath{\Conid{U}}:

\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
\column{10}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\Keyword{data}\;\Conid{W}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\mathbin{:}\;\Conid{Set}\mskip1.5mu\}\;(\Conid{C}\;\mathbin{:}\;\Conid{ICont}\;(\Conid{I}\;\Varid{+}\;\Conid{J})\;\Conid{J})\;(\Varid{j}\;\mathbin{:}\;\Conid{J})\;\mathbin{:}\;\Conid{Set}\;\Keyword{where}{}\<[E]%
\\
\>[B]{}\hsindent{3}{}\<[3]%
\>[3]{}\Varid{sup}\;\mathbin{:}\;\Conid{U}\;(\Conid{C}\;\Varid{j})\;(\Conid{W}\;\Conid{C})\;\to \;\Conid{W}\;\Conid{C}\;\Varid{j}{}\<[E]%
\\[\blanklineskip]%
\>[B]{}\Varid{foldW}\;\mathbin{:}\;{}\<[10]%
\>[10]{}\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\mathbin{:}\;\Conid{Set}\mskip1.5mu\}\;(\Conid{C}\;\mathbin{:}\;\Conid{ICont}\;(\Conid{I}\;\Varid{+}\;\Conid{J})\;\Conid{J})\;(\Conid{D}\;\mathbin{:}\;\Conid{J}\;\to \;\Conid{Set})\;\to \;{}\<[E]%
\\
\>[10]{}((\Varid{j}\;\mathbin{:}\;\Conid{J})\;\to \;\Conid{U}\;(\Conid{C}\;\Varid{j})\;\Conid{D}\;\to \;\Conid{D}\;\Varid{j})\;\to \;(\Varid{j}\;\mathbin{:}\;\Conid{J})\;\to \;\Conid{W}\;\Conid{C}\;\Varid{j}\;\to \;\Conid{D}\;\Varid{j}{}\<[E]%
\\
\>[B]{}\Varid{foldW}\;\Conid{C}\;\Conid{D}\;\Varid{m}\;\Varid{j}\;(\Varid{sup}\;\Varid{u})\;\mathrel{=}\;\Varid{m}\;\Varid{j}\;(\Varid{mapU}\;(\Conid{C}\;\Varid{j})\;(\Varid{foldW}\;\Conid{C}\;\Conid{D}\;\Varid{m})\;\Varid{u}){}\<[E]%
\ColumnHook
\end{hscode}\resethooks

Note that \ensuremath{\Conid{U}^{\mu}} from the paper is simply defined as \ensuremath{\Conid{W}}.

The postions will then be given by paths through such a tree, again we take advatage of the functor \ensuremath{\Conid{R}}.

\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\Conid{R}^{\mu}\;\mathbin{:}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\mathbin{:}\;\Conid{Set}\mskip1.5mu\}\;\to \;(\Conid{C}\;\mathbin{:}\;\Conid{ICont}\;(\Conid{I}\;\Varid{+}\;\Conid{J})\;\Conid{J})\;\to \;(\Varid{j}\;\mathbin{:}\;\Conid{J})\;\to \;\Conid{W}\;\Conid{C}\;\Varid{j}\;\to \;\Conid{I}\;\to \;\Conid{Set}{}\<[E]%
\\
\>[B]{}\Conid{R}^{\mu}\;\Conid{C}\;\Varid{j}\;(\Varid{sup}\;\Varid{u})\;\Varid{i}\;\mathrel{=}\;\Conid{R}\;(\Conid{C}\;\Varid{j})\;(\Conid{R}^{\mu}\;\Conid{C})\;\Varid{u}\;\Varid{i}{}\<[E]%
\ColumnHook
\end{hscode}\resethooks

Note that this definition is not structurally recursive, it is however terminating on the size of the \ensuremath{\Conid{W}}-type.

The fixed point of an \ensuremath{\Conid{ICont}\;(\Conid{I}\;\Varid{+}\;\Conid{J})\;\Conid{J}} is an \ensuremath{\Conid{ICont}\;\Conid{I}\;\Conid{J}}:

\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\mu\;\mathbin{:}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\mathbin{:}\;\Conid{Set}\mskip1.5mu\}\;\to \;(\Conid{F}\;\mathbin{:}\;\Conid{ICont}\;(\Conid{I}\;\Varid{+}\;\Conid{J})\;\Conid{J})\;\to \;\Conid{ICont}\;\Conid{I}\;\Conid{J}{}\<[E]%
\\
\>[B]{}\mu\;\Conid{F}\;\Varid{j}\;\mathrel{=}\;\Conid{W}\;\Conid{F}\;\Varid{j}\;\lhd\;\Conid{R}^{\mu}\;\Conid{F}\;\Varid{j}{}\<[E]%
\ColumnHook
\end{hscode}\resethooks

\pagebreak

The algebra contains a morphism from \ensuremath{\Conid{F}\;[\mskip1.5mu \mu\;\Conid{F}\mskip1.5mu]} to \ensuremath{\mu\;\Conid{F}}, given by:

\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{11}{@{}>{\hspre}l<{\hspost}@{}}%
\column{36}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\Varid{in}\mu\;\mathbin{:}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\mathbin{:}\;\Conid{Set}\mskip1.5mu\}\;(\Conid{F}\;\mathbin{:}\;\Conid{ICont}\;(\Conid{I}\;\Varid{+}\;\Conid{J})\;\Conid{J})\;\to \;(\Varid{j}\;\mathbin{:}\;\Conid{J})\;\to \;(\Conid{F}\;\Varid{j})\;[\mskip1.5mu \mu\;\Conid{F}\mskip1.5mu]\;\Rightarrow\;\mu\;\Conid{F}\;\Varid{j}{}\<[E]%
\\
\>[B]{}\Varid{in}\mu\;\Conid{F}\;\Varid{j}\;{}\<[11]%
\>[11]{}\Keyword{with}\;\Varid{ic+*}\;(\Varid{\char92 j}\;\to \;\Varid{c+}\;(\Conid{F}\;\Varid{j})){}\<[E]%
\\
\>[B]{}\Varid{in}\mu\;\Conid{F}\;\Varid{j}\;{}\<[11]%
\>[11]{}\mid \;(\Conid{S}\;\lhd\;\Conid{P}^I,\Conid{P}^J)\;\mathrel{=}\;\Varid{sup}\;\lhd\;{}\<[36]%
\>[36]{}\lambda\;\anonymous \;\anonymous \;\Varid{r}\;\to \;\Varid{r}{}\<[E]%
\ColumnHook
\end{hscode}\resethooks

And the associated fold by:

\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
\column{10}{@{}>{\hspre}l<{\hspost}@{}}%
\column{11}{@{}>{\hspre}l<{\hspost}@{}}%
\column{15}{@{}>{\hspre}l<{\hspost}@{}}%
\column{23}{@{}>{\hspre}l<{\hspost}@{}}%
\column{48}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\Varid{fold}\mu\;\mathbin{:}\;{}\<[11]%
\>[11]{}\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\mathbin{:}\;\Conid{Set}\mskip1.5mu\}\;\to \;(\Conid{F}\;\mathbin{:}\;\Conid{ICont}\;(\Conid{I}\;\Varid{+}\;\Conid{J})\;\Conid{J})\;\to \;(\Conid{H}\;\mathbin{:}\;\Conid{ICont}\;\Conid{I}\;\Conid{J})\;\to \;{}\<[E]%
\\
\>[11]{}((\Varid{j}\;\mathbin{:}\;\Conid{J})\;\to \;(\Conid{F}\;\Varid{j})\;[\mskip1.5mu \Conid{H}\mskip1.5mu]\;\Rightarrow\;\Conid{H}\;\Varid{j})\;\to \;(\Varid{j}\;\mathbin{:}\;\Conid{J})\;\to \;\mu\;\Conid{F}\;\Varid{j}\;\Rightarrow\;\Conid{H}\;\Varid{j}{}\<[E]%
\\
\>[B]{}\Varid{fold}\mu\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{J}\mskip1.5mu\}\;\Conid{F}\;\Conid{H}\;\Varid{m}\;{}\<[23]%
\>[23]{}\Keyword{with}\;\Varid{m*}\;\Varid{m}{}\<[E]%
\\
\>[B]{}\Varid{fold}\mu\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{J}\mskip1.5mu\}\;\Conid{F}\;\Conid{H}\;\Varid{m}\;{}\<[23]%
\>[23]{}\mid \;(\Varid{a}\;\lhd\;\Varid{b})\;\mathrel{=}\;\Varid{*m}\;(\Varid{foldW}\;\Conid{F}\;{}\<[48]%
\>[48]{}(\lambda\;\Varid{j}\;\to \;\Varid{sh}\;(\Conid{H}\;\Varid{j}))\;\Varid{a}\;\lhd\;\Varid{d}){}\<[E]%
\\
\>[B]{}\hsindent{3}{}\<[3]%
\>[3]{}\Keyword{where}\;{}\<[10]%
\>[10]{}\Varid{d}\;\mathbin{:}\;{}\<[15]%
\>[15]{}(\Varid{j}\;\mathbin{:}\;\Conid{J})\;(\Varid{w}\;\mathbin{:}\;\Conid{W}\;\Conid{F}\;\Varid{j})\;(\Varid{i}\;\mathbin{:}\;\Conid{I})\;\to \;{}\<[E]%
\\
\>[15]{}\Varid{po}\;(\Conid{H}\;\Varid{j})\;(\Varid{foldW}\;\Conid{F}\;(\lambda\;\Varid{j}\;\to \;\Varid{sh}\;(\Conid{H}\;\Varid{j}))\;\Varid{a}\;\Varid{j}\;\Varid{w})\;\Varid{i}\;\to \;\Conid{R}^{\mu}\;\Conid{F}\;\Varid{j}\;\Varid{w}\;\Varid{i}{}\<[E]%
\\
\>[10]{}\Varid{d}\;\Varid{j}\;(\Varid{sup}\;(\Varid{s},\Varid{f}))\;\Varid{i}\;\Varid{q}\;\mathrel{=}\;\Varid{mapR}\;(\Conid{F}\;\Varid{j})\;\Varid{d}\;(\Varid{s},\Varid{f})\;\Varid{i}\;(\Varid{b}\;\Varid{j}\;\anonymous \;\Varid{i}\;\Varid{q}){}\<[E]%
\ColumnHook
\end{hscode}\resethooks

We show that the fold square commutes by observation on the action of the 
container functor.

\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{13}{@{}>{\hspre}l<{\hspost}@{}}%
\column{17}{@{}>{\hspre}l<{\hspost}@{}}%
\column{33}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\Varid{fold}\mu\square\;\mathbin{:}\;{}\<[13]%
\>[13]{}\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\mathbin{:}\;\Conid{Set}\mskip1.5mu\}\;(\Conid{F}\;\mathbin{:}\;\Conid{ICont}\;(\Conid{I}\;\Varid{+}\;\Conid{J})\;\Conid{J})\;(\Conid{H}\;\mathbin{:}\;\Conid{ICont}\;\Conid{I}\;\Conid{J})\;{}\<[E]%
\\
\>[13]{}(\Varid{m}\;\mathbin{:}\;(\Varid{j}\;\mathbin{:}\;\Conid{J})\;\to \;(\Conid{F}\;\Varid{j})\;[\mskip1.5mu \Conid{H}\mskip1.5mu]\;\Rightarrow\;\Conid{H}\;\Varid{j})\;\to \;\{\mskip1.5mu \Conid{X}\;\mathbin{:}\;\Conid{I}\;\to \;\Conid{Set}\mskip1.5mu\}\;{}\<[E]%
\\
\>[13]{}(\Varid{j}\;\mathbin{:}\;\Conid{J})\;\to \;(\Varid{x}\;\mathbin{:}\;\llbracket\;(\Conid{F}\;\Varid{j})\;[\mskip1.5mu \mu\;\Conid{F}\mskip1.5mu]\;\rrbracket\;\Conid{X})\;\to \;{}\<[E]%
\\
\>[13]{}\hsindent{4}{}\<[17]%
\>[17]{}(((\Varid{m}\;\Varid{j})\;\cdot\;(\Varid{map}\;[\mskip1.5mu \mskip1.5mu]\;(\Conid{F}\;\Varid{j})\;(\Varid{fold}\mu\;\Conid{F}\;\Conid{H}\;\Varid{m})))\;\mathbin{\$}\;\Varid{x})\;{}\<[E]%
\\
\>[13]{}\equiv \;{}\<[17]%
\>[17]{}(((\Varid{fold}\mu\;\Conid{F}\;\Conid{H}\;\Varid{m}\;\Varid{j})\;\cdot\;(\Varid{in}\mu\;\Conid{F}\;\Varid{j}))\;\mathbin{\$}\;\Varid{x}){}\<[E]%
\\
\>[B]{}\Varid{fold}\mu\square\;\Conid{F}\;\Conid{H}\;\Varid{m}\;\Varid{j}\;((\Varid{s},\Varid{f}),\Varid{g})\;{}\<[33]%
\>[33]{}\Keyword{with}\;\Varid{m}\;\Varid{j}{}\<[E]%
\\
\>[B]{}\Varid{fold}\mu\square\;\Conid{F}\;\Conid{H}\;\Varid{m}\;\Varid{j}\;((\Varid{s},\Varid{f}),\Varid{g})\;{}\<[33]%
\>[33]{}\mid \;(\Varid{a}\;\lhd\;\Varid{b})\;\mathrel{=}\;\Conid{SigEq}\;\Varid{refl}\;(\equiv\Varid{ext}\;(\lambda\;\Varid{x}\;\Varid{y}\;\to \;\Varid{refl})){}\<[E]%
\ColumnHook
\end{hscode}\resethooks

### 2010-10-26 lics/latex8.tex
Init Repo

%
%  $Description: Author guidelines and sample document in LaTeX 2.09$ 
%
%  $Author: ienne $
%  $Date: 1995/09/15 15:20:59 $
%  $Revision: 1.4 $
%

\documentclass[times, 10pt,twocolumn]{article} 
\usepackage{latex8}
\usepackage{times}

%\documentstyle[times,art10,twocolumn,latex8]{article}

%------------------------------------------------------------------------- 
% take the % away on next line to produce the final camera-ready version 
% \pagestyle{empty}

%------------------------------------------------------------------------- 
\begin{document}

\title{\LaTeX\ Author Guidelines 
       for {\boldmath $8.5 \times 11$-Inch} Proceedings Manuscripts}

\author{Paolo Ienne\\
Swiss Federal Institute of Technology\\ Microcomputing Laboratory \\ IN-F 
Ecublens, 1015 Lausanne, Switzerland\\ Paolo.Ienne@di.epfl.ch\\
% For a paper whose authors are all at the same institution, 
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'', 
% just like the second author.
\and
Second Author\\
Institution2\\
First line of institution2 address\\ Second line of institution2 address\\ 
SecondAuthor@institution2.com\\
}

\maketitle
\thispagestyle{empty}

\begin{abstract}
   The ABSTRACT is to be in fully-justified italicized text, at the top 
   of the left-hand column, below the author and affiliation 
   information. Use the word ``Abstract'' as the title, in 12-point 
   Times, boldface type, centered relative to the column, initially 
   capitalized. The abstract is to be in 10-point, single-spaced type. 
   The abstract may be up to 3 inches (7.62 cm) long. Leave two blank 
   lines after the Abstract, then begin the main text. 
\end{abstract}

%------------------------------------------------------------------------- 
\Section{Introduction}

Please follow the steps outlined below when submitting your 
manuscript to the IEEE Computer Society Press. Note there have 
been some changes to the measurements from previous instructions.

%------------------------------------------------------------------------- 
\Section{Instructions}

Please read the following carefully.

%------------------------------------------------------------------------- 
\SubSection{Language}

All manuscripts must be in English.

%------------------------------------------------------------------------- 
\SubSection{Printing your paper}

Print your properly formatted text on high-quality, $8.5 \times 11$-inch 
white printer paper. A4 paper is also acceptable, but please leave the 
extra 0.5 inch (1.27 cm) at the BOTTOM of the page.

%------------------------------------------------------------------------- 
\SubSection{Margins and page numbering}

All printed material, including text, illustrations, and charts, must be 
kept within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches 
(22.54 cm) high. Do not write or print anything outside the print area. 
Number your pages lightly, in pencil, on the upper right-hand corners of 
the BACKS of the pages (for example, 1/10, 2/10, or 1 of 10, 2 of 10, and 
so forth). Please do not write on the fronts of the pages, nor on the 
lower halves of the backs of the pages.

%------------------------------------------------------------------------ 
\SubSection{Formatting your paper}

All text must be in a two-column format. The total allowable width of 
the text area is 6-7/8 inches (17.5 cm) wide by 8-7/8 inches (22.54 cm) 
high. Columns are to be 3-1/4 inches (8.25 cm) wide, with a 5/16 inch 
(0.8 cm) space between them. The main title (on the first page) should 
begin 1.0 inch (2.54 cm) from the top edge of the page. The second and 
following pages should begin 1.0 inch (2.54 cm) from the top edge. On 
all pages, the bottom margin should be 1-1/8 inches (2.86 cm) from the 
bottom edge of the page for $8.5 \times 11$-inch paper; for A4 paper, 
approximately 1-5/8 inches (4.13 cm) from the bottom edge of the page.

%------------------------------------------------------------------------- 
\SubSection{Type-style and fonts}

Wherever Times is specified, Times Roman may also be used. If neither is 
available on your word processor, please use the font closest in 
appearance to Times that you have access to.

MAIN TITLE. Center the title 1-3/8 inches (3.49 cm) from the top edge of 
the first page. The title should be in Times 14-point, boldface type. 
Capitalize the first letter of nouns, pronouns, verbs, adjectives, and 
adverbs; do not capitalize articles, coordinate conjunctions, or 
prepositions (unless the title begins with such a word). Leave two blank 
lines after the title.

AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title 
and printed in Times 12-point, non-boldface type. This information is to 
be followed by two blank lines.

The ABSTRACT and MAIN TEXT are to be in a two-column format.

MAIN TEXT. Type main text in 10-point Times, single-spaced. Do NOT use 
double-spacing. All paragraphs should be indented 1 pica (approx. 1/6 
inch or 0.422 cm). Make sure your text is fully justified---that is, 
flush left and flush right. Please do not place any additional blank 
lines between paragraphs. Figure and table captions should be 10-point 
Helvetica boldface type as in
\begin{figure}[h]
   \caption{Example of caption.}
\end{figure}

\noindent Long captions should be set as in 
\begin{figure}[h] 
   \caption{Example of long caption requiring more than one line. It is 
     not typed centered but aligned on both sides and indented with an 
     additional margin on both sides of 1~pica.}
\end{figure}

\noindent Callouts should be 9-point Helvetica, non-boldface type. 
Initially capitalize only the first word of section titles and first-, 
second-, and third-order headings.

FIRST-ORDER HEADINGS. (For example, {\large \bf 1. Introduction}) 
should be Times 12-point boldface, initially capitalized, flush left, 
with one blank line before, and one blank line after.

SECOND-ORDER HEADINGS. (For example, {\elvbf 1.1. Database elements}) 
should be Times 11-point boldface, initially capitalized, flush left, 
with one blank line before, and one after. If you require a third-order 
heading (we discourage it), use 10-point Times, boldface, initially 
capitalized, flush left, preceded by one blank line, followed by a period 
and your text on the same line.

%------------------------------------------------------------------------- 
\SubSection{Footnotes}

Please use footnotes sparingly%
\footnote
   {%
     Or, better still, try to avoid footnotes altogether.  To help your 
     readers, avoid using footnotes altogether and include necessary 
     peripheral observations in the text (within parentheses, if you 
     prefer, as in this sentence).
   }
and place them at the bottom of the column on the page on which they are 
referenced. Use Times 8-point type, single-spaced.

%------------------------------------------------------------------------- 
\SubSection{References}

List and number all bibliographical references in 9-point Times, 
single-spaced, at the end of your paper. When referenced in the text, 
enclose the citation number in square brackets, for example~\cite{ex1}. 
Where appropriate, include the name(s) of editors of referenced books.

%------------------------------------------------------------------------- 
\SubSection{Illustrations, graphs, and photographs}

All graphics should be centered. Your artwork must be in place in the 
article (preferably printed as part of the text rather than pasted up). 
If you are using photographs and are able to have halftones made at a 
print shop, use a 100- or 110-line screen. If you must use plain photos, 
they must be pasted onto your manuscript. Use rubber cement to affix the 
images in place. Black and white, clear, glossy-finish photos are 
preferable to color. Supply the best quality photographs and 
illustrations possible. Penciled lines and very fine lines do not 
reproduce well. Remember, the quality of the book cannot be better than 
the originals provided. Do NOT use tape on your pages!

%------------------------------------------------------------------------- 
\SubSection{Color}

The use of color on interior pages (that is, pages other
than the cover) is prohibitively expensive. We publish interior pages in 
color only when it is specifically requested and budgeted for by the 
conference organizers. DO NOT SUBMIT COLOR IMAGES IN YOUR 
PAPERS UNLESS SPECIFICALLY INSTRUCTED TO DO SO.

%------------------------------------------------------------------------- 
\SubSection{Symbols}

If your word processor or typewriter cannot produce Greek letters, 
mathematical symbols, or other graphical elements, please use 
pressure-sensitive (self-adhesive) rub-on symbols or letters (available 
in most stationery stores, art stores, or graphics shops).

%------------------------------------------------------------------------ 
\SubSection{Copyright forms}

You must include your signed IEEE copyright release form when you submit 
your finished paper. We MUST have this form before your paper can be 
published in the proceedings.

%------------------------------------------------------------------------- 
\SubSection{Conclusions}

Please direct any questions to the production editor in charge of these 
proceedings at the IEEE Computer Society Press: Phone (714) 821-8380, or 
Fax (714) 761-1784.

%------------------------------------------------------------------------- 
\nocite{ex1,ex2}
\bibliographystyle{latex8}
\bibliography{latex8}

\end{document}

### 2010-10-26 lics/paper.tex
Init Repo

\documentclass[10pt, conference, compsocconf]{IEEEtran} 
\usepackage{url}
\usepackage{times}
\usepackage{amsmath}
\usepackage{xypic}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{stmaryrd}

\usepackage{color}

%\renewcommand{\cite}[1]{\texttt{[#1]}}

\input{defs.tex}

\begin{document}
\author{\IEEEauthorblockN{Thorsten Altenkirch, Peter Morris}
\IEEEauthorblockA{University of Nottingham\\
Nottingham, UK\\
\{txa,pwm\}@cs.nott.ac.uk}}

\title{Indexed Containers}

\maketitle

\begin{abstract}
  We show that the syntactically rich notion of inductive families can
  be reduced to a core type theory with a fixed number of type
  constructors exploiting the novel notion of indexed containers.
  Indexed containers generalize simple containers, capturing strictly
  positive families instead of just strictly positive types, without
  having to extend the core type theory. Other applications of indexed
  containers include datatype-generic programming and reasoning about
  polymorphic functions. The construction presented here has been
  formalized using the Agda system.
\end{abstract}

\begin{IEEEkeywords}
Type Theory; functional programming;

\end{IEEEkeywords}

\section{Introduction}
\label{sec:intro}

\noindent Inductive datatypes are a central feature of modern Type Theory
(e.g. COQ~\cite{CIC}) or functional programming (e.g. 
Haskell\footnote{Here we shall view Haskell as an approximation of strong
  functional programming as proposed by Turner \cite{sfp} and ignore
non-termination.})
. A simple example
is the type (or set) of de Bruijn $\lambda$-terms $\Lam\in\Set$, which can be
specified as the inductive type generated by the following
constructors
\footnote{Using a 2-dimensional syntax inspired by the
Epigram~\cite{epigram}}:
\[
\ru{i\in\Nat}
{\var\,i \in \Lam}
\qquad
\ru{t,u \in \Lam}
{\app\,t\,u\in\Lam}
\qquad
\ru{t\in\Lam}{\lam\,t\in\Lam}\]\vspace{-5ex}

\noindent
Of course, we don't
have to assume the natural numbers as primitive, but instead give an inductive
definition \`{a} la Peano:

\[
\ax{0 \in \Nat}
\qquad
\ru{n\in\Nat}{\succ\,n\in\Nat}\]\vspace{-5ex}

\noindent
An elegant way to formalize and reason about inductive types is to
model them as the initial algebra of an endofunctor, e.g. in the case of
natural numbers $F_\Nat\,X = 1+X$ and in the case of $\lambda$-terms
$F_\Lam\,X = \Nat + X\times X + X$. This perspective has been very
successful in providing a generic approach to programming with and
reasoning about inductive types, e.g. see the \emph{Algebra of
  Programming} \cite{BirdDeMoor:AlgProp}.

While the theory of inductive types is well developed, we often want
to have a finer, more expressive, notion of types, for example to
ensure the absence of run time errors --- access to arrays out of
range or access to an undefined variable in the previous example of
$\lambda$-terms. To model this we move to the notion of an inductive
family in Type Theory. We can for example define the set of $\lambda$-terms
$\Lam\,n$ with at most $n$ free variables. Indeed, we can view $\Lam$
as a function $\Nat\to\Set$ which assigns to every natural number, $n$,
the type of $\lambda$-terms with $n$ free variables. Functions whose
codomain is $\Set$ we call families. To define $\Lam$ we first
introduce the family of finite sets, $\Fin\in\Nat\to\Set$, which assigns
to $n$ a type with exactly $n$ elements:
\[
\ru{n\in\Nat}{\fzero\in\Fin\,(n+1)}
\qquad
\ru{i\in\Fin\,n}{\fsucc\,i\in\Fin\,(n+1)}\]\vspace{-5ex}

\noindent
which we use to encode the de Bruijn variables in the representation
of $\lambda$-terms ($\Lam\in\Nat\to\Set$):
\[
\ru{i\in\Fin\,n} {\var\,i \in \Lam\,n} \qquad \ru{t,u \in \Lam\,n}
{\app\,t\,u\in\Lam\,n} \qquad
\ru{t\in\Lam\,(n+1)}{\lam\,t\in\Lam\,n}\] \vspace{-5ex}

\noindent
Importantly, the constructor
$\lam$ reduces the number of \emph{free} variables by one --- by
binding one. 
Inductive families may be mutually defined, for example the $\beta$
normal forms and neutral $\lambda$-terms ($\Nf,\Ne \in \Nat\to\Set$)
\[\begin{array}{c}
\ru{i\in\Fin\,n} {\var\,i \in \Ne\,n} \qquad \ru{t\in \Ne\,n\quad u \in \Nf\,n}
{\app\,t\,u\in\Ne\,n}\\
\ru{t\in\Nf\,(n+1)}{\lam\,t\in\Nf\,n}
\qquad
\ru{t\in\Ne\,n}{\mathrm{ne}\,t\in\Nf\,n}\end{array}
\] \vspace{-5ex}

\noindent
Inductive families are the backbone of
dependently typed programming as present in Epigram or
Agda~\cite{Agda}. Coq also supports the definition of inductive families
but programming with them is rather hard --- a situation which has been
improved by the new \texttt{Program} tactic~\cite{sozeau}. 
More recently, the implementation of Generalized Algebraic Datatypes 
(GADTs)~\cite{Hinze:GADT} 
allows $\Fin$ and $\Lam$ to be encoded in Haskell:
\begin{verbatim}
data Fin a where 
  FZero :: Fin (Maybe a)
  FSucc :: Fin a -> Fin (Maybe a)

data Lam a where 
  Var :: Fin a -> Lam a
  App :: Lam a -> Lam a -> Lam a
  Abs :: Lam (Maybe a) -> Lam a
\end{verbatim}
Here \texttt{Fin} and \texttt{Lam} are indexed by types instead of
natural numbers; The type constructor \texttt{Maybe} serves as a type level
copy of the $\succ$ constructor for natural numbers.
Note that \texttt{Lam} is actually just a nested datatype 
\cite{alti:csl99} while \texttt{Fin} exploits the full power of
GADTs because the range of the constructors is constrained.

The initial algebra semantics of inductive types can be extended to
model inductive families by replacing functors on the category $\Set$
with functors on the category of families indexed by a given type - in
the case of $\lambda$-terms this indexing type was $\Nat$. The objects
of the category of families indexed over a type $I \in \Set$ are
$I$-indexed families, i.e. functions of type $I\to\Set$, and a
morphism between $I$-indexed families $A,B\in I \to\Set$ is given by a
family of maps $f\in\Pi i \in I.A\,i \to B\,i$. Indeed, this category
is easily seen to be isomorphic to the slice category $\Set/ I$ but
the chosen representation is more convenient type-theoretically. Using
$\Sigma$-types and equality types from Type Theory, we can define the
following endofunctors $F_\Fin$ and $F_\Lam$ on the category of families
over $\Nat$ whose initial algebras are $\Fin$ and $\Lam$, respectively:
\begin{eqnarray*}
  F_\Fin,F_\Lam & \in & (\Nat\to\Set)\to \Nat\to\Set \\
  F_\Fin\,A\,n & = & \Sigma m\in\Nat.(m+1=n) \times (1 + A\,m)\\
  F_\Lam\,A\,n & = & \Fin\,n + A\,n \times A\, n + A\, (n+1)
\end{eqnarray*}
The equality type expresses the focussed character of the
constructors for $\Fin$.

This approach extends uniformly to more complicated examples such as
the family of typed $\lambda$-terms, using lists of types $[\Ty]$ to
represent typing contexts:
\begin{eqnarray*}
 \Ty & \in & \Set\\
 \Var,\Lam & \in & [\Ty] \to \Ty \to \Set \\
\end{eqnarray*}\vspace{-7ex}

given by the following constructors
\[
\begin{array}{l}
 \ax{\ty \in \Ty}\qquad \ru{\sigma,\tau\in\Ty}{\arr\,\sigma\,\tau\in\Ty}\\
 \ax{\vzero \in \Var\,(\sigma:\Gamma)\,\sigma}
 \qquad
 \ru{x\in \Var\,\Gamma\,\sigma}
 {\vsucc\,x \in \Var\,(\tau:\Gamma)\,\sigma}
 \\
 \ru{x\in\Var\,\Gamma\,\sigma}
 {\var\,x\in\Lam\,\Gamma\,\sigma}
 \quad
 \ru{t\in\Lam\,\Gamma\,(\arr\,\sigma\,\tau)
   \quad u\in\Lam\,\Gamma\,\sigma}
 {\app\,t\,u \in \Lam\,\Gamma\,\tau}
 \\
 \ru{t \in \Lam\,(\sigma:\Gamma)\,\tau}
 {\lam\,t \in \Lam\,\Gamma\,(\arr\,\sigma\,\tau)}
\end{array}\]

\noindent
Types like this can be used to implement a tag-free, terminating
evaluator~\cite{bsn}. To obtain the corresponding functors
is a laborious but straightforward exercise.

\subsection*{Containers}

\noindent The initial algebra semantics is useful to provide a generic
analysis of inductive types exploiting generic concepts such as
constructors and functorial map. However, it cannot say whether such inductive
types actually exist, and it falls short of providing a systematic
characterisation of generic operations such as equality or the
zipper~\cite{huet:zipper,conor:derivative}.

%  While initial algebra semantics explains the {\em inductive} nature of
% inductive types, and in particular features such as pattern
% matching, recursion combinators, inductive proofs etc, it fails to
% provide proper foundations for datatype generic programming where
% generic functions such as map or equality can be defined by analyzing
% the structure of a given datatype. Further, initial algebra semantics
% tells us nothing about which type expressions correspond to a functors
% which have initial algebras. Finally, it says nothing about the
% polymorphic functions between datatypes generated by such type
% expressions.

% There are a number of syntactic approaches to this problem ---
% \txa{Reformulate!}
% e.g. the use of schemes in COQ --- but there is no definite agreement
% on a solution as is exemplied by the number of proposals. 
In previous
work, \cite{alti:cont-tcs,alti:fossacs03}, we have proposed the notion of a container
type: A (unary) container is given by a set of shapes $S\in\Set$ and a
family of positions $P\in S\to\Set$ assigning, to each shape, the set
of positions where data can be stored in a data structure of that
shape. We write $\cont{S}{P}$ for a container, for example the type of lists
is given by $\cont{\Nat}{\Fin}$ indicating that the shape of a list is
a natural number (its length) and lists of length $n$ have $\Fin\,n$
positions where data is stored. Every container $\cont{S}{P}$ gives rise to a
functor $\llbracket \cont{S}{P} \rrbracket\, X = \Sigma s\in S.P\,s \to X$, and containers are closed under forming products, coproducts,
constant exponentiation and taking initial algebras and terminal
coalgebras which model lazy datatypes. Hence, the theory of containers
also provides a convenient way to express that a category has all
strictly positive datatypes.  We have introduced the notion of a
container morphism and showed that they uniquely capture polymorphic
functions/natural transformations between the functors generated by
the containers. The categorical infrastructure required for this interpretation is
quite modest, it works in any Locally Cartesian Closed category with
finite types (i.e.  an initial object and a disjoint boolean object)
and W-types.

While containers provide an elegant foundation for generic programming
with inductive types, in this paper we will develop the theory of
\emph{indexed containers} which allows us to provide a similar
foundation for programming with inductive families like $\Fin$ and
$\Lam$. Our results give us the best of both worlds in that the theory
of ordinary containers carries over to the more expressive indexed
setting, e.g. we can again establish a notion of container morphism
such that the interpretation functor is full and faithful. Maybe most
surprisingly all this additional expressivity comes for free, as far
as the type-theoretic infrastructure is concerned --- W-types are
still enough.

\subsection*{Main results}

\noindent We introduce the notion of indexed container which
generalizes containers allowing us to represent inductive
families. This is a further step from \emph{dependent polynomial
  functors} \cite{HylandGambino} representing endofunctors on a slice
category. Indexed containers as introduced in the present paper allow us
to represent functors between different slices and capture also mutual
and nested inductive definitions.

While Hyland and Gambino \cite{HylandGambino} show that dependent polynomial 
functors always
have initial algebras, we show that indexed containers are closed under 
parametrized initial algebras. Hence we can apply the fixpoint
construction several times. The flexibility of indexed
containers allows us to also establish closure under the adjoints of
reindexing. This leads directly to a grammar for strictly positive
families, which itself is an instance of a strictly positive family 
(section \ref{sec:spf}) --- see also our previous work \cite{alti:cats07,alti:jcats07}.

Our presentation here uses type theoretic notation while our own
previous work on containers and the work on dependent polynomial functors used
categorical notions. While Type Theory can be more bureaucratic in places, it
leads directly to an implementation in a dependently typed programming
language. This is witnessed by our formalisation of the main results
of this paper in Agda (available online~\cite{agdaform}).

 % In
% our present paper we reconstruct and generalize their results in a
% type-theoretic setting: we show closure under \emph{parametrized
%   initial algebras} which allows us to construct mutually defined
% inductive families, we define a notion of morphisms between indexed
% containers and extend our representation theorem to the indexed
% setting, show that indexed containers are closed under a number of
% semantic constructions and exploit this to provide a grammar of
% indexed inductive types.

\subsection*{Related Work}
\label{sec:related-work}

\noindent We have already discussed the relation to our own work on containers
and strictly positive families and to dependent polynomial functors.

Containers are related to Girard's normal functors \cite{GirardNormal} which
themselves are a special case of Joyal's analytic functors
\cite{JoyalA:fonaes} --- those that allow only finite sets of positions.
Fiore, Gambino, Hyland and Winskel's work on generalized species
\cite{fiore2008ccb} considers those concepts in a more generic setting ---
th e precise relation of this work to indexed containers remains to be
explored.

\noindent Perhaps the earliest publication related to indexed containers
occurs in Petersson and Synek's paper
\cite{PS89} from 1989. They present rules extending Martin-L{\"o}f's
type theory with a set constructor for `tree sets' : families of
mutually defined inductive sets, over a fixed index set.

\noindent Inspired in part by Petersson and Synek's constructor,
Hancock, Hyvernat and Setzer \cite{hancock-apal06} applied indexed (and unindexed)
containers, under the name `interaction structures' to the task of
modelling imperative interfaces such as command-response interfaces in
a number of publications.

\subsection*{Acknowledgments}
\label{sec:acknowledgements}

\noindent The present paper grew out of previous joint work with Neil
Ghani, Peter Hancock and Conor McBride. Neil Ghani provided very
elegant proofs of propositions \ref{prop:extfull} and
\ref{prop:adjoints}.  We profited greatly from comments and feedback from our
colleagues in the Functional Programming Laboratory in Nottingham.

\section{Type theoretic preliminaries}

\noindent We work in an extensional
% \footnote{Our construction doesn't rely on the equality reflection rule but can be formalized in an intensional Type Theory with an extensional propositional equality such as Observational Type Theory \cite{alti:ott-conf}.}
Type Theory \cite{martinlof:itt} 
with the following ingredients:
\begin{description}
\item[$\Set_i$] A cumulative hierarchy of universes $\Set_i\inx\Set_{i+1}$ for
  $i\in\Nat$, cumulativity means that $A\in\Set_i$ implies
  $A\in\Set_{i+1}$. We will omit the indices in our development 
  pretending that $\Set\in\Set$ but making sure that all our definitions
  can be stratified.

\item[$0,1$] An empty type $0\in\Set_i$ and a unit type
  $1\in\Set$. Categorically, those correspond to initial and
  terminal objects. For any set $A$ we write $?_A \in 0 \to A$ for the
  unique map of this type. We write $() \in 1$ for the unique
  inhabitant of $1$ and $!_A \in A \to 1$ with $!_A\,a = ()$ for the
  unique map into $1$.

\item[$2$] A type of Booleans $2\in\Set_i$, which is disjoint, i.e. we
  have that $(\mathrm{true} = \mathrm{false})\to 0$ is inhabited.

\item[$\Sigma$- and $\Pi$-types]

\item[]  Given $A\in\Set_i$ and $B\in\Set_i$
  given that $x\in A$ then $\Sigma x\inx A.B, \Pi x\inx A.B \in \Set_i$.
  Elements of $\Sigma$-types are pairs, if $a\in A$ and $b\in B[x:=a]$
  then $(a,b) \in \Sigma x\in A.B$, while elements of $\Pi$-types are
  functions: given $b\in B$ assuming $x\in A$ then $\lambda x.b \in
  \Pi x\inx A.B$% 
  \footnote{We use untyped $\lambda$-abstraction and make sure that
    the type can be inferred from the context.}.

\item[Equality types]

\item[]  Given $a,b\in A \in \Set_i$ we write $a = b \in
  \Set_i$ for the equality type. The constructor for equality is
  reflexivity $\refl\,a \in a=a$ if $a\in A$.

\item[$\WW$-types]

\item[]  As for $\Sigma$ and $\Pi$ Given $A\in\Set_i$ and
  $B\in\Set_i$ given that $x\in A$ then $\WW\,x\inx A.B \in \Set_i$.
  The elements of a $\WW$-type are well-founded trees which are
  constructed using $\sup$: if $w\in\Sigma x\inx A.B\to \WW\,x\inx A.B$ 
  then $\sup\,w \in \WW x\inx A.B$
\footnote{Usually the type of $\sup$ is curried and $\sup$ has two
  arguments instead. This version is more convenient for our purposes.}.
\end{description}
We omit a detailed treatment of eliminators and use functional
programming notation, like if-then-else, dependently typed pattern
matching and structural recursion as present in Agda and Epigram.
All our definitions can be translated into the standard
eliminators at the price of readability.
\txa{Evidence by formalizing in Agda instead?}
To avoid clutter we adopt the usual type-theoretic device of allowing
hidden arguments, if they are inferable from the use. We indicate
hidden arguments by subscripting the type, i.e. writing $\Pi_{x\in
  A}B$ and $\Sigma_{x\in A}B$ instead of $\Pi x\in A.B$ and 
$\Sigma x\in A.B$.

If we ignore the predicative hierarchy, the categorical infrastructure
corresponds to Locally Cartesian Closed category, with initial
objects, a disjoint boolean object and initial algebras for 
functors of the form 
\[F_{\WW x\in A.B} X = \Sigma x\in A.B\to X \]

While finite products arise as non-dependent $\Sigma$-types, finite
coproducts can be represented as
\[ A + B = \Sigma b\in
2. \mathrm{if}\,b\,\mathrm{then}\,A\,\mathrm{else}\,B\] 
Given $f \in A \to C, g \in B \to C$ we define
\begin{align*}
  & \mathrm{case}\,f\,g \in A+B\to C\\
  & \mathrm{case}\,f\,g\,(b,x) =
\mathrm{if}\,b\,\mathrm{then}\,(f\,x)\,\mathrm{else}\,(g\,x)
\end{align*}
Replacing
$\Sigma$ by $\Pi$ this also gives rise to an alternative way to define
$\times$.

% We can also encode the dual of $\WW$-types, i.e. the
% terminal coalgebra of the same $F_\WW$ which we dub M-types using a
% limit-like construction, see \cite{jcontainer}.

\txa{M-types ?}

\section{Indexed functors}
\label{sec:indexed-functors}

\noindent Given $I\in\Set$ we consider the category of families over
$I$. It's objects are families of types $A\in I\to\Set$ and given 
$A,B\in I\to\Set$ a morphism $f$ is a family of functions
$f\in \Pi_{i\in I}A\,i\to B\,i$, identity and composition are
obvious. We denote this category as $\Fam\,I$. Indeed $\Fam\,I$ is
isomorphic to the slice category $\Set/I$ whose objects are morphisms
$J \to I$ for some $J\in\Set$ and whose morphisms are commuting
triangles.

An indexed functor over $I\in\Set$ is a functor from $\Fam\,I$ to
$\Set$, to make this precise an indexed functor $F$ is given by
\begin{eqnarray*}
  \obj{F} & \in & (I \to \Set) \to \Set\\
  \mor{F} & \in & \Pi_{A,B\in I\to\Set}(\Pi_{i\in I} A\,i \to B\,i)
  \to F\,A \to F\,B
\end{eqnarray*}
subject to the conditions that $\mor{F}$ preserves identity and
composition. As usual we omit the annotations when the meaning is
clear from the context and overload $F$ to mean $\obj{F}$ and
$\mor{F}$.

Given two indexed functors $F,G$ a family of maps 
\[ \alpha \in \Pi A\in I\to\Set.F\,A \to G\,A\] is a natural
transformation, if the naturality condition 
($G\, f \circ \alpha\, A = \alpha\,B\circ F\,f$ for $f\in \Pi_{i\in I} A\,i \to B\,i$)
holds. 
We write $F \nattfn G$ for the set of
natural transformations and $\Func\,I$ for the category of
indexed functors and natural transformations.

$\Func$ comes with a monad-like structure, we have
\begin{align*}
& \returnF \in I \to \Func\,I\\  
& \returnF\,i\,A = A\,i
\end{align*}
and given $F\in \Func\,I$ and $H\in I\to\Func\,J$ we construct
\begin{align*}
& F \bindF H \in \Func\,J \\
& (F \bindF H)\,A = F\,(\lambda i.H\,i\,A)
\end{align*}
it is easy to see that the usual equations for a monad hold. It is not
actually a monad since $\Func : \Set_i \to \Set_{i+1}$ is not closed
at any level.
\footnote{The situation is similar as in \cite{alti:csl99} where we called this a \emph{Kleisli structure}.}
% . $\Func$ is, however, a monoid in the category of endofunctors
% from $\Set_i$ to $\Set_{i+1}$.

The opposite of the Kleisli category associated to $\Func$ has as
objects sets $I,J\in \Set$ and morphisms given by an $J$-indexed
family of $I$-indexed functors.  We overload $\Func$ and write
$\Func\,I\,J = J \to \Func\,I$. We use the opposite of the Kleisli
category so that $F\in \Func\,I\,J$ is a functor from $\Fam\,I$ to
$\Fam\,J$. Indeed given $A\in \Fam\,I$ we write:
\begin{gather*}
  F @ A \in \Fam\,J\\
  (F @ A)\,j = F\,j\,A
\end{gather*}
This construction also extends to natural transformations,
i.e. the set of natural transformation between $F,G \in \Func\,I\,O$
is given by $\Pi o\in O.F\,o \nattfn G\,o$.
% Kleisli categories inherit products
% from the underlying category and hence $\Func$ has finite products
% given by coproducts in $\Set$.

There are several operations which we can use to construct indexed
functors. Clearly the Kleisli structure gives identities and
composition in $\Func$. Assuming $f\in O\to O'$, reindexing 
is defined by composition:
\begin{align*}
  & \FDelta\,f \in \Func\,I\,O' \to \Func\,I\,O\\
  & \FDelta\,f\,F = F \circ f
\end{align*}
Notice the contravariance in the above definition which is to be
expected of reindexing. An example of the use of
reindexing occurs in the definition of the indexed functor whose
fixed point is $\Lam$ where we need to turn an indexed functor $F$
into an indexed functor $F'$ defined by $F'\,n\,X = F\,(n+1)\,X$. In
this situation, $F'$ is just $\FDelta\,(+1)\,F$.

Unsurprisingly, $\FDelta\,f$ has both left and right adjoints, those
are given by 
\begin{align*}
  &\FSigma\,f,\FPi\,f \in \Func\,I\,O \to \Func\,I\,O'\\
  &\FSigma\,f\,F = \lambda X,o.\Sigma o'\in O'.f\,o = o' \times
  F\,X\,o'\\
  &\FPi\,f\,F = 
  \lambda X,o.\Pi o'\in O'.f\,o = o' \to
  F\,X\,o'
\end{align*}
$\FSigma$ is used in the construction of $F_\Fin$:
\begin{gather*}
F_\Fin = F\,\mathrm{succ}\,(\lambda A\,m.1 + A\,m)
\end{gather*}
Finite coproducts and products of indexed functors arise as special
cases of $\FSigma$ and $\FPi$. Given $F,G \in \Func\,I$ we construct
\begin{align*}
  &H_0 \in \Func\,I\,0\\
  &H_0 = ?_{\Func\,I}\\
  &H_2 \in \Func\,I\,2\\
  &H_2 = \lambda b.\mathrm{if}\,b\,\mathrm{then}\,F\,\mathrm{else}\,G 
\end{align*}
Using the family of unique forgetful functions $!_A\in A \to 1$ we obtain
\begin{align*}
  &\FK_0,F \Fplus G, \FK_1, F\Ftimes G \in \Func\, I\,1 \simeq \Func\,I\\
  &\FK_0 = \FSigma\,!_0\,H_0\\
  &F \Fplus G = \FSigma\,!_2\,H_2\\
  &\FK_1 = \FPi\,!_0\,H_0\\
  &F \Ftimes G = \FPi\,!_2\,H_2
\end{align*}
More concretely $\FK_0,\FK_1$ are simply the constant functors
returning $0$ (resp. $1$), and $F\Fplus G$ and $F\Ftimes G$ are the point-wise
coproducts (resp. coproducts) of $F$ and $G$. The reduction to $\FSigma$ and 
$\FPi$ means we don't have to explain the behaviour of these constructs, it
is inherited.

In the examples we only used finite products, the more general case of
$\FPi$ is relevant when we define infinitely branching trees.

\section{Initial algebras of indexed functors}
\label{sec:init-algebr-index}

\noindent Given an indexed endofunctor $F\in \Func\,I\,I$ we can apply the usual
notion of initial algebra, To spell it out: an $F$-algebra $(A,a)$ is a
family $A:\Fam\,I$ together with a function in $\Fam\,I$:
$a:\Pi_{i\in I}(F @ A)\, i \to A\, i$. Given $F$-algebras $(A,a)$ and
$(B,b)$ a morphism is a function $f:\Pi_{i\in I}A\, i \to B\, i$ s.t.
\[
\xymatrix{
F @ A  \ar[r]^{a} 
\ar[d]_{F @ f} & A \ar[d]^{f}\\
F @ B \ar[r]^{b} & B}
\]
An initial $F$-algebra $(\mu^0\,F,\inn)$  is the initial object in this category, if it exists.
Initial algebras of functors don't always exist as we already know
from the non-indexed case (which arises as a special case of indexed
functors where $I=1$). For example the functor $F\in \Set \to \Set$
given by $F\,A = (A \to 2) \to 2$ hasn't got an initial algebra in a
predicative theory.

We can apply the initial algebra construction only once, because it takes us from 
an indexed functor $F\in \Func\,I\,I$ to the category of families
$\mu^0\,F\in\Fam\,I$. Hence we can't define nested or mutual inductive families.
To overcome this we introduce parametrized initial objects.

Coproducts of indexed functors correspond to indexed functors on the product of
slices, i.e. just by looking at the object part:
\begin{align*}
& \Func\,(I+J)\\
& = (I + J \to \Set) \to \Set \\
& \simeq (I \to \Set) \times (J \to \Set) \to \Set
\end{align*}
We can curry the last line:
\begin{align*}
& \simeq (I \to \Set) \to (J \to \Set) \to \Set
\end{align*}
This gives rise to partial application of an indexed functor which we
will employ in our definition of parametrized initial
algebras.
\begin{align*}
&\ru{\begin{array}{l}F \in \Func\,(I+J)\,J \\
  G \in \Func\,I\,J\end{array}}
{F[G] \in \Func\,I\,J}\\
\\
&F[G]\,j\,A = F\,j\,(\mathrm{case}\,A\,(G @ A))
\end{align*}
This definition is functorial, i.e. given $\alpha \in G \nattfn H$
we obtain $F[\alpha] \in F[G] \nattfn F[H]$.

Given $F\in \Func\,(I+J)\,J$ a parametrized $F$-algebra is given by 
an indexed functor $G\in\Func\,I\,J$ and a natural transformation
$\alpha \in F[G] \nattfn G$. A morphism between two parametrized
$F$-algebras $(G,\alpha)$ and $(H,\beta)$ is a natural
transformation $\gamma \in G \nattfn H$ such that 
\[
\xymatrix{
F[G]  \ar[r]^{\alpha} 
\ar[d]_{F[\gamma]} & G \ar[d]^{\gamma}\\
F[H] \ar[r]^{\beta} & H}
\]
The parametrized initial algebra of $F$, i.e. the initial object in
the category of parametrized $F$-algebras, we denote by
$(\mu^I\,F,\inn_F)$, if it exists. The special case of $I=0$
corresponds to non-parametrized algebras.

\section{Indexed containers}
\label{sec:indexed-container}

\noindent Given $I\in\Set$ we define the category $\Cont\,I$ of indexed
containers over $I$, together with an extension functor $\ExtC{-}\in
\Cont\,I\to\Func\,I$. While an ordinary container is a pair of a set
of shapes and a family of positions indexed by shapes, an indexed
container also consists of a set of shapes
\begin{gather*}
  S \in \Set
\end{gather*}
and a family of positions indexed by shapes and the indexing set $I$:
\begin{gather*}
  P\in S\to I \to\Set.
\end{gather*}
We denote this container as
\[\cont{S}{P}\in\Cont\,I.\] 
Its extension is given as:
\begin{align*}
& \ExtC{\cont{S}{P}} \in \Func\,I\\  
& \obj{\ExtC{\cont{S}{P}}}\,A = \Sigma s\in
  S.\Pi_{i\in I}P\,s\,i \to A\,i\\
& \mor{\ExtC{\cont{S}{P}}}\,f\,(s,h) = (s,\lambda i\in I.f\,i \circ h\,i)  
\end{align*}
Given indexed containers
$\cont{S}{P},\cont{T}{Q}\in \Cont\,I$ a container morphism is given by
a function on shapes 
\[ f\in S\to T \] 
and an $I$-indexed contravariant
function on positions 
\[r\in\Pi_{s\in S,i\in I}Q\,(f\,s)\,i\to P\,s\,i.\] 
We write the morphism as 
\[\cont{f}{r}\in \Cont\,I\,(\cont{S}{P})\,(\cont{T}{Q}) \]
The extension of a container morphism is a
natural transformation between the associated functors given by:
\begin{align*}
& \ExtC{\cont{f}{r}} \in
  \Pi X\in I\to\Set.\ExtC{\cont{S}{P}}\,X \to \ExtC{\cont{T}{Q}}\,X\\
& \ExtC{\cont{f}{r}}\,X\,.(s,h) = (f\,s,\lambda q.h\,(r\,q))
\end{align*}
As for ordinary containers (see \cite{alti:cont-tcs}) we can show 
\begin{proposition}\label{prop:extfull}
  The extension functor $\ExtC{-}\in\Cont\,I\to\Func\,I$ is full and faithful.
\end{proposition}

We will now lift the operations we have previously defined on indexed
functors to indexed containers. However, as we will see -- unlike indexed
functors -- indexed containers always admit initial algebras. We start
with identifying the monadic structure on $\Cont$ which is preserved
by $\ExtC{-}$:
\begin{align*}
  & \returnC \in I \to \Cont\,I \\
  & \returnC\,i = (1,\lambda s,j.i=j)
\end{align*}
Given 
$H = \lambda i.\cont{S\,i}{P\,i}\in I\to\Cont\,J$ with $S\in I\to
\Set$ and $P\in\Pi i\in I.S\,i\to J\to\Set$ and $\cont{T}{Q}\in \Cont\,I$:
\begin{align*}
& \cont{T}{Q} \bindC H \in \Cont\,J \\
& (\cont{T}{Q} \bindC H) = \cont{U}{R}\\
&\quad\mathrm{with}\;\;\\
&\quad\;\; U \in \Set \\
&\quad\;\; U = \ExtC{\cont{T}{Q}}\,S \\
&\quad\;\; R \in U \to I \to \Set \\
&\quad\;\; R\,(t,f)\,i = \Sigma q\in Q\,t\,i,j\in J.P\,i\,(F\,i\,q)\,j
\end{align*}
The operations satisfy the monadic laws, modulo the change in universe level,
as in the monadic structure on indexed functors. Moreover,
the monadic structure is preserved by the extension
operation.

As in the case of $\Func$ this gives rise to the category $\Cont$,
whose objects are sets $I,J\in\Set$ and morphisms are 
$\Cont\,I\,J = J \to \Cont\,I$. We will exploit that the elements of 
$\Cont\,I\,J$ can be isomorphically represented as a pair:
\begin{gather*}
  \vec{S} \in J \to \Set\\
  \vec{P} \in \Pi_{j\in J}\vec{S}\,j \to I \to \Set
\end{gather*}
and write $\cont{\vec{S}}{\vec{P}} \in \Cont\,I\,J$.

The definition of reindexing carries
over without change from indexed functors, i.e. given $f\in O\to O'$, we define 
$\CDelta\,f \in \Cont\,I\,O' \to \Cont\,I\,O$ by $\CDelta\,f\,F = F \circ f$
Moreover, we can define its adjoints on indexed containers:
\begin{align*}
  &\CSigma\,f,\CPi\,f & \in & \Cont\,I\,O \to \Cont\,I\,O'\\
  &\CSigma\,f (\cont{\vec{S}}{\vec{P}})
  & = &\lambda o.\Sigma o'\in O'.f\,o = o' \times \vec{S}\,o'\\
  && \lhd &\lambda o,(\_,\_,s).P\,s\\
  & \CSigma\,f (\cont{\vec{S}}{\vec{P}})
  & = & \lambda o.\Pi_{o'\in O'}f\,o = o' \to \vec{S}\,o' \\
  &&\lhd & \lambda o,g. \Sigma o\in O,e\in f\,o = p,\vec{P}\,(g\,e)
\end{align*}
It is easy to see that $\ExtC{\CSigma\,f\,(\cont{S}{P}} \simeq
\FSigma\,f\,\ExtC{\cont{S}{P}}$ and 
$\ExtC{\CPi\,f\,(\cont{S}{P})} \simeq
\FPi\,f\,\ExtC{\cont{S}{P}}$ and using proposition \ref{prop:extfull} we can conclude
\begin{proposition}\label{prop:adjoints}
  Reindexing of indexed containers $\CDelta\,f$ has left and right adjoints
  \[ \CSigma\,f \vdash \CDelta\,f \vdash \CPi\,F \]
  and this structure is preserved by $\ExtC{-}$.
\end{proposition}
Using the construction in section \ref{sec:indexed-functors} this entails that
indexed containers are closed under coproducts and products.

\section{Initial algebras of containers}
\label{sec:initial-algebras}

\hyphenation{endo-functor}

\noindent An indexed container $\cont{\vec{S}}{\vec{P}}\in\Cont\,I\,I$ denotes
an endofunctor on $\Fam\,I$. Unlike for functors in general, initial
algebras of indexed containers always exist. While the initial algebra
of an ordinary unary container $\cont{S}{P}$ is given by the W-type 
$\WW\,x\in S.P\,s$, the initial algebra of an indexed container is
given by an indexed generalisation of W-types. That is given
\begin{gather*}
  \vec{S} \in I\to\Set\\
  \vec{P} \in I\to\Pi_{i\in I}\vec{S}\,i \to I \to \Set
\end{gather*}
we define
\begin{gather*}
  \WW^I\,\vec{S}\,\vec{P} \in I \to \Set
\end{gather*}
as inductively generated by
\[
\ru{(s,f) \in \Sigma s\in \vec{S}\,i . \Pi_{i'\in I} 
  \vec{P}\,s\,i' \to \WW^I\,\vec{S}\,\vec{P}\,i'}
{\sup^I\,(s,f) \in \WW^I\,\vec{S}\,\vec{P}\,i}
\]
or with other words $ \WW^I\,\vec{S}\,\vec{P}$ is the initial algebra
of $\ExtC{\cont{S}{P}}$. An interesting observation is that $\WW^I$
can be constructed from ordinary $\WW$-types. The idea is to define an
approximation of $\WW^I$ as an ordinary $\WW$ type, namely 
\[\WW \,(i,s)\inx (\Sigma i\in I.\vec{S}\,i). 
  (\Sigma i'\in I.\vec{P}\,s\,i')\]
and then to identify the good trees by
\emph{type-checking}. Variants of this
construction can be found in \cite{alti:cont-tcs} and \cite{HylandGambino}.

% To construct $\WW^I$, we first approximate the correct type by an ordinary
% W-type and then identify the correct trees by \emph{type checking}.
% The approximation is given by $\WW\,\hat{S}\,\hat{P}\in\Set$ where
% \begin{eqnarray*}
%   \hat{S} & \in & \Set \\
%   \hat{S} & = & \Sigma j\in J.\vec{S}\,j \\
%   \hat{P} & \in & \hat{S} \to \Set \\
%   \hat{P}\,(j,s) & = & \Sigma j'\in J.\vec{P}\,s\,j'
% \end{eqnarray*}

% We now define two functions by primitive recursion on
% $\WW\,\hat{S}\,\hat{P}$, one $\down$ which labels a tree with the
% indizes we expect and another one $\up$ which labels a tree with the
% indizes which are given. 
% \begin{eqnarray*}
%   \down & \in & \WW\,\hat{S}\,\hat{P} \to J \to \WW\,(\hat{S}\times
%   J)\,(\hat{P}\circ\pi_1)\\
%   \down\,(\sup\,s\,f)\,j & = & \sup\,(s,j)\,\lambda
%   (j',p).\down\,(f\,(j',p))\,j'\\
%   \\
%   \up & \in & \WW\,\hat{S}\,\hat{P} \to \WW\,(\hat{S}\times
%   J)\,(\hat{P}\circ\pi_1)\\
%   \up\,(\sup\,(j,s)\,f) & = & \sup\,((j,s),j)\,\lambda p.\down\,(f\,p)
% \end{eqnarray*}
% The good trees are now the ones where both functions agree,
% initializing $\down$ with the index we want to see on the top. 
% \begin{eqnarray*}
%   \WW^J & \in & J\to\Set \\
%   \WW^J\,j & = & \Sigma w\in \WW\,\hat{S}\,\hat{P}.\down\,w\,j =
%   \up\,w
% \end{eqnarray*}
% The property that a tree type checks is hereditary, i.e. given $f \in
% \Pi_{j'\in J} P\,s\,j' \to \WW^j\,j$ if it holds
% for all subtrees $g\in \Pi_{j'\in J}p\in P\,s\,j'.\down\,(f\,p)\,j' =
%   \up\,(f\,p)$ then the whole tree type checks, i.e. we have
% $\he\,g \in \down\,(\sup\,(s,f))\,j = \up\,(\sup\,s\,f)$. Using this
% we can complete the construction by providing $\sup^J$:
% \begin{eqnarray*}
%     \sup^J & \in & \Pi_{j\in J} F_{\WW^J}\,j\,(\WW^J\,S\,P) \to
%   \WW^J\,S\,P\,j\\
%   \sup^J_j\,s\,f & = & (\sup\,(j,s)\,\pi_1\circ f,\he\,(\pi_2\circ f))
% \end{eqnarray*}
% \txa{Sketch construction of $\WW^I$, refer to Hyland & Gambino}

\begin{proposition}
  $(\WW^I\,\vec{S}\,\vec{P},\sup_I)$, i.e. the initial algebra of
  $\ExtC{\cont{\vec{S}}{\vec{P}}}$ can be constructed from $\WW$-types using
  $\Pi$, $\Sigma$ and equality types. Equivalently it exists in any
  Martin-L\"of category (Locally Cartesian Closed category with $\WW$-types).
\end{proposition}

We are going to generalize this result to parametrized initial
algebras. We first define partial application, given 
\begin{gather*}
  \cont{\vec{S}}{\vec{P}} \in \Cont\,(I+J)\,J\\
  \cont{\vec{T}}{\vec{Q}} \in \Cont\,I\,J
\end{gather*}
with 
\begin{gather*}
  \vec{S} \in J\to\Set\\
  \vec{P} \in \Pi_{j\in J} \vec{S}\,j \to I+J \to \Set\\
  \vec{T} \in J\to\Set\\
  \vec{Q} \in \Pi_{j\in J} \vec{T}\,j \to I \to \Set
\end{gather*}
we define
\begin{gather*}
  \cont{\vec{S}}{\vec{P}}[\cont{\vec{T}}{\vec{Q}}] = \cont{\vec{U}}{\vec{R}}\\
  \in \Cont\,I\,J
\end{gather*}
We observe that we can separate the $I$- and $J$-indexed positions of $\vec{P}$ by case analysis, giving rise to
\begin{gather*}
  \vec{P}^I \in \Pi_{j\in J} \vec{S}\,j \to I \to \Set\\
  \vec{P}^J \in \Pi_{j\in J} \to \vec{S}\,j \to J \to \Set\\
\end{gather*}
Clearly $\cont{\vec{S}}{\vec{P}^J} \in \Cont\,J\,J$ is a container,
and we can use its extension to construct the shapes of the resulting
container:
\begin{gather*}
  \vec{U} \in J\to\Set \\
  \vec{U} = \ExtC{\cont{\vec{S}}{\vec{P}^J}} @ \vec{T}
\end{gather*}
We also express the construction of the positions parametrically, using
\begin{gather*}
  \diamond\,\vec{Q} \in \Pi_{j\in J} \vec{U}\,j \to I \to \Set\\
  \diamond\,\vec{Q}\,(s,f)\,i = \vec{P}^I\,s\,i +
  \Sigma_{k\in J}\Sigma p\in \vec{P}^J\,s\,k.\vec{Q}\,(f\,p)\,i
\end{gather*}
This represents the possible positions in the combined container which
are either top-level positions ($\vec{P}^I$) or positions inside the
second container given by a top-level ($\vec{P}^J$) position combined with a 
position in $\vec{Q}$ of the appropriate shape. Hence we set:
\begin{gather*}
  \vec{R} \in \Pi_{j\in J} \vec{U}\,j \to I \to \Set\\
  \vec{R} = \diamond\,\vec{Q}
\end{gather*}
As expected this construction is functorial: on shapes we exploit the
morphism part of $\ExtC{\cont{\vec{S}}{\vec{P}^J}}$. To construct the 
position part of the morphism we exploit that $\diamond$ is an indexed 
functor itself and it commutes with $\ExtC{\cont{\vec{S}}{\vec{P}^J}}$, i.e.
\begin{gather*}
  \diamond\,\vec{Q'}\,(\ExtC{\cont{\vec{S}}{\vec{P}^J}}\,f\,x)
  = \diamond\,(\vec{Q'}\circ f)\,x
\end{gather*}

We are going to reuse those components in the construction of the
parametrized initial algebra of $\cont{\vec{S}}{\vec{P}}$ above:
\begin{gather*}
  \mu^I = \cont{\vec{U}_\mu}{\vec{R}_\mu}\\
  \in \Cont\,I\,J
\end{gather*}
The shapes are the trees which can be constructed using 
$\ExtC{\cont{\vec{S}}{\vec{P}^J}}$, hence
\begin{gather*}
  \vec{U}_\mu \in J \to \Set\\
  \vec{U}_\mu = \WW^J\,\vec{S}\,\vec{P}^J
\end{gather*}
The positions are the paths in the resulting trees which can be constructed 
using structural recursion of the indexed W-type:
\begin{gather*}
  \vec{R}_\mu \in \Pi_{j\in J} \vec{U}_\mu\,j \to I \to \Set\\
  \vec{R}_\mu\,(\sup^J\,(s,f)) = \diamond\,\vec{R}_\mu\,(s,f) 
\end{gather*}
We are ready to define the constructor, i.e. the morphism part of the
parametrized initial algebra:
\begin{gather*}
  \inn = \cont{f}{r} \\
  \in \Cont\,(\cont{\vec{S}}{\vec{P}}[\mu^I])
  \,\mu^I
\end{gather*}
Clearly, the shape component is just the constructor for $\WW_J$:
\begin{gather*}
  f \in \Pi_{j\in J}(\ExtC{\cont{\vec{S}}{\vec{P}^J}}@ \vec{U}_\mu)\,j \to \vec{U}_\mu\,j\\
  f = \sup^J
\end{gather*}
The morphism on positions is simply the identity, because we can exploit the recursive definition of $\vec{R}_\mu$:
\begin{gather*}
  r \in \Pi_{j\in J,i\in I}\Pi (s,f) \in \vec{U}_\mu\,j.\vec{R}_\mu\,(\sup^J\,(s,f)\,i \to \diamond\,\vec{R}\,u\,i\\
  r\,(s,f)\,r = r
\end{gather*}
The definition of fold is straightforward, it is basically forced upon us and hence unicity holds. We summarize:
\begin{proposition}
  $(\mu^I,\inn)$ is the parametrized initial algebra of $\ExtC{\cont{\vec{S}}{\vec{P}}}$.
\end{proposition}

\section{Strictly positive families}
\label{sec:spf}

Finally, we will define a syntactic representation of strictly
positive families, which itself is a strictly positive indexed
family.  Given $J\in\Set$ we
define $\SPF\in I\to\Set$ inductively. As before for $\Func$ and
$\Cont$ we define $\SPF\,I\,J = J \to \SPF\,I$. This notation will
subsequently be justified by establishing that $\SPF$ is monadic and
hence gives rise to a category of strictly positive families. 
\[
\ru{i\in I}{\returnT\,i\in\SPF\,I}
\]
\[
\ru{O'\in\Set \quad f\in O' \to O\quad F \in \SPF\,O'\,I}
{\begin{array}{c}\TPi\,f\,F\in \SPF\,I\,O\\
\TSigma\,f\,F\in \SPF\,O\,J\end{array}}
\]\[
\ru{F\in\SPF\,(I+J)\,J}{\Tmu\,F\in\SPF\,I\,J}
\]
As before $\SPF\,I\in\Set_{i+1}$ if $I\in\Set_i$ because the
constructors $\TSigma,\TPi$ are indexed by a set which should live on
the same level as the index. Ignoring size again, $\SPF$ is monadic,
$\returnT$ is a constructor. Given $G\in \SPF\,I$ and 
$F\in I \to \SPF\,J = \SPF\,J\,I$
we define $G \bindT F \in\SPF\,J$ recursively over $G$:
\begin{gather*}
  (\returnT\,i) \bindT F = F\,i\\
  (\TPi\,f\,G\,j) \bindT F = \TPi\,f\,(F\circ G) )\,j\\
  (\TSigma\,f\,G\,j) \bindT F = \TSigma\,f\,(F\circ G) )\,j\\
  (\Tmu\,G\,j) \bindT F = \Tmu\,(G\circ \SPF\,\inl)\,j
\end{gather*}
Here $F\circ G = \lambda o.(G\,o)\bindT F$ is the derived composition
operation and $\SPF\,f \,G = (\returnT\circ f) \bindT G$ is the action of the
SPF functor on morphisms. In this
presentation the algorithm isn't structurally recursive but this can
be addressed by in-lining the weakening ($\SPF\,\inl$) along the lines of 
\cite{alti:csl99}.

It is straightforward to define an interpretation of the syntax as
indexed containers, that is given $A\in\SPF\,I$ we obtain
$\ExtT{A}\in\Cont\,I$. As before this automatically extends to
morphisms: given $F\in\SPF\,I\,J$ we obtain $\ExtT{F}\in\Cont\,I\,J$.
\begin{eqnarray*}
  \ExtT{\returnT\,i} & = & \returnC\,i \\
  \ExtT{\TPi\,f\,G\,j} & = & \CPi\,f\,\ExtT{G}\,j\\
  \ExtT{\TSigma\,f\,G\,j} & = & \CSigma\,f\,\ExtT{G}\,j\\
  \ExtT{\Tmu\,G\,j} & = & \Cmu\,\ExtT{G}\,j
\end{eqnarray*}
The monadic structure is preserved by the interpretation function.

By combining $\ExtT{-}$ and $\ExtC{-}$ we obtain an interpretation of
indexed types as indexed functors $\ExtF{-} \in \SPF\,I\to\Func\,I$.
Note that it is necessary to go via indexed containers, since -- as we
have remarked earlier -- functors are not necessarily closed under initial
algebras.

As an example we encode $\Fin$ and $\Lam$ as strictly positive
families exploiting the construction of finite coproducts and
products in the syntax:
\begin{align*}
  &\Fin^T, \Lam^T \in \SPF\,0\,\Nat\\
  &\Fin^T = \Tmu\,(\lambda n.\TSigma\,\succ\,\TK_0\,n 
  \Tplus \TSigma\,\succ\,(\returnT \circ \inr))\\
  &\Lam^T = \Tmu\,(\lambda n.(\Fin^T \circ (\SPF\,\inl))\,n\\
  &\qquad \Tplus \returnT\,(\inr\,n) \Ttimes \returnT\,(\inr\,n)\\
  &\qquad \Tplus \returnT\,(\inr\,(\succ\,n)))
\end{align*}

\section{Conclusions and further work}
\label{sec:concl-furth-work}

We have shown how inductive families, a central feature in dependently
typed programming, can be constructed from the standard infrastructure
present in Type Theory, i.e. W-types together with $\Pi$, $\Sigma$ and
equality types. Indeed, we are able to reduce the syntactically rich
notion of inductive families to a small collection of categorically
inspired combinators. This is an interesting alternative to the
complex syntactic schemes present in the \emph{Calculus of Inductive
  Constructions} (CIC), or in the Agda and Epigram systems. We are
able to encode inductively defined families in a small core language
which means that we rely only on a small trusted code base. The
reduction to $\WW$-types requires an extensional propositional
equality --- our recent work on \emph{Observational Type Theory} (OTT) 
\cite{alti:ott-conf} shows that this is not an obstacle to implementation.

Central to our construction is the notion of indexed containers
generalizing both simple containers and dependent polynomial functors. 
Indexed containers, like simple containers, are closed under an initial
algebra construction and like dependent polynomial functors model
inductive families. We were able to exploit recent progress in the
implementation of the Agda system to give a certified implementation
of our main results closely following the high level structure of our
construction. We decided not to base our presentation on the
formalisation to be able to ignore irrelevant details of the actual
formalisation and provide a better narrative.

We haven't included coinductive families, i.e. terminal coalgebras of
indexed functors, in the present paper. It seems clear that we could
represent coinductive families by following our previous
work~\cite{alti:cont-tcs}; There, 
we showed how to encode M-types, i.e. the coinductive
counterpart of W-types, using a limit construction. To dualize the
construction presented here we have to replace the recursive
definition of $\vec{R}^\mu$ by an inductive definition.

A more serious challenge are mutual inductively (or coinductively)
defined families where one type depends on another. A typical example
is the syntax of Type Theory itself which, to simplify, can be encoded
by mutually defining contexts containing terms, types in a given context 
and terms in a given type:
\begin{gather*}
  \mathrm{Con} \in \Set\\
  \mathrm{Ty} \in \mathrm{Con} \to \Set \\
  \mathrm{Tm} \in \Pi \Gamma\in\mathrm{Con}.\Ty\,\Gamma \to \Set
\end{gather*}
This sort of definition can be justified using Dybjer and Setzer's
inductive-recursive definitions~\cite{DybjerSetzer99,DybjerSetzer06}. 
However, induction-recursion doesn't
seem necessary here because there are no negative occurrences of types
as in universe constructions. Can we extend indexed containers to
capture families of this kind? A promising avenue seems to be to
consider the interpretation of containers in the category of families
or more generally telescopes (arrow categories).

\bibliographystyle{IEEEtran}

\bibliography{ic}

\end{document}

### 2010-11-09 journal/paper.tex
Start adding agda to the paper

\documentclass[a4paper]{article}

%% ODER: format ==         = "\mathrel{==}"
%% ODER: format /=         = "\neq "
%
%
\makeatletter
\@ifundefined{lhs2tex.lhs2tex.sty.read}%
  {\@namedef{lhs2tex.lhs2tex.sty.read}{}%
   \newcommand\SkipToFmtEnd{}%
   \newcommand\EndFmtInput{}%
   \long\def\SkipToFmtEnd#1\EndFmtInput{}%
  }\SkipToFmtEnd

\newcommand\ReadOnlyOnce[1]{\@ifundefined{#1}{\@namedef{#1}{}}\SkipToFmtEnd}
\usepackage{amstext}
\usepackage{amssymb}
\usepackage{stmaryrd}
\DeclareFontFamily{OT1}{cmtex}{}
\DeclareFontShape{OT1}{cmtex}{m}{n}
  {<5><6><7><8>cmtex8
   <9>cmtex9
   <10><10.95><12><14.4><17.28><20.74><24.88>cmtex10}{}
\DeclareFontShape{OT1}{cmtex}{m}{it}
  {<-> ssub * cmtt/m/it}{}
\newcommand{\texfamily}{\fontfamily{cmtex}\selectfont}
\DeclareFontShape{OT1}{cmtt}{bx}{n}
  {<5><6><7><8>cmtt8
   <9>cmbtt9
   <10><10.95><12><14.4><17.28><20.74><24.88>cmbtt10}{}
\DeclareFontShape{OT1}{cmtex}{bx}{n}
  {<-> ssub * cmtt/bx/n}{}
\newcommand{\tex}[1]{\text{\texfamily#1}}	% NEU

\newcommand{\Sp}{\hskip.33334em\relax}

\newcommand{\Conid}[1]{\mathit{#1}}
\newcommand{\Varid}[1]{\mathit{#1}}
\newcommand{\anonymous}{\kern0.06em \vbox{\hrule\@width.5em}}
\newcommand{\plus}{\mathbin{+\!\!\!+}}
\newcommand{\bind}{\mathbin{>\!\!\!>\mkern-6.7mu=}}
\newcommand{\rbind}{\mathbin{=\mkern-6.7mu<\!\!\!<}}% suggested by Neil Mitchell
\newcommand{\sequ}{\mathbin{>\!\!\!>}}
\renewcommand{\leq}{\leqslant}
\renewcommand{\geq}{\geqslant}
\usepackage{polytable}

%mathindent has to be defined
\@ifundefined{mathindent}%
  {\newdimen\mathindent\mathindent\leftmargini}%
  {}%

\def\resethooks{%
  \global\let\SaveRestoreHook\empty
  \global\let\ColumnHook\empty}
\newcommand*{\savecolumns}[1][default]%
  {\g@addto@macro\SaveRestoreHook{\savecolumns[#1]}}
\newcommand*{\restorecolumns}[1][default]%
  {\g@addto@macro\SaveRestoreHook{\restorecolumns[#1]}}
\newcommand*{\aligncolumn}[2]%
  {\g@addto@macro\ColumnHook{\column{#1}{#2}}}

\resethooks

\newcommand{\onelinecommentchars}{\quad-{}- }
\newcommand{\commentbeginchars}{\enskip\{-}
\newcommand{\commentendchars}{-\}\enskip}

\newcommand{\visiblecomments}{%
  \let\onelinecomment=\onelinecommentchars
  \let\commentbegin=\commentbeginchars
  \let\commentend=\commentendchars}

\newcommand{\invisiblecomments}{%
  \let\onelinecomment=\empty
  \let\commentbegin=\empty
  \let\commentend=\empty}

\visiblecomments

\newlength{\blanklineskip}
\setlength{\blanklineskip}{0.66084ex}

\newcommand{\hsindent}[1]{\quad}% default is fixed indentation
\let\hspre\empty
\let\hspost\empty
\newcommand{\NB}{\textbf{NB}}
\newcommand{\Todo}[1]{$\langle$\textbf{To do:}~#1$\rangle$}

\EndFmtInput
\makeatother
%
%
%
%
%
%
% This package provides two environments suitable to take the place
% of hscode, called "plainhscode" and "arrayhscode". 
%
% The plain environment surrounds each code block by vertical space,
% and it uses \abovedisplayskip and \belowdisplayskip to get spacing
% similar to formulas. Note that if these dimensions are changed,
% the spacing around displayed math formulas changes as well.
% All code is indented using \leftskip.
%
% Changed 19.08.2004 to reflect changes in colorcode. Should work with
% CodeGroup.sty.
%
\ReadOnlyOnce{polycode.fmt}%
\makeatletter

\newcommand{\hsnewpar}[1]%
  {{\parskip=0pt\parindent=0pt\par\vskip #1\noindent}}

% can be used, for instance, to redefine the code size, by setting the
% command to \small or something alike
\newcommand{\hscodestyle}{}

% The command \sethscode can be used to switch the code formatting
% behaviour by mapping the hscode environment in the subst directive
% to a new LaTeX environment.

\newcommand{\sethscode}[1]%
  {\expandafter\let\expandafter\hscode\csname #1\endcsname
   \expandafter\let\expandafter\endhscode\csname end#1\endcsname}

% "compatibility" mode restores the non-polycode.fmt layout.

\newenvironment{compathscode}%
  {\par\noindent
   \advance\leftskip\mathindent
   \hscodestyle
   \let\\=\@normalcr
   \let\hspre\(\let\hspost\)%
   \pboxed}%
  {\endpboxed\)%
   \par\noindent
   \ignorespacesafterend}

\newcommand{\compaths}{\sethscode{compathscode}}

% "plain" mode is the proposed default.
% It should now work with \centering.
% This required some changes. The old version
% is still available for reference as oldplainhscode.

\newenvironment{plainhscode}%
  {\hsnewpar\abovedisplayskip
   \advance\leftskip\mathindent
   \hscodestyle
   \let\hspre\(\let\hspost\)%
   \pboxed}%
  {\endpboxed%
   \hsnewpar\belowdisplayskip
   \ignorespacesafterend}

\newenvironment{oldplainhscode}%
  {\hsnewpar\abovedisplayskip
   \advance\leftskip\mathindent
   \hscodestyle
   \let\\=\@normalcr
   \(\pboxed}%
  {\endpboxed\)%
   \hsnewpar\belowdisplayskip
   \ignorespacesafterend}

% Here, we make plainhscode the default environment.

\newcommand{\plainhs}{\sethscode{plainhscode}}
\newcommand{\oldplainhs}{\sethscode{oldplainhscode}}
\plainhs

% The arrayhscode is like plain, but makes use of polytable's
% parray environment which disallows page breaks in code blocks.

\newenvironment{arrayhscode}%
  {\hsnewpar\abovedisplayskip
   \advance\leftskip\mathindent
   \hscodestyle
   \let\\=\@normalcr
   \(\parray}%
  {\endparray\)%
   \hsnewpar\belowdisplayskip
   \ignorespacesafterend}

\newcommand{\arrayhs}{\sethscode{arrayhscode}}

% The mathhscode environment also makes use of polytable's parray 
% environment. It is supposed to be used only inside math mode 
% (I used it to typeset the type rules in my thesis).

\newenvironment{mathhscode}%
  {\parray}{\endparray}

\newcommand{\mathhs}{\sethscode{mathhscode}}

% texths is similar to mathhs, but works in text mode.

\newenvironment{texthscode}%
  {\(\parray}{\endparray\)}

\newcommand{\texths}{\sethscode{texthscode}}

% The framed environment places code in a framed box.

\def\codeframewidth{\arrayrulewidth}
\RequirePackage{calc}

\newenvironment{framedhscode}%
  {\parskip=\abovedisplayskip\par\noindent
   \hscodestyle
   \arrayrulewidth=\codeframewidth
   \tabular{@{}|p{\linewidth-2\arraycolsep-2\arrayrulewidth-2pt}|@{}}%
   \hline\framedhslinecorrect\\{-1.5ex}%
   \let\endoflinesave=\\
   \let\\=\@normalcr
   \(\pboxed}%
  {\endpboxed\)%
   \framedhslinecorrect\endoflinesave{.5ex}\hline
   \endtabular
   \parskip=\belowdisplayskip\par\noindent
   \ignorespacesafterend}

\newcommand{\framedhslinecorrect}[2]%
  {#1[#2]}

\newcommand{\framedhs}{\sethscode{framedhscode}}

% The inlinehscode environment is an experimental environment
% that can be used to typeset displayed code inline.

\newenvironment{inlinehscode}%
  {\(\def\column##1##2{}%
   \let\>\undefined\let\<\undefined\let\\\undefined
   \newcommand\>[1][]{}\newcommand\<[1][]{}\newcommand\\[1][]{}%
   \def\fromto##1##2##3{##3}%
   \def\nextline{}}{\) }%

\newcommand{\inlinehs}{\sethscode{inlinehscode}}

% The joincode environment is a separate environment that
% can be used to surround and thereby connect multiple code
% blocks.

\newenvironment{joincode}%
  {\let\orighscode=\hscode
   \let\origendhscode=\endhscode
   \def\endhscode{\def\hscode{\endgroup\def\@currenvir{hscode}\\}\begingroup}
   %\let\SaveRestoreHook=\empty
   %\let\ColumnHook=\empty
   %\let\resethooks=\empty
   \orighscode\def\hscode{\endgroup\def\@currenvir{hscode}}}%
  {\origendhscode
   \global\let\hscode=\orighscode
   \global\let\endhscode=\origendhscode}%

\makeatother
\EndFmtInput
%
%
\ReadOnlyOnce{agda.fmt}%

\RequirePackage[T1]{fontenc}
\RequirePackage[utf8x]{inputenc}
\RequirePackage{ucs}
\RequirePackage{amsfonts}

\providecommand\mathbbm{\mathbb}

% TODO: Define more of these ...
\DeclareUnicodeCharacter{737}{\textsuperscript{l}}
\DeclareUnicodeCharacter{8718}{\ensuremath{\blacksquare}}
\DeclareUnicodeCharacter{8759}{::}
\DeclareUnicodeCharacter{9669}{\ensuremath{\triangleleft}}
\DeclareUnicodeCharacter{8799}{\ensuremath{\stackrel{\scriptscriptstyle ?}{=}}}
\DeclareUnicodeCharacter{10214}{\ensuremath{\llbracket}}
\DeclareUnicodeCharacter{10215}{\ensuremath{\rrbracket}}

% TODO: This is in general not a good idea.
\providecommand\textepsilon{$\epsilon$}
\providecommand\textmu{$\mu$}

%Actually, varsyms should not occur in Agda output.

% TODO: Make this configurable. IMHO, italics doesn't work well
% for Agda code.

\renewcommand\Varid[1]{\mathord{\textsf{#1}}}
\let\Conid\Varid
\newcommand\Keyword[1]{\textsf{\textbf{#1}}}
\EndFmtInput

\begin{document}

\title{Indexed Containers}
\author{Thorsten Altenkirch 
   \and Neil Ghani 
   \and Peter Hancock 
   \and Conor McBride 
   \and Peter Morris}
\date{\today}

\maketitle

\begin{abstract}

Blah

\end{abstract}

\section{Introduction}

\section{Background}

\subsection{Type Theory}

\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\anonymous \dot{\rightarrow}\anonymous \;\mathbin{:}\;\{\mskip1.5mu \Conid{I}\;\mathbin{:}\;\Conid{Set}\mskip1.5mu\}\;\to \;(\Conid{A}\;\Conid{B}\;\mathbin{:}\;\Conid{I}\;\to \;\Conid{Set})\;\to \;\Conid{Set}{}\<[E]%
\\
\>[B]{}\anonymous \dot{\rightarrow}\anonymous \;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\Conid{A}\;\Conid{B}\;\mathrel{=}\;(\Varid{i}\;\mathbin{:}\;\Conid{I})\;\to \;\Conid{A}\;\Varid{i}\;\to \;\Conid{B}\;\Varid{i}{}\<[E]%
\ColumnHook
\end{hscode}\resethooks

\subsection{Containers}

\section{Indexed Functors}

\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{4}{@{}>{\hspre}l<{\hspost}@{}}%
\column{6}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\Keyword{record}\;\Conid{IFunc}\;(\Conid{I}\;\mathbin{:}\;\Conid{Set})\;\mathbin{:}\;\Conid{Set}\;\Keyword{where}{}\<[E]%
\\
\>[B]{}\hsindent{4}{}\<[4]%
\>[4]{}\Keyword{field}{}\<[E]%
\\
\>[4]{}\hsindent{2}{}\<[6]%
\>[6]{}\Varid{obj}\;\mathbin{:}\;(\Conid{A}\;\mathbin{:}\;\Conid{I}\;\to \;\Conid{Set})\;\to \;\Conid{Set}{}\<[E]%
\\
\>[4]{}\hsindent{2}{}\<[6]%
\>[6]{}\Varid{mor}\;\mathbin{:}\;\forall{}\;\{\mskip1.5mu \Conid{A}\;\Conid{B}\mskip1.5mu\}\;\to \;(\Conid{A}\;\dot{\rightarrow}\;\Conid{B})\;\to \;\Varid{obj}\;\Conid{A}\;\to \;\Varid{obj}\;\Conid{B}{}\<[E]%
\ColumnHook
\end{hscode}\resethooks

\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{4}{@{}>{\hspre}l<{\hspost}@{}}%
\column{12}{@{}>{\hspre}c<{\hspost}@{}}%
\column{12E}{@{}l@{}}%
\column{15}{@{}>{\hspre}l<{\hspost}@{}}%
\column{20}{@{}>{\hspre}l<{\hspost}@{}}%
\column{23}{@{}>{\hspre}l<{\hspost}@{}}%
\column{28}{@{}>{\hspre}l<{\hspost}@{}}%
\column{48}{@{}>{\hspre}l<{\hspost}@{}}%
\column{61}{@{}>{\hspre}l<{\hspost}@{}}%
\column{68}{@{}>{\hspre}l<{\hspost}@{}}%
\column{71}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\eta^{F}\;\mathbin{:}\;\forall{}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\rightarrow\;\Conid{I}\;\rightarrow\;\Conid{IFunc}\;\Conid{I}{}\<[E]%
\\
\>[B]{}\eta^{F}\;\Varid{i}\;\mathrel{=}\;\Keyword{record}\;\{\mskip1.5mu \Varid{obj}\;\mathrel{=}\;\lambda\;\Conid{A}\;\rightarrow\;\Conid{A}\;\Varid{i};\Varid{mor}\;\mathrel{=}\;\lambda\;\Varid{f}\;\rightarrow\;\Varid{f}\;\Varid{i}\mskip1.5mu\}{}\<[E]%
\\[\blanklineskip]%
\>[B]{}\_\bind ^{F}\_\;\mathbin{:}\;\forall{}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\mskip1.5mu\}\;\rightarrow\;(\Conid{I}\;\rightarrow\;\Conid{IFunc}\;\Conid{J})\;\rightarrow\;\Conid{IFunc}\;\Conid{I}\;\rightarrow\;\Conid{IFunc}\;\Conid{J}{}\<[E]%
\\
\>[B]{}\Conid{H}\;\bind ^{F}\;\Conid{F}\;\mathrel{=}{}\<[E]%
\\
\>[B]{}\hsindent{4}{}\<[4]%
\>[4]{}\Keyword{record}\;{}\<[12]%
\>[12]{}\{\mskip1.5mu {}\<[12E]%
\>[15]{}\Varid{obj}\;{}\<[20]%
\>[20]{}\mathrel{=}\;{}\<[23]%
\>[23]{}\lambda\;\Conid{A}\;{}\<[28]%
\>[28]{}\rightarrow\;\!\;\Conid{F}\;(\lambda\;\Varid{i}\;{}\<[48]%
\>[48]{}\rightarrow\;\!\;{}\<[61]%
\>[61]{}(\Conid{H}\;\Varid{i})\;{}\<[68]%
\>[68]{}\Conid{A}{}\<[71]%
\>[71]{}){}\<[E]%
\\
\>[12]{};{}\<[12E]%
\>[15]{}\Varid{mor}\;{}\<[20]%
\>[20]{}\mathrel{=}\;{}\<[23]%
\>[23]{}\lambda\;\Varid{f}\;{}\<[28]%
\>[28]{}\rightarrow\;\!\;\Conid{F}\;(\lambda\;\Varid{i}\;{}\<[48]%
\>[48]{}\rightarrow\;\!\;{}\<[61]%
\>[61]{}(\Conid{H}\;\Varid{i})\;{}\<[68]%
\>[68]{}\Varid{f}{}\<[71]%
\>[71]{})\mskip1.5mu\}{}\<[E]%
\ColumnHook
\end{hscode}\resethooks

\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{10}{@{}>{\hspre}l<{\hspost}@{}}%
\column{14}{@{}>{\hspre}l<{\hspost}@{}}%
\column{16}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\Conid{IFunc}^{\star}\;\mathbin{:}\;(\Conid{I}\;\Conid{J}\;\mathbin{:}\;\Conid{Set})\;\rightarrow\;\Conid{Set}{}\<[E]%
\\
\>[B]{}\Conid{IFunc}^{\star}\;\Conid{I}\;\Conid{J}\;\mathrel{=}\;\Conid{J}\;\rightarrow\;\Conid{IFunc}\;\Conid{I}{}\<[E]%
\\[\blanklineskip]%
\>[B]{}\Varid{obj}^{\star}\;\mathbin{:}\;\forall{}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\mskip1.5mu\}\;\rightarrow\;\Conid{IFunc}^{\star}\;\Conid{I}\;\Conid{J}\;\rightarrow\;(\Conid{I}\;\rightarrow\;\Conid{Set})\;\rightarrow\;\Conid{J}\;\rightarrow\;\Conid{Set}{}\<[E]%
\\
\>[B]{}\Varid{obj}^{\star}\;\Conid{F}\;\Conid{A}\;\Varid{j}\;{}\<[16]%
\>[16]{}\mathrel{=}\;\!\;(\Conid{F}\;\Varid{j})\;\Conid{A}{}\<[E]%
\\[\blanklineskip]%
\>[B]{}\Varid{mor}^{\star}\;\mathbin{:}\;{}\<[10]%
\>[10]{}\forall{}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\Conid{A}\;\Conid{B}\mskip1.5mu\}\;(\Conid{F}\;\mathbin{:}\;\Conid{IFunc}^{\star}\;\Conid{I}\;\Conid{J})\;\rightarrow\;\Conid{A}\;\dot{\rightarrow}\;\Conid{B}\;\rightarrow\;\Varid{obj}^{\star}\;\Conid{F}\;\Conid{A}\;\dot{\rightarrow}\;\Varid{obj}^{\star}\;\Conid{F}\;\Conid{B}{}\<[E]%
\\
\>[B]{}\Varid{mor}^{\star}\;\Conid{F}\;\Varid{m}\;\Varid{j}\;{}\<[14]%
\>[14]{}\mathrel{=}\;\!\;(\Conid{F}\;\Varid{j})\;\Varid{m}{}\<[E]%
\ColumnHook
\end{hscode}\resethooks

\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{4}{@{}>{\hspre}l<{\hspost}@{}}%
\column{12}{@{}>{\hspre}c<{\hspost}@{}}%
\column{12E}{@{}l@{}}%
\column{15}{@{}>{\hspre}l<{\hspost}@{}}%
\column{20}{@{}>{\hspre}l<{\hspost}@{}}%
\column{23}{@{}>{\hspre}l<{\hspost}@{}}%
\column{40}{@{}>{\hspre}l<{\hspost}@{}}%
\column{91}{@{}>{\hspre}c<{\hspost}@{}}%
\column{91E}{@{}l@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\Sigma^{F}\;\mathbin{:}\;\forall{}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\Conid{K}\mskip1.5mu\}\;\rightarrow\;(\Conid{J}\;\rightarrow\;\Conid{K})\;\rightarrow\;\Conid{IFunc}^{\star}\;\Conid{I}\;\Conid{J}\;\rightarrow\;\Conid{IFunc}^{\star}\;\Conid{I}\;\Conid{K}{}\<[E]%
\\
\>[B]{}\Sigma^{F}\;\{\mskip1.5mu \Conid{J}\;\mathrel{=}\;\Conid{J}\mskip1.5mu\}\;\Varid{f}\;\Conid{F}\;\Varid{k}\;\mathrel{=}{}\<[E]%
\\
\>[B]{}\hsindent{4}{}\<[4]%
\>[4]{}\Keyword{record}\;{}\<[12]%
\>[12]{}\{\mskip1.5mu {}\<[12E]%
\>[15]{}\Varid{obj}\;{}\<[20]%
\>[20]{}\mathrel{=}\;{}\<[23]%
\>[23]{}\lambda\;\Conid{A}\;\rightarrow\;\Sigma\;\Conid{J}\;\lambda\;\Varid{j}\;\rightarrow\;\Varid{f}\;\Varid{j}\;\equiv\;\Varid{k}\;\times\;\!\;\Conid{F}\;\Conid{A}\;\Varid{j}{}\<[E]%
\\
\>[12]{};{}\<[12E]%
\>[15]{}\Varid{mor}\;{}\<[20]%
\>[20]{}\mathrel{=}\;{}\<[23]%
\>[23]{}\lambda\;\Varid{m}\;\rightarrow\;\Varid{<}\;\pi_{0},{}\<[40]%
\>[40]{}\Varid{<}\;\pi_{0}\;\ensuremath{\mbox{$\circ$}}\;\pi_{1},\!\;\Conid{F}\;\Varid{m}\;\anonymous \;\ensuremath{\mbox{$\circ$}}\;\pi_{1}\;\ensuremath{\mbox{$\circ$}}\;\pi_{1}\;\Varid{>}\;\Varid{>}{}\<[91]%
\>[91]{}\mskip1.5mu\}{}\<[91E]%
\\[\blanklineskip]%
\>[B]{}\Pi^{F}\;\mathbin{:}\;\forall{}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\Conid{K}\mskip1.5mu\}\;\rightarrow\;(\Conid{J}\;\rightarrow\;\Conid{K})\;\rightarrow\;\Conid{IFunc}^{\star}\;\Conid{I}\;\Conid{J}\;\rightarrow\;\Conid{IFunc}^{\star}\;\Conid{I}\;\Conid{K}{}\<[E]%
\\
\>[B]{}\Pi^{F}\;\{\mskip1.5mu \Conid{J}\;\mathrel{=}\;\Conid{J}\mskip1.5mu\}\;\Varid{f}\;\Conid{F}\;\Varid{k}\;\mathrel{=}{}\<[E]%
\\
\>[B]{}\hsindent{4}{}\<[4]%
\>[4]{}\Keyword{record}\;{}\<[12]%
\>[12]{}\{\mskip1.5mu {}\<[12E]%
\>[15]{}\Varid{obj}\;{}\<[20]%
\>[20]{}\mathrel{=}\;{}\<[23]%
\>[23]{}\lambda\;\Conid{A}\;\rightarrow\;(\Varid{j}\;\mathbin{:}\;\Conid{J})\;\rightarrow\;\Varid{f}\;\Varid{j}\;\equiv\;\Varid{k}\;\rightarrow\;\!\;\Conid{F}\;\Conid{A}\;\Varid{j}{}\<[E]%
\\
\>[12]{};{}\<[12E]%
\>[15]{}\Varid{mor}\;{}\<[20]%
\>[20]{}\mathrel{=}\;{}\<[23]%
\>[23]{}\lambda\;\Varid{m}\;\Varid{f}\;\Varid{j}\;\Varid{p}\;\rightarrow\;\!\;\Conid{F}\;\Varid{m}\;\Varid{j}\;(\Varid{f}\;\Varid{j}\;\Varid{p})\mskip1.5mu\}{}\<[E]%
\ColumnHook
\end{hscode}\resethooks

\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
\column{11}{@{}>{\hspre}c<{\hspost}@{}}%
\column{11E}{@{}l@{}}%
\column{12}{@{}>{\hspre}l<{\hspost}@{}}%
\column{14}{@{}>{\hspre}l<{\hspost}@{}}%
\column{19}{@{}>{\hspre}l<{\hspost}@{}}%
\column{22}{@{}>{\hspre}l<{\hspost}@{}}%
\column{27}{@{}>{\hspre}l<{\hspost}@{}}%
\column{46}{@{}>{\hspre}l<{\hspost}@{}}%
\column{50}{@{}>{\hspre}l<{\hspost}@{}}%
\column{54}{@{}>{\hspre}l<{\hspost}@{}}%
\column{59}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\_[\mskip1.5mu \_\mskip1.5mu]^{F}\;\mathbin{:}\;\forall{}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\mskip1.5mu\}\;\rightarrow\;\Conid{IFunc}\;(\Conid{I}\;\uplus\;\Conid{J})\;\rightarrow\;\Conid{IFunc}^{\star}\;\Conid{I}\;\Conid{J}\;\rightarrow\;{}\<[50]%
\>[50]{}\Conid{IFunc}\;\Conid{I}{}\<[E]%
\\
\>[B]{}\Conid{F}\;[\mskip1.5mu \;\Conid{G}\;\mskip1.5mu]^{F}\;{}\<[12]%
\>[12]{}\mathrel{=}{}\<[E]%
\\
\>[B]{}\hsindent{3}{}\<[3]%
\>[3]{}\Keyword{record}\;{}\<[11]%
\>[11]{}\{\mskip1.5mu {}\<[11E]%
\>[14]{}\Varid{obj}\;{}\<[19]%
\>[19]{}\mathrel{=}\;{}\<[22]%
\>[22]{}\lambda\;\Conid{A}\;{}\<[27]%
\>[27]{}\rightarrow\;\!\;\Conid{F}\;[\mskip1.5mu \Conid{A}{}\<[46]%
\>[46]{},\!\;{}\<[54]%
\>[54]{}\Conid{G}\;\Conid{A}{}\<[59]%
\>[59]{}\mskip1.5mu]{}\<[E]%
\\
\>[11]{};{}\<[11E]%
\>[14]{}\Varid{mor}\;{}\<[19]%
\>[19]{}\mathrel{=}\;{}\<[22]%
\>[22]{}\lambda\;\Varid{f}\;{}\<[27]%
\>[27]{}\rightarrow\;\!\;\Conid{F}\;[\mskip1.5mu \Varid{f}{}\<[46]%
\>[46]{},\!\;{}\<[54]%
\>[54]{}\Conid{G}\;\Varid{f}{}\<[59]%
\>[59]{}\mskip1.5mu]\mskip1.5mu\}{}\<[E]%
\ColumnHook
\end{hscode}\resethooks

\section{Indexed containers}

\section{Initial Algebras of Indexed Containers}

\section{Strictly Positive Types}

\section{Conclusions}

\end{document}

### 2011-04-19 journal/paper.tex
19/04/11

@@
 \documentclass[a4paper]{article}
+
+\usepackage{url}
+\usepackage{times}
+\usepackage{amsmath}
+\usepackage{xypic}
+\usepackage{amssymb}
+\usepackage{amsmath}
+\usepackage{stmaryrd}
+
+\newcommand{\note}[1]{}
 
@@
 
+\newcounter{theorem}
+
+\newtheorem{proposition}[theorem]{Proposition}
+\newenvironment{proof}[1][Proof]{\begin{trivlist}
+\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
+
 \title{Indexed Containers}
@@
 
+%%Introduction
+
 \section{Introduction}
 
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{9}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Keyword{data}\;\Conid{ℕ}\;\in\;\Conid{Set}\;\Keyword{where}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{zero}\;{}\<[9]%
+\>[9]{}\in\;\Conid{ℕ}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{suc}\;{}\<[9]%
+\>[9]{}\in\;(\Varid{n}\;\in\;\Conid{ℕ})\;\rightarrow\;\Conid{ℕ}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{8}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{24}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Keyword{data}\;\Conid{List}\;(\Conid{A}\;\in\;\Conid{Set})\;\in\;\Conid{Set}\;\Keyword{where}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}[\mskip1.5mu \mskip1.5mu]\;{}\<[8]%
+\>[8]{}\in\;{}\<[24]%
+\>[24]{}\Conid{List}\;\Conid{A}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{\char95 ∷\char95 }\;{}\<[8]%
+\>[8]{}\in\;\Conid{A}\;\rightarrow\;\Conid{List}\;\Conid{A}\;\rightarrow\;{}\<[24]%
+\>[24]{}\Conid{List}\;\Conid{A}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{8}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{23}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Keyword{data}\;\Conid{Lam}\;\in\;\Conid{Set}\;\Keyword{where}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{var}\;{}\<[8]%
+\>[8]{}\in\;(\Varid{n}\;\in\;\Conid{ℕ})\;{}\<[23]%
+\>[23]{}\rightarrow\;\Conid{Lam}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{app}\;{}\<[8]%
+\>[8]{}\in\;(\Varid{f}\;\Varid{a}\;\in\;\Conid{Lam})\;{}\<[23]%
+\>[23]{}\rightarrow\;\Conid{Lam}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{lam}\;{}\<[8]%
+\>[8]{}\in\;(\Varid{t}\;\in\;\Conid{Lam})\;{}\<[23]%
+\>[23]{}\rightarrow\;\Conid{Lam}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Conid{F}_{\Conid{ℕ}}\;\in\;\Conid{Set}\;\rightarrow\;\Conid{Set}{}\<[E]%
+\\
+\>[B]{}\Conid{F}_{\Conid{ℕ}}\;\Conid{X}\;\mathrel{=}\;\top\;\uplus\;\Conid{X}{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\Conid{F}_{\Conid{List}}\;\in\;(\Conid{A}\;\in\;\Conid{Set})\;\rightarrow\;\Conid{Set}\;\rightarrow\;\Conid{Set}{}\<[E]%
+\\
+\>[B]{}\Conid{F}_{\Conid{List}}\;\Conid{A}\;\Conid{X}\;\mathrel{=}\;\top\;\uplus\;(\Conid{A}\;\times\;\Conid{X}){}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\Conid{F}_{\Conid{Lam}}\;\in\;\Conid{Set}\;\rightarrow\;\Conid{Set}{}\<[E]%
+\\
+\>[B]{}\Conid{F}_{\Conid{Lam}}\;\Conid{X}\;\mathrel{=}\;\Conid{ℕ}\;\uplus\;(\Conid{X}\;\times\;\Conid{X})\;\uplus\;\Conid{X}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{9}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{30}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Keyword{data}\;\Conid{Fin}\;\in\;\Conid{ℕ}\;\rightarrow\;\Conid{Set}\;\Keyword{where}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{zero}\;{}\<[9]%
+\>[9]{}\in\;\forall{}\;\{\mskip1.5mu \Varid{n}\mskip1.5mu\}\;{}\<[30]%
+\>[30]{}\rightarrow\;\Conid{Fin}\;(\Varid{suc}\;\Varid{n}){}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{suc}\;{}\<[9]%
+\>[9]{}\in\;\forall{}\;\{\mskip1.5mu \Varid{n}\mskip1.5mu\}\;(\Varid{i}\;\in\;\Conid{Fin}\;\Varid{n})\;{}\<[30]%
+\>[30]{}\rightarrow\;\Conid{Fin}\;(\Varid{suc}\;\Varid{n}){}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{8}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{42}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Keyword{data}\;\Conid{Vec}\;(\Conid{A}\;\in\;\Conid{Set})\;\in\;\Conid{ℕ}\;\rightarrow\;\Conid{Set}\;\Keyword{where}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}[\mskip1.5mu \mskip1.5mu]\;{}\<[8]%
+\>[8]{}\in\;{}\<[42]%
+\>[42]{}\Conid{Vec}\;\Conid{A}\;\Varid{zero}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{\char95 ∷\char95 }\;{}\<[8]%
+\>[8]{}\in\;\forall{}\;\{\mskip1.5mu \Varid{n}\mskip1.5mu\}\;(\Varid{a}\;\in\;\Conid{A})\;(\Varid{as}\;\in\;\Conid{Vec}\;\Conid{A}\;\Varid{n})\;\rightarrow\;{}\<[42]%
+\>[42]{}\Conid{Vec}\;\Conid{A}\;(\Varid{suc}\;\Varid{n}){}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{8}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{31}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Keyword{data}\;\Conid{ScLam}\;(\Varid{n}\;\in\;\Conid{ℕ})\;\in\;\Conid{Set}\;\Keyword{where}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{var}\;{}\<[8]%
+\>[8]{}\in\;(\Varid{i}\;\in\;\Conid{Fin}\;\Varid{n})\;{}\<[31]%
+\>[31]{}\rightarrow\;\Conid{ScLam}\;\Varid{n}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{app}\;{}\<[8]%
+\>[8]{}\in\;(\Varid{f}\;\Varid{a}\;\in\;\Conid{ScLam}\;\Varid{n})\;{}\<[31]%
+\>[31]{}\rightarrow\;\Conid{ScLam}\;\Varid{n}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{lam}\;{}\<[8]%
+\>[8]{}\in\;(\Varid{t}\;\in\;\Conid{ScLam}\;(\Varid{suc}\;\Varid{n}))\;{}\<[31]%
+\>[31]{}\rightarrow\;\Conid{ScLam}\;\Varid{n}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Conid{F}_{\Conid{Fin}}\;\in\;(\Conid{ℕ}\;\rightarrow\;\Conid{Set})\;\rightarrow\;\Conid{ℕ}\;\rightarrow\;\Conid{Set}{}\<[E]%
+\\
+\>[B]{}\Conid{F}_{\Conid{Fin}}\;\Conid{X}\;\Varid{n}\;\mathrel{=}\;\Sigma\;\Conid{ℕ}\;\lambda\;\Varid{m}\;\rightarrow\;(\Varid{n}\;\equiv\;\Varid{suc}\;\Varid{m})\;\times\;(\top\;\uplus\;\Conid{X}\;\Varid{m}){}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\Conid{F}_{\Conid{Vec}}\;\in\;(\Conid{A}\;\in\;\Conid{Set})\;\rightarrow\;(\Conid{ℕ}\;\rightarrow\;\Conid{Set})\;\rightarrow\;\Conid{ℕ}\;\rightarrow\;\Conid{Set}{}\<[E]%
+\\
+\>[B]{}\Conid{F}_{\Conid{Vec}}\;\Conid{A}\;\Conid{X}\;\Varid{n}\;\mathrel{=}\;\Varid{n}\;\equiv\;\Varid{zero}\;\uplus\;\Sigma\;\Conid{ℕ}\;\lambda\;\Varid{m}\;\rightarrow\;(\Varid{n}\;\equiv\;\Varid{suc}\;\Varid{m})\;\times\;(\Conid{A}\;\times\;\Conid{X}\;\Varid{m}){}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\Conid{F}_{\Conid{ScLam}}\;\in\;(\Conid{ℕ}\;\rightarrow\;\Conid{Set})\;\rightarrow\;\Conid{ℕ}\;\rightarrow\;\Conid{Set}{}\<[E]%
+\\
+\>[B]{}\Conid{F}_{\Conid{ScLam}}\;\Conid{X}\;\Varid{n}\;\mathrel{=}\;\Conid{Fin}\;\Varid{n}\;\uplus\;(\Conid{X}\;\Varid{n}\;\times\;\Conid{X}\;\Varid{n})\;\uplus\;(\Conid{X}\;\ensuremath{\mbox{$\circ$}}\;\Varid{suc})\;\Varid{n}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{5}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{10}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{41}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Keyword{mutual}{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Keyword{data}\;\Conid{NeLam}\;(\Varid{n}\;\in\;\Conid{ℕ})\;\in\;\Conid{Set}\;\Keyword{where}{}\<[E]%
+\\
+\>[3]{}\hsindent{2}{}\<[5]%
+\>[5]{}\Varid{var}\;{}\<[10]%
+\>[10]{}\in\;(\Varid{i}\;\in\;\Conid{Fin}\;\Varid{n})\;{}\<[41]%
+\>[41]{}\rightarrow\;\Conid{NeLam}\;\Varid{n}{}\<[E]%
+\\
+\>[3]{}\hsindent{2}{}\<[5]%
+\>[5]{}\Varid{app}\;{}\<[10]%
+\>[10]{}\in\;(\Varid{f}\;\in\;\Conid{NeLam}\;\Varid{n})\;(\Varid{a}\;\in\;\Conid{NfLam}\;\Varid{n})\;{}\<[41]%
+\>[41]{}\rightarrow\;\Conid{NeLam}\;\Varid{n}{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Keyword{data}\;\Conid{NfLam}\;(\Varid{n}\;\in\;\Conid{ℕ})\;\in\;\Conid{Set}\;\Keyword{where}{}\<[E]%
+\\
+\>[3]{}\hsindent{2}{}\<[5]%
+\>[5]{}\Varid{lam}\;{}\<[10]%
+\>[10]{}\in\;(\Varid{t}\;\in\;\Conid{NfLam}\;(\Varid{suc}\;\Varid{n}))\;{}\<[41]%
+\>[41]{}\rightarrow\;\Conid{NfLam}\;\Varid{n}{}\<[E]%
+\\
+\>[3]{}\hsindent{2}{}\<[5]%
+\>[5]{}\Varid{ne}\;{}\<[10]%
+\>[10]{}\in\;(\Varid{t}\;\in\;\Conid{NeLam}\;\Varid{n})\;{}\<[41]%
+\>[41]{}\rightarrow\;\Conid{NfLam}\;\Varid{n}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{6}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{8}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{9}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{11}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{19}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{34}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{44}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Keyword{data}\;\Conid{Ty}\;\in\;\Conid{Set}\;\Keyword{where}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\iota\;{}\<[6]%
+\>[6]{}\in\;\Conid{Ty}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\anonymous \Rightarrow\anonymous \;{}\<[11]%
+\>[11]{}\in\;(\sigma\;\tau\;\in\;\Conid{Ty})\;\rightarrow\;\Conid{Ty}{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\Keyword{data}\;\Conid{Var}\;(\tau\;\in\;\Conid{Ty})\;\in\;\Conid{List}\;\Conid{Ty}\;\rightarrow\;\Conid{Set}\;\Keyword{where}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{zero}\;{}\<[9]%
+\>[9]{}\in\;\forall{}\;\{\mskip1.5mu \Gamma\mskip1.5mu\}\;{}\<[34]%
+\>[34]{}\rightarrow\;\Conid{Var}\;\tau\;(\tau\;\Varid{∷}\;\Gamma){}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{suc}\;{}\<[9]%
+\>[9]{}\in\;\forall{}\;\{\mskip1.5mu \sigma\;\Gamma\mskip1.5mu\}\;(\Varid{i}\;\in\;\Conid{Var}\;\tau\;\Gamma)\;{}\<[34]%
+\>[34]{}\rightarrow\;\Conid{Var}\;\tau\;(\sigma\;\Varid{∷}\;\Gamma){}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\Keyword{data}\;\Conid{STLam}\;(\Gamma\;\in\;\Conid{List}\;\Conid{Ty})\;\in\;\Conid{Ty}\;\rightarrow\;\Conid{Set}\;\Keyword{where}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{var}\;{}\<[8]%
+\>[8]{}\in\;\forall{}\;\{\mskip1.5mu \tau\mskip1.5mu\}\;{}\<[19]%
+\>[19]{}(\Varid{i}\;\in\;\Conid{Var}\;\tau\;\Gamma)\;{}\<[44]%
+\>[44]{}\rightarrow\;\Conid{STLam}\;\Gamma\;\tau{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{app}\;{}\<[8]%
+\>[8]{}\in\;\forall{}\;\{\mskip1.5mu \sigma\;\tau\mskip1.5mu\}\;{}\<[19]%
+\>[19]{}(\Varid{f}\;\in\;\Conid{STLam}\;\Gamma\;(\sigma\;\Rightarrow\;\tau))\;{}\<[E]%
+\\
+\>[19]{}(\Varid{a}\;\in\;\Conid{STLam}\;\Gamma\;\sigma)\;{}\<[44]%
+\>[44]{}\rightarrow\;\Conid{STLam}\;\Gamma\;\tau{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{lam}\;{}\<[8]%
+\>[8]{}\in\;\forall{}\;\{\mskip1.5mu \sigma\;\tau\mskip1.5mu\}\;{}\<[19]%
+\>[19]{}(\Varid{t}\;\in\;\Conid{STLam}\;(\sigma\;\Varid{∷}\;\Gamma)\;\tau)\;{}\<[44]%
+\>[44]{}\rightarrow\;\Conid{STLam}\;\Gamma\;(\sigma\;\Rightarrow\;\tau){}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
 \section{Background}
@@
 
-\begin{hscode}\SaveRestoreHook
-\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
-\>[B]{}\anonymous \dot{\rightarrow}\anonymous \;\mathbin{:}\;\{\mskip1.5mu \Conid{I}\;\mathbin{:}\;\Conid{Set}\mskip1.5mu\}\;\to \;(\Conid{A}\;\Conid{B}\;\mathbin{:}\;\Conid{I}\;\to \;\Conid{Set})\;\to \;\Conid{Set}{}\<[E]%
-\\
-\>[B]{}\anonymous \dot{\rightarrow}\anonymous \;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\Conid{A}\;\Conid{B}\;\mathrel{=}\;(\Varid{i}\;\mathbin{:}\;\Conid{I})\;\to \;\Conid{A}\;\Varid{i}\;\to \;\Conid{B}\;\Varid{i}{}\<[E]%
-\ColumnHook
-\end{hscode}\resethooks
+\newcommand{\prodd}{\ensuremath{\mathaccent\cdot{\prod}}}
+
+Our contructions are all developed in Agda, and so we adopt its syntax, but we will take certain liberties with it's type-theory.
+For, instance we need to work in a setting with extensional type-theory, so we extend the propositional equality with this extensionality axiom:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{12}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{20}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[3]{}\Keyword{postulate}\;\Varid{ext}\;\in\;{}\<[20]%
+\>[20]{}\{\mskip1.5mu \Varid{f}\;\Varid{g}\;\in\;(\Varid{a}\;\in\;\Conid{A})\;\rightarrow\;\Conid{B}\;\Varid{a}\mskip1.5mu\}\;\rightarrow\;{}\<[E]%
+\\
+\>[20]{}((\Varid{a}\;\in\;\Conid{A})\;\rightarrow\;\Varid{f}\;\Varid{a}\;\equiv\;\Varid{g}\;\Varid{a})\;\rightarrow\;\Varid{f}\;\equiv\;\Varid{g}{}\<[E]%
+\\[\blanklineskip]%
+\>[3]{}\Varid{ext⁻¹}\;\in\;{}\<[12]%
+\>[12]{}\{\mskip1.5mu \Varid{f}\;\Varid{g}\;\in\;(\Varid{a}\;\in\;\Conid{A})\;\rightarrow\;\Conid{B}\;\Varid{a}\mskip1.5mu\}\;\rightarrow\;{}\<[E]%
+\\
+\>[12]{}\Varid{f}\;\equiv\;\Varid{g}\;\rightarrow\;((\Varid{a}\;\in\;\Conid{A})\;\rightarrow\;\Varid{f}\;\Varid{a}\;\equiv\;\Varid{g}\;\Varid{a}){}\<[E]%
+\\
+\>[3]{}\Varid{ext⁻¹}\;\Varid{refl}\;\Varid{a}\;\mathrel{=}\;\Varid{refl}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+This obviously creates non-canonical elements of \ensuremath{\Varid{\char95 ≅\char95 }}, but does not make our theory unsound.
+
+We also use the principle of uniqueness of identity types, to simplyfy some of our constructions:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[3]{}\Conid{UIP}\;\in\;\{\mskip1.5mu \Varid{a}\;\Varid{b}\;\in\;\Conid{A}\mskip1.5mu\}\;\{\mskip1.5mu \Varid{p}\;\in\;\Varid{a}\;\cong\;\Varid{b}\mskip1.5mu\}\;\{\mskip1.5mu \Varid{q}\;\in\;\Varid{a}\;\cong\;\Varid{b}\mskip1.5mu\}\;\rightarrow\;\Varid{p}\;\cong\;\Varid{q}{}\<[E]%
+\\
+\>[3]{}\Conid{UIP}\;\{\mskip1.5mu \Varid{p}\;\mathrel{=}\;\Varid{refl}\mskip1.5mu\}\;\{\mskip1.5mu \Varid{q}\;\mathrel{=}\;\Varid{refl}\mskip1.5mu\}\;\mathrel{=}\;\Varid{refl}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+Instead of having all of Agda's data-types we assume that we only have \ensuremath{\Conid{W}}-types.
+A type theory has \ensuremath{\Conid{W}} types if it has a type former \ensuremath{\Conid{W}\;\in\;(\Conid{S}\;\in\;\Conid{Set})\;(\Conid{P}\;\in\;\Conid{S}\;\rightarrow\;\Conid{Set})\;\rightarrow\;\Conid{Set}} with a constructor \ensuremath{\Varid{sup}} and an eliminator \ensuremath{\Varid{wrec}}:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{9}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{15}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Keyword{data}\;\Conid{W}\;(\Conid{S}\;\in\;\Conid{Set})\;(\Conid{P}\;\in\;\Conid{S}\;\rightarrow\;\Conid{Set})\;\in\;\Conid{Set}\;\Keyword{where}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{sup}\;\in\;(\Sigma\;\Conid{S}\;\lambda\;\Varid{s}\;\rightarrow\;\Conid{P}\;\Varid{s}\;\rightarrow\;\Conid{W}\;\Conid{S}\;\Conid{P})\;\rightarrow\;\Conid{W}\;\Conid{S}\;\Conid{P}{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\Varid{wrec}\;\in\;{}\<[9]%
+\>[9]{}\{\mskip1.5mu \Conid{S}\;\in\;\Conid{Set}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{P}\;\in\;\Conid{S}\;\rightarrow\;\Conid{Set}\mskip1.5mu\}\;(\Conid{Q}\;\in\;\Conid{W}\;\Conid{S}\;\Conid{P}\;\rightarrow\;\Conid{Set})\;{}\<[E]%
+\\
+\>[9]{}(\Varid{x}\;\in\;\Conid{W}\;\Conid{S}\;\Conid{P})\;{}\<[E]%
+\\
+\>[9]{}(\Varid{m}\;\in\;{}\<[15]%
+\>[15]{}(\Varid{s}\;\in\;\Conid{S})\;(\Varid{f}\;\in\;\Conid{P}\;\Varid{s}\;\rightarrow\;\Conid{W}\;\Conid{S}\;\Conid{P})\;{}\<[E]%
+\\
+\>[15]{}(\Varid{h}\;\in\;(\Varid{p}\;\in\;\Conid{P}\;\Varid{s})\;\rightarrow\;\Conid{Q}\;(\Varid{f}\;\Varid{p}))\;{}\<[E]%
+\\
+\>[15]{}\rightarrow\;\Conid{Q}\;(\Varid{sup}\;(\Varid{s},\Varid{f})))\;{}\<[E]%
+\\
+\>[9]{}\rightarrow\;\Conid{Q}\;\Varid{x}{}\<[E]%
+\\
+\>[B]{}\Varid{wrec}\;\Conid{Q}\;(\Varid{sup}\;(\Varid{s},\Varid{f}))\;\Varid{m}\;\mathrel{=}\;\Varid{m}\;\Varid{s}\;\Varid{f}\;(\lambda\;\Varid{p}\;\rightarrow\;\Varid{wrec}\;\Conid{Q}\;(\Varid{f}\;\Varid{p})\;\Varid{m}){}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\noindent
+We will continue to define extra Agda data-types in the rest of the paper, but in the end we will show how each of these can be reduced to a theory that contains only \ensuremath{\Conid{W}}.
+For compactness, and readablity we will also define functions using Agda's pattern matching syntax, rather than encoding them using wrec, it is an unstated lemma that each of these definitions can be reduced to terms which only use \ensuremath{\Varid{wrec}},
+
+We are going to use type theory versions of certain category theoretic concepts 
+For instance, we use ends \ensuremath{\Conid{End}} to capture natural transformations.
+Given a bifunctor \ensuremath{\Conid{F}\;\in\;\Conid{Set}^{\Varid{op}}\;\rightarrow\;\Conid{Set}\;\rightarrow\;\Conid{Set}}, an element of \ensuremath{\prodd\;\Conid{X}\;.\;\Conid{F}\;\Conid{X}\;\Conid{X}} is
+equivalent to an element of \ensuremath{\Varid{f}\;\in\;\{\mskip1.5mu \Conid{X}\;\in\;\Conid{Set}\mskip1.5mu\}\;\rightarrow\;\Conid{F}\;\Conid{X}\;\Conid{X}}, along with a proof:
+
+\[ \mbox{\ensuremath{\{\mskip1.5mu \Conid{A}\;\Conid{B}\;\in\;\Conid{Set}\mskip1.5mu\}\;(\Varid{g}\;\in\;\Conid{A}\;\rightarrow\;\Conid{B})\;\rightarrow\;\Conid{F}\;\Varid{g}\;\Conid{B}\;(\Varid{f}\;\{\mskip1.5mu \Conid{B}\mskip1.5mu\})\;\equiv\;\Conid{F}\;\Conid{A}\;\Varid{g}\;(\Varid{f}\;\{\mskip1.5mu \Conid{A}\mskip1.5mu\})}} \]
+
+\noindent
+The natural transformations between functors \ensuremath{\Conid{F}} and \ensuremath{\Conid{G}} are
+ends \ensuremath{\prodd\;\Conid{X}\;.\;\Conid{F}\;\Conid{X}\;\rightarrow\;\Conid{G}\;\Conid{X}}. We will often ignore the presence of the proofs, and 
+use such ends directly as polymorphic functions.
+
+In this setting, the Yoneda lemma can be stated as follows, for any functor \ensuremath{\Conid{F}}:
+
+\[\mbox{\ensuremath{\Conid{F}\;\Conid{X}\;\cong\;\prodd\;\Conid{Y}\;.\;(\Conid{X}\;\rightarrow\;\Conid{Y})\;\rightarrow\;\Conid{F}\;\Conid{Y}}}\]
+
+we will make use of this fact later on.
+
+Finally, for readability we will elide certain artifacts in Agda's syntax, for instance the quantification of implicit arguments when their types can be inferred from the context.
+The reader should be reassured that the paper is a literate agda file, available from the final author's webpage.
 
@@
 
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{5}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{21}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{28}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{69}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Keyword{record}\;\Conid{Cont}\;\in\;\Conid{Set₁}\;\Keyword{where}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Keyword{constructor}\;\anonymous \lhd\anonymous {}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Keyword{field}{}\<[E]%
+\\
+\>[3]{}\hsindent{2}{}\<[5]%
+\>[5]{}\Conid{S}\;\in\;\Conid{Set}{}\<[E]%
+\\
+\>[3]{}\hsindent{2}{}\<[5]%
+\>[5]{}\Conid{P}\;\in\;\Conid{S}\;\rightarrow\;\Conid{Set}{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\Varid{⟦\char95 ⟧}\;\in\;\Conid{Cont}\;\rightarrow\;\Conid{Func}{}\<[E]%
+\\
+\>[B]{}\Varid{⟦}\;\Conid{S}\;\lhd\;\Conid{P}\;\Varid{⟧}\;\mathrel{=}\;\Keyword{record}\;{}\<[21]%
+\>[21]{}\{\mskip1.5mu \Varid{obj}\;{}\<[28]%
+\>[28]{}\mathrel{=}\;\lambda\;\Conid{A}\;\rightarrow\;\Sigma\;\Conid{S}\;\lambda\;\Varid{s}\;\rightarrow\;\Conid{P}\;\Varid{s}\;\rightarrow\;\Conid{A}{}\<[E]%
+\\
+\>[21]{};\Varid{mor}\;{}\<[28]%
+\>[28]{}\mathrel{=}\;\lambda\;\Varid{m}\;\rightarrow\;\lambda (\!\;\Varid{s}\;\!,\!\;\Varid{f}\;\!\!)\;\rightarrow\;(\Varid{s},\Varid{m}\;\ensuremath{\mbox{$\circ$}}\;\Varid{f})\;{}\<[69]%
+\>[69]{}\!\;\!{}\<[E]%
+\\
+\>[21]{}\mskip1.5mu\}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+For example the list functor is a container, its shapes are given by the natural numbers (representing the list's length) and the positions for a shape \ensuremath{\Varid{n}\;\in\;\Conid{ℕ}} are given by a finite set of size \ensuremath{\Varid{n}}.
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{5}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Keyword{record}\;\anonymous \Rightarrow\anonymous \;(\Conid{C}\;\Conid{D}\;\in\;\Conid{Cont})\;\in\;\Conid{Set}\;\Keyword{where}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Keyword{constructor}\;\anonymous \lhd\anonymous {}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Keyword{field}{}\<[E]%
+\\
+\>[3]{}\hsindent{2}{}\<[5]%
+\>[5]{}\Varid{f}\;\in\;\Conid{C}\;\!.\Conid{S}\;\rightarrow\;\Conid{D}\;\!.\Conid{S}{}\<[E]%
+\\
+\>[3]{}\hsindent{2}{}\<[5]%
+\>[5]{}\Varid{r}\;\in\;(\Varid{s}\;\in\;\Conid{C}\;\!.\Conid{S})\;\rightarrow\;\Conid{D}\;\!.\Conid{P}\;\!\!\;(\Varid{f}\;\Varid{s})\;\rightarrow\;\Conid{C}\;\!.\Conid{P}\;\!\!\;\Varid{s}{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\Varid{⟦}\anonymous \Varid{⟧}\mbox{$\!^{\Rightarrow}$}\;\in\;\forall{}\;\{\mskip1.5mu \Conid{C}\;\Conid{D}\mskip1.5mu\}\;\rightarrow\;\Conid{C}\;\Rightarrow\;\Conid{D}\;\rightarrow\;\prodd\;\Conid{A}\;.\;(\!\;\Varid{⟦}\;\Conid{C}\;\Varid{⟧}\;\Conid{A}\;\rightarrow\;\!\;\Varid{⟦}\;\Conid{D}\;\Varid{⟧}\;\Conid{A}){}\<[E]%
+\\
+\>[B]{}\Varid{⟦}\;\Varid{f}\;\lhd\;\Varid{r}\;\Varid{⟧}\mbox{$\!^{\Rightarrow}$}\;(\Varid{s},\Varid{g})\;\mathrel{=}\;\Varid{f}\;\Varid{s},\Varid{g}\;\ensuremath{\mbox{$\circ$}}\;\Varid{r}\;\Varid{s}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+The category of containers is a full and faithful sub-category of the functor category.
+We have also shown that the category of containers is locally cartesian closed, and is closed under formation of co-products.
+
+Container functors have initial algebras, indeed these are exactly the \ensuremath{\Conid{W}} types we know well from Type-Theory, which we can be equivalently defined to be:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Keyword{data}\;\Conid{W}\;(\Conid{S}\;\in\;\Conid{Set})\;(\Conid{P}\;\in\;\Conid{S}\;\rightarrow\;\Conid{Set})\;\in\;\Conid{Set}\;\Keyword{where}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{sup}\;\in\;\!\;\Varid{⟦}\;\Conid{S}\;\lhd\;\Conid{P}\;\Varid{⟧}\;(\Conid{W}\;\Conid{S}\;\Conid{P})\;\rightarrow\;\Conid{W}\;\Conid{S}\;\Conid{P}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+However, we have also shown that for \ensuremath{\Varid{n}}-ary containers (containers with \ensuremath{\Varid{n}} position sets), it is possible to define a \emph{parameterised} initial algebra construction \ensuremath{\mu\;\in\;\forall{}\;\{\mskip1.5mu \Varid{n}\mskip1.5mu\}\;\rightarrow\;\Conid{Cont}\;(\Varid{suc}\;\Varid{n})\;\rightarrow\;\Conid{Cont}\;\Varid{n}}.
+This allows us to model a broad range of nested and mutual types as containers.
+We will develop an analogous construction for indexed conatainers in section ???.
+
+%%Indexed Functors
+
 \section{Indexed Functors}
 
-\begin{hscode}\SaveRestoreHook
-\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{4}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{6}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
-\>[B]{}\Keyword{record}\;\Conid{IFunc}\;(\Conid{I}\;\mathbin{:}\;\Conid{Set})\;\mathbin{:}\;\Conid{Set}\;\Keyword{where}{}\<[E]%
-\\
-\>[B]{}\hsindent{4}{}\<[4]%
-\>[4]{}\Keyword{field}{}\<[E]%
-\\
-\>[4]{}\hsindent{2}{}\<[6]%
-\>[6]{}\Varid{obj}\;\mathbin{:}\;(\Conid{A}\;\mathbin{:}\;\Conid{I}\;\to \;\Conid{Set})\;\to \;\Conid{Set}{}\<[E]%
-\\
-\>[4]{}\hsindent{2}{}\<[6]%
-\>[6]{}\Varid{mor}\;\mathbin{:}\;\forall{}\;\{\mskip1.5mu \Conid{A}\;\Conid{B}\mskip1.5mu\}\;\to \;(\Conid{A}\;\dot{\rightarrow}\;\Conid{B})\;\to \;\Varid{obj}\;\Conid{A}\;\to \;\Varid{obj}\;\Conid{B}{}\<[E]%
-\ColumnHook
-\end{hscode}\resethooks
+Given \ensuremath{\Conid{I}\;\in\;\Conid{Set}} we consider the category of families over \ensuremath{\Conid{I}}. Its objects are
+\ensuremath{\Conid{I}}-indexed families of types \ensuremath{\Conid{A}\;\in\;\Conid{I}\;\rightarrow\;\Conid{Set}} and morphisms are given by 
+\ensuremath{\Conid{I}}-indexed families of functions:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{8}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\anonymous \rightarrow^{\star}\anonymous \;\in\;\{\mskip1.5mu \Conid{I}\;\in\;\Conid{Set}\mskip1.5mu\}\;\to \;(\Conid{A}\;\Conid{B}\;\in\;\Conid{I}\;\to \;\Conid{Set})\;\to \;\Conid{Set}{}\<[E]%
+\\
+\>[B]{}\anonymous \rightarrow^{\star}\anonymous \;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\Conid{A}\;\Conid{B}\;\mathrel{=}\;(\Varid{i}\;\in\;\Conid{I})\;\to \;\Conid{A}\;\Varid{i}\;\to \;\Conid{B}\;\Varid{i}{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\Varid{id}^{\star}\;\in\;\{\mskip1.5mu \Conid{I}\;\in\;\Conid{Set}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{A}\;\in\;\Conid{I}\;\rightarrow\;\Conid{Set}\mskip1.5mu\}\;\rightarrow\;\Conid{A}\;\rightarrow^{\star}\;\Conid{A}{}\<[E]%
+\\
+\>[B]{}\Varid{id}^{\star}\;\Varid{i}\;\Varid{a}\;\mathrel{=}\;\Varid{a}{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\anonymous \circ^{\star}\anonymous \;\in\;{}\<[8]%
+\>[8]{}\{\mskip1.5mu \Conid{I}\;\in\;\Conid{Set}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{A}\;\Conid{B}\;\Conid{C}\;\in\;\Conid{I}\;\rightarrow\;\Conid{Set}\mskip1.5mu\}\;\rightarrow\;{}\<[E]%
+\\
+\>[8]{}(\Conid{B}\;\rightarrow^{\star}\;\Conid{C})\;\rightarrow\;(\Conid{A}\;\rightarrow^{\star}\;\Conid{B})\;\rightarrow\;(\Conid{A}\;\rightarrow^{\star}\;\Conid{C}){}\<[E]%
+\\
+\>[B]{}\Varid{f}\;\circ^{\star}\;\Varid{g}\;\mathrel{=}\;\lambda\;\Varid{i}\;\rightarrow\;(\Varid{f}\;\Varid{i})\;\ensuremath{\mbox{$\circ$}}\;(\Varid{g}\;\Varid{i}){}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\noindent
+We call this category \ensuremath{\Conid{Fam}\;\Conid{I}}.
+An \ensuremath{\Conid{I}}-indexed functor is then a functor from \ensuremath{\Conid{Fam}\;\Conid{I}} to \ensuremath{\Conid{Set}}, given by:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{5}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Keyword{record}\;\Conid{IFunc}\;(\Conid{I}\;\in\;\Conid{Set})\;\in\;\Conid{Set₁}\;\Keyword{where}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Keyword{field}{}\<[E]%
+\\
+\>[3]{}\hsindent{2}{}\<[5]%
+\>[5]{}\Varid{obj}\;\in\;(\Conid{A}\;\in\;\Conid{Fam}\;\Conid{I})\;\to \;\Conid{Set}{}\<[E]%
+\\
+\>[3]{}\hsindent{2}{}\<[5]%
+\>[5]{}\Varid{mor}\;\in\;\forall{}\;\{\mskip1.5mu \Conid{A}\;\Conid{B}\mskip1.5mu\}\;\to \;(\Conid{A}\;\rightarrow^{\star}\;\Conid{B})\;\to \;\Varid{obj}\;\Conid{A}\;\to \;\Varid{obj}\;\Conid{B}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\noindent
+such that both \ensuremath{\Varid{id}^{\star}} is mapped to \ensuremath{\Varid{id}} and \ensuremath{\anonymous \circ^{\star}\anonymous } to \ensuremath{\anonymous \ensuremath{\mbox{$\circ$}}\anonymous } under the action of
+\ensuremath{\Varid{mor}}. We adopt the convention that the projections \ensuremath{\Varid{obj}} and \ensuremath{\Varid{mor}} are silent, 
+\emph{i.e.} depending on the context \ensuremath{\Conid{F}\;\in\;\Conid{IFunc}\;\Conid{I}} can stand for either the 
+functor's action on objects, or on morphisms. A morphism between to such 
+indexed functors is a natural transormation:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{12}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\anonymous \Rightarrow^{\text{\tiny F}}\anonymous \;\in\;\forall{}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\rightarrow\;(\Conid{F}\;\Conid{G}\;\in\;\Conid{IFunc}\;\Conid{I})\;\rightarrow\;\Conid{Set₁}{}\<[E]%
+\\
+\>[B]{}\Conid{F}\;\Rightarrow^{\text{\tiny F}}\;\Conid{G}\;\mathrel{=}\;{}\<[12]%
+\>[12]{}\prodd\;\Conid{A}\;.\;\!\;\Conid{F}\;\Conid{A}\;\rightarrow\;\!\;\Conid{G}\;\Conid{A}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\noindent
+
+\ensuremath{\Conid{IFunc}} comes with a monad like structure given by:
 
@@
 \column{E}{@{}>{\hspre}l<{\hspost}@{}}%
-\>[B]{}\eta^{F}\;\mathbin{:}\;\forall{}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\rightarrow\;\Conid{I}\;\rightarrow\;\Conid{IFunc}\;\Conid{I}{}\<[E]%
-\\
-\>[B]{}\eta^{F}\;\Varid{i}\;\mathrel{=}\;\Keyword{record}\;\{\mskip1.5mu \Varid{obj}\;\mathrel{=}\;\lambda\;\Conid{A}\;\rightarrow\;\Conid{A}\;\Varid{i};\Varid{mor}\;\mathrel{=}\;\lambda\;\Varid{f}\;\rightarrow\;\Varid{f}\;\Varid{i}\mskip1.5mu\}{}\<[E]%
-\\[\blanklineskip]%
-\>[B]{}\_\bind ^{F}\_\;\mathbin{:}\;\forall{}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\mskip1.5mu\}\;\rightarrow\;(\Conid{I}\;\rightarrow\;\Conid{IFunc}\;\Conid{J})\;\rightarrow\;\Conid{IFunc}\;\Conid{I}\;\rightarrow\;\Conid{IFunc}\;\Conid{J}{}\<[E]%
-\\
-\>[B]{}\Conid{H}\;\bind ^{F}\;\Conid{F}\;\mathrel{=}{}\<[E]%
+\>[B]{}\eta^{\text{\tiny F}}\;\in\;\forall{}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\rightarrow\;\Conid{I}\;\rightarrow\;\Conid{IFunc}\;\Conid{I}{}\<[E]%
+\\
+\>[B]{}\eta^{\text{\tiny F}}\;\Varid{i}\;\mathrel{=}\;\Keyword{record}\;\{\mskip1.5mu \Varid{obj}\;\mathrel{=}\;\lambda\;\Conid{A}\;\rightarrow\;\Conid{A}\;\Varid{i};\Varid{mor}\;\mathrel{=}\;\lambda\;\Varid{f}\;\rightarrow\;\Varid{f}\;\Varid{i}\mskip1.5mu\}{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\anonymous \bind ^{\text{\tiny F}}\anonymous \;\in\;\forall{}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\mskip1.5mu\}\;\rightarrow\;\Conid{IFunc}\;\Conid{I}\;\rightarrow\;(\Conid{I}\;\rightarrow\;\Conid{IFunc}\;\Conid{J})\;\rightarrow\;\Conid{IFunc}\;\Conid{J}{}\<[E]%
+\\
+\>[B]{}\Conid{F}\;\bind ^{\text{\tiny F}}\;\Conid{H}\;\mathrel{=}{}\<[E]%
 \\
@@
 
-\begin{hscode}\SaveRestoreHook
-\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{10}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{14}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{16}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
-\>[B]{}\Conid{IFunc}^{\star}\;\mathbin{:}\;(\Conid{I}\;\Conid{J}\;\mathbin{:}\;\Conid{Set})\;\rightarrow\;\Conid{Set}{}\<[E]%
+\noindent
+It's clear that \ensuremath{\Conid{IFunc}} cannot be a monad in the usual sense, since it is not 
+an endo-functor, it does how ever fit with the notion of relative monad 
+presented by Altenkirch \emph{et al.} Note that in the code above we have 
+elided the use of the lifting functor.
+
+\begin{proposition} 
+\ensuremath{(\Conid{IFunc},\eta^{\text{\tiny F}},\anonymous \bind ^{\text{\tiny F}}\anonymous )} is a \emph{relative monad}\cite{relmonads} on the 
+lifting functor \ensuremath{\uparrow\;\in\;\Conid{Set}_{i}\;\rightarrow\;\Conid{Set}_{i+1}}.
+\end{proposition}
+
+\begin{proof}
+To prove the structure is a relative 
+monad we observe that the following equlities hold up to 
+Agda's $\beta\eta$-equality, and our postulate \ensuremath{\Varid{ext}}.
+
+For \ensuremath{\Conid{F}\;\in\;\Conid{IFunc}\;\Conid{I}}, \ensuremath{\Conid{G}\;\in\;\Conid{I}\;\rightarrow\;\Conid{IFunc}\;\Conid{J}}, \ensuremath{\Conid{H}\;\in\;\Conid{J}\;\rightarrow\;\Conid{IFunc}\;\Conid{K}}:
+\begin{align}
+\ensuremath{\Conid{H}\;\Varid{i}}                 &\quad& \equiv &&\quad& \ensuremath{(\eta^{\text{\tiny F}}\;\Varid{i})\;\bind ^{\text{\tiny F}}\;\Conid{H}}               \\
+\ensuremath{\Conid{F}}                   && \equiv &&& \ensuremath{\Conid{F}\;\bind ^{\text{\tiny F}}\;\eta^{\text{\tiny F}}}                 \\
+\ensuremath{(\Conid{F}\;\bind ^{\text{\tiny F}}\;\Conid{G})\;\bind ^{\text{\tiny F}}\;\Conid{F}} && \equiv &&& \ensuremath{\Conid{F}\;\bind ^{\text{\tiny F}}\;(\lambda\;\Varid{i}\;\rightarrow\;(\Conid{G}\;\Varid{i})\;\bind ^{\text{\tiny F}}\;\Conid{H})}
+\end{align}
+
+\end{proof}
+
+\noindent
+The opposite of the Kleisli category associated with \ensuremath{\Conid{IFunc}} has objects 
+\ensuremath{\Conid{I},\Conid{J}\;\in\;\Conid{Set}} and morphisms given by \ensuremath{\Conid{J}}-indexed families of \ensuremath{\Conid{I}}-indexed 
+functors. We denote this notion of indexed functor \ensuremath{\Conid{IFunc}^{\star}}:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{9}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{13}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{15}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Conid{IFunc}^{\star}\;\in\;(\Conid{I}\;\Conid{J}\;\in\;\Conid{Set})\;\rightarrow\;\Conid{Set₁}{}\<[E]%
 \\
@@
 \\[\blanklineskip]%
-\>[B]{}\Varid{obj}^{\star}\;\mathbin{:}\;\forall{}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\mskip1.5mu\}\;\rightarrow\;\Conid{IFunc}^{\star}\;\Conid{I}\;\Conid{J}\;\rightarrow\;(\Conid{I}\;\rightarrow\;\Conid{Set})\;\rightarrow\;\Conid{J}\;\rightarrow\;\Conid{Set}{}\<[E]%
-\\
-\>[B]{}\Varid{obj}^{\star}\;\Conid{F}\;\Conid{A}\;\Varid{j}\;{}\<[16]%
-\>[16]{}\mathrel{=}\;\!\;(\Conid{F}\;\Varid{j})\;\Conid{A}{}\<[E]%
-\\[\blanklineskip]%
-\>[B]{}\Varid{mor}^{\star}\;\mathbin{:}\;{}\<[10]%
-\>[10]{}\forall{}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\Conid{A}\;\Conid{B}\mskip1.5mu\}\;(\Conid{F}\;\mathbin{:}\;\Conid{IFunc}^{\star}\;\Conid{I}\;\Conid{J})\;\rightarrow\;\Conid{A}\;\dot{\rightarrow}\;\Conid{B}\;\rightarrow\;\Varid{obj}^{\star}\;\Conid{F}\;\Conid{A}\;\dot{\rightarrow}\;\Varid{obj}^{\star}\;\Conid{F}\;\Conid{B}{}\<[E]%
-\\
-\>[B]{}\Varid{mor}^{\star}\;\Conid{F}\;\Varid{m}\;\Varid{j}\;{}\<[14]%
-\>[14]{}\mathrel{=}\;\!\;(\Conid{F}\;\Varid{j})\;\Varid{m}{}\<[E]%
-\ColumnHook
-\end{hscode}\resethooks
+\>[B]{}\Varid{obj}^{\star}\;\in\;\forall{}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\mskip1.5mu\}\;\rightarrow\;\Conid{IFunc}^{\star}\;\Conid{I}\;\Conid{J}\;\rightarrow\;\Conid{Fam}\;\Conid{I}\;\rightarrow\;\Conid{Fam}\;\Conid{J}{}\<[E]%
+\\
+\>[B]{}\Varid{obj}^{\star}\;\Conid{F}\;\Conid{A}\;\Varid{j}\;{}\<[15]%
+\>[15]{}\mathrel{=}\;\!\;(\Conid{F}\;\Varid{j})\;\Conid{A}{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\Varid{mor}^{\star}\;\in\;{}\<[9]%
+\>[9]{}\forall{}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\Conid{A}\;\Conid{B}\mskip1.5mu\}\;(\Conid{F}\;\in\;\Conid{IFunc}^{\star}\;\Conid{I}\;\Conid{J})\;\rightarrow\;\Conid{A}\;\rightarrow^{\star}\;\Conid{B}\;\rightarrow\;\Varid{obj}^{\star}\;\Conid{F}\;\Conid{A}\;\rightarrow^{\star}\;\Varid{obj}^{\star}\;\Conid{F}\;\Conid{B}{}\<[E]%
+\\
+\>[B]{}\Varid{mor}^{\star}\;\Conid{F}\;\Varid{m}\;\Varid{j}\;{}\<[13]%
+\>[13]{}\mathrel{=}\;\!\;(\Conid{F}\;\Varid{j})\;\Varid{m}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\noindent
+Again, we will omit \ensuremath{\Varid{obj}^{\star}} and \ensuremath{\Varid{mor}^{\star}} when inferable from the context 
+in which they appear. Natural transformations extend to this double index 
+setting, too:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\anonymous \Rightarrow^{\text{\tiny F}^{\star}}\anonymous \;\in\;\forall{}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\mskip1.5mu\}\;\rightarrow\;(\Conid{F}\;\Conid{G}\;\in\;\Conid{IFunc}^{\star}\;\Conid{I}\;\Conid{J})\;\rightarrow\;\Conid{Set₁}{}\<[E]%
+\\
+\>[B]{}\Conid{F}\;\Rightarrow^{\text{\tiny F}^{\star}}\;\Conid{G}\;\mathrel{=}\;\prodd\;\Conid{A}\;.\;\;\Conid{F}\;\Conid{A}\;\rightarrow^{\star}\;\;\Conid{G}\;\Conid{A}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\noindent
+Clearly, the Kleisli structure gives rise to identities and composition in 
+\ensuremath{\Conid{IFunc}^{\star}}. Indeed, composition gives rise to a \emph{re-indexing} operation which
+we denote \ensuremath{\Delta^{\text{\tiny F}}}:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Delta^{\text{\tiny F}}\;\in\;\forall{}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\Conid{K}\mskip1.5mu\}\;\rightarrow\;(\Conid{J}\;\rightarrow\;\Conid{K})\;\rightarrow\;\Conid{IFunc}^{\star}\;\Conid{I}\;\Conid{K}\;\rightarrow\;\Conid{IFunc}^{\star}\;\Conid{I}\;\Conid{J}{}\<[E]%
+\\
+\>[B]{}\Delta^{\text{\tiny F}}\;\Varid{f}\;\Conid{F}\;\mathrel{=}\;\Conid{F}\;\ensuremath{\mbox{$\circ$}}\;\Varid{f}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\noindent
+This construction is used, for instance, in building the pattern functor for \ensuremath{\Conid{ScLam}} as in the introduction; Concentranting only on the \ensuremath{\Varid{abs}} case we want to build
+\ensuremath{\Conid{FScLam′}\;\Conid{X}\;\Varid{n}\;\mathrel{=}\;(\Conid{X}\;\ensuremath{\mbox{$\circ$}}\;\Varid{suc})\;\Varid{n}}.
+Or simply \ensuremath{\Conid{LScLam′}\;\Conid{X}\;\mathrel{=}\;\Delta^{\text{\tiny F}}\;\Varid{suc}\;\Conid{X}}.
+In general this combinator
+restricts the functor \ensuremath{\Conid{X}} to the indexes in the image of the
+function \ensuremath{\Varid{f}}.
+
+What if the restriction appears on the right of such an equation? As an example,
+consider the successor constructor for \ensuremath{\Conid{Fin}}; here we want to build the pattern functor: \ensuremath{\Conid{FFin′}\;\Conid{X}\;(\Varid{1}\;\Varid{+}\;\Varid{n})\;\mathrel{=}\;\Conid{F}\;\Varid{n}\;\Conid{X}}.
+To do this we observe that this is equivalent to
+the equation \ensuremath{\Conid{FFin′}\;\Conid{X}\;\Varid{n}\;\mathrel{=}\;\Sigma\;\Conid{Nat}\;\lambda\;\Varid{m}\;\rightarrow\;\Varid{n}\;\equiv\;\Varid{1}\;\Varid{+}\;\Varid{m}\;\times\;\Conid{X}\;\Varid{m}}.
+We denote the general
+construction \ensuremath{\Sigma^{\text{\tiny F}}}, so the 2nd equation can be written \ensuremath{\Conid{FFin′}\;\Conid{X}\;\mathrel{=}\;\Sigma^{\text{\tiny F}}\;\Varid{suc}\;\Conid{X}}:
 
@@
 \column{23}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{40}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{91}{@{}>{\hspre}c<{\hspost}@{}}%
-\column{91E}{@{}l@{}}%
-\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
-\>[B]{}\Sigma^{F}\;\mathbin{:}\;\forall{}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\Conid{K}\mskip1.5mu\}\;\rightarrow\;(\Conid{J}\;\rightarrow\;\Conid{K})\;\rightarrow\;\Conid{IFunc}^{\star}\;\Conid{I}\;\Conid{J}\;\rightarrow\;\Conid{IFunc}^{\star}\;\Conid{I}\;\Conid{K}{}\<[E]%
-\\
-\>[B]{}\Sigma^{F}\;\{\mskip1.5mu \Conid{J}\;\mathrel{=}\;\Conid{J}\mskip1.5mu\}\;\Varid{f}\;\Conid{F}\;\Varid{k}\;\mathrel{=}{}\<[E]%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Sigma^{\text{\tiny F}}\;\in\;\forall{}\;\{\mskip1.5mu \Conid{J}\;\Conid{I}\;\Conid{K}\mskip1.5mu\}\;\rightarrow\;(\Conid{J}\;\rightarrow\;\Conid{K})\;\rightarrow\;\Conid{IFunc}^{\star}\;\Conid{I}\;\Conid{J}\;\rightarrow\;\Conid{IFunc}^{\star}\;\Conid{I}\;\Conid{K}{}\<[E]%
+\\
+\>[B]{}\Sigma^{\text{\tiny F}}\;\{\mskip1.5mu \Conid{J}\mskip1.5mu\}\;\Varid{f}\;\Conid{F}\;\Varid{k}\;\mathrel{=}{}\<[E]%
 \\
@@
 \>[20]{}\mathrel{=}\;{}\<[23]%
-\>[23]{}\lambda\;\Conid{A}\;\rightarrow\;\Sigma\;\Conid{J}\;\lambda\;\Varid{j}\;\rightarrow\;\Varid{f}\;\Varid{j}\;\equiv\;\Varid{k}\;\times\;\!\;\Conid{F}\;\Conid{A}\;\Varid{j}{}\<[E]%
+\>[23]{}\lambda\;\Conid{A}\;\rightarrow\;\Sigma\;\Conid{J}\;\lambda\;\Varid{j}\;\rightarrow\;\Varid{f}\;\Varid{j}\;\equiv\;\Varid{k}\;\times\;\;\Conid{F}\;\Conid{A}\;\Varid{j}{}\<[E]%
 \\
@@
 \>[20]{}\mathrel{=}\;{}\<[23]%
-\>[23]{}\lambda\;\Varid{m}\;\rightarrow\;\Varid{<}\;\pi_{0},{}\<[40]%
-\>[40]{}\Varid{<}\;\pi_{0}\;\ensuremath{\mbox{$\circ$}}\;\pi_{1},\!\;\Conid{F}\;\Varid{m}\;\anonymous \;\ensuremath{\mbox{$\circ$}}\;\pi_{1}\;\ensuremath{\mbox{$\circ$}}\;\pi_{1}\;\Varid{>}\;\Varid{>}{}\<[91]%
-\>[91]{}\mskip1.5mu\}{}\<[91E]%
-\\[\blanklineskip]%
-\>[B]{}\Pi^{F}\;\mathbin{:}\;\forall{}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\Conid{K}\mskip1.5mu\}\;\rightarrow\;(\Conid{J}\;\rightarrow\;\Conid{K})\;\rightarrow\;\Conid{IFunc}^{\star}\;\Conid{I}\;\Conid{J}\;\rightarrow\;\Conid{IFunc}^{\star}\;\Conid{I}\;\Conid{K}{}\<[E]%
-\\
-\>[B]{}\Pi^{F}\;\{\mskip1.5mu \Conid{J}\;\mathrel{=}\;\Conid{J}\mskip1.5mu\}\;\Varid{f}\;\Conid{F}\;\Varid{k}\;\mathrel{=}{}\<[E]%
+\>[23]{}\lambda\;\Varid{m}\;\rightarrow\;\lambda (\!\;\Varid{j}\;\!,\!\;\Varid{p}\;\!,\!\;\Varid{x}\;\!\!)\;\rightarrow\;(\Varid{j},\Varid{p},\;\Conid{F}\;\Varid{m}\;\Varid{j}\;\Varid{x})\;\!\;\!\mskip1.5mu\}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\noindent
+Perhaps unsuprisingly, \ensuremath{\Sigma^{\text{\tiny F}}} turns out to be the left adjoint to re-indexing 
+(\ensuremath{\Delta^{\text{\tiny F}}}). Its right adjoint, we denote \ensuremath{\Pi^{\text{\tiny F}}}:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{4}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{12}{@{}>{\hspre}c<{\hspost}@{}}%
+\column{12E}{@{}l@{}}%
+\column{15}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{20}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{23}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Pi^{\text{\tiny F}}\;\in\;\forall{}\;\{\mskip1.5mu \Conid{J}\;\Conid{I}\;\Conid{K}\mskip1.5mu\}\;\rightarrow\;(\Conid{J}\;\rightarrow\;\Conid{K})\;\rightarrow\;\Conid{IFunc}^{\star}\;\Conid{I}\;\Conid{J}\;\rightarrow\;\Conid{IFunc}^{\star}\;\Conid{I}\;\Conid{K}{}\<[E]%
+\\
+\>[B]{}\Pi^{\text{\tiny F}}\;\{\mskip1.5mu \Conid{J}\mskip1.5mu\}\;\Varid{f}\;\Conid{F}\;\Varid{k}\;\mathrel{=}{}\<[E]%
 \\
@@
 \>[20]{}\mathrel{=}\;{}\<[23]%
-\>[23]{}\lambda\;\Conid{A}\;\rightarrow\;(\Varid{j}\;\mathbin{:}\;\Conid{J})\;\rightarrow\;\Varid{f}\;\Varid{j}\;\equiv\;\Varid{k}\;\rightarrow\;\!\;\Conid{F}\;\Conid{A}\;\Varid{j}{}\<[E]%
+\>[23]{}\lambda\;\Conid{A}\;\rightarrow\;(\Varid{j}\;\in\;\Conid{J})\;\rightarrow\;\Varid{f}\;\Varid{j}\;\equiv\;\Varid{k}\;\rightarrow\;\;\Conid{F}\;\Conid{A}\;\Varid{j}{}\<[E]%
 \\
@@
 \>[20]{}\mathrel{=}\;{}\<[23]%
-\>[23]{}\lambda\;\Varid{m}\;\Varid{f}\;\Varid{j}\;\Varid{p}\;\rightarrow\;\!\;\Conid{F}\;\Varid{m}\;\Varid{j}\;(\Varid{f}\;\Varid{j}\;\Varid{p})\mskip1.5mu\}{}\<[E]%
-\ColumnHook
-\end{hscode}\resethooks
+\>[23]{}\lambda\;\Varid{m}\;\Varid{g}\;\Varid{j}\;\Varid{p}\;\rightarrow\;\;\Conid{F}\;\Varid{m}\;\Varid{j}\;(\Varid{g}\;\Varid{j}\;\Varid{p})\mskip1.5mu\}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\begin{proposition}
+\ensuremath{\Sigma^{\text{\tiny F}}} and \ensuremath{\Pi^{\text{\tiny F}}} are left and right adjoint to re-indexing (\ensuremath{\Delta^{\text{\tiny F}}}). 
+\end{proposition}
+
+\begin{proof}
+
+To show this we need to show that for all \ensuremath{\Varid{f}\;\in\;\Conid{J}\;\rightarrow\;\Conid{K}}, \ensuremath{\Varid{g}\;\in\;\Conid{K}\;\rightarrow\;\Conid{J}}, \ensuremath{\Conid{F}\;\in\;\Conid{IFunc}^{\star}\;\Conid{I}\;\Conid{J}} and \ensuremath{\Conid{G}\;\in\;\Conid{IFunc}^{\star}\;\Conid{I}\;\Conid{K}}:
+
+\[\begin{array}{c}
+\ensuremath{\Sigma^{\text{\tiny F}}\;\Varid{f}\;\Conid{F}\;\Rightarrow^{\text{\tiny F}^{\star}}\;\Conid{G}}
+\\\hline\hline
+\ensuremath{\Conid{F}\;\Rightarrow^{\text{\tiny F}^{\star}}\;\Delta^{\text{\tiny F}}\;\Varid{f}\;\Conid{G}}\\
+\end{array}
+\quad
+\begin{array}{c}
+\ensuremath{\Delta^{\text{\tiny F}}\;\Varid{f}\;\Conid{F}\;\Rightarrow^{\text{\tiny F}^{\star}}\;\Conid{G}}
+\\\hline\hline
+\ensuremath{\Conid{F}\;\Rightarrow^{\text{\tiny F}^{\star}}\;\Pi^{\text{\tiny F}}\;\Varid{f}\;\Conid{G}}\\
+\end{array}
+\]
+
+We can build the components of these isomorphisms easily:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[3]{}\Sigma\!\dashv\!\Delta\;\in\;(\Varid{f}\;\in\;\Conid{J}\;\rightarrow\;\Conid{K})\;\rightarrow\;(\Sigma^{\text{\tiny F}}\;\Varid{f}\;\Conid{F}\;\Rightarrow^{\text{\tiny F}^{\star}}\;\Conid{G})\;\rightarrow\;(\Conid{F}\;\Rightarrow^{\text{\tiny F}^{\star}}\;\Delta^{\text{\tiny F}}\;\Varid{f}\;\Conid{G}){}\<[E]%
+\\
+\>[3]{}\Sigma\!\dashv\!\Delta\;\Varid{f}\;\Varid{m}\;\Varid{j}\;\Varid{x}\;\mathrel{=}\;\Varid{m}\;(\Varid{f}\;\Varid{j})\;(\Varid{j},\Varid{refl},\Varid{x}){}\<[E]%
+\\[\blanklineskip]%
+\>[3]{}\Sigma\!\dashv\!\Delta\Varid{⁻¹}\;\in\;(\Varid{f}\;\in\;\Conid{J}\;\rightarrow\;\Conid{K})\;\rightarrow\;(\Conid{F}\;\Rightarrow^{\text{\tiny F}^{\star}}\;\Delta^{\text{\tiny F}}\;\Varid{f}\;\Conid{G})\;\rightarrow\;(\Sigma^{\text{\tiny F}}\;\Varid{f}\;\Conid{F}\;\Rightarrow^{\text{\tiny F}^{\star}}\;\Conid{G}){}\<[E]%
+\\
+\>[3]{}\Sigma\!\dashv\!\Delta\Varid{⁻¹}\;\Varid{f}\;\Varid{m}\;.\;(\Varid{f}\;\Varid{j})\;(\Varid{j},\Varid{refl},\Varid{x})\;\mathrel{=}\;\Varid{m}\;\Varid{j}\;\Varid{x}{}\<[E]%
+\\[\blanklineskip]%
+\>[3]{}\Delta\!\dashv\!\Pi\;\in\;(\Varid{g}\;\in\;\Conid{K}\;\rightarrow\;\Conid{J})\;\rightarrow\;(\Delta^{\text{\tiny F}}\;\Varid{g}\;\Conid{F}\;\Rightarrow^{\text{\tiny F}^{\star}}\;\Conid{G})\;\rightarrow\;(\Conid{F}\;\Rightarrow^{\text{\tiny F}^{\star}}\;\Pi^{\text{\tiny F}}\;\Varid{g}\;\Conid{G}){}\<[E]%
+\\
+\>[3]{}\Delta\!\dashv\!\Pi\;\Varid{g}\;\Varid{m}\;.\;(\Varid{g}\;\Varid{k})\;\Varid{x}\;\Varid{k}\;\Varid{refl}\;\mathrel{=}\;\Varid{m}\;\Varid{k}\;\Varid{x}{}\<[E]%
+\\[\blanklineskip]%
+\>[3]{}\Delta\!\dashv\!\Pi\Varid{⁻¹}\;\in\;(\Varid{g}\;\in\;\Conid{K}\;\rightarrow\;\Conid{J})\;\rightarrow\;(\Conid{F}\;\Rightarrow^{\text{\tiny F}^{\star}}\;\Pi^{\text{\tiny F}}\;\Varid{g}\;\Conid{G})\;\rightarrow\;(\Delta^{\text{\tiny F}}\;\Varid{g}\;\Conid{F}\;\Rightarrow^{\text{\tiny F}^{\star}}\;\Conid{G}){}\<[E]%
+\\
+\>[3]{}\Delta\!\dashv\!\Pi\Varid{⁻¹}\;\Varid{g}\;\Varid{m}\;\Varid{k}\;\Varid{x}\;\mathrel{=}\;\Varid{m}\;(\Varid{g}\;\Varid{k})\;\Varid{x}\;\Varid{k}\;\Varid{refl}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\noindent
+It only remains to observe that these pairs or functions are mutual inverses, 
+which is a simple proof.
+
+\end{proof}
+
+In abstracting over all possible values for the extra indexing information \ensuremath{\Pi^{\text{\tiny F}}}
+allows for the construction of infinitely branching trees, such as rose trees. 
+We also note that finite co-products and products can be derived from \ensuremath{\Sigma^{\text{\tiny F}}} and 
+\ensuremath{\Pi^{\text{\tiny F}}} respectively:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{12}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\bot^{\text{\tiny F}}\;\in\;\forall{}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\rightarrow\;\Conid{IFunc}^{\star}\;\Conid{I}\;\top{}\<[E]%
+\\
+\>[B]{}\bot^{\text{\tiny F}}\;\mathrel{=}\;\Sigma^{\text{\tiny F}}\;{}\<[12]%
+\>[12]{}\{\mskip1.5mu \Conid{J}\;\mathrel{=}\;\bot\mskip1.5mu\}\;\anonymous \;\lambda\;(){}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\anonymous \Varid{⊎\char94 F}\anonymous \;\in\;\forall{}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\rightarrow\;(\Conid{F}\;\Conid{G}\;\in\;\Conid{IFunc}\;\Conid{I})\;\rightarrow\;\Conid{IFunc}^{\star}\;\Conid{I}\;\top{}\<[E]%
+\\
+\>[B]{}\Conid{F}\;\mathbin{\uplus^{\text{\tiny F}}}\;\Conid{G}\;\mathrel{=}\;\Sigma^{\text{\tiny F}}\;\anonymous \;\lambda\;\Varid{b}\;\rightarrow\;\Varid{if}\;\Varid{b}\;\Varid{then}\;\Conid{F}\;\Varid{else}\;\Conid{G}{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\top^{\text{\tiny F}}\;\in\;\forall{}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\rightarrow\;\Conid{IFunc}^{\star}\;\Conid{I}\;\top{}\<[E]%
+\\
+\>[B]{}\top^{\text{\tiny F}}\;\mathrel{=}\;\Pi^{\text{\tiny F}}\;{}\<[12]%
+\>[12]{}\{\mskip1.5mu \Conid{J}\;\mathrel{=}\;\bot\mskip1.5mu\}\;\anonymous \;\lambda\;(){}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\anonymous \mathbin{\times^{\text{\tiny F}}}\anonymous \;\in\;\forall{}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\rightarrow\;(\Conid{F}\;\Conid{G}\;\in\;\Conid{IFunc}\;\Conid{I})\;\rightarrow\;\Conid{IFunc}^{\star}\;\Conid{I}\;\top{}\<[E]%
+\\
+\>[B]{}\Conid{F}\;\mathbin{\times^{\text{\tiny F}}}\;\Conid{G}\;\mathrel{=}\;\Pi^{\text{\tiny F}}\;\anonymous \;\lambda\;\Varid{b}\;\rightarrow\;\Varid{if}\;\Varid{b}\;\Varid{then}\;\Conid{F}\;\Varid{else}\;\Conid{G}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\noindent
+Clearly these are simply the constantly \ensuremath{\top} and \ensuremath{\bot} valued functors, and the 
+point-wise product and co-product of functors, but this encoding allows us to 
+keep the number of constants in out vocabulary to a minimum.
+
+\subsection{Initial algebras of indexed functors}
+
+We observe that an \ensuremath{\Conid{F}\;\in\;\Conid{IFunc}^{\star}\;\Conid{I}\;\Conid{I}} is an endo-functor on the category \ensuremath{\Conid{Fam}\;\Conid{I}}. 
+Using this observation we know that an algebra of such a functor is a family 
+\ensuremath{\Conid{A}\;\in\;\Conid{Fam}\;\Conid{I}} and a map \ensuremath{\alpha\;\in\;\;\Conid{F}\;\Conid{A}\;\rightarrow^{\star}\;\Conid{A}}. A morphism, then, between two such 
+algebras \ensuremath{(\Conid{A},\alpha)} and \ensuremath{(\Conid{B},\beta)} is a map \ensuremath{\Varid{f}\;\in\;\Conid{A}\;\rightarrow^{\star}\;\Conid{B}} such that the follow 
+diagram commutes:
+
+ \[
+\xymatrix{
+\mbox{\ensuremath{\;\Conid{F}\;\Conid{A}}}  \ar[r]^{\;\mbox{\ensuremath{\alpha}}} 
+\ar[d]_{\mbox{\ensuremath{\;\Conid{F}\;\Varid{f}}}} & \mbox{\ensuremath{\Conid{A}}} \ar[d]^{\mbox{\ensuremath{\Varid{f}}}}\\
+\mbox{\ensuremath{\;\Conid{F}\;\Conid{B}}} \ar[r]^{\;\mbox{\ensuremath{\beta}}} & \mbox{\ensuremath{\Conid{B}}}}
+\]
+
+\noindent
+If it exists then the initial algebra of \ensuremath{\Conid{F}} is the initial object of the 
+category of \ensuremath{\Conid{F}}-algebras spelt out above. It follows from the fact that not all
+functors in \ensuremath{\Conid{Set}\;\rightarrow\;\Conid{Set}} (for instance \ensuremath{\Conid{F}\;\Conid{A}\;\mathrel{=}\;(\Conid{A}\;\rightarrow\;\Conid{Bool})\;\rightarrow\;\Conid{Bool}}) have initial
+algebras that neither do all indexed-functors.
+
+We also know that we cannot iterate the construction of initial algebras given 
+above, an endo-functor \ensuremath{\Conid{IFunc}^{\star}\;\Conid{I}\;\Conid{I}} gives rise to an initial algebra in \ensuremath{\Conid{Fam}\;\Conid{I}}.
+This prevents us from being able to define nested, or mutual inductive families 
+in this way.
+
+For the morphism part of an indexed-functor over a co-product we can eliminate
+the coproduct and curry the result ing definition in this way:
+
+\begin{align*}
+\ensuremath{\Conid{IFunc}\;(\Conid{I}\;\uplus\;\Conid{J})} 
+  & \equiv      & \ensuremath{(\Conid{I}\;\uplus\;\Conid{J}\;\rightarrow\;\Conid{Set})\;\rightarrow\;\Conid{Set}} \\
+  & \cong       & \ensuremath{(\Conid{I}\;\rightarrow\;\Conid{Set})\;\times\;(\Conid{J}\;\rightarrow\;\Conid{Set})\;\rightarrow\;\Conid{Set}}\\
+  & \cong       & \ensuremath{(\Conid{I}\;\rightarrow\;\Conid{Set})\;\rightarrow\;(\Conid{J}\;\rightarrow\;\Conid{Set})\;\rightarrow\;\Conid{Set}}\\
+\end{align*}
+
+\noindent
+This gives us partial application for indexed 
+functors of the form \ensuremath{\Conid{IFunc}\;(\Conid{I}\;\uplus\;\Conid{J})}. Spelt out concretely we have:
 
@@
 \column{11E}{@{}l@{}}%
-\column{12}{@{}>{\hspre}l<{\hspost}@{}}%
 \column{14}{@{}>{\hspre}l<{\hspost}@{}}%
 \column{19}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{22}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{27}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{46}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{50}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{54}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{59}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
-\>[B]{}\_[\mskip1.5mu \_\mskip1.5mu]^{F}\;\mathbin{:}\;\forall{}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\mskip1.5mu\}\;\rightarrow\;\Conid{IFunc}\;(\Conid{I}\;\uplus\;\Conid{J})\;\rightarrow\;\Conid{IFunc}^{\star}\;\Conid{I}\;\Conid{J}\;\rightarrow\;{}\<[50]%
-\>[50]{}\Conid{IFunc}\;\Conid{I}{}\<[E]%
-\\
-\>[B]{}\Conid{F}\;[\mskip1.5mu \;\Conid{G}\;\mskip1.5mu]^{F}\;{}\<[12]%
-\>[12]{}\mathrel{=}{}\<[E]%
+\column{26}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{45}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{49}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{53}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{58}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\anonymous [\mskip1.5mu \anonymous \mskip1.5mu]^{\text{\tiny F}}\;\in\;\forall{}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\mskip1.5mu\}\;\rightarrow\;\Conid{IFunc}\;(\Conid{I}\;\uplus\;\Conid{J})\;\rightarrow\;\Conid{IFunc}^{\star}\;\Conid{I}\;\Conid{J}\;\rightarrow\;{}\<[49]%
+\>[49]{}\Conid{IFunc}\;\Conid{I}{}\<[E]%
+\\
+\>[B]{}\Conid{F}\;[\mskip1.5mu \;\Conid{G}\;\mskip1.5mu]^{\text{\tiny F}}\;{}\<[11]%
+\>[11]{}\mathrel{=}{}\<[11E]%
 \\
@@
 \>[14]{}\Varid{obj}\;{}\<[19]%
-\>[19]{}\mathrel{=}\;{}\<[22]%
-\>[22]{}\lambda\;\Conid{A}\;{}\<[27]%
-\>[27]{}\rightarrow\;\!\;\Conid{F}\;[\mskip1.5mu \Conid{A}{}\<[46]%
-\>[46]{},\!\;{}\<[54]%
-\>[54]{}\Conid{G}\;\Conid{A}{}\<[59]%
-\>[59]{}\mskip1.5mu]{}\<[E]%
+\>[19]{}\mathrel{=}\;\lambda\;\Conid{A}\;{}\<[26]%
+\>[26]{}\rightarrow\;\!\;\Conid{F}\;[\mskip1.5mu \Conid{A}{}\<[45]%
+\>[45]{},\;{}\<[53]%
+\>[53]{}\Conid{G}\;\Conid{A}{}\<[58]%
+\>[58]{}\mskip1.5mu]{}\<[E]%
 \\
@@
 \>[14]{}\Varid{mor}\;{}\<[19]%
-\>[19]{}\mathrel{=}\;{}\<[22]%
-\>[22]{}\lambda\;\Varid{f}\;{}\<[27]%
-\>[27]{}\rightarrow\;\!\;\Conid{F}\;[\mskip1.5mu \Varid{f}{}\<[46]%
-\>[46]{},\!\;{}\<[54]%
-\>[54]{}\Conid{G}\;\Varid{f}{}\<[59]%
-\>[59]{}\mskip1.5mu]\mskip1.5mu\}{}\<[E]%
-\ColumnHook
-\end{hscode}\resethooks
+\>[19]{}\mathrel{=}\;\lambda\;\Varid{f}\;{}\<[26]%
+\>[26]{}\rightarrow\;\!\;\Conid{F}\;[\mskip1.5mu \Varid{f}{}\<[45]%
+\>[45]{},\;{}\<[53]%
+\>[53]{}\Conid{G}\;\Varid{f}{}\<[58]%
+\>[58]{}\mskip1.5mu]\mskip1.5mu\}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\noindent
+This construction is functorial:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{10}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{12}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{16}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{19}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{21}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{28}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{37}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{42}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\anonymous [\mskip1.5mu \anonymous \mskip1.5mu]^{\text{\tiny F}}\;\in\;{}\<[10]%
+\>[10]{}\forall{}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\mskip1.5mu\}\;{}\<[19]%
+\>[19]{}(\Conid{F}\;\in\;\Conid{IFunc}\;(\Conid{I}\;\uplus\;\Conid{J}))\;\{\mskip1.5mu \Conid{G}\;\Conid{H}\;\in\;\Conid{IFunc}^{\star}\;\Conid{I}\;\Conid{J}\mskip1.5mu\}\;{}\<[E]%
+\\
+\>[10]{}\hsindent{2}{}\<[12]%
+\>[12]{}\rightarrow\;{}\<[21]%
+\>[21]{}\Conid{G}\;{}\<[28]%
+\>[28]{}\Rightarrow^{\text{\tiny F}^{\star}}\;{}\<[42]%
+\>[42]{}\Conid{H}\;{}\<[E]%
+\\
+\>[10]{}\hsindent{2}{}\<[12]%
+\>[12]{}\rightarrow\;{}\<[16]%
+\>[16]{}\Conid{F}\;[\mskip1.5mu \;{}\<[21]%
+\>[21]{}\Conid{G}\;\mskip1.5mu]^{\text{\tiny F}}\;{}\<[28]%
+\>[28]{}\Rightarrow^{\text{\tiny F}}\;{}\<[37]%
+\>[37]{}\Conid{F}\;[\mskip1.5mu \;{}\<[42]%
+\>[42]{}\Conid{H}\;\mskip1.5mu]^{\text{\tiny F}}{}\<[E]%
+\\
+\>[B]{}\Conid{F}\;[\mskip1.5mu \;\gamma\;\mskip1.5mu]^{\text{\tiny F}}\;\mathrel{=}\;\!\;\Conid{F}\;[\mskip1.5mu (\lambda\;\anonymous \;\Varid{a}\;\rightarrow\;\Varid{a}),\gamma\mskip1.5mu]{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\noindent
+Each of these definitions generalises to \ensuremath{\Conid{IFunc}^{\star}}:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{11}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{12}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{13}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{20}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{22}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{25}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{33}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{35}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{41}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{46}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{55}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\anonymous [\mskip1.5mu \anonymous \mskip1.5mu]^{\text{\tiny{F}}^{\star}}\;\in\;\forall{}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\Conid{K}\mskip1.5mu\}\;\rightarrow\;\Conid{IFunc}^{\star}\;(\Conid{I}\;\uplus\;\Conid{J})\;\Conid{K}\;\rightarrow\;\Conid{IFunc}^{\star}\;\Conid{I}\;\Conid{J}\;\rightarrow\;{}\<[55]%
+\>[55]{}\Conid{IFunc}^{\star}\;\Conid{I}\;\Conid{K}{}\<[E]%
+\\
+\>[B]{}\Conid{F}\;[\mskip1.5mu \;\Conid{G}\;\mskip1.5mu]^{\text{\tiny{F}}^{\star}}\;{}\<[12]%
+\>[12]{}\mathrel{=}\;\lambda\;\Varid{k}\;\rightarrow\;(\Conid{F}\;\Varid{k})\;[\mskip1.5mu \;\Conid{G}\;\mskip1.5mu]^{\text{\tiny F}}{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\anonymous [\mskip1.5mu \anonymous \mskip1.5mu]^{\text{\tiny{F}}^{\star}}\;\in\;{}\<[11]%
+\>[11]{}\forall{}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\Conid{K}\mskip1.5mu\}\;{}\<[22]%
+\>[22]{}(\Conid{F}\;\in\;\Conid{IFunc}^{\star}\;(\Conid{I}\;\uplus\;\Conid{J})\;\Conid{K})\;\{\mskip1.5mu \Conid{G}\;\Conid{H}\;\in\;\Conid{IFunc}^{\star}\;\Conid{I}\;\Conid{J}\mskip1.5mu\}\;{}\<[E]%
+\\
+\>[11]{}\hsindent{2}{}\<[13]%
+\>[13]{}\rightarrow\;{}\<[25]%
+\>[25]{}\Conid{G}\;{}\<[33]%
+\>[33]{}\Rightarrow^{\text{\tiny F}^{\star}}\;{}\<[46]%
+\>[46]{}\Conid{H}\;{}\<[E]%
+\\
+\>[11]{}\hsindent{2}{}\<[13]%
+\>[13]{}\rightarrow\;{}\<[20]%
+\>[20]{}\Conid{F}\;[\mskip1.5mu \;{}\<[25]%
+\>[25]{}\Conid{G}\;\mskip1.5mu]^{\text{\tiny{F}}^{\star}}\;{}\<[33]%
+\>[33]{}\Rightarrow^{\text{\tiny F}^{\star}}\;{}\<[41]%
+\>[41]{}\Conid{F}\;[\mskip1.5mu \;{}\<[46]%
+\>[46]{}\Conid{H}\;\mskip1.5mu]^{\text{\tiny{F}}^{\star}}{}\<[E]%
+\\
+\>[B]{}\anonymous [\mskip1.5mu \anonymous \mskip1.5mu]^{\text{\tiny{F}}^{\star}}\;\Conid{F}\;\{\mskip1.5mu \Conid{G}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{H}\mskip1.5mu\}\;\gamma\;\mathrel{=}\;\lambda\;\Varid{k}\;\rightarrow\;\anonymous [\mskip1.5mu \anonymous \mskip1.5mu]^{\text{\tiny F}}\;{}\<[35]%
+\>[35]{}(\Conid{F}\;\Varid{k})\;\{\mskip1.5mu \Conid{G}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{H}\mskip1.5mu\}\;\gamma{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\noindent
+A parametrized \ensuremath{\Conid{F}}-algebra for \ensuremath{\Conid{F}\;\in\;\Conid{IFunc}^{\star}\;(\Conid{I}\;\uplus\;\Conid{J})\;\Conid{I}} is a pair of an 
+indexed-functor \ensuremath{\Conid{G}\;\in\;\Conid{IFunc}\;\Conid{J}\;\Conid{I}} and a natural transformation
+\ensuremath{\alpha\;\in\;\Conid{F}\;[\mskip1.5mu \;\Conid{G}\;\mskip1.5mu]^{\text{\tiny{F}}^{\star}}\;\Rightarrow^{\text{\tiny F}^{\star}}\;\Conid{G}}. A morphism between two such algebras 
+\ensuremath{(\Conid{G},\alpha)} and \ensuremath{(\Conid{H},\beta)} is a natural transformation \ensuremath{\gamma\;\in\;\Conid{G}\;\Rightarrow^{\text{\tiny F}^{\star}}\;\Conid{H}} 
+such that the follow diagram commutes:
+
+\[
+\xymatrix{
+\mbox{\ensuremath{\Conid{F}\;[\mskip1.5mu \;\Conid{G}\;\mskip1.5mu]^{\text{\tiny{F}}^{\star}}}}  \ar[r]^{\quad\mbox{\ensuremath{\alpha}}} 
+\ar[d]_{\mbox{\ensuremath{\Conid{F}\;[\mskip1.5mu \;\gamma\;\mskip1.5mu]^{\text{\tiny{F}}^{\star}}}}} & \mbox{\ensuremath{\Conid{G}}} \ar[d]^{\mbox{\ensuremath{\gamma}}}\\
+\mbox{\ensuremath{\Conid{F}\;[\mskip1.5mu \;\Conid{H}\;\mskip1.5mu]^{\text{\tiny{F}}^{\star}}}} \ar[r]^{\quad\mbox{\ensuremath{\beta}}} & \mbox{\ensuremath{\Conid{H}}}}
+\]
+
+\noindent
+As you might expect, a parametrized initial algebra for \ensuremath{\Conid{F}}, if it is exists, 
+will be the initial object in the category of parametrized \ensuremath{\Conid{F}}-algebras.
+
+The fact that the parametrized initial algebra construction can be iterated, 
+means that we can define nested and mutual families of data-types, such as the
+triple of terms, types and contexts outlined in the introduction.
+
+As before we know that not all \ensuremath{\Conid{IFunc}^{\star}\;(\Conid{I}\;\uplus\;\Conid{J})\;\Conid{I}} functors have initial 
+algebras. In the next section, however we spell out what it is for a functor to 
+be given by an indexed container, and these functors are those which have such 
+initial algebras.
+
+%%Indexed Containers
 
@@
 
+An \ensuremath{\Conid{I}}-indexed container is given by a set of shapes, and an \ensuremath{\Conid{I}}-indexed \emph{family} of positions:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{5}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Keyword{record}\;\Conid{ICont}\;(\Conid{I}\;\in\;\Conid{Set})\;\in\;\Conid{Set₁}\;\Keyword{where}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Keyword{constructor}\;\_\mbox{$\lhd$}\_{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Keyword{field}{}\<[E]%
+\\
+\>[3]{}\hsindent{2}{}\<[5]%
+\>[5]{}\Conid{S}\;\in\;\Conid{Set}{}\<[E]%
+\\
+\>[3]{}\hsindent{2}{}\<[5]%
+\>[5]{}\Conid{P}\;\in\;\Conid{S}\;\rightarrow\;\Conid{I}\;\rightarrow\;\Conid{Set}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+The extension of such a container is an \ensuremath{\Conid{IFunc}\;\Conid{I}}:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{11}{@{}>{\hspre}c<{\hspost}@{}}%
+\column{11E}{@{}l@{}}%
+\column{14}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{19}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{26}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Varid{⟦\char95 ⟧}\;\in\;\forall{}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\rightarrow\;\Conid{ICont}\;\Conid{I}\;\rightarrow\;\Conid{IFunc}\;\Conid{I}{}\<[E]%
+\\
+\>[B]{}\Varid{⟦\char95 ⟧}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;(\Conid{S}\;\lhd\;\Conid{P})\;\mathrel{=}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Keyword{record}\;{}\<[11]%
+\>[11]{}\{\mskip1.5mu {}\<[11E]%
+\>[14]{}\Varid{obj}\;{}\<[19]%
+\>[19]{}\mathrel{=}\;\lambda\;\Conid{A}\;{}\<[26]%
+\>[26]{}\rightarrow\;\Sigma\;\Conid{S}\;(\lambda\;\Varid{s}\;\rightarrow\;(\Varid{i}\;\in\;\Conid{I})\;\rightarrow\;\Conid{P}\;\Varid{s}\;\Varid{i}\;\rightarrow\;\Conid{A}\;\Varid{i}){}\<[E]%
+\\
+\>[11]{};{}\<[11E]%
+\>[14]{}\Varid{mor}\;{}\<[19]%
+\>[19]{}\mathrel{=}\;\lambda\;\Varid{m}\;{}\<[26]%
+\>[26]{}\rightarrow\;\lambda (\!\;\Varid{s}\;\!,\!\;\Varid{f}\;\!\!)\;\rightarrow\;(\Varid{s},\Varid{m}\;\circ^{\star}\;\Varid{f})\;\!\;\!\mskip1.5mu\}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+As with \ensuremath{\Conid{IFunc}} we can extend this notion to doubly indexed containers, where
+an \ensuremath{\Conid{ICont}^{\star}\;\Conid{I}\;\Conid{J}} is a function from \ensuremath{\Conid{J}} to \ensuremath{\Conid{ICont}\;\Conid{I}}:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{5}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Keyword{record}\;\Conid{ICont}^{\star}\;(\Conid{I}\;\Conid{J}\;\in\;\Conid{Set})\;\in\;\Conid{Set₁}\;\Keyword{where}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Keyword{constructor}\;\anonymous \lhd^{\star}\anonymous {}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Keyword{field}{}\<[E]%
+\\
+\>[3]{}\hsindent{2}{}\<[5]%
+\>[5]{}\Conid{S}\;\in\;\Conid{J}\;\rightarrow\;\Conid{Set}{}\<[E]%
+\\
+\>[3]{}\hsindent{2}{}\<[5]%
+\>[5]{}\Conid{P}\;\in\;(\Varid{j}\;\in\;\Conid{J})\;\rightarrow\;\Conid{S}\;\Varid{j}\;\rightarrow\;\Conid{I}\;\rightarrow\;\Conid{Set}{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\Varid{⟦\char95 ⟧*}\;\in\;\forall{}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\mskip1.5mu\}\;\rightarrow\;\Conid{ICont}^{\star}\;\Conid{I}\;\Conid{J}\;\rightarrow\;\Conid{IFunc}^{\star}\;\Conid{I}\;\Conid{J}{}\<[E]%
+\\
+\>[B]{}\Varid{⟦}\;\Conid{S}\;\lhd^{\star}\;\Conid{P}\;\Varid{⟧}^{\star}\;\Varid{i}\;\mathrel{=}\;\Varid{⟦}\;\Conid{S}\;\Varid{i}\;\lhd\;\Conid{P}\;\Varid{i}\;\Varid{⟧}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+We will denote the two projections for an \ensuremath{\Conid{ICont}} postfix as \ensuremath{\anonymous \;\!.\Conid{S}} and
+\ensuremath{\anonymous \;\!.\Conid{P}}.
+
+\noindent
+We can establish what denotes a morphism between a container \ensuremath{\Conid{S}\;\lhd\;\Conid{P}\;\in\;\Conid{ICont}\;\Conid{I}}
+and functor \ensuremath{\Conid{F}\;\in\;\Conid{IFunc}\;\Conid{I}}, simply by expanding the definition and employing 
+the following derivation:
+
+\begin{align*}
+                & \ensuremath{\Varid{⟦}\;\Conid{S}\;\lhd\;\Conid{P}\;\Varid{⟧}\;\Rightarrow^{\text{\tiny F}}\;\Conid{F}} & \\
+  \equiv  \;    & \ensuremath{\prodd\;\Conid{X}\;.\;(\Sigma\;\Conid{S}\;\lambda\;\Varid{s}\;\rightarrow\;\Conid{P}\;\Varid{s}\;\rightarrow^{\star}\;\Conid{X})\;\rightarrow\;\Conid{F}\;\Conid{X}} & \{\mbox{by definition}\} \\
+  \equiv  \;    & \ensuremath{\prodd\;\Conid{X}\;.\;(\Varid{s}\;\in\;\Varid{s})\;\rightarrow\;(\Conid{P}\;\Varid{s}\;\rightarrow^{\star}\;\Conid{X})\;\rightarrow\;\Conid{F}\;\Conid{X}} & \{\mbox{currying}\} \\
+  \cong   \;    & \ensuremath{(\Varid{s}\;\in\;\Conid{S})\;\rightarrow\;\prodd\;\Conid{X}\;.\;(\Conid{P}\;\Varid{s}\;\rightarrow^{\star}\;\Conid{X})\;\rightarrow\;\Conid{F}\;\Conid{X}} & \{\mbox{commuting end and pi} \} \\
+  \cong   \;    & \ensuremath{(\Varid{s}\;\in\;\Conid{S})\;\rightarrow\;\Conid{F}\;(\Conid{P}\;\Varid{s})} & \{\mbox{Yoneda}\} \\
+\end{align*}
+
+\noindent
+If \ensuremath{\Conid{F}} is also an indexed container \ensuremath{\Conid{T}\;\lhd\;\Conid{Q}} then we have:
+
+\begin{align*}
+           & \ensuremath{\Varid{⟦}\;\Conid{S}\;\lhd\;\Conid{P}\;\Varid{⟧}\;\Rightarrow^{\text{\tiny F}}\;\Varid{⟦}\;\Conid{T}\;\lhd\;\Conid{Q}\;\Varid{⟧}} \\
+ \cong \;  & \ensuremath{(\Varid{s}\;\in\;\Conid{S})\;\rightarrow\;\Sigma\;\Conid{T}\;\lambda\;\Varid{t}\;\rightarrow\;\Conid{Q}\;\Varid{t}\;\rightarrow^{\star}\;\Conid{P}\;\Varid{s}} \\
+ \cong \;  & \ensuremath{\Sigma\;(\Conid{S}\;\rightarrow\;\Conid{T})\;\lambda\;\Varid{f}\;\rightarrow\;(\Varid{s}\;\in\;\Conid{S})\;\rightarrow\;\Conid{Q}\;(\Varid{f}\;\Varid{s})\;\rightarrow^{\star}\;\Conid{P}\;\Varid{s}}
+\end{align*}
+
+We will use this last line as the definition for container morphisms, captured by 
+this record type:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{5}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Keyword{record}\;\anonymous \Rightarrow^{\text{\tiny C}}\anonymous \;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;(\Conid{C}\;\Conid{D}\;\in\;\Conid{ICont}\;\Conid{I})\;\in\;\Conid{Set₁}\;\Keyword{where}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Keyword{constructor}\;\_\mbox{$\lhd$}\_{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Keyword{field}{}\<[E]%
+\\
+\>[3]{}\hsindent{2}{}\<[5]%
+\>[5]{}\Varid{f}\;\in\;\Conid{C}\;\!.\Conid{S}\;\rightarrow\;\Conid{D}\;\!.\Conid{S}{}\<[E]%
+\\
+\>[3]{}\hsindent{2}{}\<[5]%
+\>[5]{}\Varid{r}\;\in\;(\Varid{s}\;\in\;\Conid{C}\;\!.\Conid{S})\;\rightarrow\;(\Conid{D}\;\!.\Conid{P}\;\!\!\;(\Varid{f}\;\Varid{s}))\;\rightarrow^{\star}\;(\Conid{C}\;\!.\Conid{P}\;\!\!\;\Varid{s}){}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\noindent
+We witness one side of the isomorphism between container morphisms and natural 
+transformations:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{15}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{41}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{44}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Varid{⟦}\anonymous \Varid{⟧}\mbox{$\!^{\Rightarrow}$}\;\in\;\forall{}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;{}\<[15]%
+\>[15]{}\{\mskip1.5mu \Conid{C}\;\Conid{D}\;\in\;\Conid{ICont}\;\Conid{I}\mskip1.5mu\}\;(\Varid{m}\;\in\;\Conid{C}\;\Rightarrow^{\text{\tiny C}}\;\Conid{D})\;{}\<[44]%
+\>[44]{}\rightarrow\;{}\<[E]%
+\\
+\>[15]{}\prodd\;\Conid{A}\;.\;\!\;\Varid{⟦}\;\Conid{C}\;\Varid{⟧}\;\Conid{A}\;{}\<[41]%
+\>[41]{}\rightarrow\;\!\;\Varid{⟦}\;\Conid{D}\;\Varid{⟧}\;\Conid{A}{}\<[E]%
+\\
+\>[B]{}\Varid{⟦}\;\Varid{f}\;\lhd\;\Varid{r}\;\Varid{⟧}\mbox{$\!^{\Rightarrow}$}\;(\Varid{s},\Varid{g})\;\mathrel{=}\;\Varid{f}\;\Varid{s},\Varid{g}\;\circ^{\star}\;\Varid{r}\;\Varid{s}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\begin{proposition}
+
+The functor \ensuremath{(\Varid{⟦\char95 ⟧\char95 },\Varid{⟦\char95 ⟧⇒\char95 })} in \ensuremath{[\mskip1.5mu \Conid{ICont}\;\Conid{I},\Conid{IFunc}\;\Conid{I}\mskip1.5mu]} is full and faithful.
+
+\end{proposition}
+
+\begin{proof}
+
+By construction.
+
+%%\begin{code}
+%%
+%%q : {I : Set} (C D : ICont I) → ({A : I → Set}  → IFunc.obj ⟦  C ⟧ A  → IFunc.%%obj ⟦  D ⟧ A) 
+%%                                                →              C      ⇒       %%       D
+%%q C D m = (proj₁ ∘ eureka) ◁ (proj₂ ∘ eureka)
+%% where
+%%  eureka : (s : C projS) → IFunc.obj ⟦ D ⟧ (C projP $$ s)
+%%  eureka s =  m (s , idd)
+%%
+%%\end{code}
+%%
+%%By naturality this must be the unique inverse to the extesion of a container
+%%morphism given above.
+%%
+
+\end{proof}
+
+We can lift this functor to the doubly indexed variant:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{5}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{12}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{35}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Keyword{record}\;\anonymous \Rightarrow^{\text{\tiny C}^{\star}}\anonymous \;\{\mskip1.5mu \Conid{I}\;\Conid{J}\mskip1.5mu\}\;(\Conid{C}\;\Conid{D}\;\in\;\Conid{ICont}^{\star}\;\Conid{I}\;\Conid{J})\;\in\;\Conid{Set₁}\;\Keyword{where}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Keyword{constructor}\;\anonymous \lhd^{\star}\anonymous {}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Keyword{field}{}\<[E]%
+\\
+\>[3]{}\hsindent{2}{}\<[5]%
+\>[5]{}\Varid{f}\;\in\;\Conid{C}\;\!.\Conid{S}\;\rightarrow^{\star}\;\Conid{D}\;\!.\Conid{S}{}\<[E]%
+\\
+\>[3]{}\hsindent{2}{}\<[5]%
+\>[5]{}\Varid{r}\;\in\;\{\mskip1.5mu \Varid{j}\;\in\;\Conid{J}\mskip1.5mu\}\;(\Varid{s}\;\in\;\Conid{C}\;\!.\Conid{S}\;\!\!\;\Varid{j})\;\rightarrow\;(\Conid{D}\;\!.\Conid{P}\;\!\!\;\Varid{j}\;\!\!\;(\Varid{f}\;\Varid{j}\;\Varid{s}))\;\rightarrow^{\star}\;(\Conid{C}\;\!.\Conid{P}\;\!\!\;\Varid{j}\;\!\!\;\Varid{s}){}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\Varid{⟦\char95 ⟧⇒*}\;\in\;\forall{}\;{}\<[12]%
+\>[12]{}\{\mskip1.5mu \Conid{I}\;\Conid{J}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{C}\;\Conid{D}\;\in\;\Conid{ICont}^{\star}\;\Conid{I}\;\Conid{J}\mskip1.5mu\}\;(\Varid{m}\;\in\;\Conid{C}\;\Rightarrow^{\text{\tiny C}^{\star}}\;\Conid{D})\;\rightarrow\;{}\<[E]%
+\\
+\>[12]{}\prodd\;\Conid{A}\;.\;(\;\Varid{⟦}\;\Conid{C}\;\Varid{⟧}^{\star}\;\Conid{A}\;{}\<[35]%
+\>[35]{}\rightarrow^{\star}\;\;\Varid{⟦}\;\Conid{D}\;\Varid{⟧}^{\star}\;\Conid{A}){}\<[E]%
+\\
+\>[B]{}\Varid{⟦}\;\Varid{f}\;\lhd^{\star}\;\Varid{r}\;\Varid{⟧}\mbox{$\!^{\Rightarrow^{\!\star}}$}\;\Varid{j}\;\mathrel{=}\;\Varid{⟦}\;(\Varid{f}\;\Varid{j})\;\lhd\;\Varid{r}\;\Varid{⟧}\mbox{$\!^{\Rightarrow}$}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+As with \ensuremath{\Conid{IFunc}}, we can equip \ensuremath{\Conid{ICont}} with a relative monadic structure:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{6}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{34}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\eta^{\text{\tiny C}}\;\in\;\forall{}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\rightarrow\;\Conid{I}\;\rightarrow\;\Conid{ICont}\;\Conid{I}{}\<[E]%
+\\
+\>[B]{}\eta^{\text{\tiny C}}\;\Varid{i}\;\mathrel{=}\;\top\;\lhd\;\lambda\;\anonymous \;\Varid{i′}\;\rightarrow\;\Varid{i}\;\equiv\;\Varid{i′}{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\anonymous \bind ^{\text{\tiny C}}\anonymous \;\in\;\forall{}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\mskip1.5mu\}\;\rightarrow\;\Conid{ICont}\;\Conid{I}\;\rightarrow\;\Conid{ICont}^{\star}\;\Conid{J}\;\Conid{I}\;\rightarrow\;\Conid{ICont}\;\Conid{J}{}\<[E]%
+\\
+\>[B]{}\anonymous \bind ^{\text{\tiny C}}\anonymous \;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;(\Conid{S}\;\lhd\;\Conid{P})\;(\Conid{T}\;\lhd^{\star}\;\Conid{Q})\;\mathrel{=}\;{}\<[E]%
+\\
+\>[B]{}\hsindent{6}{}\<[6]%
+\>[6]{}(\!\;\Varid{⟦}\;\Conid{S}\;\lhd\;\Conid{P}\;\Varid{⟧}\;\Conid{T})\;{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\lhd\;{}\<[6]%
+\>[6]{}\lambda (\!\;\Varid{s}\;\!,\!\;\Varid{f}\;\!\!)\;\Varid{j}\;\!\;\rightarrow\;\Sigma\;{}\<[34]%
+\>[34]{}(\Sigma\;\Conid{I}\;(\Conid{P}\;\Varid{s}))\;(\lambda (\!\;\Varid{i}\;\!,\!\;\Varid{p}\;\!\!)\;\rightarrow\;\Conid{Q}\;\Varid{i}\;(\Varid{f}\;\Varid{i}\;\Varid{p})\;\Varid{j}\;\!\;\!)\;\!\;\!{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\begin{proposition}
+
+The triple \ensuremath{(\Conid{ICont},\eta^{\text{\tiny C}},\anonymous \bind ^{\text{\tiny C}}\anonymous )} is a relative monad.
+
+\end{proposition}
+
+\begin{proof}
+
+Instead of proving this directly, we observe that the \ensuremath{\eta^{\text{\tiny C}}} and \ensuremath{\anonymous \bind ^{\text{\tiny C}}\anonymous }
+are preserved under \ensuremath{\Varid{⟦\char95 ⟧\char95 }}, i.e.:
+
+\begin{align*}
+\ensuremath{\Varid{⟦}\;\eta^{\text{\tiny C}}\;\Varid{i}\;\Varid{⟧}} && \approx &&& \ensuremath{\eta^{\text{\tiny F}}\;\Varid{i}} \\
+\ensuremath{\Varid{⟦}\;\Conid{C}\;\bind ^{\text{\tiny C}}\;\Conid{D}\;\Varid{⟧}} && \approx &&& \ensuremath{\Varid{⟦}\;\Conid{C}\;\Varid{⟧}^{\star}\;\bind ^{\text{\tiny F}}\;\Varid{⟦}\;\Conid{D}\;\Varid{⟧}} \\
+\end{align*}
+
+Which follow from the extensionality of our propositional equality, the 
+assosciativity of \ensuremath{\Sigma} and the terminality of \ensuremath{\top}. By the full and faithful 
+nature of the embedding into \ensuremath{\Conid{IFunc}} we can then reuse the result that
+\ensuremath{(\Conid{IFunc},\eta^{\text{\tiny F}},\anonymous \bind ^{\text{\tiny F}}\anonymous )} is a relative monad.
+
+\end{proof}
+
+As with indexed functors, the re-indexing \ensuremath{\Delta^{\text{\tiny C}}} is defined by composition, and 
+has left and right adjoints \ensuremath{\Sigma^{\text{\tiny C}}} and \ensuremath{\Pi^{\text{\tiny C}}}:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{5}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{8}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{21}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[3]{}\Delta^{\text{\tiny C}}\;\in\;(\Conid{J}\;\rightarrow\;\Conid{K})\;\rightarrow\;\Conid{ICont}^{\star}\;\Conid{I}\;\Conid{K}\;\rightarrow\;\Conid{ICont}^{\star}\;\Conid{I}\;\Conid{J}{}\<[E]%
+\\
+\>[3]{}\Delta^{\text{\tiny C}}\;\Varid{f}\;\Conid{F}\;\mathrel{=}\;\!\!\;\lambda\;\Varid{k}\;\rightarrow\;\Conid{F}\;\!\!\;(\Varid{f}\;\Varid{k}){}\<[E]%
+\\[\blanklineskip]%
+\>[3]{}\Sigma^{\text{\tiny C}}\;\in\;(\Conid{J}\;\rightarrow\;\Conid{K})\;\rightarrow\;\Conid{ICont}^{\star}\;\Conid{I}\;\Conid{J}\;\rightarrow\;\Conid{ICont}^{\star}\;\Conid{I}\;\Conid{K}{}\<[E]%
+\\
+\>[3]{}\Sigma^{\text{\tiny C}}\;\Varid{f}\;(\Conid{S}\;\lhd^{\star}\;\Conid{P})\;\mathrel{=}\;\!\!\;\lambda\;\Varid{k}\;\rightarrow\;{}\<[E]%
+\\
+\>[3]{}\hsindent{5}{}\<[8]%
+\>[8]{}(\Sigma\;\Conid{J}\;\lambda\;\Varid{j}\;\rightarrow\;\Varid{f}\;\Varid{j}\;\equiv\;\Varid{k}\;\times\;\Conid{S}\;\Varid{j})\;{}\<[E]%
+\\
+\>[3]{}\hsindent{2}{}\<[5]%
+\>[5]{}\lhd\;{}\<[8]%
+\>[8]{}\lambda (\!\;\Varid{j}\;\!,\!\;\Varid{eq}\;\!,\!\;\Varid{s}\;\!\!)\;\rightarrow\;\Conid{P}\;\Varid{j}\;\Varid{s}\;\!\;\!{}\<[E]%
+\\[\blanklineskip]%
+\>[3]{}\Pi^{\text{\tiny C}}\;\in\;(\Conid{J}\;\rightarrow\;\Conid{K})\;\rightarrow\;\Conid{ICont}^{\star}\;\Conid{I}\;\Conid{J}\;\rightarrow\;\Conid{ICont}^{\star}\;\Conid{I}\;\Conid{K}{}\<[E]%
+\\
+\>[3]{}\Pi^{\text{\tiny C}}\;\Varid{f}\;(\Conid{S}\;\lhd^{\star}\;\Conid{P})\;\mathrel{=}\;{}\<[21]%
+\>[21]{}\!\!\;\lambda\;\Varid{k}\;\rightarrow\;{}\<[E]%
+\\
+\>[3]{}\hsindent{5}{}\<[8]%
+\>[8]{}((\Varid{j}\;\in\;\Conid{J})\;\rightarrow\;\Varid{f}\;\Varid{j}\;\equiv\;\Varid{k}\;\rightarrow\;\Conid{S}\;\Varid{j})\;{}\<[E]%
+\\
+\>[3]{}\hsindent{2}{}\<[5]%
+\>[5]{}\lhd\;{}\<[8]%
+\>[8]{}\lambda\;\Varid{s}\;\Varid{i}\;\rightarrow\;\Sigma\;\Conid{J}\;\lambda\;\Varid{j}\;\rightarrow\;\Sigma\;(\Varid{f}\;\Varid{j}\;\equiv\;\Varid{k})\;\lambda\;\Varid{eq}\;\rightarrow\;\Conid{P}\;\Varid{j}\;(\Varid{s}\;\Varid{j}\;\Varid{eq})\;\Varid{i}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\begin{proposition}
+\ensuremath{\Sigma^{\text{\tiny C}}} and \ensuremath{\Pi^{\text{\tiny C}}} are left and right adjoint to re-indexing (\ensuremath{\Delta^{\text{\tiny C}}}).
+\end{proposition}
+
+\begin{proof}
+
+Again we appeal to the full and faithfullness of \ensuremath{\Varid{⟦\char95 ⟧\char95 }} and show instead that
+the embedding into \ensuremath{\Conid{IFunc}} preserves these constructions. That, is we want to show that the following three statements hold:
+
+\begin{align*}
+\ensuremath{\Varid{⟦}\;\Sigma^{\text{\tiny C}}\;\Varid{f}\;\Conid{F}\;\Varid{j}\;\Varid{⟧}} && \approx &&& \ensuremath{\Sigma^{\text{\tiny F}}\;\Varid{f}\;\Varid{⟦}\;\Conid{F}\;\Varid{⟧}^{\star}\;\Varid{j}} \\
+\ensuremath{\Varid{⟦}\;\Delta^{\text{\tiny C}}\;\Varid{f}\;\Conid{F}\;\Varid{j}\;\Varid{⟧}} && \equiv &&& \ensuremath{\Delta^{\text{\tiny F}}\;\Varid{f}\;\Varid{⟦}\;\Conid{F}\;\Varid{⟧}^{\star}\;\Varid{j}} \\
+\ensuremath{\Varid{⟦}\;\Pi^{\text{\tiny C}}\;\Varid{f}\;\Conid{F}\;\Varid{j}\;\Varid{⟧}} && \approx &&& \ensuremath{\Pi^{\text{\tiny F}}\;\Varid{f}\;\Varid{⟦}\;\Conid{F}\;\Varid{⟧}^{\star}\;\Varid{j}} \\
+\end{align*}
+
+These can be proved simply by employing the associativity of \ensuremath{\Sigma}.
+
+\end{proof}
+
+Before we build the initial algebras of indexed containers, it will help to 
+define their partial application.
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{8}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{12}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{17}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{22}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{34}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{37}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{39}{@{}>{\hspre}c<{\hspost}@{}}%
+\column{39E}{@{}l@{}}%
+\column{42}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{46}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{49}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{52}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\anonymous [\mskip1.5mu \anonymous \mskip1.5mu]^{\text{\tiny C}}\;\in\;\forall{}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\mskip1.5mu\}\;\rightarrow\;\Conid{ICont}\;(\Conid{I}\;\uplus\;\Conid{J})\;\rightarrow\;\Conid{ICont}^{\star}\;\Conid{I}\;\Conid{J}\;\rightarrow\;\Conid{ICont}\;\Conid{I}{}\<[E]%
+\\
+\>[B]{}\anonymous [\mskip1.5mu \anonymous \mskip1.5mu]^{\text{\tiny C}}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{J}\mskip1.5mu\}\;(\Conid{S}\;\lhd\;\Conid{P})\;(\Conid{T}\;\lhd^{\star}\;\Conid{Q})\;\mathrel{=}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Keyword{let}\;{}\<[8]%
+\>[8]{}\Conid{P}^{\Conid{I}}\;{}\<[12]%
+\>[12]{}\in\;\Conid{S}\;{}\<[17]%
+\>[17]{}\rightarrow\;\Conid{I}\;{}\<[22]%
+\>[22]{}\rightarrow\;\Conid{Set}{}\<[39]%
+\>[39]{};{}\<[39E]%
+\>[42]{}\Conid{P}^{\Conid{I}}\;{}\<[46]%
+\>[46]{}\Varid{s}\;{}\<[49]%
+\>[49]{}\Varid{i}\;{}\<[52]%
+\>[52]{}\mathrel{=}\;\Conid{P}\;\Varid{s}\;(\Varid{inl}\;\Varid{i}){}\<[E]%
+\\
+\>[8]{}\Conid{P}^{\Conid{J}}\;{}\<[12]%
+\>[12]{}\in\;\Conid{S}\;{}\<[17]%
+\>[17]{}\rightarrow\;\Conid{J}\;{}\<[22]%
+\>[22]{}\rightarrow\;\Conid{Set}{}\<[39]%
+\>[39]{};{}\<[39E]%
+\>[42]{}\Conid{P}^{\Conid{J}}\;{}\<[46]%
+\>[46]{}\Varid{s}\;{}\<[49]%
+\>[49]{}\Varid{j}\;{}\<[52]%
+\>[52]{}\mathrel{=}\;\Conid{P}\;\Varid{s}\;(\Varid{inr}\;\Varid{j}){}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Keyword{in}\;{}\<[8]%
+\>[8]{}\!\;\Varid{⟦}\;\Conid{S}\;\lhd\;\Conid{P}^{\Conid{J}}\;\Varid{⟧}\;\Conid{T}\;\lhd\;{}\<[37]%
+\>[37]{}(\lambda (\!\;\Varid{s}\;\!,\!\;\Varid{f}\;\!\!)\;\Varid{i}\;\!\;\rightarrow\;\Conid{P}^{\Conid{I}}\;\Varid{s}\;\Varid{i}{}\<[E]%
+\\
+\>[8]{}\hsindent{26}{}\<[34]%
+\>[34]{}\uplus\;{}\<[37]%
+\>[37]{}(\Sigma\;\Conid{J}\;\lambda\;\Varid{j}\;\rightarrow\;\Sigma\;(\Conid{P}^{\Conid{J}}\;\Varid{s}\;\Varid{j})\;\lambda\;\Varid{p}\;\rightarrow\;\Conid{Q}\;\Varid{j}\;(\Varid{f}\;\Varid{j}\;\Varid{p})\;\Varid{i})\;\!\;\!){}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\noindent
+The composite container has shapes given by a shape \ensuremath{\Varid{s}\;\in\;\Conid{S}} and an assigment of \ensuremath{\Conid{T}} 
+shapes to \ensuremath{\Conid{P}^{\Conid{J}}\;\Varid{s}} positions. Positions are then a choice between 
+a \ensuremath{\Conid{I}}-indexed position, or a pair of an \ensuremath{\Conid{J}}-indexed position, and a \ensuremath{\Conid{Q}} position
+\emph{underneath} the appropriate \ensuremath{\Conid{T}} shape.
+
+\noindent
+As with indexed functors, this construction is functorial in its second 
+argument, and lifts container morphisms in this way:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}c<{\hspost}@{}}%
+\column{3E}{@{}l@{}}%
+\column{6}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{11}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{14}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{21}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{28}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{33}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{38}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\anonymous [\mskip1.5mu \anonymous \mskip1.5mu]^{\text{\tiny C}}\;\in\;{}\<[11]%
+\>[11]{}\forall{}\;{}\<[14]%
+\>[14]{}\{\mskip1.5mu \Conid{I}\;\Conid{J}\mskip1.5mu\}\;(\Conid{C}\;\in\;\Conid{ICont}\;(\Conid{I}\;\uplus\;\Conid{J}))\;\{\mskip1.5mu \Conid{D}\;\Conid{E}\;\in\;\Conid{ICont}^{\star}\;\Conid{I}\;\Conid{J}\mskip1.5mu\}\;\rightarrow\;{}\<[E]%
+\\
+\>[14]{}\hsindent{7}{}\<[21]%
+\>[21]{}\Conid{D}\;{}\<[28]%
+\>[28]{}\Rightarrow^{\text{\tiny C}^{\star}}\;{}\<[38]%
+\>[38]{}\Conid{E}\;{}\<[E]%
+\\
+\>[14]{}\rightarrow\;\Conid{C}\;[\mskip1.5mu \;{}\<[21]%
+\>[21]{}\Conid{D}\;\mskip1.5mu]^{\text{\tiny C}}\;{}\<[28]%
+\>[28]{}\Rightarrow^{\text{\tiny C}}\;{}\<[33]%
+\>[33]{}\Conid{C}\;[\mskip1.5mu \;{}\<[38]%
+\>[38]{}\Conid{E}\;\mskip1.5mu]^{\text{\tiny C}}{}\<[E]%
+\\
+\>[B]{}\Conid{C}\;[\mskip1.5mu \;\gamma\;\mskip1.5mu]^{\text{\tiny C}}\;\mathrel{=}\;{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}({}\<[3E]%
+\>[6]{}\lambda (\!\;\Varid{s}\;\!,\!\;\Varid{f}\;\!\!)\;\rightarrow\;(\Varid{s},\lambda\;\Varid{j}\;\Varid{p}\;\rightarrow\;\gamma\;\!.\Varid{f}\;\!\!\;\Varid{j}\;\!\!\;(\Varid{f}\;\Varid{j}\;\Varid{p}))\;\!\;\!)\;\lhd\;{}\<[E]%
+\\
+\>[6]{}\lambda (\!\;\Varid{s}\;\!,\!\;\Varid{f}\;\!\!)\;\Varid{i}\;\!\;\rightarrow\;[\mskip1.5mu \Varid{inl},(\lambda (\!\;\Varid{j}\;\!,\!\;\Varid{p}\;\!,\!\;\Varid{q}\;\!\!)\;\rightarrow\;\Varid{inr}\;(\Varid{j},\Varid{p},\gamma\;\!.\Varid{r}\;\!\!\;\Varid{j}\;\!\!\;(\Varid{f}\;\Varid{j}\;\Varid{p})\;\!\!\;\Varid{i}\;\!\!\;\Varid{q})\;\!\;\!)\mskip1.5mu]\;\!\;\!{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+%%Init Alg ICont
+
 \section{Initial Algebras of Indexed Containers}
 
-\section{Strictly Positive Types}
+We will now examine how to construct the initial algebra of a container of the form \ensuremath{\Conid{F}\;\in\;\Conid{ICont}^{\star}\;(\Conid{I}\;\uplus\;\Conid{J})\;\Conid{J}}.
+The shapes of such a container are an \ensuremath{\Conid{J}}-indexed family of \ensuremath{\Conid{Set}}s and the positions are in \ensuremath{(\Varid{j}\;\in\;\Conid{J})\;\rightarrow\;\Conid{S}\;\Varid{j}\;\rightarrow\;\Conid{I}\;\uplus\;\Conid{J}\;\rightarrow\;\Conid{Set}}; we will treat these position as two separate entities, those positions indexed by \ensuremath{\Conid{I}} (\ensuremath{\Conid{P}^{\Conid{I}}\;\in\;(\Varid{j}\;\in\;\Conid{J})\;\rightarrow\;\Conid{S}\;\Varid{j}\;\rightarrow\;\Conid{I}\;\rightarrow\;\Conid{Set}}) -- the recusive positions -- and those by \ensuremath{\Conid{J}}
+(\ensuremath{\Conid{P}^{\Conid{J}}\;\in\;(\Varid{j}\;\in\;\Conid{J})\;\rightarrow\;\Conid{S}\;\Varid{i}\;\rightarrow\;\Conid{J}\;\rightarrow\;\Conid{Set}}) -- the payload positions.
+
+The shapes of initial algebra we are constructing will be trees with S shapes at the nodes and which branch over the recursive \ensuremath{\Conid{P}^{\Conid{I}}} positions.
+We call these trees \emph{indexed} \ensuremath{\Conid{W}}-types, denoted \ensuremath{\Conid{WI}} and they are the initial algebra of the functor \ensuremath{\Varid{⟦}\;\Conid{S}\;\lhd\;\Conid{P}^{\Conid{J}}\;\Varid{⟧}^{\star}}:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{10}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{11}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{14}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{18}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{38}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Keyword{data}\;\Conid{WI}\;{}\<[10]%
+\>[10]{}\{\mskip1.5mu \Conid{J}\;\in\;\Conid{Set}\mskip1.5mu\}\;(\Conid{S}\;\in\;\Conid{J}\;\rightarrow\;\Conid{Set})\;{}\<[E]%
+\\
+\>[10]{}(\Conid{P}^{\Conid{J}}\;\in\;(\Varid{j}\;\in\;\Conid{J})\;\rightarrow\;\Conid{S}\;\Varid{j}\;\rightarrow\;\Conid{J}\;\rightarrow\;\Conid{Set})\;\in\;\Conid{J}\;\rightarrow\;\Conid{Set}\;\Keyword{where}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{sup}\;\in\;\;\Varid{⟦}\;\Conid{S}\;\lhd^{\star}\;\Conid{P}^{\Conid{J}}\;\Varid{⟧}^{\star}\;(\Conid{WI}\;\Conid{S}\;\Conid{P}^{\Conid{J}})\;{}\<[38]%
+\>[38]{}\rightarrow^{\star}\;\Conid{WI}\;\Conid{S}\;\Conid{P}^{\Conid{J}}{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\Conid{WIfold}\;\in\;{}\<[11]%
+\>[11]{}\forall{}\;{}\<[14]%
+\>[14]{}\{\mskip1.5mu \Conid{J}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{X}\;\in\;\Conid{J}\;\rightarrow\;\Conid{Set}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{S}\;\in\;\Conid{J}\;\rightarrow\;\Conid{Set}\mskip1.5mu\}\;{}\<[E]%
+\\
+\>[14]{}\{\mskip1.5mu \Conid{P}^{\Conid{J}}\;\in\;(\Varid{j}\;\in\;\Conid{J})\;\rightarrow\;\Conid{S}\;\Varid{j}\;\rightarrow\;\Conid{J}\;\rightarrow\;\Conid{Set}\mskip1.5mu\}\;\rightarrow\;\;{}\<[E]%
+\\
+\>[14]{}\hsindent{4}{}\<[18]%
+\>[18]{}\Varid{⟦}\;\Conid{S}\;\lhd^{\star}\;\Conid{P}^{\Conid{J}}\;\Varid{⟧}^{\star}\;\Conid{X}\;\rightarrow^{\star}\;\Conid{X}\;\rightarrow\;\Conid{WI}\;\Conid{S}\;\Conid{P}^{\Conid{J}}\;\rightarrow^{\star}\;\Conid{X}{}\<[E]%
+\\
+\>[B]{}\Conid{WIfold}\;\Varid{f}\;\Varid{j}\;(\Varid{sup}\;(\Varid{s},\Varid{g}))\;\mathrel{=}\;\Varid{f}\;\Varid{j}\;(\Varid{s},\lambda\;\Varid{j′}\;\Varid{p}\;\rightarrow\;\Conid{WIfold}\;\Varid{f}\;\Varid{j′}\;(\Varid{g}\;\Varid{j′}\;\Varid{p})){}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\noindent
+This mirrors the construction for plain containers, where we can view ordinary \ensuremath{\Conid{W}} types as the initial algebra of a container functor.
+
+Positions are given by paths through such a tree, terminated by a non-recursive \ensuremath{\Conid{P}^{\Conid{I}}}:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{12}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{13}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{16}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{17}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{38}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Keyword{data}\;\Conid{Path}\;{}\<[12]%
+\>[12]{}\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\in\;\Conid{Set}\mskip1.5mu\}\;(\Conid{S}\;\in\;\Conid{J}\;\rightarrow\;\Conid{Set})\;{}\<[E]%
+\\
+\>[12]{}(\Conid{P}^{\Conid{I}}\;{}\<[17]%
+\>[17]{}\in\;(\Varid{j}\;\in\;\Conid{J})\;\rightarrow\;\Conid{S}\;\Varid{j}\;\rightarrow\;\Conid{I}\;{}\<[38]%
+\>[38]{}\rightarrow\;\Conid{Set})\;{}\<[E]%
+\\
+\>[12]{}(\Conid{P}^{\Conid{J}}\;{}\<[17]%
+\>[17]{}\in\;(\Varid{j}\;\in\;\Conid{J})\;\rightarrow\;\Conid{S}\;\Varid{j}\;\rightarrow\;\Conid{J}\;{}\<[38]%
+\>[38]{}\rightarrow\;\Conid{Set})\;{}\<[E]%
+\\
+\>[12]{}\in\;(\Varid{j}\;\in\;\Conid{J})\;\rightarrow\;\Conid{WI}\;\Conid{S}\;\Conid{P}^{\Conid{J}}\;\Varid{j}\;\rightarrow\;\Conid{I}\;\rightarrow\;\Conid{Set}\;\Keyword{where}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{path}\;\in\;\forall{}\;{}\<[13]%
+\>[13]{}\{\mskip1.5mu \Varid{j}\;\Varid{s}\;\Varid{f}\;\Varid{i}\mskip1.5mu\}\;\rightarrow\;{}\<[E]%
+\\
+\>[13]{}\hsindent{3}{}\<[16]%
+\>[16]{}\Conid{P}^{\Conid{I}}\;\Varid{j}\;\Varid{s}\;\Varid{i}\;{}\<[E]%
+\\
+\>[13]{}\uplus\;{}\<[16]%
+\>[16]{}(\Sigma\;\Conid{J}\;\lambda\;\Varid{j′}\;\rightarrow\;\Sigma\;(\Conid{P}^{\Conid{J}}\;\Varid{j}\;\Varid{s}\;\Varid{j′})\;\lambda\;\Varid{p}\;\rightarrow\;\Conid{Path}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\;\Conid{P}^{\Conid{J}}\;\Varid{j′}\;(\Varid{f}\;\Varid{j′}\;\Varid{p})\;\Varid{i})\;{}\<[E]%
+\\
+\>[13]{}\rightarrow\;\Conid{Path}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\;\Conid{P}^{\Conid{J}}\;\Varid{j}\;(\Varid{sup}\;(\Varid{s},\Varid{f}))\;\Varid{i}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\noindent
+Again this mirrors the partial application construction where positions were 
+given by a \ensuremath{\Conid{P}^{\Conid{J}}} position at the top level, or a pair of a \ensuremath{\Conid{P}^{\Conid{J}}} position and a 
+sub \ensuremath{\Conid{Q}} position. Here the \ensuremath{\Conid{Q}} positions are recursive \ensuremath{\Conid{Path}} positions.
+
+\noindent
+We can now give the object part of the patrametrized initial algebra of a container, given by:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{8}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{12}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{33}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{42}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{46}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{54}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\mu^{\text{\tiny C}}\;\in\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\in\;\Conid{Set}\mskip1.5mu\}\;\rightarrow\;\Conid{ICont}^{\star}\;(\Conid{I}\;\uplus\;\Conid{J})\;\Conid{J}\;\rightarrow\;\Conid{ICont}^{\star}\;\Conid{I}\;\Conid{J}{}\<[E]%
+\\
+\>[B]{}\mu^{\text{\tiny C}}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{J}\mskip1.5mu\}\;(\Conid{S}\;\lhd^{\star}\;\Conid{P})\;\mathrel{=}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Keyword{let}\;{}\<[8]%
+\>[8]{}\Conid{P}^{\Conid{I}}\;{}\<[12]%
+\>[12]{}\in\;(\Varid{j}\;\in\;\Conid{J})\;\rightarrow\;\Conid{S}\;\Varid{j}\;\rightarrow\;\Conid{I}\;{}\<[33]%
+\>[33]{}\rightarrow\;\Conid{Set};{}\<[42]%
+\>[42]{}\Conid{P}^{\Conid{I}}\;{}\<[46]%
+\>[46]{}\Varid{j}\;\Varid{s}\;\Varid{i}\;{}\<[54]%
+\>[54]{}\mathrel{=}\;\Conid{P}\;\!\!\;\Varid{j}\;\!\!\;\Varid{s}\;\!\!\;(\Varid{inl}\;\Varid{i}){}\<[E]%
+\\
+\>[8]{}\Conid{P}^{\Conid{J}}\;{}\<[12]%
+\>[12]{}\in\;(\Varid{j}\;\in\;\Conid{J})\;\rightarrow\;\Conid{S}\;\Varid{j}\;\rightarrow\;\Conid{J}\;{}\<[33]%
+\>[33]{}\rightarrow\;\Conid{Set};{}\<[42]%
+\>[42]{}\Conid{P}^{\Conid{J}}\;{}\<[46]%
+\>[46]{}\Varid{j}\;\Varid{s}\;\Varid{j′}\;{}\<[54]%
+\>[54]{}\mathrel{=}\;\Conid{P}\;\!\!\;\Varid{j}\;\!\!\;\Varid{s}\;\!\!\;(\Varid{inr}\;\Varid{j′}){}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Keyword{in}\;{}\<[8]%
+\>[8]{}\Conid{WI}\;\Conid{S}\;\Conid{P}^{\Conid{J}}\;\lhd^{\star}\;\Conid{Path}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\;\Conid{P}^{\Conid{J}}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\noindent
+The algebra map is a container morphism from the partial aplication of \ensuremath{\Conid{F}} and its parametrised initial algebra, to the initial algebra, given by the algebra map of \ensuremath{\Conid{WI}} (\ensuremath{\Varid{sup}}) and our mediation funtion \ensuremath{\Varid{path}}:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Varid{in}^{\text{\tiny C}}\;\in\;\forall{}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\mskip1.5mu\}\;\rightarrow\;(\Conid{F}\;\in\;\Conid{ICont}^{\star}\;(\Conid{I}\;\uplus\;\Conid{J})\;\Conid{J})\;\rightarrow\;\Conid{F}\;[\mskip1.5mu \;\mu^{\text{\tiny C}}\;\Conid{F}\;\mskip1.5mu]^{\text{\tiny{C}}^{\star}}\;\Rightarrow^{\text{\tiny C}^{\star}}\;\mu^{\text{\tiny C}}\;\Conid{F}{}\<[E]%
+\\
+\>[B]{}\Varid{in}^{\text{\tiny C}}\;\Conid{F}\;\mathrel{=}\;(\lambda\;\anonymous \;\rightarrow\;\Varid{sup})\;\lhd^{\star}\;\lambda\;\anonymous \;\anonymous \;\Varid{p}\;\rightarrow\;\Varid{path}\Varid{⁻¹}\;\Varid{p}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{5}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{12}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{13}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{16}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{19}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{21}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{37}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{38}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{47}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{51}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{59}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{60}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Varid{fold}^{\text{\tiny C}}\;\in\;\forall{}\;{}\<[13]%
+\>[13]{}\{\mskip1.5mu \Conid{I}\;\Conid{J}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{F}\;\in\;\Conid{ICont}^{\star}\;(\Conid{I}\;\uplus\;\Conid{J})\;\Conid{J}\mskip1.5mu\}\;(\Conid{G}\;\in\;\Conid{ICont}^{\star}\;\Conid{I}\;\Conid{J})\;\rightarrow\;{}\<[E]%
+\\
+\>[13]{}\Conid{F}\;[\mskip1.5mu \;\Conid{G}\;\mskip1.5mu]^{\text{\tiny{C}}^{\star}}\;\Rightarrow^{\text{\tiny C}^{\star}}\;\Conid{G}\;\rightarrow\;\mu^{\text{\tiny C}}\;\Conid{F}\;\Rightarrow^{\text{\tiny C}^{\star}}\;\Conid{G}{}\<[E]%
+\\
+\>[B]{}\Varid{fold}^{\text{\tiny C}}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{J}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{S}\;\lhd^{\star}\;\Conid{P}\mskip1.5mu\}\;(\Conid{T}\;\lhd^{\star}\;\Conid{Q})\;(\Varid{f}\;\lhd^{\star}\;\Varid{r})\;\mathrel{=}\;\Varid{ffold}\;\lhd^{\star}\;\Varid{rfold}{}\<[E]%
+\\
+\>[B]{}\hsindent{5}{}\<[5]%
+\>[5]{}\Keyword{where}\;{}\<[12]%
+\>[12]{}\Conid{P}^{\Conid{I}}\;{}\<[16]%
+\>[16]{}\in\;{}\<[19]%
+\>[19]{}(\Varid{j}\;\in\;\Conid{J})\;\rightarrow\;\Conid{S}\;\Varid{j}\;\rightarrow\;\Conid{I}\;{}\<[38]%
+\>[38]{}\rightarrow\;\Conid{Set};{}\<[47]%
+\>[47]{}\Conid{P}^{\Conid{I}}\;{}\<[51]%
+\>[51]{}\Varid{j}\;\Varid{s}\;\Varid{i}\;{}\<[59]%
+\>[59]{}\mathrel{=}\;\Conid{P}\;\Varid{j}\;\Varid{s}\;(\Varid{inl}\;\Varid{i}){}\<[E]%
+\\
+\>[12]{}\Conid{P}^{\Conid{J}}\;{}\<[16]%
+\>[16]{}\in\;{}\<[19]%
+\>[19]{}(\Varid{j}\;\in\;\Conid{J})\;\rightarrow\;\Conid{S}\;\Varid{j}\;\rightarrow\;\Conid{J}\;{}\<[38]%
+\>[38]{}\rightarrow\;\Conid{Set};{}\<[47]%
+\>[47]{}\Conid{P}^{\Conid{J}}\;{}\<[51]%
+\>[51]{}\Varid{j}\;\Varid{s}\;\Varid{j′}\;{}\<[59]%
+\>[59]{}\mathrel{=}\;\Conid{P}\;\Varid{j}\;\Varid{s}\;(\Varid{inr}\;\Varid{j′}){}\<[E]%
+\\
+\>[12]{}\Varid{ffold}\;\mathrel{=}\;\Conid{WIfold}\;\Varid{f}{}\<[E]%
+\\
+\>[12]{}\Varid{rfold}\;\in\;{}\<[21]%
+\>[21]{}\{\mskip1.5mu \Varid{j}\;\in\;\Conid{J}\mskip1.5mu\}\;(\Varid{s}\;\in\;\Conid{WI}\;\Conid{S}\;\Conid{P}^{\Conid{J}}\;\Varid{j})\;(\Varid{i}\;\in\;\Conid{I})\;\rightarrow\;\Conid{Q}\;\Varid{j}\;(\Varid{ffold}\;\Varid{j}\;\Varid{s})\;\Varid{i}\;\rightarrow\;\Conid{Path}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\;\Conid{P}^{\Conid{J}}\;\Varid{j}\;\Varid{s}\;\Varid{i}{}\<[E]%
+\\
+\>[12]{}\Varid{rfold}\;(\Varid{sup}\;(\Varid{s},\Varid{f}))\;\Varid{i}\;\Varid{p}\;{}\<[37]%
+\>[37]{}\Keyword{with}\;\Varid{r}\;(\Varid{s},\anonymous )\;\Varid{i}\;\Varid{p}{}\<[E]%
+\\
+\>[12]{}\Varid{rfold}\;(\Varid{sup}\;(\Varid{s},\Varid{f}))\;\Varid{i}\;\Varid{p}\;{}\<[37]%
+\>[37]{}\mid \;\Varid{inl}\;\Varid{x}\;{}\<[60]%
+\>[60]{}\mathrel{=}\;\Varid{path}\;(\Varid{inl}\;\Varid{x}){}\<[E]%
+\\
+\>[12]{}\Varid{rfold}\;(\Varid{sup}\;(\Varid{s},\Varid{f}))\;\Varid{i}\;\Varid{p}\;{}\<[37]%
+\>[37]{}\mid \;\Varid{inr}\;(\Varid{j′},(\Varid{q},\Varid{y}))\;{}\<[60]%
+\>[60]{}\mathrel{=}\;\Varid{path}\;(\Varid{inr}\;(\Varid{j′},(\Varid{q},\Varid{rfold}\;(\Varid{f}\;\Varid{j′}\;\Varid{q})\;\Varid{i}\;\Varid{y}))){}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+%%Term Co-Alg ICont
+
+\section{Terminal Co-Algebras of Indexed Containers}
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{10}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{11}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{50}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Keyword{data}\;\Conid{MI}\;{}\<[10]%
+\>[10]{}\{\mskip1.5mu \Conid{I}\;\in\;\Conid{Set}\mskip1.5mu\}\;(\Conid{S}\;\in\;\Conid{I}\;\rightarrow\;\Conid{Set})\;{}\<[E]%
+\\
+\>[10]{}(\Conid{P}^{\Conid{I}}\;\in\;(\Varid{i}\;\in\;\Conid{I})\;\rightarrow\;\Conid{S}\;\Varid{i}\;\rightarrow\;\Conid{I}\;\rightarrow\;\Conid{Set})\;\in\;\Conid{I}\;\rightarrow\;\Conid{Set}\;\Keyword{where}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{sup}\;\in\;\;\Varid{⟦}\;\Conid{S}\;\lhd^{\star}\;\Conid{P}^{\Conid{I}}\;\Varid{⟧}^{\star}\;(\lambda\;\Varid{i}\;\rightarrow\;\infty\;(\Conid{MI}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\;\Varid{i}))\;{}\<[50]%
+\>[50]{}\rightarrow^{\star}\;\Conid{MI}\;\Conid{S}\;\Conid{P}^{\Conid{I}}{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\Varid{sup⁻¹}\;\in\;{}\<[10]%
+\>[10]{}\{\mskip1.5mu \Conid{I}\;\in\;\Conid{Set}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{S}\;\in\;\Conid{I}\;\rightarrow\;\Conid{Set}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{P}^{\Conid{I}}\;\in\;(\Varid{i}\;\in\;\Conid{I})\;\rightarrow\;\Conid{S}\;\Varid{i}\;\rightarrow\;\Conid{I}\;\rightarrow\;\Conid{Set}\mskip1.5mu\}\;\rightarrow\;{}\<[E]%
+\\
+\>[10]{}\hsindent{1}{}\<[11]%
+\>[11]{}\Conid{MI}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\;\rightarrow^{\star}\;\;\Varid{⟦}\;\Conid{S}\;\lhd^{\star}\;\Conid{P}^{\Conid{I}}\;\Varid{⟧}^{\star}\;(\Conid{MI}\;\Conid{S}\;\Conid{P}^{\Conid{I}}){}\<[E]%
+\\
+\>[B]{}\Varid{sup⁻¹}\;(\Varid{sup}\;(\Varid{s},\Varid{f}))\;\mathrel{=}\;\Varid{s},\lambda\;\Varid{i}\;\Varid{p}\;\rightarrow\;\flat\;(\Varid{f}\;\Varid{i}\;\Varid{p}){}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{5}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{7}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{8}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{10}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{12}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{13}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{14}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{15}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{16}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{17}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{19}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{23}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{33}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{38}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{42}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{46}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{47}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{51}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{54}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{59}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Conid{MIunfold}\;\in\;{}\<[13]%
+\>[13]{}\forall{}\;{}\<[16]%
+\>[16]{}\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{X}\;\in\;\Conid{I}\;\rightarrow\;\Conid{Set}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{S}\;\in\;\Conid{I}\;\rightarrow\;\Conid{Set}\mskip1.5mu\}\;{}\<[E]%
+\\
+\>[13]{}\hsindent{1}{}\<[14]%
+\>[14]{}\{\mskip1.5mu \Conid{P}^{\Conid{I}}\;\in\;(\Varid{i}\;\in\;\Conid{I})\;\rightarrow\;\Conid{S}\;\Varid{i}\;\rightarrow\;\Conid{I}\;\rightarrow\;\Conid{Set}\mskip1.5mu\}\;\rightarrow\;{}\<[E]%
+\\
+\>[13]{}\hsindent{1}{}\<[14]%
+\>[14]{}\Conid{X}\;\rightarrow^{\star}\;\;\Varid{⟦}\;\Conid{S}\;\lhd^{\star}\;\Conid{P}^{\Conid{I}}\;\Varid{⟧}^{\star}\;\Conid{X}\;\rightarrow\;\Conid{X}\;\rightarrow^{\star}\;\Conid{MI}\;\Conid{S}\;\Conid{P}^{\Conid{I}}{}\<[E]%
+\\
+\>[B]{}\Conid{MIunfold}\;\Varid{m}\;\Varid{i}\;\Varid{x}\;\Keyword{with}\;\Varid{m}\;\Varid{i}\;\Varid{x}{}\<[E]%
+\\
+\>[B]{}\Conid{MIunfold}\;\Varid{m}\;\Varid{i}\;\Varid{x}\;\mid \;\Varid{s},\Varid{f}\;\mathrel{=}\;\Varid{sup}\;(\Varid{s},(\lambda\;\Varid{i′}\;\Varid{p}\;\rightarrow\;\sharp\;\Conid{MIunfold}\;\Varid{m}\;\Varid{i′}\;(\Varid{f}\;\Varid{i′}\;\Varid{p}))){}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\Keyword{data}\;\Conid{Path}\;{}\<[12]%
+\>[12]{}\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\in\;\Conid{Set}\mskip1.5mu\}\;(\Conid{S}\;\in\;\Conid{I}\;\rightarrow\;\Conid{Set})\;{}\<[E]%
+\\
+\>[12]{}(\Conid{P}^{\Conid{I}}\;{}\<[17]%
+\>[17]{}\in\;(\Varid{i}\;\in\;\Conid{I})\;\rightarrow\;\Conid{S}\;\Varid{i}\;\rightarrow\;\Conid{I}\;{}\<[38]%
+\>[38]{}\rightarrow\;\Conid{Set})\;{}\<[E]%
+\\
+\>[12]{}(\Conid{P}^{\Conid{J}}\;{}\<[17]%
+\>[17]{}\in\;(\Varid{i}\;\in\;\Conid{I})\;\rightarrow\;\Conid{S}\;\Varid{i}\;\rightarrow\;\Conid{J}\;{}\<[38]%
+\>[38]{}\rightarrow\;\Conid{Set})\;{}\<[E]%
+\\
+\>[12]{}\in\;(\Varid{i}\;\in\;\Conid{I})\;\rightarrow\;\Conid{MI}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\;\Varid{i}\;\rightarrow\;\Conid{J}\;\rightarrow\;\Conid{Set}\;\Keyword{where}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{path}\;\in\;\forall{}\;{}\<[13]%
+\>[13]{}\{\mskip1.5mu \Varid{i}\;\Varid{s}\;\Varid{f}\;\Varid{j}\mskip1.5mu\}\;\rightarrow\;{}\<[E]%
+\\
+\>[13]{}\hsindent{3}{}\<[16]%
+\>[16]{}\Conid{P}^{\Conid{J}}\;\Varid{i}\;\Varid{s}\;\Varid{j}\;{}\<[E]%
+\\
+\>[13]{}\uplus\;{}\<[16]%
+\>[16]{}(\Sigma\;\Conid{I}\;\lambda\;\Varid{i′}\;\rightarrow\;\Sigma\;(\Conid{P}^{\Conid{I}}\;\Varid{i}\;\Varid{s}\;\Varid{i′})\;\lambda\;\Varid{p}\;\rightarrow\;\Conid{Path}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\;\Conid{P}^{\Conid{J}}\;\Varid{i′}\;(\flat\;(\Varid{f}\;\Varid{i′}\;\Varid{p}))\;\Varid{j})\;{}\<[E]%
+\\
+\>[13]{}\rightarrow\;\Conid{Path}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\;\Conid{P}^{\Conid{J}}\;\Varid{i}\;(\Varid{sup}\;(\Varid{s},\Varid{f}))\;\Varid{j}{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\nu^{\text{\tiny C}}\;\in\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\in\;\Conid{Set}\mskip1.5mu\}\;\rightarrow\;\Conid{ICont}^{\star}\;(\Conid{I}\;\uplus\;\Conid{J})\;\Conid{I}\;\rightarrow\;\Conid{ICont}^{\star}\;\Conid{J}\;\Conid{I}{}\<[E]%
+\\
+\>[B]{}\nu^{\text{\tiny C}}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{J}\mskip1.5mu\}\;(\Conid{S}\;\lhd^{\star}\;\Conid{P})\;\mathrel{=}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Keyword{let}\;{}\<[8]%
+\>[8]{}\Conid{P}^{\Conid{I}}\;{}\<[12]%
+\>[12]{}\in\;(\Varid{i}\;\in\;\Conid{I})\;\rightarrow\;\Conid{S}\;\Varid{i}\;\rightarrow\;\Conid{I}\;{}\<[33]%
+\>[33]{}\rightarrow\;\Conid{Set};{}\<[42]%
+\>[42]{}\Conid{P}^{\Conid{I}}\;{}\<[46]%
+\>[46]{}\Varid{i}\;\Varid{s}\;\Varid{i′}\;{}\<[54]%
+\>[54]{}\mathrel{=}\;\Conid{P}\;\!\!\;\Varid{i}\;\!\!\;\Varid{s}\;\!\!\;(\Varid{inl}\;\Varid{i′}){}\<[E]%
+\\
+\>[8]{}\Conid{P}^{\Conid{J}}\;{}\<[12]%
+\>[12]{}\in\;(\Varid{i}\;\in\;\Conid{I})\;\rightarrow\;\Conid{S}\;\Varid{i}\;\rightarrow\;\Conid{J}\;{}\<[33]%
+\>[33]{}\rightarrow\;\Conid{Set};{}\<[42]%
+\>[42]{}\Conid{P}^{\Conid{J}}\;{}\<[46]%
+\>[46]{}\Varid{i}\;\Varid{s}\;\Varid{j}\;{}\<[54]%
+\>[54]{}\mathrel{=}\;\Conid{P}\;\!\!\;\Varid{i}\;\!\!\;\Varid{s}\;\!\!\;(\Varid{inr}\;\Varid{j}){}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Keyword{in}\;{}\<[8]%
+\>[8]{}\Conid{MI}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\;\lhd^{\star}\;\Conid{Path}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\;\Conid{P}^{\Conid{J}}{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\Varid{out}^{\text{\tiny C}}\;\in\;\forall{}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\mskip1.5mu\}\;\rightarrow\;(\Conid{F}\;\in\;\Conid{ICont}^{\star}\;(\Conid{I}\;\uplus\;\Conid{J})\;\Conid{I})\;\rightarrow\;\nu^{\text{\tiny C}}\;\Conid{F}\;\Rightarrow^{\text{\tiny C}^{\star}}\;\Conid{F}\;[\mskip1.5mu \;\nu^{\text{\tiny C}}\;\Conid{F}\;\mskip1.5mu]^{\text{\tiny{C}}^{\star}}{}\<[E]%
+\\
+\>[B]{}\Varid{out}^{\text{\tiny C}}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{J}\mskip1.5mu\}\;(\Conid{S}\;\lhd^{\star}\;\Conid{P})\;\mathrel{=}\;(\lambda\;\anonymous \;\rightarrow\;\Varid{sup⁻¹})\;\lhd^{\star}\;\Varid{unsup}\;\{\mskip1.5mu \anonymous \mskip1.5mu\}\;\{\mskip1.5mu \anonymous \mskip1.5mu\}\;\{\mskip1.5mu \anonymous \mskip1.5mu\}\;\{\mskip1.5mu \lambda\;\Varid{j}\;\Varid{s}\;\rightarrow\;(\Varid{i}\;\in\;\Conid{J})\;\rightarrow\;\Conid{P}\;\Varid{j}\;(\pi_{0}\;(\Varid{sup⁻¹}\;\Varid{s}))\;(\Varid{inr}\;\Varid{i})\;\uplus{}\<[E]%
+\\
+\>[B]{}\hsindent{7}{}\<[7]%
+\>[7]{}\Sigma\;\Conid{I}{}\<[E]%
+\\
+\>[B]{}\hsindent{7}{}\<[7]%
+\>[7]{}(\lambda\;\Varid{i'}\;\rightarrow\;{}\<[E]%
+\\
+\>[7]{}\hsindent{3}{}\<[10]%
+\>[10]{}\Sigma\;(\Conid{P}\;\Varid{j}\;(\pi_{0}\;(\Varid{sup⁻¹}\;\Varid{s}))\;(\Varid{inl}\;\Varid{i'}))\;{}\<[E]%
+\\
+\>[7]{}\hsindent{3}{}\<[10]%
+\>[10]{}(\lambda\;\Varid{p}\;\rightarrow\;{}\<[E]%
+\\
+\>[10]{}\hsindent{3}{}\<[13]%
+\>[13]{}\Conid{Path}\;\Conid{S}\;(\lambda\;\Varid{i0}\;\Varid{s'}\;\Varid{i′}\;\rightarrow\;\Conid{P}\;\Varid{i0}\;\Varid{s'}\;(\Varid{inl}\;\Varid{i′}))\;{}\<[E]%
+\\
+\>[10]{}\hsindent{3}{}\<[13]%
+\>[13]{}(\lambda\;\Varid{i0}\;\Varid{s'}\;\Varid{j'}\;\rightarrow\;\Conid{P}\;\Varid{i0}\;\Varid{s'}\;(\Varid{inr}\;\Varid{j'}))\;\Varid{i'}\;(\pi_{1}\;(\Varid{sup⁻¹}\;\Varid{s})\;\Varid{i'}\;\Varid{p})\;\Varid{i}))\;\rightarrow{}\<[E]%
+\\
+\>[B]{}\hsindent{7}{}\<[7]%
+\>[7]{}\Conid{Path}\;\Conid{S}\;(\lambda\;\Varid{i'}\;\Varid{s'}\;\Varid{i′}\;\rightarrow\;\Conid{P}\;\Varid{i'}\;\Varid{s'}\;(\Varid{inl}\;\Varid{i′})){}\<[E]%
+\\
+\>[B]{}\hsindent{7}{}\<[7]%
+\>[7]{}(\lambda\;\Varid{i'}\;\Varid{s'}\;\Varid{j'}\;\rightarrow\;\Conid{P}\;\Varid{i'}\;\Varid{s'}\;(\Varid{inr}\;\Varid{j'}))\;\Varid{j}\;\Varid{s}\;\Varid{i}\mskip1.5mu\}\;(\lambda\;\Varid{sf}\;\Varid{i′}\;\Varid{p}\;\rightarrow\;\Varid{path}\;\Varid{p}){}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\Varid{unfold}^{\text{\tiny C}}\;\in\;\forall{}\;{}\<[15]%
+\>[15]{}\{\mskip1.5mu \Conid{I}\;\Conid{J}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{F}\;\in\;\Conid{ICont}^{\star}\;(\Conid{I}\;\uplus\;\Conid{J})\;\Conid{I}\mskip1.5mu\}\;(\Conid{G}\;\in\;\Conid{ICont}^{\star}\;\Conid{J}\;\Conid{I})\;\rightarrow\;{}\<[E]%
+\\
+\>[15]{}\Conid{G}\;\Rightarrow^{\text{\tiny C}^{\star}}\;\Conid{F}\;[\mskip1.5mu \;\Conid{G}\;\mskip1.5mu]^{\text{\tiny{C}}^{\star}}\;\rightarrow\;\Conid{G}\;\Rightarrow^{\text{\tiny C}^{\star}}\;\nu^{\text{\tiny C}}\;\Conid{F}{}\<[E]%
+\\
+\>[B]{}\Varid{unfold}^{\text{\tiny C}}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{J}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{S}\;\lhd^{\star}\;\Conid{P}\mskip1.5mu\}\;(\Conid{T}\;\lhd^{\star}\;\Conid{Q})\;(\Varid{f}\;\lhd^{\star}\;\Varid{r})\;\mathrel{=}\;\Varid{funfold}\;\lhd^{\star}\;\Varid{runfold}{}\<[E]%
+\\
+\>[B]{}\hsindent{5}{}\<[5]%
+\>[5]{}\Keyword{where}\;{}\<[12]%
+\>[12]{}\Conid{P}^{\Conid{I}}\;{}\<[16]%
+\>[16]{}\in\;{}\<[19]%
+\>[19]{}(\Varid{i}\;\in\;\Conid{I})\;\rightarrow\;\Conid{S}\;\Varid{i}\;\rightarrow\;\Conid{I}\;{}\<[38]%
+\>[38]{}\rightarrow\;\Conid{Set};{}\<[47]%
+\>[47]{}\Conid{P}^{\Conid{I}}\;{}\<[51]%
+\>[51]{}\Varid{i}\;\Varid{s}\;\Varid{i′}\;{}\<[59]%
+\>[59]{}\mathrel{=}\;\Conid{P}\;\Varid{i}\;\Varid{s}\;(\Varid{inl}\;\Varid{i′}){}\<[E]%
+\\
+\>[12]{}\Conid{P}^{\Conid{J}}\;{}\<[16]%
+\>[16]{}\in\;{}\<[19]%
+\>[19]{}(\Varid{i}\;\in\;\Conid{I})\;\rightarrow\;\Conid{S}\;\Varid{i}\;\rightarrow\;\Conid{J}\;{}\<[38]%
+\>[38]{}\rightarrow\;\Conid{Set};{}\<[47]%
+\>[47]{}\Conid{P}^{\Conid{J}}\;{}\<[51]%
+\>[51]{}\Varid{i}\;\Varid{s}\;\Varid{j}\;{}\<[59]%
+\>[59]{}\mathrel{=}\;\Conid{P}\;\Varid{i}\;\Varid{s}\;(\Varid{inr}\;\Varid{j}){}\<[E]%
+\\
+\>[12]{}\Varid{funfold}\;\mathrel{=}\;\Conid{MIunfold}\;\Varid{f}{}\<[E]%
+\\
+\>[12]{}\Varid{runfold}\;\in\;{}\<[23]%
+\>[23]{}\{\mskip1.5mu \Varid{i}\;\in\;\Conid{I}\mskip1.5mu\}\;(\Varid{t}\;\in\;\Conid{T}\;\Varid{i})\;(\Varid{j}\;\in\;\Conid{J})\;\rightarrow\;\Conid{Path}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\;\Conid{P}^{\Conid{J}}\;\Varid{i}\;(\Varid{funfold}\;\Varid{i}\;\Varid{t})\;\Varid{j}\;\rightarrow\;\Conid{Q}\;\Varid{i}\;\Varid{t}\;\Varid{j}{}\<[E]%
+\\
+\>[12]{}\Varid{runfold}\;\Varid{t}\;\Varid{j}\;(\Varid{path}\;(\Varid{inl}\;\Varid{x}))\;\mathrel{=}\;\Varid{r}\;\Varid{t}\;\Varid{j}\;(\Varid{inl}\;\Varid{x}){}\<[E]%
+\\
+\>[12]{}\Varid{runfold}\;\Varid{t}\;\Varid{j}\;(\Varid{path}\;(\Varid{inr}\;(\Varid{i},(\Varid{p},\Varid{q}))))\;\mathrel{=}\;\Varid{r}\;\Varid{t}\;\Varid{j}\;(\Varid{inr}\;(\Varid{i},\Varid{p},\Varid{runfold}\;(\pi_{1}\;(\Varid{f}\;\anonymous \;\Varid{t})\;\Varid{i}\;\Varid{p})\;\Varid{j}\;\Varid{q})){}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\section{W is still enough}
+
+\subsubsection{\ensuremath{\Conid{WI}} from \ensuremath{\Conid{W}}}
+
+How, then, can we build \ensuremath{\Conid{WI}} from \ensuremath{\Conid{W}}?
+The initial step is to create a type of \emph{pre}-\ensuremath{\Conid{WI}} trees, with nodes containing a shape \emph{and} its index, and branching over positions \emph{and their} indicies:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Conid{WI′}\;\in\;\{\mskip1.5mu \Conid{I}\;\in\;\Conid{Set}\mskip1.5mu\}\;(\Conid{S}\;\in\;\Conid{I}\;\rightarrow\;\Conid{Set})\;(\Conid{P}\;\in\;(\Varid{i}\;\in\;\Conid{I})\;(\Varid{s}\;\in\;\Conid{S}\;\Varid{i})\;\rightarrow\;\Conid{I}\;\rightarrow\;\Conid{Set})\;\rightarrow\;\Conid{Set}{}\<[E]%
+\\
+\>[B]{}\Conid{WI′}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\Conid{S}\;\Conid{P}\;\mathrel{=}\;\Conid{W}\;(\Sigma\;\Conid{I}\;\Conid{S})\;(\lambda (\!\;\Varid{i}\;\!,\!\;\Varid{s}\;\!\!)\;\rightarrow\;\Sigma\;\Conid{I}\;(\Conid{P}\;\Varid{i}\;\Varid{s})\;\!\;\!){}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+Given such a tree we want to express the property that the subtrees of such a pre-tree have the correct index in their node information.
+In order to do this we need a second \ensuremath{\Conid{W}}-type, which is similar to \ensuremath{\Conid{WWI′}}, but with an extra copy of the index information stored in that node:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Conid{WIl}\;\in\;\{\mskip1.5mu \Conid{I}\;\in\;\Conid{Set}\mskip1.5mu\}\;(\Conid{S}\;\in\;\Conid{I}\;\rightarrow\;\Conid{Set})\;(\Conid{P}\;\in\;(\Varid{i}\;\in\;\Conid{I})\;(\Varid{s}\;\in\;\Conid{S}\;\Varid{i})\;\rightarrow\;\Conid{I}\;\rightarrow\;\Conid{Set})\;\rightarrow\;\Conid{Set}{}\<[E]%
+\\
+\>[B]{}\Conid{WIl}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\Conid{S}\;\Conid{P}\;\mathrel{=}\;\Conid{W}\;(\Conid{I}\;\times\;(\Sigma\;\Conid{I}\;\Conid{S}))\;(\lambda (\!\;\Varid{i′}\;\!,\!\;\Varid{i}\;\!,\!\;\Varid{s}\;\!\!)\;\rightarrow\;\Sigma\;\Conid{I}\;(\Conid{P}\;\Varid{i}\;\Varid{s})\;\!\;\!){}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+There are two possible completions of this extra indexing information, either we push the indexes down to the subtrees, or we copy it from the sub-trees themselves:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[3]{}\Varid{lup}\;\in\;\Conid{WI′}\;\Conid{S}\;\Conid{P}\;\rightarrow\;\Conid{WIl}\;\Conid{S}\;\Conid{P}{}\<[E]%
+\\
+\>[3]{}\Varid{lup}\;(\Varid{sup}\;(\Varid{i},\Varid{s})\;\Varid{f})\;\mathrel{=}\;\Varid{sup}\;(\Varid{i},(\Varid{i},\Varid{s}))\;(\lambda\;\Varid{p}\;\rightarrow\;\Varid{lup}\;(\Varid{f}\;\Varid{p})){}\<[E]%
+\\[\blanklineskip]%
+\>[3]{}\Varid{ldown}\;\in\;\Conid{I}\;\rightarrow\;\Conid{WI′}\;\Conid{S}\;\Conid{P}\;\rightarrow\;\Conid{WIl}\;\Conid{S}\;\Conid{P}{}\<[E]%
+\\
+\>[3]{}\Varid{ldown}\;\Varid{i}\;(\Varid{sup}\;\Varid{s}\;\Varid{f})\;\mathrel{=}\;\Varid{sup}\;(\Varid{i},\Varid{s})\;\lambda (\!\;\Varid{i′}\;\!,\!\;\Varid{p}\;\!\!)\;\rightarrow\;\Varid{ldown}\;\Varid{i′}\;(\Varid{f}\;(\Varid{i′},\Varid{p}))\;\!\;\!{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+The property of a pre-tree being type correct can be stated as its two possible labellings being equal:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Conid{WI}\;\in\;\{\mskip1.5mu \Conid{I}\;\in\;\Conid{Set}\mskip1.5mu\}\;(\Conid{S}\;\in\;\Conid{I}\;\rightarrow\;\Conid{Set})\;(\Conid{P}\;\in\;(\Varid{i}\;\in\;\Conid{I})\;(\Varid{s}\;\in\;\Conid{S}\;\Varid{i})\;\rightarrow\;\Conid{I}\;\rightarrow\;\Conid{Set})\;\rightarrow\;\Conid{I}\;\rightarrow\;\Conid{Set}{}\<[E]%
+\\
+\>[B]{}\Conid{WI}\;\Conid{S}\;\Conid{P}\;\Varid{i}\;\mathrel{=}\;\Sigma\;(\Conid{WI′}\;\Conid{S}\;\Conid{P})\;\lambda\;\Varid{x}\;\rightarrow\;\Varid{lup}\;\{\mskip1.5mu \anonymous \mskip1.5mu\}\;\{\mskip1.5mu \Conid{S}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{P}\mskip1.5mu\}\;\Varid{x}\;\equiv\;\Varid{ldown}\;\{\mskip1.5mu \anonymous \mskip1.5mu\}\;\{\mskip1.5mu \Conid{S}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{P}\mskip1.5mu\}\;\Varid{i}\;\Varid{x}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+We rely on function extensionality to define the constructor \ensuremath{\Varid{sup}}:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{19}{@{}>{\hspre}c<{\hspost}@{}}%
+\column{19E}{@{}l@{}}%
+\column{22}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{37}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[3]{}\Keyword{open}\;\Keyword{import}\;\Varid{ifunc}{}\<[E]%
+\\
+\>[3]{}\Keyword{open}\;\Keyword{import}\;\Varid{icont}{}\<[E]%
+\\[\blanklineskip]%
+\>[3]{}\Varid{sup}\;\in\;\;\Varid{⟦}\;\Conid{S}\;\lhd^{\star}\;\Conid{P}\;\Varid{⟧}^{\star}\;(\Conid{WI}\;\Conid{S}\;\Conid{P})\;{}\<[37]%
+\>[37]{}\rightarrow^{\star}\;\Conid{WI}\;\Conid{S}\;\Conid{P}{}\<[E]%
+\\
+\>[3]{}\Varid{sup}\;(\Varid{s},\Varid{f})\;\mathrel{=}\;{}\<[19]%
+\>[19]{}({}\<[19E]%
+\>[22]{}\Varid{sup}\;(\anonymous ,\Varid{s})\;(\lambda (\!\;\Varid{i}\;\!,\!\;\Varid{p}\;\!\!)\;\rightarrow\;\pi_{0}\;(\Varid{f}\;\Varid{i}\;\Varid{p})\;\!\;\!)){}\<[E]%
+\\
+\>[19]{},{}\<[19E]%
+\>[22]{}\Varid{cong}\;(\Varid{sup}\;(\anonymous ,\anonymous ,\Varid{s}))\;(\Varid{ext}\;\lambda (\!\;\Varid{i}\;\!,\!\;\Varid{p}\;\!\!)\;\rightarrow\;\pi_{1}\;(\Varid{f}\;\Varid{i}\;\Varid{p})\;\!\;\!){}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+The recursion principle inevitably then relies on the uniqueness of identity 
+proofs.
+It's also the case that in its form below \ensuremath{\Varid{wirec}} does not pass Agda's termination checker.
+The direct encoding via \ensuremath{\Varid{wrec}} would avoid this problem, at the expense of being even more verbose:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{5}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{7}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{11}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{12}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{17}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[3]{}\Varid{wirec}\;\in\;\{\mskip1.5mu \Varid{i}\;\in\;\Conid{I}\mskip1.5mu\}\;(\Varid{x}\;\in\;\Conid{WI}\;\Conid{S}\;\Conid{P}\;\Varid{i})\;(\Conid{Q}\;\in\;\{\mskip1.5mu \Varid{i}\;\in\;\Conid{I}\mskip1.5mu\}\;\rightarrow\;\Conid{WI}\;\Conid{S}\;\Conid{P}\;\Varid{i}\;\rightarrow\;\Conid{Set})\;{}\<[E]%
+\\
+\>[3]{}\hsindent{8}{}\<[11]%
+\>[11]{}(\Varid{m}\;\in\;{}\<[17]%
+\>[17]{}\{\mskip1.5mu \Varid{i}\;\in\;\Conid{I}\mskip1.5mu\}\;(\Varid{s}\;\in\;\Conid{S}\;\Varid{i})\;(\Varid{f}\;\in\;\Conid{P}\;\Varid{i}\;\Varid{s}\;\rightarrow^{\star}\;\Conid{WI}\;\Conid{S}\;\Conid{P})\;{}\<[E]%
+\\
+\>[17]{}(\Varid{h}\;\in\;\{\mskip1.5mu \Varid{i′}\;\in\;\Conid{I}\mskip1.5mu\}\;(\Varid{p}\;\in\;\Conid{P}\;\Varid{i}\;\Varid{s}\;\Varid{i′})\;\rightarrow\;\Conid{Q}\;(\Varid{f}\;\Varid{i′}\;\Varid{p}))\;\rightarrow\;\Conid{Q}\;\{\mskip1.5mu \Varid{i}\mskip1.5mu\}\;(\Varid{sup}\;(\Varid{s},\Varid{f})))\;{}\<[E]%
+\\
+\>[3]{}\hsindent{8}{}\<[11]%
+\>[11]{}\rightarrow\;\Conid{Q}\;\Varid{x}{}\<[E]%
+\\
+\>[3]{}\Varid{wirec}\;\{\mskip1.5mu \Varid{i}\mskip1.5mu\}\;(\Varid{sup}\;(\Varid{i′},\Varid{s})\;\Varid{f},\Varid{ok})\;\Conid{Q}\;\Varid{m}\;\Keyword{with}\;\pi_{0}\equiv\;(\Varid{sup₁≡}\;\Varid{ok}){}\<[E]%
+\\
+\>[3]{}\Varid{wirec}\;\{\mskip1.5mu \Varid{i}\mskip1.5mu\}\;(\Varid{sup}\;(\Varid{.i},\Varid{s})\;\Varid{f},\Varid{ok})\;\Conid{Q}\;\Varid{m}\;\mid \;\Varid{refl}\;\mathrel{=}\;{}\<[E]%
+\\
+\>[3]{}\hsindent{2}{}\<[5]%
+\>[5]{}\Varid{subst}\;\Conid{Q}\;(\Varid{cong}\;\{\mskip1.5mu \Conid{B}\;\mathrel{=}\;\lambda\;\anonymous \;\rightarrow\;\Conid{WI}\;\Conid{S}\;\Conid{P}\;\Varid{i}\mskip1.5mu\}\;(\lambda\;\Varid{x}\;\rightarrow\;\Varid{sup}\;(\Varid{i},\Varid{s})\;\Varid{f},\Varid{x})\;\Conid{UIP})\;{}\<[E]%
+\\
+\>[5]{}\hsindent{2}{}\<[7]%
+\>[7]{}(\Varid{m}\;\Varid{s}\;(\lambda\;\Varid{i}\;\Varid{p}\;\rightarrow\;\Varid{f}\;(\Varid{i},\Varid{p}),\Varid{ext⁻¹}\;(\Varid{sup₂≡}\;\Varid{ok})\;(\Varid{i},\Varid{p}))\;{}\<[E]%
+\\
+\>[7]{}\hsindent{5}{}\<[12]%
+\>[12]{}(\lambda\;\{\mskip1.5mu \Varid{i′}\mskip1.5mu\}\;\Varid{p}\;\rightarrow\;\Varid{wirec}\;(\Varid{f}\;(\Varid{i′},\Varid{p}),\Varid{ext⁻¹}\;(\Varid{sup₂≡}\;\Varid{ok})\;(\Varid{i′},\Varid{p}))\;\Conid{Q}\;\Varid{m})){}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+It's then straight forward but labourious to prove the $\beta$ law for \ensuremath{\Varid{wirec}}, which would have this type:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{12}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{18}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[3]{}\beta\Varid{wirec}\;\in\;{}\<[E]%
+\\
+\>[3]{}\hsindent{9}{}\<[12]%
+\>[12]{}\{\mskip1.5mu \Varid{i}\;\in\;\Conid{I}\mskip1.5mu\}\;(\Varid{s}\;\in\;\Conid{S}\;\Varid{i})\;(\Varid{f}\;\in\;\Conid{P}\;\Varid{i}\;\Varid{s}\;\rightarrow^{\star}\;\Conid{WI}\;\Conid{I}\;\Conid{S}\;\Conid{P})\;{}\<[E]%
+\\
+\>[3]{}\hsindent{9}{}\<[12]%
+\>[12]{}(\Conid{Q}\;\in\;\{\mskip1.5mu \Varid{i}\;\in\;\Conid{I}\mskip1.5mu\}\;\rightarrow\;\Conid{WI}\;\Conid{I}\;\Conid{S}\;\Conid{P}\;\Varid{i}\;\rightarrow\;\Conid{Set})\;{}\<[E]%
+\\
+\>[3]{}\hsindent{9}{}\<[12]%
+\>[12]{}(\Varid{m}\;\in\;{}\<[18]%
+\>[18]{}\{\mskip1.5mu \Varid{i}\;\in\;\Conid{I}\mskip1.5mu\}\;(\Varid{s}\;\in\;\Conid{S}\;\Varid{i})\;(\Varid{f}\;\in\;\{\mskip1.5mu \Varid{i′}\;\in\;\Conid{I}\mskip1.5mu\}\;\rightarrow\;\Conid{P}\;\Varid{i}\;\Varid{s}\;\Varid{i′}\;\rightarrow\;\Conid{WI}\;\Conid{I}\;\Conid{S}\;\Conid{P}\;\Varid{i′})\;{}\<[E]%
+\\
+\>[18]{}(\Varid{h}\;\in\;\{\mskip1.5mu \Varid{i′}\;\in\;\Conid{I}\mskip1.5mu\}\;(\Varid{p}\;\in\;\Conid{P}\;\Varid{i}\;\Varid{s}\;\Varid{i′})\;\rightarrow\;\Conid{Q}\;(\Varid{f}\;\Varid{p}))\;\rightarrow\;\Conid{Q}\;\{\mskip1.5mu \Varid{i}\mskip1.5mu\}\;(\Varid{sup}\;\Varid{s}\;\Varid{f}))\;{}\<[E]%
+\\
+\>[3]{}\hsindent{9}{}\<[12]%
+\>[12]{}\rightarrow\;\Varid{wirec}\;\{\mskip1.5mu \Varid{i}\mskip1.5mu\}\;(\Varid{sup}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{S}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{P}\mskip1.5mu\}\;\Varid{s}\;\Varid{f})\;\Conid{Q}\;\Varid{m}\;\equiv\;\Varid{m}\;\{\mskip1.5mu \Varid{i}\mskip1.5mu\}\;\Varid{s}\;\Varid{f}\;(\lambda\;\{\mskip1.5mu \Varid{i′}\mskip1.5mu\}\;\Varid{p}\;\rightarrow\;\Varid{wirec}\;(\Varid{f}\;\Varid{p})\;\Conid{Q}\;\Varid{m}){}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+We can use this proof that \ensuremath{\Conid{WI}}-types can be encoded by \ensuremath{\Conid{W}} to explain where 
+\ensuremath{\Conid{Path}} fits in, since it is straight forwardly encoded as a \ensuremath{\Conid{WI}}:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{9}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{11}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{12}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{14}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{18}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{22}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{25}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{35}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Conid{Path}\;\in\;{}\<[9]%
+\>[9]{}\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\in\;\Conid{Set}\mskip1.5mu\}\;(\Conid{S}\;\in\;\Conid{I}\;\rightarrow\;\Conid{Set})\;{}\<[E]%
+\\
+\>[9]{}(\Conid{P}^{\Conid{I}}\;{}\<[14]%
+\>[14]{}\in\;(\Varid{i}\;\in\;\Conid{I})\;\rightarrow\;\Conid{S}\;\Varid{i}\;\rightarrow\;\Conid{I}\;{}\<[35]%
+\>[35]{}\rightarrow\;\Conid{Set})\;{}\<[E]%
+\\
+\>[9]{}(\Conid{P}^{\Conid{J}}\;{}\<[14]%
+\>[14]{}\in\;(\Varid{i}\;\in\;\Conid{I})\;\rightarrow\;\Conid{S}\;\Varid{i}\;\rightarrow\;\Conid{J}\;{}\<[35]%
+\>[35]{}\rightarrow\;\Conid{Set})\;{}\<[E]%
+\\
+\>[9]{}(\Varid{i}\;\in\;\Conid{I})\;\rightarrow\;\Conid{WI}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\;\Varid{i}\;\rightarrow\;\Conid{J}\;\rightarrow\;\Conid{Set}{}\<[E]%
+\\
+\>[B]{}\Conid{Pathk}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{J}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{S}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{P}^{\Conid{I}}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{P}^{\Conid{J}}\mskip1.5mu\}\;\Varid{i}\;\Varid{w}\;\mathrel{=}\;\Conid{WI}\;\Conid{PathS}\;\Conid{PathP}\;(\Varid{i},\Varid{w}){}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Keyword{where}\;\Conid{PathS}\;\in\;\Sigma\;\Conid{I}\;(\Conid{WI}\;\Conid{S}\;\Conid{P}^{\Conid{I}})\;\rightarrow\;\Conid{Set}{}\<[E]%
+\\
+\>[3]{}\hsindent{6}{}\<[9]%
+\>[9]{}\Conid{PathS}\;(\Varid{i},\Varid{sup}\;(\Varid{s},\Varid{f}))\;\mathrel{=}\;\Conid{P}^{\Conid{J}}\;\Varid{i}\;\Varid{s}\;\Varid{j}\;\uplus\;\Sigma\;\Conid{I}\;(\Conid{P}^{\Conid{I}}\;\Varid{i}\;\Varid{s}){}\<[E]%
+\\
+\>[3]{}\hsindent{6}{}\<[9]%
+\>[9]{}\Conid{PathP}\;\in\;(\Varid{iw}\;\in\;\Sigma\;\Conid{I}\;(\Conid{WI}\;\Conid{S}\;\Conid{P}^{\Conid{I}}))\;(\Varid{s}\;\in\;\Conid{PathS}\;\Varid{iw})\;\rightarrow\;\Sigma\;\Conid{I}\;(\Conid{WI}\;\Conid{S}\;\Conid{P}^{\Conid{I}})\;\rightarrow\;\Conid{Set}{}\<[E]%
+\\
+\>[3]{}\hsindent{6}{}\<[9]%
+\>[9]{}\Conid{PathP}\;(\Varid{i},\Varid{sup}\;(\Varid{s},\Varid{f}))\;(\Varid{inl}\;\Varid{p})\;(\Varid{i′},\Varid{w′})\;\mathrel{=}\;\bot{}\<[E]%
+\\
+\>[3]{}\hsindent{6}{}\<[9]%
+\>[9]{}\Conid{PathP}\;(\Varid{i},\Varid{sup}\;(\Varid{s},\Varid{f}))\;(\Varid{inr}\;(\Varid{i′′},\Varid{p}))\;(\Varid{i′},\Varid{w′})\;\mathrel{=}\;{}\<[E]%
+\\
+\>[9]{}\hsindent{2}{}\<[11]%
+\>[11]{}(\Varid{i′′}\;\equiv\;\Varid{i′})\;\times\;(\Varid{f}\;\Varid{i′′}\;\Varid{p}\;\cong\;\Varid{w′}){}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\Varid{path}\;\in\;{}\<[9]%
+\>[9]{}\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\in\;\Conid{Set}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{S}\;\in\;\Conid{I}\;\rightarrow\;\Conid{Set}\mskip1.5mu\}\;{}\<[E]%
+\\
+\>[9]{}\{\mskip1.5mu \Conid{P}^{\Conid{I}}\;{}\<[14]%
+\>[14]{}\in\;(\Varid{i}\;\in\;\Conid{I})\;\rightarrow\;\Conid{S}\;\Varid{i}\;\rightarrow\;\Conid{I}\;{}\<[35]%
+\>[35]{}\rightarrow\;\Conid{Set}\mskip1.5mu\}\;{}\<[E]%
+\\
+\>[9]{}\{\mskip1.5mu \Conid{P}^{\Conid{J}}\;{}\<[14]%
+\>[14]{}\in\;(\Varid{i}\;\in\;\Conid{I})\;\rightarrow\;\Conid{S}\;\Varid{i}\;\rightarrow\;\Conid{J}\;{}\<[35]%
+\>[35]{}\rightarrow\;\Conid{Set}\mskip1.5mu\}\;{}\<[E]%
+\\
+\>[9]{}\{\mskip1.5mu \Varid{i}\;\in\;\Conid{I}\mskip1.5mu\}\;\rightarrow\;\{\mskip1.5mu \Varid{s}\;\in\;\Conid{S}\;\Varid{i}\mskip1.5mu\}\;\{\mskip1.5mu \Varid{f}\;\in\;\Conid{P}^{\Conid{I}}\;\Varid{i}\;\Varid{s}\;\rightarrow^{\star}\;\Conid{WI}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\mskip1.5mu\}\;\rightarrow\;\{\mskip1.5mu \Varid{j}\;\in\;\Conid{J}\mskip1.5mu\}\;{}\<[E]%
+\\
+\>[9]{}\rightarrow\;{}\<[12]%
+\>[12]{}\Conid{P}^{\Conid{J}}\;\Varid{i}\;\Varid{s}\;\Varid{j}\;{}\<[22]%
+\>[22]{}\uplus\;{}\<[25]%
+\>[25]{}(\Sigma\;\Conid{I}\;\lambda\;\Varid{i′}\;\rightarrow\;\Sigma\;(\Conid{P}^{\Conid{I}}\;\Varid{i}\;\Varid{s}\;\Varid{i′})\;\lambda\;\Varid{p}\;\rightarrow\;\Conid{Pathk}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\;\Conid{P}^{\Conid{J}}\;\Varid{i′}\;(\Varid{f}\;\Varid{i′}\;\Varid{p})\;\Varid{j})\;{}\<[E]%
+\\
+\>[9]{}\rightarrow\;{}\<[12]%
+\>[12]{}\Conid{Pathk}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\;\Conid{P}^{\Conid{J}}\;\Varid{i}\;(\Varid{sup}\;(\Varid{s},\Varid{f}))\;\Varid{j}{}\<[E]%
+\\
+\>[B]{}\Varid{pathk}\;(\Varid{inl}\;\Varid{p})\;\mathrel{=}\;\Varid{sup}\;(\Varid{inl}\;\Varid{p},\lambda\;\Varid{i}\;()){}\<[E]%
+\\
+\>[B]{}\Varid{pathk}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{J}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{S}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{P}^{\Conid{I}}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{P}^{\Conid{J}}\mskip1.5mu\}\;\{\mskip1.5mu \Varid{i}\mskip1.5mu\}\;\{\mskip1.5mu \Varid{s}\mskip1.5mu\}\;\{\mskip1.5mu \Varid{f}\mskip1.5mu\}\;\{\mskip1.5mu \Varid{j}\mskip1.5mu\}\;(\Varid{inr}\;(\Varid{i′′},(\Varid{q},\Varid{r})))\;\mathrel{=}\;\Varid{sup}\;((\Varid{inr}\;(\Varid{i′′},\Varid{q})),\Varid{sub}){}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Keyword{where}\;\Varid{sub}\;\in\;(\Varid{iw}\;\in\;\Sigma\;\Conid{I}\;(\Conid{WI}\;\Conid{S}\;\Conid{P}^{\Conid{I}}))\;\rightarrow\;{}\<[E]%
+\\
+\>[3]{}\hsindent{15}{}\<[18]%
+\>[18]{}(\Varid{i′′}\;\equiv\;\pi_{0}\;\Varid{iw})\;\times\;(\Varid{f}\;\Varid{i′′}\;\Varid{q}\;\cong\;\pi_{1}\;\Varid{iw})\;\rightarrow\;\Conid{Pathk}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\;\Conid{P}^{\Conid{J}}\;(\pi_{0}\;\Varid{iw})\;(\pi_{1}\;\Varid{iw})\;\Varid{j}{}\<[E]%
+\\
+\>[3]{}\hsindent{6}{}\<[9]%
+\>[9]{}\Varid{sub}\;(\Varid{i′},\Varid{w′})\;(\Varid{eqi},\Varid{eqw})\;\mathrel{=}\;\Varid{subst}\;(\Conid{WI}\;\anonymous \;\anonymous )\;(\Varid{cong₂}\;\anonymous ,\anonymous \;\Varid{eqi}\;\Varid{eqw})\;\Varid{r}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\subsection{\ensuremath{\Conid{M}} from \ensuremath{\Conid{W}}}
+Since we have shown that both \ensuremath{\Conid{WI}} and \ensuremath{\Conid{MI}} types can be reduced to their 
+non-indexed counterparts, it only remains to show that \ensuremath{\Conid{M}} types can be, reduced
+to \ensuremath{\Conid{W}} types. This is a result from \cite{C-CSPTs}, though in the setting of 
+indexed \ensuremath{\Conid{WI}} types, we can give a better intuition.
+
+In category therory, an $\omega$-chain, is an infinite diagram:
+
+\[
+\xymatrix{
+\ensuremath{\Conid{A}}_{0} &
+\ar[l]_{\ensuremath{\Varid{a}}_{0}}
+\ensuremath{\Conid{A}}_{1} &
+\ar[l]_{\ensuremath{\Varid{a}}_{1}}
+\ensuremath{\Conid{A}}_{2} &
+\cdots &
+\ensuremath{\Conid{A}}_{n-1} &
+\ar[l]_{\ensuremath{\Varid{a}}_{n-1}} 
+\ensuremath{\Conid{A}}_{n} &
+\ar[l]_{\ensuremath{\Varid{a}}_{n}} 
+\ensuremath{\Conid{A}}_{n+1} &
+\cdots} 
+\]
+
+In type-theroy, we can represent such a chain, as a pair of functions:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Conid{Chain}\;\in\;\Conid{Set₁}{}\<[E]%
+\\
+\>[B]{}\Conid{Chain}\;\mathrel{=}\;\Sigma\;(\Conid{ℕ}\;\rightarrow\;\Conid{Set})\;\lambda\;\Conid{A}\;\rightarrow\;(\Varid{n}\;\in\;\Conid{ℕ})\;\rightarrow\;\Conid{A}\;(\Varid{suc}\;\Varid{n})\;\rightarrow\;\Conid{A}\;\Varid{n}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+The limit of a chain is an object \ensuremath{\Conid{X}} and family of projections 
+$\pi_{n} \in \mbox{\ensuremath{\Conid{X}}} → \mbox{\ensuremath{\Conid{A}}}_{n}$ such that in the following diagram, 
+all the small triangles commute:
+
+\[
+\xymatrix{
+\ensuremath{\Conid{A}}_{\ensuremath{\Varid{0}}} &
+\ar[l]_{\ensuremath{\Varid{a}}_{\ensuremath{\Varid{0}}}}
+\ensuremath{\Conid{A}}_{1} &
+\ar[l]_{\ensuremath{\Varid{a}}_{\ensuremath{\Varid{1}}}}
+\ensuremath{\Conid{A}}_{2} &
+\cdots &
+\ensuremath{\Conid{A}}_{n-\ensuremath{\Varid{1}}} &
+\ar[l]_{\ensuremath{\Varid{a}}_{n-1}} 
+\ensuremath{\Conid{A}}_{n} &
+\ar[l]_{\ensuremath{\Varid{a}}_{n}} 
+\ensuremath{\Conid{A}}_{n+\ensuremath{\Varid{1}}} &
+\cdots
+\\
+\\
+& & & & 
+\ensuremath{\Conid{X}}
+\ar[uullll]_{\pi_{\ensuremath{\Varid{0}}}}
+\ar[uulll]_{\pi_{\ensuremath{\Varid{1}}}}
+\ar[uull]_{\pi_{\ensuremath{\Varid{2}}}}
+\ar[uu]_{\pi_{n - \ensuremath{\Varid{1}}}}
+\ar[uur]_{\pi_{n}}
+\ar[uurr]_{\pi_{n + \ensuremath{\Varid{1}}}}
+&&&\\
+} 
+\]
+
+It is also required that the limit is the least such cone. 
+Again, we can encode the limit of a chain, its projections, and this universal 
+property in type theory:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{8}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Conid{LIM}\;\in\;\Conid{Chain}\;\rightarrow\;\Conid{Set}{}\<[E]%
+\\
+\>[B]{}\Conid{LIM}\;(\Conid{A},\Varid{a})\;\mathrel{=}\;\Sigma\;((\Varid{n}\;\in\;\Conid{ℕ})\;\rightarrow\;\Conid{A}\;\Varid{n})\;\lambda\;\Varid{f}\;\rightarrow\;((\Varid{n}\;\in\;\Conid{ℕ})\;\rightarrow\;\Varid{a}\;\Varid{n}\;(\Varid{f}\;(\Varid{suc}\;\Varid{n}))\;\equiv\;\Varid{f}\;\Varid{n}){}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\pi\;\in\;\{\mskip1.5mu \Varid{c}\;\in\;\Conid{Chain}\mskip1.5mu\}\;\rightarrow\;(\Varid{n}\;\in\;\Conid{ℕ})\;\rightarrow\;\Conid{LIM}\;\Varid{c}\;\rightarrow\;\pi_{0}\;\Varid{c}\;\Varid{n}{}\<[E]%
+\\
+\>[B]{}\pi\;\Varid{n}\;(\Varid{f},\Varid{p})\;\mathrel{=}\;\Varid{f}\;\Varid{n}{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\Varid{comm}\;\in\;\{\mskip1.5mu \Varid{c}\;\in\;\Conid{Chain}\mskip1.5mu\}\;(\Varid{n}\;\in\;\Conid{ℕ})\;(\Varid{l}\;\in\;\Conid{LIM}\;\Varid{c})\;\rightarrow\;\pi_{1}\;\Varid{c}\;\Varid{n}\;(\pi\;\{\mskip1.5mu \Varid{c}\mskip1.5mu\}\;(\Varid{suc}\;\Varid{n})\;\Varid{l})\;\equiv\;\pi\;\{\mskip1.5mu \Varid{c}\mskip1.5mu\}\;\Varid{n}\;\Varid{l}{}\<[E]%
+\\
+\>[B]{}\Varid{comm}\;\Varid{n}\;(\Varid{f},\Varid{p})\;\mathrel{=}\;\Varid{p}\;\Varid{n}{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\Varid{univ}\;\in\;\{\mskip1.5mu \Varid{c}\;\in\;\Conid{Chain}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{X}\;\in\;\Conid{Set}\mskip1.5mu\}\;(\Varid{pro}\;\in\;(\Varid{n}\;\in\;\Conid{ℕ})\;\rightarrow\;\Conid{X}\;\rightarrow\;\pi_{0}\;\Varid{c}\;\Varid{n})\;{}\<[E]%
+\\
+\>[B]{}\hsindent{8}{}\<[8]%
+\>[8]{}(\Varid{com}\;\in\;(\Varid{n}\;\in\;\Conid{ℕ})\;(\Varid{x}\;\in\;\Conid{X})\;\rightarrow\;\pi_{1}\;\Varid{c}\;\Varid{n}\;(\Varid{pro}\;(\Varid{suc}\;\Varid{n})\;\Varid{x})\;\equiv\;\Varid{pro}\;\Varid{n}\;\Varid{x})\;\rightarrow\;{}\<[E]%
+\\
+\>[B]{}\hsindent{8}{}\<[8]%
+\>[8]{}\Conid{X}\;\rightarrow\;\Conid{LIM}\;\Varid{c}{}\<[E]%
+\\
+\>[B]{}\Varid{univ}\;\Varid{pro}\;\Varid{com}\;\Varid{x}\;\mathrel{=}\;(\lambda\;\Varid{n}\;\rightarrow\;\Varid{pro}\;\Varid{n}\;\Varid{x}),(\lambda\;\Varid{n}\;\rightarrow\;\Varid{com}\;\Varid{n}\;\Varid{x}){}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+Given a functor \ensuremath{\Conid{F}}, we can build a chain:
+
+\[
+\xymatrix{
+\ensuremath{\top} &
+\ar[l]_{\ensuremath{\mathbin{!}}}
+\ensuremath{\Conid{F}} \ensuremath{\top} &
+\ar[l]_{\ensuremath{\Conid{F}} \ensuremath{\mathbin{!}}}
+\ensuremath{\Conid{F}}^{\ensuremath{\Varid{2}}} \ensuremath{\top} &
+\ar[l]_{\ensuremath{\Conid{F}}^{\ensuremath{\Varid{2}}} \ensuremath{\mathbin{!}}}
+\ensuremath{\Conid{F}}^{\ensuremath{\Varid{3}}} \ensuremath{\top} &
+\cdots &
+} 
+\]
+
+\noindent
+For the moment denote this chain \ensuremath{\Conid{F}\;\!^{\omega}\;\mathrel{=}\;((\lambda\;\Varid{n}\;\rightarrow\;\Conid{F}\;\!^{\Varid{n}}\;\top),\lambda\;\Varid{n}\;\rightarrow\;\Conid{F}\;\!^{\Varid{n}}\;\mathbin{!})}.
+We know from Asperti and Longo \cite{AspertiLongo} that if \ensuremath{\Conid{F}} is 
+$\omega$-continuous, \emph{i.e.} that for any chain \ensuremath{(\Conid{A},\Varid{a})}:
+
+\ensuremath{\Conid{F}\;(\Conid{LIM}\;(\Conid{A},\Varid{a}))\;\cong\;\Conid{LIM}\;((\Conid{F}\;\ensuremath{\mbox{$\circ$}}\;\Conid{A}),(\Conid{F}\;\ensuremath{\mbox{$\circ$}}\;\Varid{a}))}
+
+\noindent
+then the limit of \ensuremath{\Conid{Fo}} will be the terminal co-algebra of \ensuremath{\Conid{F}}.
+
+To see this we first observe that there exists an isomorphism between 
+\ensuremath{\Conid{LIM}\;(\Conid{A},\Varid{a})} and \ensuremath{\Conid{LIM}\;(\Conid{A}\;\ensuremath{\mbox{$\circ$}}\;\Varid{suc},\Varid{a}\;\ensuremath{\mbox{$\circ$}}\;\Varid{suc})}:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{9}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Varid{tailC}\;\in\;(\Varid{c}\;\in\;\Conid{Chain})\;\rightarrow\;\Conid{LIM}\;\Varid{c}\;\rightarrow\;\Conid{LIM}\;(\pi_{0}\;\Varid{c}\;\ensuremath{\mbox{$\circ$}}\;\Varid{suc},\pi_{1}\;\Varid{c}\;\ensuremath{\mbox{$\circ$}}\;\Varid{suc}){}\<[E]%
+\\
+\>[B]{}\Varid{tailC}\;(\Conid{A},\Varid{a})\;(\Varid{f},\Varid{p})\;\mathrel{=}\;\Varid{f}\;\ensuremath{\mbox{$\circ$}}\;\Varid{suc},\Varid{p}\;\ensuremath{\mbox{$\circ$}}\;\Varid{suc}{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\Varid{tailC⁻¹}\;\in\;(\Varid{c}\;\in\;\Conid{Chain})\;\rightarrow\;\Conid{LIM}\;(\pi_{0}\;\Varid{c}\;\ensuremath{\mbox{$\circ$}}\;\Varid{suc},\pi_{1}\;\Varid{c}\;\ensuremath{\mbox{$\circ$}}\;\Varid{suc})\;\rightarrow\;\Conid{LIM}\;\Varid{c}{}\<[E]%
+\\
+\>[B]{}\Varid{tailC⁻¹}\;(\Conid{A},\Varid{a})\;(\Varid{f},\Varid{p})\;\mathrel{=}\;\Varid{f′},\Varid{p′}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Keyword{where}\;\Varid{f′}\;\in\;(\Varid{n}\;\in\;\Conid{ℕ})\;\rightarrow\;\Conid{A}\;\Varid{n}{}\<[E]%
+\\
+\>[3]{}\hsindent{6}{}\<[9]%
+\>[9]{}\Varid{f′}\;\Varid{zero}\;\mathrel{=}\;\Varid{a}\;\anonymous \;(\Varid{f}\;\Varid{zero}){}\<[E]%
+\\
+\>[3]{}\hsindent{6}{}\<[9]%
+\>[9]{}\Varid{f′}\;(\Varid{suc}\;\Varid{n})\;\mathrel{=}\;\Varid{f}\;\Varid{n}{}\<[E]%
+\\
+\>[3]{}\hsindent{6}{}\<[9]%
+\>[9]{}\Varid{p′}\;\in\;(\Varid{n}\;\in\;\Conid{ℕ})\;\rightarrow\;\Varid{a}\;\anonymous \;(\Varid{f}\;\Varid{n})\;\cong\;\Varid{f′}\;\Varid{n}{}\<[E]%
+\\
+\>[3]{}\hsindent{6}{}\<[9]%
+\>[9]{}\Varid{p′}\;\Varid{zero}\;\mathrel{=}\;\Varid{refl}{}\<[E]%
+\\
+\>[3]{}\hsindent{6}{}\<[9]%
+\>[9]{}\Varid{p′}\;(\Varid{suc}\;\Varid{n})\;\mathrel{=}\;\Varid{p}\;\Varid{n}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\noindent 
+this allows us to construct the isomorphism between \ensuremath{\Conid{F}\;(\Conid{LIM}\;\Conid{F}\;\!^{\omega})} and 
+\ensuremath{\Conid{LIM}\;\Conid{F}\;\!^{\omega}}:
+
+\begin{align*}
+&&& \ensuremath{\Conid{F}\;(\Conid{LIM}\;\Conid{F}\;\!^{\omega})} & \\
+&\cong&& \ensuremath{\Conid{LIM}\;(\Conid{F}\;\ensuremath{\mbox{$\circ$}}\;(\lambda\;\Varid{n}\;\rightarrow\;\Conid{F}\;\!^{\Varid{n}}\;\top),\Conid{F}\;\ensuremath{\mbox{$\circ$}}\;(\lambda\;\Varid{n}\;\rightarrow\;\Conid{F}\;\!^{\Varid{n}}\;\mathbin{!}))} & \{\mbox{\ensuremath{\Conid{F}} is $\omega$-continuous}\} \\
+&\equiv&& \ensuremath{\Conid{LIM}\;((\lambda\;\Varid{n}\;\rightarrow\;\Conid{F}\;\!^{\Varid{suc}\Varid{n}}\;\top),(\lambda\;\Varid{n}\;\rightarrow\;\Conid{F}\;\!^{\Varid{suc}\Varid{n}}\;\mathbin{!}))} & \{\mbox{definition}\}\\
+&\cong&& \ensuremath{\Conid{LIM}\;\Conid{F}\;\!^{\omega}} & \{\mbox{ \ensuremath{\Varid{tailC}} }\} \\
+\end{align*}
+
+This isomorphism is witnessed from right to left by the co-algebra map \ensuremath{\Varid{out}}.
+To show that the co-algebra is terminal, we employ the universal property of
+\ensuremath{\Conid{LIM}}. Given a co-algebra for \ensuremath{\alpha\;\in\;\Conid{X}\;\rightarrow\;\Conid{F}\;\Conid{X}} we construct an \ensuremath{\Conid{F}\;\!^{\omega}} cone:
+
+\[
+\xymatrix{
+\ensuremath{\top} &
+\ar[l]_{\ensuremath{\mathbin{!}}}
+\ensuremath{\Conid{F}} \ensuremath{\top} &
+\ar[l]_{\ensuremath{\Conid{F}} \ensuremath{\mathbin{!}}}
+\ensuremath{\Conid{F}}^{2} \ensuremath{\top} &
+\ar[l]_{\ensuremath{\Conid{F}}^{\ensuremath{\Varid{2}}} \ensuremath{\mathbin{!}}}
+\ensuremath{\Conid{F}}^{3} \ensuremath{\top} &
+\cdots & \\
+\ensuremath{\Conid{X}} 
+\ar[u]_{\ensuremath{\mathbin{!}}}
+\ar[r]_{\ensuremath{\Varid{f}}} &
+\ensuremath{\Conid{F}} \ensuremath{\Conid{X}} 
+\ar[u]_{\ensuremath{\Conid{F}} \ensuremath{\mathbin{!}}}
+\ar[r]_{\ensuremath{\Conid{F}} \ensuremath{\Varid{f}}} &
+\ensuremath{\Conid{F}}^{2} \ensuremath{\Conid{X}}
+\ar[u]_{\ensuremath{\Conid{F}}^{\ensuremath{\Varid{2}}} \ensuremath{\mathbin{!}}} 
+\ar[r]_{\ensuremath{\Conid{F}}^{\ensuremath{\Varid{2}}} \ensuremath{\Varid{f}}} &
+\ensuremath{\Conid{F}}^{3} \ensuremath{\Conid{X}}
+\ar[u]_{\ensuremath{\Conid{F}}^{\ensuremath{\Varid{3}}} \ensuremath{\mathbin{!}}} 
+ &
+\cdots \\
+}
+\]
+
+We 
+want to build \ensuremath{\Conid{M}}-types, which we know to be the terminal co-algebras of 
+container functors. In order to do this, we must construct 
+iteration of container functors (to build the chain) and show that all container
+functors are $\omega$ continuous.
+
+Since we only need to build iterations of container functors applied to the 
+terminal object \ensuremath{\top}, we build that directly. We define the following variation 
+of \ensuremath{\Conid{W}}, cut off at a know depth:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Keyword{data}\;\Conid{WM}\;(\Conid{S}\;\in\;\Conid{Set})\;(\Conid{P}\;\in\;\Conid{S}\;\rightarrow\;\Conid{Set})\;\in\;\Conid{ℕ}\;\rightarrow\;\Conid{Set}\;\Keyword{where}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{wm⊤}\;\in\;\Conid{WM}\;\Conid{S}\;\Conid{P}\;\Varid{zero}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{sup}\;\in\;\forall{}\;\{\mskip1.5mu \Varid{n}\mskip1.5mu\}\;\rightarrow\;\!\;\Varid{⟦}\;\Conid{S}\;\lhd\;\Conid{P}\;\Varid{⟧}\;(\Conid{WM}\;\Conid{S}\;\Conid{P}\;\Varid{n})\;\rightarrow\;\Conid{WM}\;\Conid{S}\;\Conid{P}\;(\Varid{suc}\;\Varid{n}){}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\noindent
+It should be obvious that \ensuremath{\Conid{WM}\;\Varid{zero}} is indeed terminal in \ensuremath{\Conid{Set}} and that 
+\ensuremath{\Varid{⟦}\;\Conid{S}\;\lhd\;\Conid{P}\;\Varid{⟧}\;(\Conid{WM}\;\Conid{S}\;\Conid{P}\;\Varid{n})\;\cong\;\Conid{WM}\;\Conid{S}\;\Conid{P}\;(\Varid{suc}\;\Varid{n})}, so upto to isomorphism, this just the
+thing we need to construct \ensuremath{\Varid{⟦}\;\Conid{S}\;\lhd\;\Conid{P}\;\Varid{⟧}}$^{\omega}$.
+
+Note that \ensuremath{\Conid{WM}} is itself encodable as an indexed \ensuremath{\Conid{WI}} type, and by the result 
+above, a \ensuremath{\Conid{W}} type:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{5}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Conid{WM′}\;\in\;(\Conid{S}\;\in\;\Conid{Set})\;(\Conid{P}\;\in\;\Conid{S}\;\rightarrow\;\Conid{Set})\;\rightarrow\;\Conid{ℕ}\;\rightarrow\;\Conid{Set}{}\<[E]%
+\\
+\>[B]{}\Conid{WM′}\;\Conid{S}\;\Conid{P}\;\mathrel{=}\;\Conid{WI}\;\Conid{S′}\;\Conid{P′}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Keyword{where}{}\<[E]%
+\\
+\>[3]{}\hsindent{2}{}\<[5]%
+\>[5]{}\Conid{S′}\;\in\;\Conid{ℕ}\;\rightarrow\;\Conid{Set}{}\<[E]%
+\\
+\>[3]{}\hsindent{2}{}\<[5]%
+\>[5]{}\Conid{S′}\;\Varid{zero}\;\mathrel{=}\;\top{}\<[E]%
+\\
+\>[3]{}\hsindent{2}{}\<[5]%
+\>[5]{}\Conid{S′}\;(\Varid{suc}\;\Varid{n})\;\mathrel{=}\;\Conid{S}{}\<[E]%
+\\
+\>[3]{}\hsindent{2}{}\<[5]%
+\>[5]{}\Conid{P′}\;\in\;(\Varid{n}\;\in\;\Conid{ℕ})\;\rightarrow\;\Conid{S′}\;\Varid{n}\;\rightarrow\;\Conid{ℕ}\;\rightarrow\;\Conid{Set}{}\<[E]%
+\\
+\>[3]{}\hsindent{2}{}\<[5]%
+\>[5]{}\Conid{P′}\;\Varid{zero}\;\anonymous \;\anonymous \;\mathrel{=}\;\bot{}\<[E]%
+\\
+\>[3]{}\hsindent{2}{}\<[5]%
+\>[5]{}\Conid{P′}\;(\Varid{suc}\;\Varid{m})\;\Varid{s}\;\Varid{n}\;\Keyword{with}\;\Varid{m}\;\Varid{≟}\;\Varid{n}{}\<[E]%
+\\
+\>[3]{}\hsindent{2}{}\<[5]%
+\>[5]{}\Conid{P′}\;(\Varid{suc}\;\Varid{.n})\;\Varid{s}\;\Varid{n}\;\mid \;\Varid{yes}\;\Varid{refl}\;\mathrel{=}\;\Conid{P}\;\Varid{s}{}\<[E]%
+\\
+\>[3]{}\hsindent{2}{}\<[5]%
+\>[5]{}\Conid{P′}\;(\Varid{suc}\;\Varid{m})\;\Varid{s}\;\Varid{n}\;\mid \;\Varid{no}\;\Varid{¬p}\;\mathrel{=}\;\bot{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\noindent
+We can truncate any given tree of depth greater than 1, this amounts to the 
+iteration of the morphism part of the container functor applied to the unique 
+moprhism into the terminal object:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Varid{trunc}\;\in\;\forall{}\;\{\mskip1.5mu \Conid{S}\;\Conid{P}\mskip1.5mu\}\;\rightarrow\;(\Varid{n}\;\in\;\Conid{ℕ})\;\rightarrow\;\Conid{WM}\;\Conid{S}\;\Conid{P}\;(\Varid{suc}\;\Varid{n})\;\rightarrow\;\Conid{WM}\;\Conid{S}\;\Conid{P}\;\Varid{n}{}\<[E]%
+\\
+\>[B]{}\Varid{trunc}\;\Varid{zero}\;(\Varid{sup}\;(\Varid{s},\Varid{f}))\;\mathrel{=}\;\Varid{wm⊤}{}\<[E]%
+\\
+\>[B]{}\Varid{trunc}\;(\Varid{suc}\;\Varid{n})\;(\Varid{sup}\;(\Varid{s},\Varid{f}))\;\mathrel{=}\;\Varid{sup}\;(\Varid{s},\Varid{trunc}\;\Varid{n}\;\ensuremath{\mbox{$\circ$}}\;\Varid{f}){}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+So now we can build the chain of finitie itererations of a container functor:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Conid{M-chain}\;\in\;(\Conid{S}\;\in\;\Conid{Set})\;(\Conid{P}\;\in\;\Conid{S}\;\rightarrow\;\Conid{Set})\;\rightarrow\;\Conid{Chain}{}\<[E]%
+\\
+\>[B]{}\Conid{M-chain}\;\Conid{S}\;\Conid{P}\;\mathrel{=}\;\Conid{WM}\;\Conid{S}\;\Conid{P},\Varid{trunc}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\begin{proposition}
+All container functors are $\omega$-continuous. That is, they preserve 
+$\omega$-limits.
+\end{proposition}
+
+\begin{proof}
+We want to build the isomorphism 
+\ensuremath{\Conid{F}\;(\Conid{LIM}\;(\Conid{A},\Varid{a}))\;\cong\;\Conid{LIM}\;((\Conid{F}\;\ensuremath{\mbox{$\circ$}}\;\Conid{A}),\Conid{F}\;\ensuremath{\mbox{$\circ$}}\;\Varid{a})} in the case that \ensuremath{\Conid{F}}
+is a container functor. However, the function from left to right is uniquely 
+given by the universal property of \ensuremath{\Conid{LIM}} for all functors \ensuremath{\Conid{F}\;\in\;\Conid{Set}\;\rightarrow\;\Conid{Set}}. 
+To show this we build the cone for the chain \ensuremath{((\Conid{F}\;\ensuremath{\mbox{$\circ$}}\;\Conid{A}),\Conid{F}\;\ensuremath{\mbox{$\circ$}}\;\Varid{a})}:
+
+\[
+\xymatrix{
+\ensuremath{\Conid{F}} \ensuremath{\Conid{A}}_{0} &
+\ar[l]_{\ensuremath{\Conid{F}} \ensuremath{\Varid{a}}_{0}}
+\ensuremath{\Conid{F}} \ensuremath{\Conid{A}}_{1} &
+\ar[l]_{\ensuremath{\Conid{F}} \ensuremath{\Varid{a}}_{1}}
+\ensuremath{\Conid{F}} \ensuremath{\Conid{A}}_{2} &
+\cdots &
+\ensuremath{\Conid{F}} \ensuremath{\Conid{A}}_{n-1} &
+\ar[l]_{\ensuremath{\Conid{F}} \ensuremath{\Varid{a}}_{n-1}} 
+\ensuremath{\Conid{F}} \ensuremath{\Conid{A}}_{n} &
+\cdots
+\\
+\\
+& & &  
+\ensuremath{\Conid{F}\;(\Conid{LIM}\;(\Conid{A},\Varid{a}))}
+\ar[uulll]^{\ensuremath{\Conid{F}} \pi_{0}}
+\ar[uull]_{\ensuremath{\Conid{F}} \pi_{1}}
+\ar[uul]_{\ensuremath{\Conid{F}} \pi_{2}}
+\ar[uur]_{\ensuremath{\Conid{F}} \pi_{n-1}}
+\ar[uurr]_{\ensuremath{\Conid{F}} \pi_{n}}
+&&&\\
+} 
+\]
+
+\noindent
+The small triangles in the diagram above obviously commute, so there exists a 
+unique morphism from \ensuremath{\Conid{F}\;(\Conid{LIM}\;(\Conid{A},\Varid{a}))} into 
+\ensuremath{\Conid{LIM}\;((\Conid{F}\;\ensuremath{\mbox{$\circ$}}\;\Conid{A}),\Conid{F}\;\ensuremath{\mbox{$\circ$}}\;\Varid{a})}.
+All that remains then, is to construct an inverse to this unique morphism, in 
+the case that \ensuremath{\Conid{F}\;\equiv\;\Varid{⟦}\;\Conid{S}\;\lhd\;\Conid{P}\;\Varid{⟧}}, that is we must build a function:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{11}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{13}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{18}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{21}{@{}>{\hspre}c<{\hspost}@{}}%
+\column{21E}{@{}l@{}}%
+\column{24}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{51}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[3]{}\omega\Varid{-cont}\;\in\;{}\<[13]%
+\>[13]{}\Conid{LIM}\;{}\<[18]%
+\>[18]{}({}\<[21]%
+\>[21]{}({}\<[21E]%
+\>[24]{}\lambda\;\Varid{n}\;\rightarrow\;\Sigma\;\Conid{S}\;\lambda\;\Varid{s}\;\rightarrow\;\Conid{P}\;\Varid{s}\;\rightarrow\;\Conid{A}\;\Varid{n}){}\<[E]%
+\\
+\>[18]{},{}\<[24]%
+\>[24]{}\lambda\;\Varid{n}\;\rightarrow\;\lambda (\!\;\Varid{s}\;\!,\!\;\Varid{f}\;\!\!)\;\rightarrow\;{}\<[51]%
+\>[51]{}(\Varid{s},\Varid{a}\;\Varid{n}\;\ensuremath{\mbox{$\circ$}}\;\Varid{f})\;\!\;\!{}\<[E]%
+\\
+\>[18]{})\;{}\<[E]%
+\\
+\>[3]{}\hsindent{8}{}\<[11]%
+\>[11]{}\rightarrow\;(\Sigma\;\Conid{S}\;\lambda\;\Varid{s}\;\rightarrow\;\Conid{P}\;\Varid{s}\;\rightarrow\;(\Conid{LIM}\;(\Conid{A},\Varid{a}))){}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+Note that the shape picked at every point along the chain must be the same, in 
+order to make the diagrams commute. This is the key insight
+into constructing this function.
+
+\end{proof}
+
+We now entitled to derive \ensuremath{\Conid{M}} types from \ensuremath{\Conid{W}} by defining:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Conid{M}\;\in\;(\Conid{S}\;\in\;\Conid{Set})\;(\Conid{P}\;\in\;\Conid{S}\;\rightarrow\;\Conid{Set})\;\rightarrow\;\Conid{Set}{}\<[E]%
+\\
+\>[B]{}\Conid{M}\;\Conid{S}\;\Conid{P}\;\mathrel{=}\;\Conid{LIM}\;(\Conid{M-chain}\;\Conid{S}\;\Conid{P}){}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+%%Strictly Positive Families
+
+\section{Strictly Positive Families}
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{5}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{12}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{20}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{46}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{47}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Keyword{mutual}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Conid{SPF}\;\in\;(\Conid{I}\;\Conid{J}\;\in\;\Conid{Set})\;\rightarrow\;\Conid{Set₁}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Conid{SPF}\;\Conid{I}\;\Conid{J}\;\mathrel{=}\;\Conid{J}\;\rightarrow\;\Conid{ISPT}\;\Conid{I}{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Keyword{data}\;\Conid{ISPT}\;(\Conid{I}\;\in\;\Conid{Set})\;\in\;\Conid{Set₁}\;\Keyword{where}{}\<[E]%
+\\
+\>[3]{}\hsindent{2}{}\<[5]%
+\>[5]{}\eta^{\text{\tiny T}}\;\in\;{}\<[20]%
+\>[20]{}(\Varid{i}\;\in\;\Conid{I})\;{}\<[47]%
+\>[47]{}\rightarrow\;\Conid{ISPT}\;\Conid{I}{}\<[E]%
+\\
+\>[3]{}\hsindent{2}{}\<[5]%
+\>[5]{}\Delta^{\text{\tiny T}}\;\in\;\forall{}\;\{\mskip1.5mu \Conid{J}\;\Conid{K}\mskip1.5mu\}\;{}\<[20]%
+\>[20]{}(\Varid{f}\;\in\;\Conid{J}\;\rightarrow\;\Conid{K})\;(\Conid{F}\;\in\;\Conid{SPF}\;\Conid{I}\;\Conid{K})\;{}\<[47]%
+\>[47]{}\rightarrow\;\Conid{SPF}\;\Conid{I}\;\Conid{J}{}\<[E]%
+\\
+\>[3]{}\hsindent{2}{}\<[5]%
+\>[5]{}\Sigma^{\text{\tiny T}}\;\in\;\forall{}\;\{\mskip1.5mu \Conid{J}\;\Conid{K}\mskip1.5mu\}\;{}\<[20]%
+\>[20]{}(\Varid{f}\;\in\;\Conid{J}\;\rightarrow\;\Conid{K})\;(\Conid{F}\;\in\;\Conid{SPF}\;\Conid{I}\;\Conid{J})\;{}\<[47]%
+\>[47]{}\rightarrow\;\Conid{SPF}\;\Conid{I}\;\Conid{K}{}\<[E]%
+\\
+\>[3]{}\hsindent{2}{}\<[5]%
+\>[5]{}\Pi^{\text{\tiny T}}\;\in\;\forall{}\;\{\mskip1.5mu \Conid{J}\;\Conid{K}\mskip1.5mu\}\;{}\<[20]%
+\>[20]{}(\Varid{f}\;\in\;\Conid{J}\;\rightarrow\;\Conid{K})\;(\Conid{F}\;\in\;\Conid{SPF}\;\Conid{I}\;\Conid{J})\;{}\<[47]%
+\>[47]{}\rightarrow\;\Conid{SPF}\;\Conid{I}\;\Conid{K}{}\<[E]%
+\\
+\>[3]{}\hsindent{2}{}\<[5]%
+\>[5]{}\mu^{\text{\tiny T}}\;\in\;\forall{}\;\{\mskip1.5mu \Conid{J}\mskip1.5mu\}\;{}\<[20]%
+\>[20]{}(\Conid{F}\;\in\;\Conid{SPF}\;(\Conid{I}\;\uplus\;\Conid{J})\;\Conid{J})\;{}\<[47]%
+\>[47]{}\rightarrow\;\Conid{SPF}\;\Conid{I}\;\Conid{J}{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\anonymous \bind ^{\text{\tiny T}}\anonymous \;\in\;\forall{}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\mskip1.5mu\}\;\rightarrow\;\Conid{ISPT}\;\Conid{I}\;\rightarrow\;\Conid{SPF}\;\Conid{J}\;\Conid{I}\;\rightarrow\;\Conid{ISPT}\;\Conid{J}{}\<[E]%
+\\
+\>[B]{}\eta^{\text{\tiny T}}\;\Varid{i}\;{}\<[12]%
+\>[12]{}\bind ^{\text{\tiny T}}\;\Conid{F}\;\mathrel{=}\;\Conid{F}\;\Varid{i}{}\<[E]%
+\\
+\>[B]{}\Delta^{\text{\tiny T}}\;\Varid{f}\;\Conid{G}\;\Varid{j}\;{}\<[12]%
+\>[12]{}\bind ^{\text{\tiny T}}\;\Conid{F}\;\mathrel{=}\;\Delta^{\text{\tiny T}}\;\Varid{f}\;(\lambda\;\Varid{k}\;\rightarrow\;\Conid{G}\;\Varid{k}\;\bind ^{\text{\tiny T}}\;\Conid{F})\;\Varid{j}{}\<[E]%
+\\
+\>[B]{}\Sigma^{\text{\tiny T}}\;\Varid{f}\;\Conid{G}\;\Varid{k}\;{}\<[12]%
+\>[12]{}\bind ^{\text{\tiny T}}\;\Conid{F}\;\mathrel{=}\;\Sigma^{\text{\tiny T}}\;\Varid{f}\;(\lambda\;\Varid{j}\;\rightarrow\;\Conid{G}\;\Varid{j}\;\bind ^{\text{\tiny T}}\;\Conid{F})\;\Varid{k}{}\<[E]%
+\\
+\>[B]{}\Pi^{\text{\tiny T}}\;\Varid{f}\;\Conid{G}\;\Varid{k}\;{}\<[12]%
+\>[12]{}\bind ^{\text{\tiny T}}\;\Conid{F}\;\mathrel{=}\;\Pi^{\text{\tiny T}}\;\Varid{f}\;(\lambda\;\Varid{j}\;\rightarrow\;\Conid{G}\;\Varid{j}\;\bind ^{\text{\tiny T}}\;\Conid{F})\;\Varid{k}{}\<[E]%
+\\
+\>[B]{}\mu^{\text{\tiny T}}\;\Conid{G}\;\Varid{j}\;{}\<[12]%
+\>[12]{}\bind ^{\text{\tiny T}}\;\Conid{F}\;\mathrel{=}\;\mu^{\text{\tiny T}}\;(\lambda\;\Varid{k}\;\rightarrow\;\Conid{G}\;\Varid{k}\;\bind ^{\text{\tiny T}}\;[\mskip1.5mu {}\<[46]%
+\>[46]{}(\lambda\;\Varid{i}\;\rightarrow\;\Conid{F}\;\Varid{i}\;\bind ^{\text{\tiny T}}\;(\eta^{\text{\tiny T}}\;\ensuremath{\mbox{$\circ$}}\;\Varid{inl})),(\eta^{\text{\tiny T}}\;\ensuremath{\mbox{$\circ$}}\;\Varid{inr})\mskip1.5mu])\;\Varid{j}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{20}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Keyword{mutual}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{⟦}\anonymous \Varid{⟧}^{\text{\tiny T}\star}\;\in\;\forall{}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\mskip1.5mu\}\;\rightarrow\;\Conid{SPF}\;\Conid{I}\;\Conid{J}\;\rightarrow\;\Conid{ICont}^{\star}\;\Conid{I}\;\Conid{J}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{⟦}\;\Conid{F}\;\Varid{⟧}^{\text{\tiny T}\star}\;\mathrel{=}\;\!\!\;\lambda\;\Varid{j}\;\rightarrow\;\Varid{⟦}\;\Conid{F}\;\Varid{j}\;\Varid{⟧}^{\text{\tiny T}}{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{⟦}\anonymous \Varid{⟧}^{\text{\tiny T}}\;\in\;\forall{}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\rightarrow\;\Conid{ISPT}\;\Conid{I}\;\rightarrow\;\Conid{ICont}\;\Conid{I}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{⟦}\;\eta^{\text{\tiny T}}\;\Varid{i}\;\Varid{⟧}^{\text{\tiny T}}\;{}\<[20]%
+\>[20]{}\mathrel{=}\;\eta^{\text{\tiny C}}\;\Varid{i}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{⟦}\;\Delta^{\text{\tiny T}}\;\Varid{f}\;\Conid{F}\;\Varid{j}\;\Varid{⟧}^{\text{\tiny T}}\;{}\<[20]%
+\>[20]{}\mathrel{=}\;\!\;\!\!\;\Delta^{\text{\tiny C}}\;\Varid{f}\;\Varid{⟦}\;\Conid{F}\;\Varid{⟧}^{\text{\tiny T}\star}\;\!\!\;\Varid{j}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{⟦}\;\Sigma^{\text{\tiny T}}\;\Varid{f}\;\Conid{F}\;\Varid{k}\;\Varid{⟧}^{\text{\tiny T}}\;{}\<[20]%
+\>[20]{}\mathrel{=}\;\!\;\!\!\;\Sigma^{\text{\tiny C}}\;\Varid{f}\;\Varid{⟦}\;\Conid{F}\;\Varid{⟧}^{\text{\tiny T}\star}\;\!\!\;\Varid{k}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{⟦}\;\Pi^{\text{\tiny T}}\;\Varid{f}\;\Conid{F}\;\Varid{k}\;\Varid{⟧}^{\text{\tiny T}}\;{}\<[20]%
+\>[20]{}\mathrel{=}\;\!\;\!\!\;\Pi^{\text{\tiny C}}\;\Varid{f}\;\Varid{⟦}\;\Conid{F}\;\Varid{⟧}^{\text{\tiny T}\star}\;\!\!\;\Varid{k}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{⟦}\;\mu^{\text{\tiny T}}\;\Conid{F}\;\Varid{j}\;\Varid{⟧}^{\text{\tiny T}}\;{}\<[20]%
+\>[20]{}\mathrel{=}\;\!\;\!\!\;\mu^{\text{\tiny C}}\;\Varid{⟦}\;\Conid{F}\;\Varid{⟧}^{\text{\tiny T}\star}\;\!\!\;\Varid{j}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\begin{proposition} 
+\ensuremath{(\Conid{ISPT},\eta^{\text{\tiny T}},\anonymous \bind ^{\text{\tiny T}}\anonymous )} is a \emph{relative monad} on the 
+lifting functor \ensuremath{\uparrow\;\in\;\Conid{Set}_{i}\;\rightarrow\;\Conid{Set}_{i+1}}.
+Moreover, this structure is preserved under the translation to containers \ensuremath{\Varid{⟦}\anonymous \Varid{⟧}^{\text{\tiny T}}}.
+\end{proposition}
+
+\begin{proof}
+To prove the structure is a relative 
+monad we observe that the following equlities hold:
+
+For \ensuremath{\Conid{F}\;\in\;\Conid{ISPT}\;\Conid{K}}, \ensuremath{\Conid{G}\;\in\;\Conid{SPF}\;\Conid{J}\;\Conid{K}}, \ensuremath{\Conid{H}\;\in\;\Conid{ISPT}\;\Conid{I}\;\Conid{J}}:
+\begin{align}
+\ensuremath{\Conid{H}\;\Varid{j}}                 &\quad& \equiv &&\quad& \ensuremath{(\eta^{\text{\tiny T}}\;\Varid{j})\;\bind ^{\text{\tiny T}}\;\Conid{H}}               \\
+\ensuremath{\Conid{F}}                   && \equiv &&& \ensuremath{\Conid{F}\;\bind ^{\text{\tiny T}}\;\eta^{\text{\tiny F}}}                 \\
+\ensuremath{(\Conid{F}\;\bind ^{\text{\tiny T}}\;\Conid{G})\;\bind ^{\text{\tiny T}}\;\Conid{F}} && \equiv &&& \ensuremath{\Conid{F}\;\bind ^{\text{\tiny T}}\;(\lambda\;\Varid{k}\;\rightarrow\;(\Conid{G}\;\Varid{k})\;\bind ^{\text{\tiny T}}\;\Conid{H})}
+\end{align}
+
+The 1st is by definition, and the others follow by induction of \ensuremath{\Conid{F}}. 
+To show that the structure is preserved by \ensuremath{\Varid{⟦}\anonymous \Varid{⟧}^{\text{\tiny T}}} it is sufficient to suw that for are \ensuremath{\Conid{F}\;\in\;\Conid{ISPT}\;\Conid{J}} and \ensuremath{\Conid{G}\;\in\;\Conid{SPF}\;\Conid{I}\;\Conid{J}} there exist mutually inverse container
+morphisms:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{15}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{18}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{44}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[3]{}\Varid{bindpres}\;{}\<[15]%
+\>[15]{}\in\;{}\<[18]%
+\>[18]{}(\Varid{⟦}\;\Conid{F}\;\bind ^{\text{\tiny T}}\;\Conid{G}\;\Varid{⟧}^{\text{\tiny T}})\;{}\<[44]%
+\>[44]{}\Rightarrow^{\text{\tiny C}}\;(\Varid{⟦}\;\Conid{F}\;\Varid{⟧}^{\text{\tiny T}}\;\bind ^{\text{\tiny C}}\;\Varid{⟦}\;\Conid{G}\;\Varid{⟧}^{\text{\tiny T}\star}){}\<[E]%
+\\
+\>[3]{}\Varid{bindpres⁻¹}\;{}\<[15]%
+\>[15]{}\in\;{}\<[18]%
+\>[18]{}(\Varid{⟦}\;\Conid{F}\;\Varid{⟧}^{\text{\tiny T}}\;\bind ^{\text{\tiny C}}\;\Varid{⟦}\;\Conid{G}\;\Varid{⟧}^{\text{\tiny T}\star})\;{}\<[44]%
+\>[44]{}\Rightarrow^{\text{\tiny C}}\;(\Varid{⟦}\;\Conid{F}\;\bind ^{\text{\tiny T}}\;\Conid{G}\;\Varid{⟧}^{\text{\tiny T}}){}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\end{proof}
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\bot^{\text{\tiny T}}\;\in\;\forall{}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\rightarrow\;\Conid{ISPT}\;\Conid{I}{}\<[E]%
+\\
+\>[B]{}\bot^{\text{\tiny T}}\;\mathrel{=}\;\Sigma^{\text{\tiny T}}\;\{\mskip1.5mu \Conid{J}\;\mathrel{=}\;\bot\mskip1.5mu\}\;\{\mskip1.5mu \Conid{K}\;\mathrel{=}\;\top\mskip1.5mu\}\;\anonymous \;(\lambda\;())\;\anonymous {}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\anonymous \Varid{⊎\char94 T}\anonymous \;\in\;\forall{}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\rightarrow\;(\Conid{F}\;\Conid{G}\;\in\;\Conid{ISPT}\;\Conid{I})\;\rightarrow\;\Conid{ISPT}\;\Conid{I}{}\<[E]%
+\\
+\>[B]{}\Conid{F}\;\mathbin{\uplus^{\text{\tiny T}}}\;\Conid{G}\;\mathrel{=}\;\Sigma^{\text{\tiny T}}\;\{\mskip1.5mu \Conid{K}\;\mathrel{=}\;\top\mskip1.5mu\}\;\anonymous \;(\lambda\;\Varid{b}\;\rightarrow\;\Varid{if}\;\Varid{b}\;\Varid{then}\;\Conid{F}\;\Varid{else}\;\Conid{G})\;\anonymous {}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\top^{\text{\tiny T}}\;\in\;\forall{}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\rightarrow\;\Conid{ISPT}\;\Conid{I}{}\<[E]%
+\\
+\>[B]{}\top^{\text{\tiny T}}\;\mathrel{=}\;\Pi^{\text{\tiny T}}\;\{\mskip1.5mu \Conid{J}\;\mathrel{=}\;\bot\mskip1.5mu\}\;\{\mskip1.5mu \Conid{K}\;\mathrel{=}\;\top\mskip1.5mu\}\;\anonymous \;(\lambda\;())\;\anonymous {}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\anonymous \mathbin{\times^{\text{\tiny T}}}\anonymous \;\in\;\forall{}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\rightarrow\;(\Conid{F}\;\Conid{G}\;\in\;\Conid{ISPT}\;\Conid{I})\;\rightarrow\;\Conid{ISPT}\;\Conid{I}{}\<[E]%
+\\
+\>[B]{}\Conid{F}\;\mathbin{\times^{\text{\tiny T}}}\;\Conid{G}\;\mathrel{=}\;\Pi^{\text{\tiny T}}\;\{\mskip1.5mu \Conid{K}\;\mathrel{=}\;\top\mskip1.5mu\}\;\anonymous \;(\lambda\;\Varid{b}\;\rightarrow\;\Varid{if}\;\Varid{b}\;\Varid{then}\;\Conid{F}\;\Varid{else}\;\Conid{G})\;\anonymous {}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{9}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{15}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{21}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Conid{T}_{Fin}\;\in\;\Conid{SPF}\;\bot\;\Conid{ℕ}{}\<[E]%
+\\
+\>[B]{}\Conid{T}_{Fin}\;\mathrel{=}\;\mu^{\text{\tiny T}}\;(\Sigma^{\text{\tiny T}}\;\Varid{suc}\;(\Varid{⊤\char94 T*}\;\Varid{+\char94 T*}\;(\eta^{\text{\tiny T}}\;\ensuremath{\mbox{$\circ$}}\;\Varid{inr}))){}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\Conid{T}_{Fin}\;\in\;\Conid{SPF}\;\top\;\Conid{ℕ}{}\<[E]%
+\\
+\>[B]{}\Conid{T}_{Fin}\;\mathrel{=}\;{}\<[9]%
+\>[9]{}\mu^{\text{\tiny T}}\;{}\<[15]%
+\>[15]{}({}\<[21]%
+\>[21]{}\Sigma^{\text{\tiny T}}\;\{\mskip1.5mu \Conid{J}\;\mathrel{=}\;\top\mskip1.5mu\}\;(\lambda\;\anonymous \;\rightarrow\;\Varid{zero})\;(\lambda\;\anonymous \;\rightarrow\;\top^{\text{\tiny T}}){}\<[E]%
+\\
+\>[15]{}\Varid{+\char94 T*}\;{}\<[21]%
+\>[21]{}\Sigma^{\text{\tiny T}}\;\Varid{suc}\;(\lambda\;\Varid{n}\;\rightarrow\;\eta^{\text{\tiny T}}\;(\Varid{inl}\;\anonymous )\;\mathbin{\times^{\text{\tiny T}}}\;\eta^{\text{\tiny T}}\;(\Varid{inr}\;\Varid{n}))){}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\Conid{T}_{ScLam}\;\in\;\Conid{SPF}\;\bot\;\Conid{ℕ}{}\<[E]%
+\\
+\>[B]{}\Conid{T}_{ScLam}\;\mathrel{=}\;\mu^{\text{\tiny T}}\;{}\<[15]%
+\>[15]{}({}\<[21]%
+\>[21]{}(\eta^{\text{\tiny T}}\;\ensuremath{\mbox{$\circ$}}\;\Varid{inr}){}\<[E]%
+\\
+\>[15]{}\Varid{+\char94 T*}\;{}\<[21]%
+\>[21]{}(((\eta^{\text{\tiny T}}\;\ensuremath{\mbox{$\circ$}}\;\Varid{inr})\;\Varid{×\char94 T*}\;(\eta^{\text{\tiny T}}\;\ensuremath{\mbox{$\circ$}}\;\Varid{inr})){}\<[E]%
+\\
+\>[15]{}\Varid{+\char94 T*}\;{}\<[21]%
+\>[21]{}\Delta^{\text{\tiny T}}\;\Varid{suc}\;(\eta^{\text{\tiny T}}\;\ensuremath{\mbox{$\circ$}}\;\Varid{inr}))){}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
 
@@
 
+\bibliographystyle{plain}
+\bibliography{paper}
+
 \end{document}

### 2011-05-02 journal/paper.tex
19/04/11 (2)
02/05/11

@@
 
-Our contructions are all developed in Agda, and so we adopt its syntax, but we will take certain liberties with it's type-theory.
-For, instance we need to work in a setting with extensional type-theory, so we extend the propositional equality with this extensionality axiom:
+Our contructions are all developed in Agda, and so we adopt its syntax, but we will take certain liberties with its type-theory.
+
+We have $\Pi$-types, denoted \ensuremath{(\Varid{a}\;\in\;\Conid{A})\;\rightarrow\;\Conid{B}\;\Varid{a}} and $\Sigma$-types, which we denote in a non-standard way: \ensuremath{\Sigma(\!\;\Varid{a}\;\in\;\Conid{A}\;\!)\!\times\!\;\Conid{B}\;\Varid{a}}.
+In fact this is sugar for the record type:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{5}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Keyword{record}\;\Sigma\;(\Conid{A}\;\in\;\Conid{Set})\;(\Conid{B}\;\in\;\Conid{A}\;\rightarrow\;\Conid{Set})\;\in\;\Conid{Set}\;\Keyword{where}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Keyword{constructor}\;\anonymous ,\anonymous {}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Keyword{field}{}\<[E]%
+\\
+\>[3]{}\hsindent{2}{}\<[5]%
+\>[5]{}\pi_0\;\in\;\Conid{A}{}\<[E]%
+\\
+\>[3]{}\hsindent{2}{}\<[5]%
+\>[5]{}\pi_1\;\in\;\Conid{B}\;\pi_0{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+We will, however assume that the type-theory we work in has $\Sigma$-types as primative, and has no native support for data-types. 
+Instead, we only have \ensuremath{\Conid{W}}-types, the empty-type \ensuremath{\bot}, the unit type \ensuremath{\Varid{tt}\;\in\;\top} and the booleans \ensuremath{\Varid{true},\Varid{false}\;\in\;\Conid{Bool}}.
+
+A type theory has \ensuremath{\Conid{W}} types if it has a type former \ensuremath{\Conid{W}\;\in\;(\Conid{S}\;\in\;\Conid{Set})\;(\Conid{P}\;\in\;\Conid{S}\;\rightarrow\;\Conid{Set})\;\rightarrow\;\Conid{Set}} with a constructor \ensuremath{\Varid{sup}} and an eliminator \ensuremath{\Varid{wrec}}:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{9}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{15}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Keyword{data}\;\Conid{W}\;(\Conid{S}\;\in\;\Conid{Set})\;(\Conid{P}\;\in\;\Conid{S}\;\rightarrow\;\Conid{Set})\;\in\;\Conid{Set}\;\Keyword{where}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{sup}\;\in\;\Sigma(\!\;\Varid{s}\;\in\;\Conid{S}\;\!)\!\times\!\;(\Conid{P}\;\Varid{s}\;\rightarrow\;\Conid{W}\;\Conid{S}\;\Conid{P})\;\rightarrow\;\Conid{W}\;\Conid{S}\;\Conid{P}{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\Varid{wrec}\;\in\;{}\<[9]%
+\>[9]{}\{\mskip1.5mu \Conid{S}\;\in\;\Conid{Set}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{P}\;\in\;\Conid{S}\;\rightarrow\;\Conid{Set}\mskip1.5mu\}\;(\Conid{Q}\;\in\;\Conid{W}\;\Conid{S}\;\Conid{P}\;\rightarrow\;\Conid{Set})\;{}\<[E]%
+\\
+\>[9]{}(\Varid{x}\;\in\;\Conid{W}\;\Conid{S}\;\Conid{P})\;{}\<[E]%
+\\
+\>[9]{}(\Varid{m}\;\in\;{}\<[15]%
+\>[15]{}(\Varid{s}\;\in\;\Conid{S})\;(\Varid{f}\;\in\;\Conid{P}\;\Varid{s}\;\rightarrow\;\Conid{W}\;\Conid{S}\;\Conid{P})\;{}\<[E]%
+\\
+\>[15]{}(\Varid{h}\;\in\;(\Varid{p}\;\in\;\Conid{P}\;\Varid{s})\;\rightarrow\;\Conid{Q}\;(\Varid{f}\;\Varid{p}))\;{}\<[E]%
+\\
+\>[15]{}\rightarrow\;\Conid{Q}\;(\Varid{sup}\;(\Varid{s},\Varid{f})))\;{}\<[E]%
+\\
+\>[9]{}\rightarrow\;\Conid{Q}\;\Varid{x}{}\<[E]%
+\\
+\>[B]{}\Varid{wrec}\;\Conid{Q}\;(\Varid{sup}\;(\Varid{s},\Varid{f}))\;\Varid{m}\;\mathrel{=}\;\Varid{m}\;\Varid{s}\;\Varid{f}\;(\lambda\;\Varid{p}\;\rightarrow\;\Varid{wrec}\;\Conid{Q}\;(\Varid{f}\;\Varid{p})\;\Varid{m}){}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\noindent
+As a notational convenience, we will continue to define extra Agda data-types in the rest of the paper, but in the end we will show how each of these can be reduced to a theory that contains only \ensuremath{\Conid{W}}.
+For compactness, and readablity we will also define functions using Agda's pattern matching syntax, rather than encoding them using wrec, it is an unstated lemma that each of these definitions can be reduced to terms which only use \ensuremath{\Varid{wrec}}.
+
+We'll also require a notion of propositional equality, in Agda this is defined via a data-type:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Keyword{data}\;\Varid{\char95 ≅\char95 }\;\{\mskip1.5mu \Conid{A}\;\in\;\Conid{Set}\mskip1.5mu\}\;(\Varid{x}\;\in\;\Conid{A})\;\in\;\{\mskip1.5mu \Conid{B}\;\in\;\Conid{Set}\mskip1.5mu\}\;\rightarrow\;\Conid{B}\;\rightarrow\;\Conid{Set}\;\Keyword{where}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{refl}\;\in\;\Varid{x}\;\cong\;\Varid{x}{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\Varid{subst}\;\in\;\{\mskip1.5mu \Conid{A}\;\in\;\Conid{Set}\mskip1.5mu\}\;(\Conid{P}\;\in\;\Conid{A}\;\rightarrow\;\Conid{Set})\;\{\mskip1.5mu \Varid{x}\;\Varid{y}\;\in\;\Conid{A}\mskip1.5mu\}\;\rightarrow\;\Varid{x}\;\cong\;\Varid{y}\;\rightarrow\;\Conid{P}\;\Varid{x}\;\rightarrow\;\Conid{P}\;\Varid{y}{}\<[E]%
+\\
+\>[B]{}\Varid{subst}\;\Conid{P}\;\Varid{refl}\;\Varid{p}\;\mathrel{=}\;\Varid{p}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+This is an intensioanl equality, but we want to work in a setting with extensional type-theory, so we extend the propositional equality with this extensionality axiom:
 
@@
 
-This obviously creates non-canonical elements of \ensuremath{\Varid{\char95 ≅\char95 }}, but does not make our theory unsound.
-
-We also use the principle of uniqueness of identity types, to simplyfy some of our constructions:
+This creates non-canonical elements of \ensuremath{\Varid{\char95 ≅\char95 }}, \emph{i.e.} closed terms in equality types which are not \ensuremath{\Varid{refl}}.
+In order to deal with these non-canonical elements, we also rely on axiom \ensuremath{\Conid{K}}, or the uniqueness of idenity proofs:
 
@@
 \end{hscode}\resethooks
-
-Instead of having all of Agda's data-types we assume that we only have \ensuremath{\Conid{W}}-types.
-A type theory has \ensuremath{\Conid{W}} types if it has a type former \ensuremath{\Conid{W}\;\in\;(\Conid{S}\;\in\;\Conid{Set})\;(\Conid{P}\;\in\;\Conid{S}\;\rightarrow\;\Conid{Set})\;\rightarrow\;\Conid{Set}} with a constructor \ensuremath{\Varid{sup}} and an eliminator \ensuremath{\Varid{wrec}}:
-
-\begin{hscode}\SaveRestoreHook
-\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{9}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{15}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
-\>[B]{}\Keyword{data}\;\Conid{W}\;(\Conid{S}\;\in\;\Conid{Set})\;(\Conid{P}\;\in\;\Conid{S}\;\rightarrow\;\Conid{Set})\;\in\;\Conid{Set}\;\Keyword{where}{}\<[E]%
-\\
-\>[B]{}\hsindent{3}{}\<[3]%
-\>[3]{}\Varid{sup}\;\in\;(\Sigma\;\Conid{S}\;\lambda\;\Varid{s}\;\rightarrow\;\Conid{P}\;\Varid{s}\;\rightarrow\;\Conid{W}\;\Conid{S}\;\Conid{P})\;\rightarrow\;\Conid{W}\;\Conid{S}\;\Conid{P}{}\<[E]%
-\\[\blanklineskip]%
-\>[B]{}\Varid{wrec}\;\in\;{}\<[9]%
-\>[9]{}\{\mskip1.5mu \Conid{S}\;\in\;\Conid{Set}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{P}\;\in\;\Conid{S}\;\rightarrow\;\Conid{Set}\mskip1.5mu\}\;(\Conid{Q}\;\in\;\Conid{W}\;\Conid{S}\;\Conid{P}\;\rightarrow\;\Conid{Set})\;{}\<[E]%
-\\
-\>[9]{}(\Varid{x}\;\in\;\Conid{W}\;\Conid{S}\;\Conid{P})\;{}\<[E]%
-\\
-\>[9]{}(\Varid{m}\;\in\;{}\<[15]%
-\>[15]{}(\Varid{s}\;\in\;\Conid{S})\;(\Varid{f}\;\in\;\Conid{P}\;\Varid{s}\;\rightarrow\;\Conid{W}\;\Conid{S}\;\Conid{P})\;{}\<[E]%
-\\
-\>[15]{}(\Varid{h}\;\in\;(\Varid{p}\;\in\;\Conid{P}\;\Varid{s})\;\rightarrow\;\Conid{Q}\;(\Varid{f}\;\Varid{p}))\;{}\<[E]%
-\\
-\>[15]{}\rightarrow\;\Conid{Q}\;(\Varid{sup}\;(\Varid{s},\Varid{f})))\;{}\<[E]%
-\\
-\>[9]{}\rightarrow\;\Conid{Q}\;\Varid{x}{}\<[E]%
-\\
-\>[B]{}\Varid{wrec}\;\Conid{Q}\;(\Varid{sup}\;(\Varid{s},\Varid{f}))\;\Varid{m}\;\mathrel{=}\;\Varid{m}\;\Varid{s}\;\Varid{f}\;(\lambda\;\Varid{p}\;\rightarrow\;\Varid{wrec}\;\Conid{Q}\;(\Varid{f}\;\Varid{p})\;\Varid{m}){}\<[E]%
-\ColumnHook
-\end{hscode}\resethooks
-
-\noindent
-We will continue to define extra Agda data-types in the rest of the paper, but in the end we will show how each of these can be reduced to a theory that contains only \ensuremath{\Conid{W}}.
-For compactness, and readablity we will also define functions using Agda's pattern matching syntax, rather than encoding them using wrec, it is an unstated lemma that each of these definitions can be reduced to terms which only use \ensuremath{\Varid{wrec}},
 
@@
 
-In this setting, the Yoneda lemma can be stated as follows, for any functor \ensuremath{\Conid{F}}:
+In this setting, the Yoneda lemma can be stated as follows, for any functor \ensuremath{\Conid{F}\;\in\;\Conid{Set}\;\rightarrow\;\Conid{Set}}:
 
@@
 \>[21]{}\{\mskip1.5mu \Varid{obj}\;{}\<[28]%
-\>[28]{}\mathrel{=}\;\lambda\;\Conid{A}\;\rightarrow\;\Sigma\;\Conid{S}\;\lambda\;\Varid{s}\;\rightarrow\;\Conid{P}\;\Varid{s}\;\rightarrow\;\Conid{A}{}\<[E]%
+\>[28]{}\mathrel{=}\;\lambda\;\Conid{A}\;\rightarrow\;\Sigma(\!\;\Varid{s}\;\in\;\Conid{S}\;\!)\!\times\!\;(\Conid{P}\;\Varid{s}\;\rightarrow\;\Conid{A}){}\<[E]%
 \\
@@
 To prove the structure is a relative 
-monad we observe that the following equlities hold up to 
+monad we observe that the following equalities hold up to 
 Agda's $\beta\eta$-equality, and our postulate \ensuremath{\Varid{ext}}.
 
-For \ensuremath{\Conid{F}\;\in\;\Conid{IFunc}\;\Conid{I}}, \ensuremath{\Conid{G}\;\in\;\Conid{I}\;\rightarrow\;\Conid{IFunc}\;\Conid{J}}, \ensuremath{\Conid{H}\;\in\;\Conid{J}\;\rightarrow\;\Conid{IFunc}\;\Conid{K}}:
+For \ensuremath{\Conid{F}\;\in\;\Conid{IFunc}\;\Conid{I}}, \ensuremath{\Conid{G}\;\in\;\Conid{IFunc*}\;\Conid{J}\;\Conid{I}}, \ensuremath{\Conid{H}\;\in\;\Conid{IFunc*}\;\Conid{K}\;\Conid{J}}:
 \begin{align}
@@
 This construction is used, for instance, in building the pattern functor for \ensuremath{\Conid{ScLam}} as in the introduction; Concentranting only on the \ensuremath{\Varid{abs}} case we want to build
-\ensuremath{\Conid{FScLam′}\;\Conid{X}\;\Varid{n}\;\mathrel{=}\;(\Conid{X}\;\ensuremath{\mbox{$\circ$}}\;\Varid{suc})\;\Varid{n}}.
-Or simply \ensuremath{\Conid{LScLam′}\;\Conid{X}\;\mathrel{=}\;\Delta^{\text{\tiny F}}\;\Varid{suc}\;\Conid{X}}.
+\ensuremath{\Conid{ScLam′}\;\Conid{X}\;\Varid{n}\;\mathrel{=}\;(\Conid{X}\;\ensuremath{\mbox{$\circ$}}\;\Varid{suc})\;\Varid{n}}.
+Or simply \ensuremath{\Conid{ScLam′}\;\Conid{X}\;\mathrel{=}\;\Delta^{\text{\tiny F}}\;\Varid{suc}\;\Conid{X}}.
 In general this combinator
-restricts the functor \ensuremath{\Conid{X}} to the indexes in the image of the
+restricts the functor \ensuremath{\Conid{X}} to the indicies in the image of the
 function \ensuremath{\Varid{f}}.
@@
 What if the restriction appears on the right of such an equation? As an example,
-consider the successor constructor for \ensuremath{\Conid{Fin}}; here we want to build the pattern functor: \ensuremath{\Conid{FFin′}\;\Conid{X}\;(\Varid{1}\;\Varid{+}\;\Varid{n})\;\mathrel{=}\;\Conid{F}\;\Varid{n}\;\Conid{X}}.
+consider the successor constructor for \ensuremath{\Conid{Fin}}; here we want to build the pattern functor: \ensuremath{\Conid{FFin′}\;\Conid{X}\;(\Varid{1}\;\Varid{+}\;\Varid{n})\;\mathrel{=}\;\Conid{X}\;\Varid{n}}.
 To do this we observe that this is equivalent to
@@
 \>[20]{}\mathrel{=}\;{}\<[23]%
-\>[23]{}\lambda\;\Conid{A}\;\rightarrow\;\Sigma\;\Conid{J}\;\lambda\;\Varid{j}\;\rightarrow\;\Varid{f}\;\Varid{j}\;\equiv\;\Varid{k}\;\times\;\;\Conid{F}\;\Conid{A}\;\Varid{j}{}\<[E]%
+\>[23]{}\lambda\;\Conid{A}\;\rightarrow\;\Sigma(\!\;\Varid{j}\;\in\;\Conid{J}\;\!)\!\times\!\;(\Varid{f}\;\Varid{j}\;\equiv\;\Varid{k}\;\times\;\;\Conid{F}\;\Conid{A}\;\Varid{j}){}\<[E]%
 \\
@@
 \\[\blanklineskip]%
-\>[B]{}\anonymous \Varid{⊎\char94 F}\anonymous \;\in\;\forall{}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\rightarrow\;(\Conid{F}\;\Conid{G}\;\in\;\Conid{IFunc}\;\Conid{I})\;\rightarrow\;\Conid{IFunc}^{\star}\;\Conid{I}\;\top{}\<[E]%
+\>[B]{}\anonymous \uplus^{\text{\tiny F}}\anonymous \;\in\;\forall{}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\rightarrow\;(\Conid{F}\;\Conid{G}\;\in\;\Conid{IFunc}\;\Conid{I})\;\rightarrow\;\Conid{IFunc}^{\star}\;\Conid{I}\;\top{}\<[E]%
 \\
@@
 point-wise product and co-product of functors, but this encoding allows us to 
-keep the number of constants in out vocabulary to a minimum.
+keep the number of constants in our vocabulary to a minimum.
 
@@
 means that we can define nested and mutual families of data-types, such as the
-triple of terms, types and contexts outlined in the introduction.
+tuple of neutral and normal \ensuremath{\lambda}-terms outlined in the introduction.
 
@@
 \>[19]{}\mathrel{=}\;\lambda\;\Conid{A}\;{}\<[26]%
-\>[26]{}\rightarrow\;\Sigma\;\Conid{S}\;(\lambda\;\Varid{s}\;\rightarrow\;(\Varid{i}\;\in\;\Conid{I})\;\rightarrow\;\Conid{P}\;\Varid{s}\;\Varid{i}\;\rightarrow\;\Conid{A}\;\Varid{i}){}\<[E]%
+\>[26]{}\rightarrow\;\Sigma(\!\;\Varid{s}\;\in\;\Conid{S}\;\!)\!\times\!\;(\Conid{P}\;\Varid{s}\;\rightarrow^{\star}\;\Conid{A}){}\<[E]%
 \\
@@
                 & \ensuremath{\Varid{⟦}\;\Conid{S}\;\lhd\;\Conid{P}\;\Varid{⟧}\;\Rightarrow^{\text{\tiny F}}\;\Conid{F}} & \\
-  \equiv  \;    & \ensuremath{\prodd\;\Conid{X}\;.\;(\Sigma\;\Conid{S}\;\lambda\;\Varid{s}\;\rightarrow\;\Conid{P}\;\Varid{s}\;\rightarrow^{\star}\;\Conid{X})\;\rightarrow\;\Conid{F}\;\Conid{X}} & \{\mbox{by definition}\} \\
+  \equiv  \;    & \ensuremath{\prodd\;\Conid{X}\;.\;\Sigma(\!\;\Varid{s}\;\in\;\Conid{S}\;(\Conid{P}\;\Varid{s}\;\rightarrow^{\star}\;\Conid{X})\;\rightarrow\;\Conid{F}\;\Conid{X}} & \{\mbox{by definition}\} \\
   \equiv  \;    & \ensuremath{\prodd\;\Conid{X}\;.\;(\Varid{s}\;\in\;\Varid{s})\;\rightarrow\;(\Conid{P}\;\Varid{s}\;\rightarrow^{\star}\;\Conid{X})\;\rightarrow\;\Conid{F}\;\Conid{X}} & \{\mbox{currying}\} \\
@@
            & \ensuremath{\Varid{⟦}\;\Conid{S}\;\lhd\;\Conid{P}\;\Varid{⟧}\;\Rightarrow^{\text{\tiny F}}\;\Varid{⟦}\;\Conid{T}\;\lhd\;\Conid{Q}\;\Varid{⟧}} \\
- \cong \;  & \ensuremath{(\Varid{s}\;\in\;\Conid{S})\;\rightarrow\;\Sigma\;\Conid{T}\;\lambda\;\Varid{t}\;\rightarrow\;\Conid{Q}\;\Varid{t}\;\rightarrow^{\star}\;\Conid{P}\;\Varid{s}} \\
- \cong \;  & \ensuremath{\Sigma\;(\Conid{S}\;\rightarrow\;\Conid{T})\;\lambda\;\Varid{f}\;\rightarrow\;(\Varid{s}\;\in\;\Conid{S})\;\rightarrow\;\Conid{Q}\;(\Varid{f}\;\Varid{s})\;\rightarrow^{\star}\;\Conid{P}\;\Varid{s}}
+ \cong \;  & \ensuremath{(\Varid{s}\;\in\;\Conid{S})\;\rightarrow\;\Sigma(\!\;\Varid{t}\;\in\;\Conid{T}\;^{\star}\;\!)\!\times\!\;(\Conid{Q}\;\Varid{t}\;\rightarrow^{\star}\;\Conid{P}\;\Varid{s})} \\
+ \cong \;  & \ensuremath{\Sigma(\!\;\Varid{f}\;\in\;\Conid{S}\;\rightarrow\;\Conid{T}\;\!)\!\times\!\;((\Varid{s}\;\in\;\Conid{S})\;\rightarrow\;\Conid{Q}\;(\Varid{f}\;\Varid{s})\;\rightarrow^{\star}\;\Conid{P}\;\Varid{s})}
 \end{align*}
@@
 \>[6]{}\lambda (\!\;\Varid{s}\;\!,\!\;\Varid{f}\;\!\!)\;\Varid{j}\;\!\;\rightarrow\;\Sigma\;{}\<[34]%
-\>[34]{}(\Sigma\;\Conid{I}\;(\Conid{P}\;\Varid{s}))\;(\lambda (\!\;\Varid{i}\;\!,\!\;\Varid{p}\;\!\!)\;\rightarrow\;\Conid{Q}\;\Varid{i}\;(\Varid{f}\;\Varid{i}\;\Varid{p})\;\Varid{j}\;\!\;\!)\;\!\;\!{}\<[E]%
+\>[34]{}(\Sigma(\!\;\Varid{i}\;\in\;\Conid{I}\;\!)\!\times\!\;\Conid{P}\;\Varid{s}\;\Varid{i})\;(\lambda (\!\;\Varid{i}\;\!,\!\;\Varid{p}\;\!\!)\;\rightarrow\;\Conid{Q}\;\Varid{i}\;(\Varid{f}\;\Varid{i}\;\Varid{p})\;\Varid{j}\;\!\;\!)\;\!\;\!{}\<[E]%
 \ColumnHook
@@
 \>[3]{}\hsindent{5}{}\<[8]%
-\>[8]{}(\Sigma\;\Conid{J}\;\lambda\;\Varid{j}\;\rightarrow\;\Varid{f}\;\Varid{j}\;\equiv\;\Varid{k}\;\times\;\Conid{S}\;\Varid{j})\;{}\<[E]%
+\>[8]{}(\Sigma(\!\;\Varid{j}\;\in\;\Conid{J}\;\!)\!\times\!\;(\Varid{f}\;\Varid{j}\;\equiv\;\Varid{k}\;\times\;\Conid{S}\;\Varid{j}))\;{}\<[E]%
 \\
@@
 \>[5]{}\lhd\;{}\<[8]%
-\>[8]{}\lambda\;\Varid{s}\;\Varid{i}\;\rightarrow\;\Sigma\;\Conid{J}\;\lambda\;\Varid{j}\;\rightarrow\;\Sigma\;(\Varid{f}\;\Varid{j}\;\equiv\;\Varid{k})\;\lambda\;\Varid{eq}\;\rightarrow\;\Conid{P}\;\Varid{j}\;(\Varid{s}\;\Varid{j}\;\Varid{eq})\;\Varid{i}{}\<[E]%
+\>[8]{}\lambda\;\Varid{s}\;\Varid{i}\;\rightarrow\;\Sigma(\!\;\Varid{j}\;\in\;\Conid{J}\;\!)\!\times\!\;(\Sigma(\!\;\Varid{eq}\;\in\;\Varid{f}\;\Varid{j}\;\equiv\;\Varid{k}\;\!)\!\times\!\;\Conid{P}\;\Varid{j}\;(\Varid{s}\;\Varid{j}\;\Varid{eq})\;\Varid{i}){}\<[E]%
 \ColumnHook
@@
 \column{8}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{10}{@{}>{\hspre}l<{\hspost}@{}}%
 \column{12}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{13}{@{}>{\hspre}l<{\hspost}@{}}%
 \column{17}{@{}>{\hspre}l<{\hspost}@{}}%
 \column{22}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{34}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{37}{@{}>{\hspre}l<{\hspost}@{}}%
 \column{39}{@{}>{\hspre}c<{\hspost}@{}}%
@@
 \>[3]{}\Keyword{in}\;{}\<[8]%
-\>[8]{}\!\;\Varid{⟦}\;\Conid{S}\;\lhd\;\Conid{P}^{\Conid{J}}\;\Varid{⟧}\;\Conid{T}\;\lhd\;{}\<[37]%
-\>[37]{}(\lambda (\!\;\Varid{s}\;\!,\!\;\Varid{f}\;\!\!)\;\Varid{i}\;\!\;\rightarrow\;\Conid{P}^{\Conid{I}}\;\Varid{s}\;\Varid{i}{}\<[E]%
-\\
-\>[8]{}\hsindent{26}{}\<[34]%
-\>[34]{}\uplus\;{}\<[37]%
-\>[37]{}(\Sigma\;\Conid{J}\;\lambda\;\Varid{j}\;\rightarrow\;\Sigma\;(\Conid{P}^{\Conid{J}}\;\Varid{s}\;\Varid{j})\;\lambda\;\Varid{p}\;\rightarrow\;\Conid{Q}\;\Varid{j}\;(\Varid{f}\;\Varid{j}\;\Varid{p})\;\Varid{i})\;\!\;\!){}\<[E]%
+\>[8]{}\!\;\Varid{⟦}\;\Conid{S}\;\lhd\;\Conid{P}^{\Conid{J}}\;\Varid{⟧}\;\Conid{T}\;\lhd\;{}\<[E]%
+\\
+\>[8]{}\hsindent{5}{}\<[13]%
+\>[13]{}(\lambda (\!\;\Varid{s}\;\!,\!\;\Varid{f}\;\!\!)\;\Varid{i}\;\!\;\rightarrow\;\Conid{P}^{\Conid{I}}\;\Varid{s}\;\Varid{i}{}\<[E]%
+\\
+\>[8]{}\hsindent{2}{}\<[10]%
+\>[10]{}\uplus\;{}\<[13]%
+\>[13]{}(\Sigma(\!\;\Varid{j}\;\in\;\Conid{J}\;\!)\!\times\!\;(\Sigma(\!\;\Varid{p}\;\in\;\Conid{P}^{\Conid{J}}\;\Varid{s}\;\Varid{j}\;\!)\!\times\!\;\Conid{Q}\;\Varid{j}\;(\Varid{f}\;\Varid{j}\;\Varid{p})\;\Varid{i}))\;\!\;\!){}\<[E]%
 \ColumnHook
@@
 We will now examine how to construct the initial algebra of a container of the form \ensuremath{\Conid{F}\;\in\;\Conid{ICont}^{\star}\;(\Conid{I}\;\uplus\;\Conid{J})\;\Conid{J}}.
-The shapes of such a container are an \ensuremath{\Conid{J}}-indexed family of \ensuremath{\Conid{Set}}s and the positions are in \ensuremath{(\Varid{j}\;\in\;\Conid{J})\;\rightarrow\;\Conid{S}\;\Varid{j}\;\rightarrow\;\Conid{I}\;\uplus\;\Conid{J}\;\rightarrow\;\Conid{Set}}; we will treat these position as two separate entities, those positions indexed by \ensuremath{\Conid{I}} (\ensuremath{\Conid{P}^{\Conid{I}}\;\in\;(\Varid{j}\;\in\;\Conid{J})\;\rightarrow\;\Conid{S}\;\Varid{j}\;\rightarrow\;\Conid{I}\;\rightarrow\;\Conid{Set}}) -- the recusive positions -- and those by \ensuremath{\Conid{J}}
-(\ensuremath{\Conid{P}^{\Conid{J}}\;\in\;(\Varid{j}\;\in\;\Conid{J})\;\rightarrow\;\Conid{S}\;\Varid{i}\;\rightarrow\;\Conid{J}\;\rightarrow\;\Conid{Set}}) -- the payload positions.
+The shapes of such a container are an \ensuremath{\Conid{J}}-indexed family of \ensuremath{\Conid{Set}}s and the positions are indexed by \ensuremath{\Conid{I}\;\uplus\;\Conid{J}}; we will treat these position as two separate entities, those positions indexed by \ensuremath{\Conid{I}} -- the recusive positions -- and those by \ensuremath{\Conid{J}} -- the payload positions.
 
@@
 \>[13]{}\uplus\;{}\<[16]%
-\>[16]{}(\Sigma\;\Conid{J}\;\lambda\;\Varid{j′}\;\rightarrow\;\Sigma\;(\Conid{P}^{\Conid{J}}\;\Varid{j}\;\Varid{s}\;\Varid{j′})\;\lambda\;\Varid{p}\;\rightarrow\;\Conid{Path}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\;\Conid{P}^{\Conid{J}}\;\Varid{j′}\;(\Varid{f}\;\Varid{j′}\;\Varid{p})\;\Varid{i})\;{}\<[E]%
+\>[16]{}(\Sigma(\!\;\Varid{j′}\;\in\;\Conid{J}\;\!)\!\times\!\;(\Sigma(\!\;\Varid{p}\;\in\;\Conid{P}^{\Conid{J}}\;\Varid{j}\;\Varid{s}\;\Varid{j′}\;\!)\!\times\!\;\Conid{Path}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\;\Conid{P}^{\Conid{J}}\;\Varid{j′}\;(\Varid{f}\;\Varid{j′}\;\Varid{p})\;\Varid{i}))\;{}\<[E]%
 \\
@@
 \\
-\>[B]{}\Varid{in}^{\text{\tiny C}}\;\Conid{F}\;\mathrel{=}\;(\lambda\;\anonymous \;\rightarrow\;\Varid{sup})\;\lhd^{\star}\;\lambda\;\anonymous \;\anonymous \;\Varid{p}\;\rightarrow\;\Varid{path}\Varid{⁻¹}\;\Varid{p}{}\<[E]%
+\>[B]{}\Varid{in}^{\text{\tiny C}}\;\Conid{F}\;\mathrel{=}\;(\lambda\;\anonymous \;\rightarrow\;\Varid{sup})\;\lhd^{\star}\;\lambda\;\anonymous \;\anonymous \;(\Varid{path}\;\Varid{p})\;\rightarrow\;\Varid{p}{}\<[E]%
 \ColumnHook
@@
 \column{13}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{14}{@{}>{\hspre}l<{\hspost}@{}}%
 \column{16}{@{}>{\hspre}l<{\hspost}@{}}%
@@
 \>[12]{}\Varid{rfold}\;\in\;{}\<[21]%
-\>[21]{}\{\mskip1.5mu \Varid{j}\;\in\;\Conid{J}\mskip1.5mu\}\;(\Varid{s}\;\in\;\Conid{WI}\;\Conid{S}\;\Conid{P}^{\Conid{J}}\;\Varid{j})\;(\Varid{i}\;\in\;\Conid{I})\;\rightarrow\;\Conid{Q}\;\Varid{j}\;(\Varid{ffold}\;\Varid{j}\;\Varid{s})\;\Varid{i}\;\rightarrow\;\Conid{Path}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\;\Conid{P}^{\Conid{J}}\;\Varid{j}\;\Varid{s}\;\Varid{i}{}\<[E]%
+\>[21]{}\{\mskip1.5mu \Varid{j}\;\in\;\Conid{J}\mskip1.5mu\}\;(\Varid{s}\;\in\;\Conid{WI}\;\Conid{S}\;\Conid{P}^{\Conid{J}}\;\Varid{j})\;{}\<[E]%
+\\
+\>[21]{}(\Varid{i}\;\in\;\Conid{I})\;\rightarrow\;\Conid{Q}\;\Varid{j}\;(\Varid{ffold}\;\Varid{j}\;\Varid{s})\;\Varid{i}\;\rightarrow\;\Conid{Path}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\;\Conid{P}^{\Conid{J}}\;\Varid{j}\;\Varid{s}\;\Varid{i}{}\<[E]%
 \\
@@
 \>[37]{}\mid \;\Varid{inl}\;\Varid{x}\;{}\<[60]%
-\>[60]{}\mathrel{=}\;\Varid{path}\;(\Varid{inl}\;\Varid{x}){}\<[E]%
+\>[60]{}\mathrel{=}\;{}\<[E]%
+\\
+\>[12]{}\hsindent{2}{}\<[14]%
+\>[14]{}\Varid{path}\;(\Varid{inl}\;\Varid{x}){}\<[E]%
 \\
@@
 \>[37]{}\mid \;\Varid{inr}\;(\Varid{j′},(\Varid{q},\Varid{y}))\;{}\<[60]%
-\>[60]{}\mathrel{=}\;\Varid{path}\;(\Varid{inr}\;(\Varid{j′},(\Varid{q},\Varid{rfold}\;(\Varid{f}\;\Varid{j′}\;\Varid{q})\;\Varid{i}\;\Varid{y}))){}\<[E]%
+\>[60]{}\mathrel{=}\;{}\<[E]%
+\\
+\>[12]{}\hsindent{2}{}\<[14]%
+\>[14]{}\Varid{path}\;(\Varid{inr}\;(\Varid{j′},(\Varid{q},\Varid{rfold}\;(\Varid{f}\;\Varid{j′}\;\Varid{q})\;\Varid{i}\;\Varid{y}))){}\<[E]%
 \ColumnHook
@@
 \section{Terminal Co-Algebras of Indexed Containers}
+
+Dually to the initial algebra construction out-lined above, we can also show that indexed-containers are closed under parameterized terminal co-algebras.
+We proceed in much the same way as before, by first constructing the dual of the indexed \ensuremath{\Conid{W}}-type, which we refer to as an indexed \ensuremath{\Conid{M}}-type.
+As you might expect this is in fact the plain (as opposed to parametrized) terminal co-algebra of an indexed container functor:
 
@@
 \column{B}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{5}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{7}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{8}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{10}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{13}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{14}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{16}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Conid{MIunfold}\;\in\;{}\<[13]%
+\>[13]{}\forall{}\;{}\<[16]%
+\>[16]{}\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{X}\;\in\;\Conid{I}\;\rightarrow\;\Conid{Set}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{S}\;\in\;\Conid{I}\;\rightarrow\;\Conid{Set}\mskip1.5mu\}\;{}\<[E]%
+\\
+\>[13]{}\hsindent{1}{}\<[14]%
+\>[14]{}\{\mskip1.5mu \Conid{P}^{\Conid{I}}\;\in\;(\Varid{i}\;\in\;\Conid{I})\;\rightarrow\;\Conid{S}\;\Varid{i}\;\rightarrow\;\Conid{I}\;\rightarrow\;\Conid{Set}\mskip1.5mu\}\;\rightarrow\;{}\<[E]%
+\\
+\>[13]{}\hsindent{1}{}\<[14]%
+\>[14]{}\Conid{X}\;\rightarrow^{\star}\;\;\Varid{⟦}\;\Conid{S}\;\lhd^{\star}\;\Conid{P}^{\Conid{I}}\;\Varid{⟧}^{\star}\;\Conid{X}\;\rightarrow\;\Conid{X}\;\rightarrow^{\star}\;\Conid{MI}\;\Conid{S}\;\Conid{P}^{\Conid{I}}{}\<[E]%
+\\
+\>[B]{}\Conid{MIunfold}\;\Varid{m}\;\Varid{i}\;\Varid{x}\;\Keyword{with}\;\Varid{m}\;\Varid{i}\;\Varid{x}{}\<[E]%
+\\
+\>[B]{}\Conid{MIunfold}\;\Varid{m}\;\Varid{i}\;\Varid{x}\;\mid \;\Varid{s},\Varid{f}\;\mathrel{=}\;\Varid{sup}\;(\Varid{s},(\lambda\;\Varid{i′}\;\Varid{p}\;\rightarrow\;\sharp\;\Conid{MIunfold}\;\Varid{m}\;\Varid{i′}\;(\Varid{f}\;\Varid{i′}\;\Varid{p}))){}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+Here we employ Agda's approach to co-programming, where we mark (possibly) infinite subtrees with \ensuremath{\infty}, \ensuremath{\sharp\;\in\;\Conid{A}\;\rightarrow\;\infty\;\Conid{A}} and \ensuremath{\flat\;\in\;\infty\;\Conid{A}\;\rightarrow\;\Conid{A}} pack and unpack infinite objects respectively.
+
+The paths to positions in and indexed \ensuremath{\Conid{M}} tree, are always finite -- in fact modulo the use of \ensuremath{\flat}, this \ensuremath{\Conid{Path}} is the same as the definition for the initial algebra case.
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
 \column{12}{@{}>{\hspre}l<{\hspost}@{}}%
 \column{13}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{16}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{17}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{38}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Keyword{data}\;\Conid{Path}\;{}\<[12]%
+\>[12]{}\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\in\;\Conid{Set}\mskip1.5mu\}\;(\Conid{S}\;\in\;\Conid{J}\;\rightarrow\;\Conid{Set})\;{}\<[E]%
+\\
+\>[12]{}(\Conid{P}^{\Conid{I}}\;{}\<[17]%
+\>[17]{}\in\;(\Varid{j}\;\in\;\Conid{J})\;\rightarrow\;\Conid{S}\;\Varid{j}\;\rightarrow\;\Conid{I}\;{}\<[38]%
+\>[38]{}\rightarrow\;\Conid{Set})\;{}\<[E]%
+\\
+\>[12]{}(\Conid{P}^{\Conid{J}}\;{}\<[17]%
+\>[17]{}\in\;(\Varid{j}\;\in\;\Conid{J})\;\rightarrow\;\Conid{S}\;\Varid{j}\;\rightarrow\;\Conid{J}\;{}\<[38]%
+\>[38]{}\rightarrow\;\Conid{Set})\;{}\<[E]%
+\\
+\>[12]{}\in\;(\Varid{j}\;\in\;\Conid{J})\;\rightarrow\;\Conid{MI}\;\Conid{S}\;\Conid{P}^{\Conid{J}}\;\Varid{j}\;\rightarrow\;\Conid{I}\;\rightarrow\;\Conid{Set}\;\Keyword{where}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{path}\;\in\;\forall{}\;{}\<[13]%
+\>[13]{}\{\mskip1.5mu \Varid{j}\;\Varid{s}\;\Varid{f}\;\Varid{i}\mskip1.5mu\}\;\rightarrow\;{}\<[E]%
+\\
+\>[13]{}\hsindent{3}{}\<[16]%
+\>[16]{}\Conid{P}^{\Conid{I}}\;\Varid{j}\;\Varid{s}\;\Varid{i}\;{}\<[E]%
+\\
+\>[13]{}\uplus\;{}\<[16]%
+\>[16]{}(\Sigma(\!\;\Varid{j′}\;\in\;\Conid{J}\;\!)\!\times\!\;(\Sigma(\!\;\Varid{p}\;\in\;\Conid{P}^{\Conid{J}}\;\Varid{j}\;\Varid{s}\;\Varid{j′}\;\!)\!\times\!\;\Conid{Path}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\;\Conid{P}^{\Conid{J}}\;\Varid{j′}\;(\flat\;(\Varid{f}\;\Varid{j′}\;\Varid{p}))\;\Varid{i}))\;{}\<[E]%
+\\
+\>[13]{}\rightarrow\;\Conid{Path}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\;\Conid{P}^{\Conid{J}}\;\Varid{j}\;(\Varid{sup}\;(\Varid{s},\Varid{f}))\;\Varid{i}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+The parameterised terminal co-algebra of an indexed container is, then, given by a choice of \ensuremath{\Conid{MI}} shapes and positions given by \ensuremath{\Conid{Path}}.
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{8}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{12}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{33}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{42}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{46}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{54}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\nu^{\text{\tiny C}}\;\in\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\in\;\Conid{Set}\mskip1.5mu\}\;\rightarrow\;\Conid{ICont}^{\star}\;(\Conid{I}\;\uplus\;\Conid{J})\;\Conid{J}\;\rightarrow\;\Conid{ICont}^{\star}\;\Conid{I}\;\Conid{J}{}\<[E]%
+\\
+\>[B]{}\nu^{\text{\tiny C}}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{J}\mskip1.5mu\}\;(\Conid{S}\;\lhd^{\star}\;\Conid{P})\;\mathrel{=}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Keyword{let}\;{}\<[8]%
+\>[8]{}\Conid{P}^{\Conid{I}}\;{}\<[12]%
+\>[12]{}\in\;(\Varid{j}\;\in\;\Conid{J})\;\rightarrow\;\Conid{S}\;\Varid{j}\;\rightarrow\;\Conid{I}\;{}\<[33]%
+\>[33]{}\rightarrow\;\Conid{Set};{}\<[42]%
+\>[42]{}\Conid{P}^{\Conid{I}}\;{}\<[46]%
+\>[46]{}\Varid{j}\;\Varid{s}\;\Varid{i}\;{}\<[54]%
+\>[54]{}\mathrel{=}\;\Conid{P}\;\!\!\;\Varid{j}\;\!\!\;\Varid{s}\;\!\!\;(\Varid{inl}\;\Varid{i}){}\<[E]%
+\\
+\>[8]{}\Conid{P}^{\Conid{J}}\;{}\<[12]%
+\>[12]{}\in\;(\Varid{j}\;\in\;\Conid{J})\;\rightarrow\;\Conid{S}\;\Varid{j}\;\rightarrow\;\Conid{J}\;{}\<[33]%
+\>[33]{}\rightarrow\;\Conid{Set};{}\<[42]%
+\>[42]{}\Conid{P}^{\Conid{J}}\;{}\<[46]%
+\>[46]{}\Varid{j}\;\Varid{s}\;\Varid{j′}\;{}\<[54]%
+\>[54]{}\mathrel{=}\;\Conid{P}\;\!\!\;\Varid{j}\;\!\!\;\Varid{s}\;\!\!\;(\Varid{inr}\;\Varid{j′}){}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Keyword{in}\;{}\<[8]%
+\>[8]{}\Conid{MI}\;\Conid{S}\;\Conid{P}^{\Conid{J}}\;\lhd^{\star}\;\Conid{Path}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\;\Conid{P}^{\Conid{J}}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Varid{out}^{\text{\tiny C}}\;\in\;\forall{}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\mskip1.5mu\}\;\rightarrow\;(\Conid{F}\;\in\;\Conid{ICont}^{\star}\;(\Conid{I}\;\uplus\;\Conid{J})\;\Conid{J})\;\rightarrow\;\nu^{\text{\tiny C}}\;\Conid{F}\;\Rightarrow^{\text{\tiny C}^{\star}}\;\Conid{F}\;[\mskip1.5mu \;\nu^{\text{\tiny C}}\;\Conid{F}\;\mskip1.5mu]^{\text{\tiny{C}}^{\star}}{}\<[E]%
+\\
+\>[B]{}\Varid{out}^{\text{\tiny C}}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{J}\mskip1.5mu\}\;(\Conid{S}\;\lhd^{\star}\;\Conid{P})\;\mathrel{=}\;(\lambda\;\anonymous \;(\Varid{sup}\;\Varid{x})\;\rightarrow\;\Varid{x})\;\lhd^{\star}\;\lambda\;(\Varid{sup}\;\Varid{x})\;\Varid{i′}\;\Varid{p}\;\rightarrow\;\Varid{path}\;\Varid{p}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{5}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{12}{@{}>{\hspre}l<{\hspost}@{}}%
 \column{14}{@{}>{\hspre}l<{\hspost}@{}}%
@@
 \column{16}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{17}{@{}>{\hspre}l<{\hspost}@{}}%
 \column{19}{@{}>{\hspre}l<{\hspost}@{}}%
 \column{23}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{33}{@{}>{\hspre}l<{\hspost}@{}}%
 \column{38}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{42}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{46}{@{}>{\hspre}l<{\hspost}@{}}%
 \column{47}{@{}>{\hspre}l<{\hspost}@{}}%
 \column{51}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{54}{@{}>{\hspre}l<{\hspost}@{}}%
 \column{59}{@{}>{\hspre}l<{\hspost}@{}}%
 \column{E}{@{}>{\hspre}l<{\hspost}@{}}%
-\>[B]{}\Conid{MIunfold}\;\in\;{}\<[13]%
-\>[13]{}\forall{}\;{}\<[16]%
-\>[16]{}\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{X}\;\in\;\Conid{I}\;\rightarrow\;\Conid{Set}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{S}\;\in\;\Conid{I}\;\rightarrow\;\Conid{Set}\mskip1.5mu\}\;{}\<[E]%
-\\
-\>[13]{}\hsindent{1}{}\<[14]%
-\>[14]{}\{\mskip1.5mu \Conid{P}^{\Conid{I}}\;\in\;(\Varid{i}\;\in\;\Conid{I})\;\rightarrow\;\Conid{S}\;\Varid{i}\;\rightarrow\;\Conid{I}\;\rightarrow\;\Conid{Set}\mskip1.5mu\}\;\rightarrow\;{}\<[E]%
-\\
-\>[13]{}\hsindent{1}{}\<[14]%
-\>[14]{}\Conid{X}\;\rightarrow^{\star}\;\;\Varid{⟦}\;\Conid{S}\;\lhd^{\star}\;\Conid{P}^{\Conid{I}}\;\Varid{⟧}^{\star}\;\Conid{X}\;\rightarrow\;\Conid{X}\;\rightarrow^{\star}\;\Conid{MI}\;\Conid{S}\;\Conid{P}^{\Conid{I}}{}\<[E]%
-\\
-\>[B]{}\Conid{MIunfold}\;\Varid{m}\;\Varid{i}\;\Varid{x}\;\Keyword{with}\;\Varid{m}\;\Varid{i}\;\Varid{x}{}\<[E]%
-\\
-\>[B]{}\Conid{MIunfold}\;\Varid{m}\;\Varid{i}\;\Varid{x}\;\mid \;\Varid{s},\Varid{f}\;\mathrel{=}\;\Varid{sup}\;(\Varid{s},(\lambda\;\Varid{i′}\;\Varid{p}\;\rightarrow\;\sharp\;\Conid{MIunfold}\;\Varid{m}\;\Varid{i′}\;(\Varid{f}\;\Varid{i′}\;\Varid{p}))){}\<[E]%
-\\[\blanklineskip]%
-\>[B]{}\Keyword{data}\;\Conid{Path}\;{}\<[12]%
-\>[12]{}\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\in\;\Conid{Set}\mskip1.5mu\}\;(\Conid{S}\;\in\;\Conid{I}\;\rightarrow\;\Conid{Set})\;{}\<[E]%
-\\
-\>[12]{}(\Conid{P}^{\Conid{I}}\;{}\<[17]%
-\>[17]{}\in\;(\Varid{i}\;\in\;\Conid{I})\;\rightarrow\;\Conid{S}\;\Varid{i}\;\rightarrow\;\Conid{I}\;{}\<[38]%
-\>[38]{}\rightarrow\;\Conid{Set})\;{}\<[E]%
-\\
-\>[12]{}(\Conid{P}^{\Conid{J}}\;{}\<[17]%
-\>[17]{}\in\;(\Varid{i}\;\in\;\Conid{I})\;\rightarrow\;\Conid{S}\;\Varid{i}\;\rightarrow\;\Conid{J}\;{}\<[38]%
-\>[38]{}\rightarrow\;\Conid{Set})\;{}\<[E]%
-\\
-\>[12]{}\in\;(\Varid{i}\;\in\;\Conid{I})\;\rightarrow\;\Conid{MI}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\;\Varid{i}\;\rightarrow\;\Conid{J}\;\rightarrow\;\Conid{Set}\;\Keyword{where}{}\<[E]%
-\\
-\>[B]{}\hsindent{3}{}\<[3]%
-\>[3]{}\Varid{path}\;\in\;\forall{}\;{}\<[13]%
-\>[13]{}\{\mskip1.5mu \Varid{i}\;\Varid{s}\;\Varid{f}\;\Varid{j}\mskip1.5mu\}\;\rightarrow\;{}\<[E]%
-\\
-\>[13]{}\hsindent{3}{}\<[16]%
-\>[16]{}\Conid{P}^{\Conid{J}}\;\Varid{i}\;\Varid{s}\;\Varid{j}\;{}\<[E]%
-\\
-\>[13]{}\uplus\;{}\<[16]%
-\>[16]{}(\Sigma\;\Conid{I}\;\lambda\;\Varid{i′}\;\rightarrow\;\Sigma\;(\Conid{P}^{\Conid{I}}\;\Varid{i}\;\Varid{s}\;\Varid{i′})\;\lambda\;\Varid{p}\;\rightarrow\;\Conid{Path}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\;\Conid{P}^{\Conid{J}}\;\Varid{i′}\;(\flat\;(\Varid{f}\;\Varid{i′}\;\Varid{p}))\;\Varid{j})\;{}\<[E]%
-\\
-\>[13]{}\rightarrow\;\Conid{Path}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\;\Conid{P}^{\Conid{J}}\;\Varid{i}\;(\Varid{sup}\;(\Varid{s},\Varid{f}))\;\Varid{j}{}\<[E]%
-\\[\blanklineskip]%
-\>[B]{}\nu^{\text{\tiny C}}\;\in\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\in\;\Conid{Set}\mskip1.5mu\}\;\rightarrow\;\Conid{ICont}^{\star}\;(\Conid{I}\;\uplus\;\Conid{J})\;\Conid{I}\;\rightarrow\;\Conid{ICont}^{\star}\;\Conid{J}\;\Conid{I}{}\<[E]%
-\\
-\>[B]{}\nu^{\text{\tiny C}}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{J}\mskip1.5mu\}\;(\Conid{S}\;\lhd^{\star}\;\Conid{P})\;\mathrel{=}{}\<[E]%
-\\
-\>[B]{}\hsindent{3}{}\<[3]%
-\>[3]{}\Keyword{let}\;{}\<[8]%
-\>[8]{}\Conid{P}^{\Conid{I}}\;{}\<[12]%
-\>[12]{}\in\;(\Varid{i}\;\in\;\Conid{I})\;\rightarrow\;\Conid{S}\;\Varid{i}\;\rightarrow\;\Conid{I}\;{}\<[33]%
-\>[33]{}\rightarrow\;\Conid{Set};{}\<[42]%
-\>[42]{}\Conid{P}^{\Conid{I}}\;{}\<[46]%
-\>[46]{}\Varid{i}\;\Varid{s}\;\Varid{i′}\;{}\<[54]%
-\>[54]{}\mathrel{=}\;\Conid{P}\;\!\!\;\Varid{i}\;\!\!\;\Varid{s}\;\!\!\;(\Varid{inl}\;\Varid{i′}){}\<[E]%
-\\
-\>[8]{}\Conid{P}^{\Conid{J}}\;{}\<[12]%
-\>[12]{}\in\;(\Varid{i}\;\in\;\Conid{I})\;\rightarrow\;\Conid{S}\;\Varid{i}\;\rightarrow\;\Conid{J}\;{}\<[33]%
-\>[33]{}\rightarrow\;\Conid{Set};{}\<[42]%
-\>[42]{}\Conid{P}^{\Conid{J}}\;{}\<[46]%
-\>[46]{}\Varid{i}\;\Varid{s}\;\Varid{j}\;{}\<[54]%
-\>[54]{}\mathrel{=}\;\Conid{P}\;\!\!\;\Varid{i}\;\!\!\;\Varid{s}\;\!\!\;(\Varid{inr}\;\Varid{j}){}\<[E]%
-\\
-\>[B]{}\hsindent{3}{}\<[3]%
-\>[3]{}\Keyword{in}\;{}\<[8]%
-\>[8]{}\Conid{MI}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\;\lhd^{\star}\;\Conid{Path}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\;\Conid{P}^{\Conid{J}}{}\<[E]%
-\\[\blanklineskip]%
-\>[B]{}\Varid{out}^{\text{\tiny C}}\;\in\;\forall{}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\mskip1.5mu\}\;\rightarrow\;(\Conid{F}\;\in\;\Conid{ICont}^{\star}\;(\Conid{I}\;\uplus\;\Conid{J})\;\Conid{I})\;\rightarrow\;\nu^{\text{\tiny C}}\;\Conid{F}\;\Rightarrow^{\text{\tiny C}^{\star}}\;\Conid{F}\;[\mskip1.5mu \;\nu^{\text{\tiny C}}\;\Conid{F}\;\mskip1.5mu]^{\text{\tiny{C}}^{\star}}{}\<[E]%
-\\
-\>[B]{}\Varid{out}^{\text{\tiny C}}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{J}\mskip1.5mu\}\;(\Conid{S}\;\lhd^{\star}\;\Conid{P})\;\mathrel{=}\;(\lambda\;\anonymous \;\rightarrow\;\Varid{sup⁻¹})\;\lhd^{\star}\;\Varid{unsup}\;\{\mskip1.5mu \anonymous \mskip1.5mu\}\;\{\mskip1.5mu \anonymous \mskip1.5mu\}\;\{\mskip1.5mu \anonymous \mskip1.5mu\}\;\{\mskip1.5mu \lambda\;\Varid{j}\;\Varid{s}\;\rightarrow\;(\Varid{i}\;\in\;\Conid{J})\;\rightarrow\;\Conid{P}\;\Varid{j}\;(\pi_{0}\;(\Varid{sup⁻¹}\;\Varid{s}))\;(\Varid{inr}\;\Varid{i})\;\uplus{}\<[E]%
-\\
-\>[B]{}\hsindent{7}{}\<[7]%
-\>[7]{}\Sigma\;\Conid{I}{}\<[E]%
-\\
-\>[B]{}\hsindent{7}{}\<[7]%
-\>[7]{}(\lambda\;\Varid{i'}\;\rightarrow\;{}\<[E]%
-\\
-\>[7]{}\hsindent{3}{}\<[10]%
-\>[10]{}\Sigma\;(\Conid{P}\;\Varid{j}\;(\pi_{0}\;(\Varid{sup⁻¹}\;\Varid{s}))\;(\Varid{inl}\;\Varid{i'}))\;{}\<[E]%
-\\
-\>[7]{}\hsindent{3}{}\<[10]%
-\>[10]{}(\lambda\;\Varid{p}\;\rightarrow\;{}\<[E]%
-\\
-\>[10]{}\hsindent{3}{}\<[13]%
-\>[13]{}\Conid{Path}\;\Conid{S}\;(\lambda\;\Varid{i0}\;\Varid{s'}\;\Varid{i′}\;\rightarrow\;\Conid{P}\;\Varid{i0}\;\Varid{s'}\;(\Varid{inl}\;\Varid{i′}))\;{}\<[E]%
-\\
-\>[10]{}\hsindent{3}{}\<[13]%
-\>[13]{}(\lambda\;\Varid{i0}\;\Varid{s'}\;\Varid{j'}\;\rightarrow\;\Conid{P}\;\Varid{i0}\;\Varid{s'}\;(\Varid{inr}\;\Varid{j'}))\;\Varid{i'}\;(\pi_{1}\;(\Varid{sup⁻¹}\;\Varid{s})\;\Varid{i'}\;\Varid{p})\;\Varid{i}))\;\rightarrow{}\<[E]%
-\\
-\>[B]{}\hsindent{7}{}\<[7]%
-\>[7]{}\Conid{Path}\;\Conid{S}\;(\lambda\;\Varid{i'}\;\Varid{s'}\;\Varid{i′}\;\rightarrow\;\Conid{P}\;\Varid{i'}\;\Varid{s'}\;(\Varid{inl}\;\Varid{i′})){}\<[E]%
-\\
-\>[B]{}\hsindent{7}{}\<[7]%
-\>[7]{}(\lambda\;\Varid{i'}\;\Varid{s'}\;\Varid{j'}\;\rightarrow\;\Conid{P}\;\Varid{i'}\;\Varid{s'}\;(\Varid{inr}\;\Varid{j'}))\;\Varid{j}\;\Varid{s}\;\Varid{i}\mskip1.5mu\}\;(\lambda\;\Varid{sf}\;\Varid{i′}\;\Varid{p}\;\rightarrow\;\Varid{path}\;\Varid{p}){}\<[E]%
-\\[\blanklineskip]%
 \>[B]{}\Varid{unfold}^{\text{\tiny C}}\;\in\;\forall{}\;{}\<[15]%
@@
 \>[12]{}\Varid{runfold}\;\in\;{}\<[23]%
-\>[23]{}\{\mskip1.5mu \Varid{i}\;\in\;\Conid{I}\mskip1.5mu\}\;(\Varid{t}\;\in\;\Conid{T}\;\Varid{i})\;(\Varid{j}\;\in\;\Conid{J})\;\rightarrow\;\Conid{Path}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\;\Conid{P}^{\Conid{J}}\;\Varid{i}\;(\Varid{funfold}\;\Varid{i}\;\Varid{t})\;\Varid{j}\;\rightarrow\;\Conid{Q}\;\Varid{i}\;\Varid{t}\;\Varid{j}{}\<[E]%
-\\
-\>[12]{}\Varid{runfold}\;\Varid{t}\;\Varid{j}\;(\Varid{path}\;(\Varid{inl}\;\Varid{x}))\;\mathrel{=}\;\Varid{r}\;\Varid{t}\;\Varid{j}\;(\Varid{inl}\;\Varid{x}){}\<[E]%
-\\
-\>[12]{}\Varid{runfold}\;\Varid{t}\;\Varid{j}\;(\Varid{path}\;(\Varid{inr}\;(\Varid{i},(\Varid{p},\Varid{q}))))\;\mathrel{=}\;\Varid{r}\;\Varid{t}\;\Varid{j}\;(\Varid{inr}\;(\Varid{i},\Varid{p},\Varid{runfold}\;(\pi_{1}\;(\Varid{f}\;\anonymous \;\Varid{t})\;\Varid{i}\;\Varid{p})\;\Varid{j}\;\Varid{q})){}\<[E]%
+\>[23]{}\{\mskip1.5mu \Varid{i}\;\in\;\Conid{I}\mskip1.5mu\}\;(\Varid{t}\;\in\;\Conid{T}\;\Varid{i})\;{}\<[E]%
+\\
+\>[23]{}(\Varid{j}\;\in\;\Conid{J})\;\rightarrow\;\Conid{Path}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\;\Conid{P}^{\Conid{J}}\;\Varid{i}\;(\Varid{funfold}\;\Varid{i}\;\Varid{t})\;\Varid{j}\;\rightarrow\;\Conid{Q}\;\Varid{i}\;\Varid{t}\;\Varid{j}{}\<[E]%
+\\
+\>[12]{}\Varid{runfold}\;\Varid{t}\;\Varid{j}\;(\Varid{path}\;(\Varid{inl}\;\Varid{x}))\;\mathrel{=}\;{}\<[E]%
+\\
+\>[12]{}\hsindent{2}{}\<[14]%
+\>[14]{}\Varid{r}\;\Varid{t}\;\Varid{j}\;(\Varid{inl}\;\Varid{x}){}\<[E]%
+\\
+\>[12]{}\Varid{runfold}\;\Varid{t}\;\Varid{j}\;(\Varid{path}\;(\Varid{inr}\;(\Varid{i},(\Varid{p},\Varid{q}))))\;\mathrel{=}\;{}\<[E]%
+\\
+\>[12]{}\hsindent{2}{}\<[14]%
+\>[14]{}\Varid{r}\;\Varid{t}\;\Varid{j}\;(\Varid{inr}\;(\Varid{i},\Varid{p},\Varid{runfold}\;(\pi_{1}\;(\Varid{f}\;\anonymous \;\Varid{t})\;\Varid{i}\;\Varid{p})\;\Varid{j}\;\Varid{q})){}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\Varid{-}\mskip1.5mu\}{}\<[E]%
 \ColumnHook
@@
 
-\subsubsection{\ensuremath{\Conid{WI}} from \ensuremath{\Conid{W}}}
+\subsection*{\ensuremath{\Conid{WI}} from \ensuremath{\Conid{W}}}
 
@@
 \column{B}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
-\>[B]{}\Conid{WI′}\;\in\;\{\mskip1.5mu \Conid{I}\;\in\;\Conid{Set}\mskip1.5mu\}\;(\Conid{S}\;\in\;\Conid{I}\;\rightarrow\;\Conid{Set})\;(\Conid{P}\;\in\;(\Varid{i}\;\in\;\Conid{I})\;(\Varid{s}\;\in\;\Conid{S}\;\Varid{i})\;\rightarrow\;\Conid{I}\;\rightarrow\;\Conid{Set})\;\rightarrow\;\Conid{Set}{}\<[E]%
-\\
-\>[B]{}\Conid{WI′}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\Conid{S}\;\Conid{P}\;\mathrel{=}\;\Conid{W}\;(\Sigma\;\Conid{I}\;\Conid{S})\;(\lambda (\!\;\Varid{i}\;\!,\!\;\Varid{s}\;\!\!)\;\rightarrow\;\Sigma\;\Conid{I}\;(\Conid{P}\;\Varid{i}\;\Varid{s})\;\!\;\!){}\<[E]%
+\column{8}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Conid{WI′}\;\in\;{}\<[8]%
+\>[8]{}\{\mskip1.5mu \Conid{I}\;\in\;\Conid{Set}\mskip1.5mu\}\;(\Conid{S}\;\in\;\Conid{I}\;\rightarrow\;\Conid{Set})\;{}\<[E]%
+\\
+\>[8]{}(\Conid{P}\;\in\;(\Varid{i}\;\in\;\Conid{I})\;(\Varid{s}\;\in\;\Conid{S}\;\Varid{i})\;\rightarrow\;\Conid{I}\;\rightarrow\;\Conid{Set})\;\rightarrow\;\Conid{Set}{}\<[E]%
+\\
+\>[B]{}\Conid{WI′}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\Conid{S}\;\Conid{P}\;\mathrel{=}\;\Conid{W}\;(\Sigma(\!\;\Varid{i}\;\in\;\Conid{I}\;\!)\!\times\!\;\Conid{S}\;\Varid{i})\;(\lambda (\!\;\Varid{i}\;\!,\!\;\Varid{s}\;\!\!)\;\rightarrow\;\Sigma(\!\;\Varid{i′}\;\in\;\Conid{I}\;\!)\!\times\!\;\Conid{P}\;\Varid{i}\;\Varid{s}\;\Varid{i′}\;\!\;\!){}\<[E]%
 \ColumnHook
@@
 \column{B}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
-\>[B]{}\Conid{WIl}\;\in\;\{\mskip1.5mu \Conid{I}\;\in\;\Conid{Set}\mskip1.5mu\}\;(\Conid{S}\;\in\;\Conid{I}\;\rightarrow\;\Conid{Set})\;(\Conid{P}\;\in\;(\Varid{i}\;\in\;\Conid{I})\;(\Varid{s}\;\in\;\Conid{S}\;\Varid{i})\;\rightarrow\;\Conid{I}\;\rightarrow\;\Conid{Set})\;\rightarrow\;\Conid{Set}{}\<[E]%
-\\
-\>[B]{}\Conid{WIl}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\Conid{S}\;\Conid{P}\;\mathrel{=}\;\Conid{W}\;(\Conid{I}\;\times\;(\Sigma\;\Conid{I}\;\Conid{S}))\;(\lambda (\!\;\Varid{i′}\;\!,\!\;\Varid{i}\;\!,\!\;\Varid{s}\;\!\!)\;\rightarrow\;\Sigma\;\Conid{I}\;(\Conid{P}\;\Varid{i}\;\Varid{s})\;\!\;\!){}\<[E]%
+\column{8}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Conid{WIl}\;\in\;{}\<[8]%
+\>[8]{}\{\mskip1.5mu \Conid{I}\;\in\;\Conid{Set}\mskip1.5mu\}\;(\Conid{S}\;\in\;\Conid{I}\;\rightarrow\;\Conid{Set})\;{}\<[E]%
+\\
+\>[8]{}(\Conid{P}\;\in\;(\Varid{i}\;\in\;\Conid{I})\;(\Varid{s}\;\in\;\Conid{S}\;\Varid{i})\;\rightarrow\;\Conid{I}\;\rightarrow\;\Conid{Set})\;\rightarrow\;\Conid{Set}{}\<[E]%
+\\
+\>[B]{}\Conid{WIl}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\Conid{S}\;\Conid{P}\;\mathrel{=}\;\Conid{W}\;(\Conid{I}\;\times\;(\Sigma(\!\;\Varid{i}\;\in\;\Conid{I}\;\!)\!\times\!\;\Conid{S}\;\Varid{i}))\;(\lambda (\!\;\Varid{i′}\;\!,\!\;\Varid{i}\;\!,\!\;\Varid{s}\;\!\!)\;\rightarrow\;\Sigma(\!\;\Varid{i′}\;\in\;\Conid{I}\;\!)\!\times\!\;\Conid{P}\;\Varid{i}\;\Varid{s}\;\Varid{i′}\;\!\;\!){}\<[E]%
 \ColumnHook
@@
 \\
-\>[3]{}\Varid{lup}\;(\Varid{sup}\;(\Varid{i},\Varid{s})\;\Varid{f})\;\mathrel{=}\;\Varid{sup}\;(\Varid{i},(\Varid{i},\Varid{s}))\;(\lambda\;\Varid{p}\;\rightarrow\;\Varid{lup}\;(\Varid{f}\;\Varid{p})){}\<[E]%
+\>[3]{}\Varid{lup}\;(\Varid{sup}\;((\Varid{i},\Varid{s}),\Varid{f}))\;\mathrel{=}\;\Varid{sup}\;((\Varid{i},(\Varid{i},\Varid{s})),(\lambda\;\Varid{p}\;\rightarrow\;\Varid{lup}\;(\Varid{f}\;\Varid{p}))){}\<[E]%
 \\[\blanklineskip]%
@@
 \\
-\>[3]{}\Varid{ldown}\;\Varid{i}\;(\Varid{sup}\;\Varid{s}\;\Varid{f})\;\mathrel{=}\;\Varid{sup}\;(\Varid{i},\Varid{s})\;\lambda (\!\;\Varid{i′}\;\!,\!\;\Varid{p}\;\!\!)\;\rightarrow\;\Varid{ldown}\;\Varid{i′}\;(\Varid{f}\;(\Varid{i′},\Varid{p}))\;\!\;\!{}\<[E]%
+\>[3]{}\Varid{ldown}\;\Varid{i}\;(\Varid{sup}\;(\Varid{s},\Varid{f}))\;\mathrel{=}\;\Varid{sup}\;((\Varid{i},\Varid{s}),\lambda (\!\;\Varid{i′}\;\!,\!\;\Varid{p}\;\!\!)\;\rightarrow\;\Varid{ldown}\;\Varid{i′}\;(\Varid{f}\;(\Varid{i′},\Varid{p}))\;\!\;\!){}\<[E]%
 \ColumnHook
@@
 \column{B}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
-\>[B]{}\Conid{WI}\;\in\;\{\mskip1.5mu \Conid{I}\;\in\;\Conid{Set}\mskip1.5mu\}\;(\Conid{S}\;\in\;\Conid{I}\;\rightarrow\;\Conid{Set})\;(\Conid{P}\;\in\;(\Varid{i}\;\in\;\Conid{I})\;(\Varid{s}\;\in\;\Conid{S}\;\Varid{i})\;\rightarrow\;\Conid{I}\;\rightarrow\;\Conid{Set})\;\rightarrow\;\Conid{I}\;\rightarrow\;\Conid{Set}{}\<[E]%
+\column{7}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Conid{WI}\;\in\;{}\<[7]%
+\>[7]{}\{\mskip1.5mu \Conid{I}\;\in\;\Conid{Set}\mskip1.5mu\}\;(\Conid{S}\;\in\;\Conid{I}\;\rightarrow\;\Conid{Set})\;{}\<[E]%
+\\
+\>[7]{}(\Conid{P}\;\in\;(\Varid{i}\;\in\;\Conid{I})\;(\Varid{s}\;\in\;\Conid{S}\;\Varid{i})\;\rightarrow\;\Conid{I}\;\rightarrow\;\Conid{Set})\;\rightarrow\;\Conid{I}\;\rightarrow\;\Conid{Set}{}\<[E]%
 \\
@@
 \column{E}{@{}>{\hspre}l<{\hspost}@{}}%
-\>[3]{}\Keyword{open}\;\Keyword{import}\;\Varid{ifunc}{}\<[E]%
-\\
-\>[3]{}\Keyword{open}\;\Keyword{import}\;\Varid{icont}{}\<[E]%
-\\[\blanklineskip]%
 \>[3]{}\Varid{sup}\;\in\;\;\Varid{⟦}\;\Conid{S}\;\lhd^{\star}\;\Conid{P}\;\Varid{⟧}^{\star}\;(\Conid{WI}\;\Conid{S}\;\Conid{P})\;{}\<[37]%
@@
 \>[19]{}({}\<[19E]%
-\>[22]{}\Varid{sup}\;(\anonymous ,\Varid{s})\;(\lambda (\!\;\Varid{i}\;\!,\!\;\Varid{p}\;\!\!)\;\rightarrow\;\pi_{0}\;(\Varid{f}\;\Varid{i}\;\Varid{p})\;\!\;\!)){}\<[E]%
+\>[22]{}\Varid{sup}\;((\anonymous ,\Varid{s}),\lambda (\!\;\Varid{i}\;\!,\!\;\Varid{p}\;\!\!)\;\rightarrow\;\pi_{0}\;(\Varid{f}\;\Varid{i}\;\Varid{p})\;\!\;\!)){}\<[E]%
 \\
 \>[19]{},{}\<[19E]%
-\>[22]{}\Varid{cong}\;(\Varid{sup}\;(\anonymous ,\anonymous ,\Varid{s}))\;(\Varid{ext}\;\lambda (\!\;\Varid{i}\;\!,\!\;\Varid{p}\;\!\!)\;\rightarrow\;\pi_{1}\;(\Varid{f}\;\Varid{i}\;\Varid{p})\;\!\;\!){}\<[E]%
-\ColumnHook
-\end{hscode}\resethooks
-
-The recursion principle inevitably then relies on the uniqueness of identity 
+\>[22]{}\Varid{cong}\;(\lambda\;\Varid{x}\;\rightarrow\;\Varid{sup}\;((\anonymous ,\anonymous ,\Varid{s}),\Varid{x}))\;(\Varid{ext}\;\lambda (\!\;\Varid{i}\;\!,\!\;\Varid{p}\;\!\!)\;\rightarrow\;\pi_{1}\;(\Varid{f}\;\Varid{i}\;\Varid{p})\;\!\;\!){}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+The recursion principle then relies on the uniqueness of identity 
 proofs.
@@
 \\
-\>[3]{}\Varid{wirec}\;\{\mskip1.5mu \Varid{i}\mskip1.5mu\}\;(\Varid{sup}\;(\Varid{i′},\Varid{s})\;\Varid{f},\Varid{ok})\;\Conid{Q}\;\Varid{m}\;\Keyword{with}\;\pi_{0}\equiv\;(\Varid{sup₁≡}\;\Varid{ok}){}\<[E]%
-\\
-\>[3]{}\Varid{wirec}\;\{\mskip1.5mu \Varid{i}\mskip1.5mu\}\;(\Varid{sup}\;(\Varid{.i},\Varid{s})\;\Varid{f},\Varid{ok})\;\Conid{Q}\;\Varid{m}\;\mid \;\Varid{refl}\;\mathrel{=}\;{}\<[E]%
-\\
-\>[3]{}\hsindent{2}{}\<[5]%
-\>[5]{}\Varid{subst}\;\Conid{Q}\;(\Varid{cong}\;\{\mskip1.5mu \Conid{B}\;\mathrel{=}\;\lambda\;\anonymous \;\rightarrow\;\Conid{WI}\;\Conid{S}\;\Conid{P}\;\Varid{i}\mskip1.5mu\}\;(\lambda\;\Varid{x}\;\rightarrow\;\Varid{sup}\;(\Varid{i},\Varid{s})\;\Varid{f},\Varid{x})\;\Conid{UIP})\;{}\<[E]%
+\>[3]{}\Varid{wirec}\;\{\mskip1.5mu \Varid{i}\mskip1.5mu\}\;(\Varid{sup}\;((\Varid{i′},\Varid{s}),\Varid{f}),\Varid{ok})\;\Conid{Q}\;\Varid{m}\;\Keyword{with}\;\pi_{0}\equiv\;(\Varid{sup₁≡}\;\Varid{ok}){}\<[E]%
+\\
+\>[3]{}\Varid{wirec}\;\{\mskip1.5mu \Varid{i}\mskip1.5mu\}\;(\Varid{sup}\;((\Varid{.i},\Varid{s}),\Varid{f}),\Varid{ok})\;\Conid{Q}\;\Varid{m}\;\mid \;\Varid{refl}\;\mathrel{=}\;{}\<[E]%
+\\
+\>[3]{}\hsindent{2}{}\<[5]%
+\>[5]{}\Varid{subst}\;\Conid{Q}\;(\Varid{cong}\;\{\mskip1.5mu \Conid{B}\;\mathrel{=}\;\lambda\;\anonymous \;\rightarrow\;\Conid{WI}\;\Conid{S}\;\Conid{P}\;\Varid{i}\mskip1.5mu\}\;(\lambda\;\Varid{x}\;\rightarrow\;\Varid{sup}\;((\Varid{i},\Varid{s}),\Varid{f}),\Varid{x})\;\Conid{UIP})\;{}\<[E]%
 \\
@@
 
-It's then straight forward but labourious to prove the $\beta$ law for \ensuremath{\Varid{wirec}}, which would have this type:
+It's then straight forward but labourious to prove the $\beta$ law for \ensuremath{\Varid{wirec}}, which would has type:
 
@@
 \column{11}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{12}{@{}>{\hspre}l<{\hspost}@{}}%
 \column{14}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{18}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{22}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{25}{@{}>{\hspre}l<{\hspost}@{}}%
 \column{35}{@{}>{\hspre}l<{\hspost}@{}}%
@@
 \>[B]{}\Conid{Path}\;\in\;{}\<[9]%
-\>[9]{}\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\in\;\Conid{Set}\mskip1.5mu\}\;(\Conid{S}\;\in\;\Conid{I}\;\rightarrow\;\Conid{Set})\;{}\<[E]%
+\>[9]{}\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\in\;\Conid{Set}\mskip1.5mu\}\;(\Conid{S}\;\in\;\Conid{J}\;\rightarrow\;\Conid{Set})\;{}\<[E]%
 \\
 \>[9]{}(\Conid{P}^{\Conid{I}}\;{}\<[14]%
-\>[14]{}\in\;(\Varid{i}\;\in\;\Conid{I})\;\rightarrow\;\Conid{S}\;\Varid{i}\;\rightarrow\;\Conid{I}\;{}\<[35]%
+\>[14]{}\in\;(\Varid{j}\;\in\;\Conid{J})\;\rightarrow\;\Conid{S}\;\Varid{j}\;\rightarrow\;\Conid{I}\;{}\<[35]%
 \>[35]{}\rightarrow\;\Conid{Set})\;{}\<[E]%
@@
 \>[9]{}(\Conid{P}^{\Conid{J}}\;{}\<[14]%
-\>[14]{}\in\;(\Varid{i}\;\in\;\Conid{I})\;\rightarrow\;\Conid{S}\;\Varid{i}\;\rightarrow\;\Conid{J}\;{}\<[35]%
+\>[14]{}\in\;(\Varid{j}\;\in\;\Conid{J})\;\rightarrow\;\Conid{S}\;\Varid{j}\;\rightarrow\;\Conid{J}\;{}\<[35]%
 \>[35]{}\rightarrow\;\Conid{Set})\;{}\<[E]%
 \\
-\>[9]{}(\Varid{i}\;\in\;\Conid{I})\;\rightarrow\;\Conid{WI}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\;\Varid{i}\;\rightarrow\;\Conid{J}\;\rightarrow\;\Conid{Set}{}\<[E]%
-\\
-\>[B]{}\Conid{Pathk}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{J}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{S}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{P}^{\Conid{I}}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{P}^{\Conid{J}}\mskip1.5mu\}\;\Varid{i}\;\Varid{w}\;\mathrel{=}\;\Conid{WI}\;\Conid{PathS}\;\Conid{PathP}\;(\Varid{i},\Varid{w}){}\<[E]%
-\\
-\>[B]{}\hsindent{3}{}\<[3]%
-\>[3]{}\Keyword{where}\;\Conid{PathS}\;\in\;\Sigma\;\Conid{I}\;(\Conid{WI}\;\Conid{S}\;\Conid{P}^{\Conid{I}})\;\rightarrow\;\Conid{Set}{}\<[E]%
+\>[9]{}(\Varid{j}\;\in\;\Conid{J})\;\rightarrow\;\Conid{WI}\;\Conid{S}\;\Conid{P}^{\Conid{J}}\;\Varid{j}\;\rightarrow\;\Conid{I}\;\rightarrow\;\Conid{Set}{}\<[E]%
+\\
+\>[B]{}\Conid{Path}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{J}\mskip1.5mu\}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\;\Conid{P}^{\Conid{J}}\;\Varid{j}\;\Varid{w}\;\Varid{i}\;\mathrel{=}\;\Conid{WI}\;\Conid{PathS}\;\Conid{PathP}\;(\Varid{j},\Varid{w}){}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Keyword{where}\;\Conid{PathS}\;\in\;\Sigma(\!\;\Varid{j}\;\in\;\Conid{J}\;\!)\!\times\!\;\Conid{WI}\;\Conid{S}\;\Conid{P}^{\Conid{J}}\;\Varid{j}\;\rightarrow\;\Conid{Set}{}\<[E]%
 \\
 \>[3]{}\hsindent{6}{}\<[9]%
-\>[9]{}\Conid{PathS}\;(\Varid{i},\Varid{sup}\;(\Varid{s},\Varid{f}))\;\mathrel{=}\;\Conid{P}^{\Conid{J}}\;\Varid{i}\;\Varid{s}\;\Varid{j}\;\uplus\;\Sigma\;\Conid{I}\;(\Conid{P}^{\Conid{I}}\;\Varid{i}\;\Varid{s}){}\<[E]%
+\>[9]{}\Conid{PathS}\;(\Varid{j},\Varid{sup}\;(\Varid{s},\Varid{f}))\;\mathrel{=}\;\Conid{P}^{\Conid{I}}\;\Varid{j}\;\Varid{s}\;\Varid{i}\;\uplus\;\Sigma\;\Conid{J}\;(\Conid{P}^{\Conid{J}}\;\Varid{j}\;\Varid{s}){}\<[E]%
 \\
 \>[3]{}\hsindent{6}{}\<[9]%
-\>[9]{}\Conid{PathP}\;\in\;(\Varid{iw}\;\in\;\Sigma\;\Conid{I}\;(\Conid{WI}\;\Conid{S}\;\Conid{P}^{\Conid{I}}))\;(\Varid{s}\;\in\;\Conid{PathS}\;\Varid{iw})\;\rightarrow\;\Sigma\;\Conid{I}\;(\Conid{WI}\;\Conid{S}\;\Conid{P}^{\Conid{I}})\;\rightarrow\;\Conid{Set}{}\<[E]%
+\>[9]{}\Conid{PathP}\;\in\;(\Varid{jw}\;\in\;\Sigma(\!\;\Varid{j}\;\in\;\Conid{J}\;\!)\!\times\!\;\Conid{WI}\;\Conid{S}\;\Conid{P}^{\Conid{J}}\;\Varid{j})\;(\Varid{s}\;\in\;\Conid{PathS}\;\Varid{jw})\;\rightarrow\;\Sigma(\!\;\Varid{j}\;\in\;\Conid{J}\;\!)\!\times\!\;\Conid{WI}\;\Conid{S}\;\Conid{P}^{\Conid{J}}\;\Varid{j}\;\rightarrow\;\Conid{Set}{}\<[E]%
 \\
 \>[3]{}\hsindent{6}{}\<[9]%
-\>[9]{}\Conid{PathP}\;(\Varid{i},\Varid{sup}\;(\Varid{s},\Varid{f}))\;(\Varid{inl}\;\Varid{p})\;(\Varid{i′},\Varid{w′})\;\mathrel{=}\;\bot{}\<[E]%
+\>[9]{}\Conid{PathP}\;(\Varid{j},\Varid{sup}\;(\Varid{s},\Varid{f}))\;(\Varid{inl}\;\Varid{p})\;(\Varid{j′},\Varid{w′})\;\mathrel{=}\;\bot{}\<[E]%
 \\
 \>[3]{}\hsindent{6}{}\<[9]%
-\>[9]{}\Conid{PathP}\;(\Varid{i},\Varid{sup}\;(\Varid{s},\Varid{f}))\;(\Varid{inr}\;(\Varid{i′′},\Varid{p}))\;(\Varid{i′},\Varid{w′})\;\mathrel{=}\;{}\<[E]%
+\>[9]{}\Conid{PathP}\;(\Varid{j},\Varid{sup}\;(\Varid{s},\Varid{f}))\;(\Varid{inr}\;(\Varid{j′′},\Varid{p}))\;(\Varid{j′},\Varid{w′})\;\mathrel{=}\;{}\<[E]%
 \\
 \>[9]{}\hsindent{2}{}\<[11]%
-\>[11]{}(\Varid{i′′}\;\equiv\;\Varid{i′})\;\times\;(\Varid{f}\;\Varid{i′′}\;\Varid{p}\;\cong\;\Varid{w′}){}\<[E]%
-\\[\blanklineskip]%
-\>[B]{}\Varid{path}\;\in\;{}\<[9]%
-\>[9]{}\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\in\;\Conid{Set}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{S}\;\in\;\Conid{I}\;\rightarrow\;\Conid{Set}\mskip1.5mu\}\;{}\<[E]%
-\\
-\>[9]{}\{\mskip1.5mu \Conid{P}^{\Conid{I}}\;{}\<[14]%
-\>[14]{}\in\;(\Varid{i}\;\in\;\Conid{I})\;\rightarrow\;\Conid{S}\;\Varid{i}\;\rightarrow\;\Conid{I}\;{}\<[35]%
-\>[35]{}\rightarrow\;\Conid{Set}\mskip1.5mu\}\;{}\<[E]%
-\\
-\>[9]{}\{\mskip1.5mu \Conid{P}^{\Conid{J}}\;{}\<[14]%
-\>[14]{}\in\;(\Varid{i}\;\in\;\Conid{I})\;\rightarrow\;\Conid{S}\;\Varid{i}\;\rightarrow\;\Conid{J}\;{}\<[35]%
-\>[35]{}\rightarrow\;\Conid{Set}\mskip1.5mu\}\;{}\<[E]%
-\\
-\>[9]{}\{\mskip1.5mu \Varid{i}\;\in\;\Conid{I}\mskip1.5mu\}\;\rightarrow\;\{\mskip1.5mu \Varid{s}\;\in\;\Conid{S}\;\Varid{i}\mskip1.5mu\}\;\{\mskip1.5mu \Varid{f}\;\in\;\Conid{P}^{\Conid{I}}\;\Varid{i}\;\Varid{s}\;\rightarrow^{\star}\;\Conid{WI}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\mskip1.5mu\}\;\rightarrow\;\{\mskip1.5mu \Varid{j}\;\in\;\Conid{J}\mskip1.5mu\}\;{}\<[E]%
-\\
-\>[9]{}\rightarrow\;{}\<[12]%
-\>[12]{}\Conid{P}^{\Conid{J}}\;\Varid{i}\;\Varid{s}\;\Varid{j}\;{}\<[22]%
-\>[22]{}\uplus\;{}\<[25]%
-\>[25]{}(\Sigma\;\Conid{I}\;\lambda\;\Varid{i′}\;\rightarrow\;\Sigma\;(\Conid{P}^{\Conid{I}}\;\Varid{i}\;\Varid{s}\;\Varid{i′})\;\lambda\;\Varid{p}\;\rightarrow\;\Conid{Pathk}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\;\Conid{P}^{\Conid{J}}\;\Varid{i′}\;(\Varid{f}\;\Varid{i′}\;\Varid{p})\;\Varid{j})\;{}\<[E]%
-\\
-\>[9]{}\rightarrow\;{}\<[12]%
-\>[12]{}\Conid{Pathk}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\;\Conid{P}^{\Conid{J}}\;\Varid{i}\;(\Varid{sup}\;(\Varid{s},\Varid{f}))\;\Varid{j}{}\<[E]%
-\\
-\>[B]{}\Varid{pathk}\;(\Varid{inl}\;\Varid{p})\;\mathrel{=}\;\Varid{sup}\;(\Varid{inl}\;\Varid{p},\lambda\;\Varid{i}\;()){}\<[E]%
-\\
-\>[B]{}\Varid{pathk}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{J}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{S}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{P}^{\Conid{I}}\mskip1.5mu\}\;\{\mskip1.5mu \Conid{P}^{\Conid{J}}\mskip1.5mu\}\;\{\mskip1.5mu \Varid{i}\mskip1.5mu\}\;\{\mskip1.5mu \Varid{s}\mskip1.5mu\}\;\{\mskip1.5mu \Varid{f}\mskip1.5mu\}\;\{\mskip1.5mu \Varid{j}\mskip1.5mu\}\;(\Varid{inr}\;(\Varid{i′′},(\Varid{q},\Varid{r})))\;\mathrel{=}\;\Varid{sup}\;((\Varid{inr}\;(\Varid{i′′},\Varid{q})),\Varid{sub}){}\<[E]%
-\\
-\>[B]{}\hsindent{3}{}\<[3]%
-\>[3]{}\Keyword{where}\;\Varid{sub}\;\in\;(\Varid{iw}\;\in\;\Sigma\;\Conid{I}\;(\Conid{WI}\;\Conid{S}\;\Conid{P}^{\Conid{I}}))\;\rightarrow\;{}\<[E]%
-\\
-\>[3]{}\hsindent{15}{}\<[18]%
-\>[18]{}(\Varid{i′′}\;\equiv\;\pi_{0}\;\Varid{iw})\;\times\;(\Varid{f}\;\Varid{i′′}\;\Varid{q}\;\cong\;\pi_{1}\;\Varid{iw})\;\rightarrow\;\Conid{Pathk}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\;\Conid{P}^{\Conid{J}}\;(\pi_{0}\;\Varid{iw})\;(\pi_{1}\;\Varid{iw})\;\Varid{j}{}\<[E]%
-\\
-\>[3]{}\hsindent{6}{}\<[9]%
-\>[9]{}\Varid{sub}\;(\Varid{i′},\Varid{w′})\;(\Varid{eqi},\Varid{eqw})\;\mathrel{=}\;\Varid{subst}\;(\Conid{WI}\;\anonymous \;\anonymous )\;(\Varid{cong₂}\;\anonymous ,\anonymous \;\Varid{eqi}\;\Varid{eqw})\;\Varid{r}{}\<[E]%
-\ColumnHook
-\end{hscode}\resethooks
-
-\subsection{\ensuremath{\Conid{M}} from \ensuremath{\Conid{W}}}
+\>[11]{}(\Varid{j′′}\;\equiv\;\Varid{j′})\;\times\;(\Varid{f}\;\Varid{j′′}\;\Varid{p}\;\cong\;\Varid{w′}){}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+\subsection*{\ensuremath{\Conid{M}} from \ensuremath{\Conid{W}}}
 Since we have shown that both \ensuremath{\Conid{WI}} and \ensuremath{\Conid{MI}} types can be reduced to their 
@@
 
-In category therory, an $\omega$-chain, is an infinite diagram:
+In category theory, an $\omega$-chain, is an infinite diagram:
 
@@
 \\
-\>[B]{}\Conid{Chain}\;\mathrel{=}\;\Sigma\;(\Conid{ℕ}\;\rightarrow\;\Conid{Set})\;\lambda\;\Conid{A}\;\rightarrow\;(\Varid{n}\;\in\;\Conid{ℕ})\;\rightarrow\;\Conid{A}\;(\Varid{suc}\;\Varid{n})\;\rightarrow\;\Conid{A}\;\Varid{n}{}\<[E]%
+\>[B]{}\Conid{Chain}\;\mathrel{=}\;\Sigma(\!\;\Conid{A}\;\in\;(\Conid{ℕ}\;\rightarrow\;\Conid{Set})\;\!)\!\times\!\;((\Varid{n}\;\in\;\Conid{ℕ})\;\rightarrow\;\Conid{A}\;(\Varid{suc}\;\Varid{n})\;\rightarrow\;\Conid{A}\;\Varid{n}){}\<[E]%
 \ColumnHook
@@
 
-It is also required that the limit is the least such cone. 
+It is also required that the limit is the terminal cone with this property. 
 Again, we can encode the limit of a chain, its projections, and this universal 
@@
 \\
-\>[B]{}\Conid{LIM}\;(\Conid{A},\Varid{a})\;\mathrel{=}\;\Sigma\;((\Varid{n}\;\in\;\Conid{ℕ})\;\rightarrow\;\Conid{A}\;\Varid{n})\;\lambda\;\Varid{f}\;\rightarrow\;((\Varid{n}\;\in\;\Conid{ℕ})\;\rightarrow\;\Varid{a}\;\Varid{n}\;(\Varid{f}\;(\Varid{suc}\;\Varid{n}))\;\equiv\;\Varid{f}\;\Varid{n}){}\<[E]%
+\>[B]{}\Conid{LIM}\;(\Conid{A},\Varid{a})\;\mathrel{=}\;\Sigma(\!\;\Varid{f}\;\in\;((\Varid{n}\;\in\;\Conid{ℕ})\;\rightarrow\;\Conid{A}\;\Varid{n})\;\!)\!\times\!\;((\Varid{n}\;\in\;\Conid{ℕ})\;\rightarrow\;\Varid{a}\;\Varid{n}\;(\Varid{f}\;(\Varid{suc}\;\Varid{n}))\;\equiv\;\Varid{f}\;\Varid{n}){}\<[E]%
 \\[\blanklineskip]%
@@
 \noindent
-then the limit of \ensuremath{\Conid{Fo}} will be the terminal co-algebra of \ensuremath{\Conid{F}}.
+then the limit of \ensuremath{\Conid{F}\;\!^{\omega}} will be the terminal co-algebra of \ensuremath{\Conid{F}}.
 
@@
 \>[21]{}({}\<[21E]%
-\>[24]{}\lambda\;\Varid{n}\;\rightarrow\;\Sigma\;\Conid{S}\;\lambda\;\Varid{s}\;\rightarrow\;\Conid{P}\;\Varid{s}\;\rightarrow\;\Conid{A}\;\Varid{n}){}\<[E]%
+\>[24]{}\lambda\;\Varid{n}\;\rightarrow\;\Sigma(\!\;\Varid{s}\;\in\;\Conid{S}\;\!)\!\times\!\;(\Conid{P}\;\Varid{s}\;\rightarrow\;\Conid{A}\;\Varid{n})){}\<[E]%
 \\
@@
 \>[3]{}\hsindent{8}{}\<[11]%
-\>[11]{}\rightarrow\;(\Sigma\;\Conid{S}\;\lambda\;\Varid{s}\;\rightarrow\;\Conid{P}\;\Varid{s}\;\rightarrow\;(\Conid{LIM}\;(\Conid{A},\Varid{a}))){}\<[E]%
+\>[11]{}\rightarrow\;\Sigma(\!\;\Varid{s}\;\in\;\Conid{S}\;\!)\!\times\!\;(\Conid{P}\;\Varid{s}\;\rightarrow\;(\Conid{LIM}\;(\Conid{A},\Varid{a}))){}\<[E]%
 \ColumnHook
@@
 
-The 1st is by definition, and the others follow by induction of \ensuremath{\Conid{F}}. 
-To show that the structure is preserved by \ensuremath{\Varid{⟦}\anonymous \Varid{⟧}^{\text{\tiny T}}} it is sufficient to suw that for are \ensuremath{\Conid{F}\;\in\;\Conid{ISPT}\;\Conid{J}} and \ensuremath{\Conid{G}\;\in\;\Conid{SPF}\;\Conid{I}\;\Conid{J}} there exist mutually inverse container
-morphisms:
+The firstst is by definition, and the others follow by induction on \ensuremath{\Conid{F}}. 
+To show that the structure is preserved by \ensuremath{\Varid{⟦}\anonymous \Varid{⟧}^{\text{\tiny T}}} it is sufficient to show that for all \ensuremath{\Conid{F}\;\in\;\Conid{ISPT}\;\Conid{J}} and \ensuremath{\Conid{G}\;\in\;\Conid{SPF}\;\Conid{I}\;\Conid{J}} there exist mutually inverse container
+morphisms \ensuremath{\Varid{bindpres}} and \ensuremath{\Varid{bindpres⁻¹}}:
 
@@
 \\[\blanklineskip]%
-\>[B]{}\anonymous \Varid{⊎\char94 T}\anonymous \;\in\;\forall{}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\rightarrow\;(\Conid{F}\;\Conid{G}\;\in\;\Conid{ISPT}\;\Conid{I})\;\rightarrow\;\Conid{ISPT}\;\Conid{I}{}\<[E]%
+\>[B]{}\anonymous \uplus^{\text{\tiny T}}\anonymous \;\in\;\forall{}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\rightarrow\;(\Conid{F}\;\Conid{G}\;\in\;\Conid{ISPT}\;\Conid{I})\;\rightarrow\;\Conid{ISPT}\;\Conid{I}{}\<[E]%
 \\
@@
 \\[\blanklineskip]%
-\>[B]{}\anonymous \mathbin{\times^{\text{\tiny T}}}\anonymous \;\in\;\forall{}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\rightarrow\;(\Conid{F}\;\Conid{G}\;\in\;\Conid{ISPT}\;\Conid{I})\;\rightarrow\;\Conid{ISPT}\;\Conid{I}{}\<[E]%
+\>[B]{}\anonymous \times^{\text{\tiny T}}\anonymous \;\in\;\forall{}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\rightarrow\;(\Conid{F}\;\Conid{G}\;\in\;\Conid{ISPT}\;\Conid{I})\;\rightarrow\;\Conid{ISPT}\;\Conid{I}{}\<[E]%
 \\
@@
 \column{E}{@{}>{\hspre}l<{\hspost}@{}}%
-\>[B]{}\Conid{T}_{Fin}\;\in\;\Conid{SPF}\;\bot\;\Conid{ℕ}{}\<[E]%
-\\
-\>[B]{}\Conid{T}_{Fin}\;\mathrel{=}\;\mu^{\text{\tiny T}}\;(\Sigma^{\text{\tiny T}}\;\Varid{suc}\;(\Varid{⊤\char94 T*}\;\Varid{+\char94 T*}\;(\eta^{\text{\tiny T}}\;\ensuremath{\mbox{$\circ$}}\;\Varid{inr}))){}\<[E]%
-\\[\blanklineskip]%
-\>[B]{}\Conid{T}_{Fin}\;\in\;\Conid{SPF}\;\top\;\Conid{ℕ}{}\<[E]%
-\\
-\>[B]{}\Conid{T}_{Fin}\;\mathrel{=}\;{}\<[9]%
+\>[B]{}\Conid{T}_{\Conid{Fin}}\;\in\;\Conid{SPF}\;\bot\;\Conid{ℕ}{}\<[E]%
+\\
+\>[B]{}\Conid{T}_{\Conid{Fin}}\;\mathrel{=}\;\mu^{\text{\tiny T}}\;(\Sigma^{\text{\tiny T}}\;\Varid{suc}\;(\top^{\text{\tiny T}}\;\mathbin{\uplus^{\text{\tiny T}}}\;(\eta^{\text{\tiny T}}\;\ensuremath{\mbox{$\circ$}}\;\Varid{inr}))){}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\Conid{T}_{\Conid{Vec}}\;\in\;\Conid{SPF}\;\top\;\Conid{ℕ}{}\<[E]%
+\\
+\>[B]{}\Conid{T}_{\Conid{Vec}}\;\mathrel{=}\;{}\<[9]%
 \>[9]{}\mu^{\text{\tiny T}}\;{}\<[15]%
@@
 \\
-\>[15]{}\Varid{+\char94 T*}\;{}\<[21]%
+\>[15]{}\mathbin{\uplus^{\text{\tiny T}}}\;{}\<[21]%
 \>[21]{}\Sigma^{\text{\tiny T}}\;\Varid{suc}\;(\lambda\;\Varid{n}\;\rightarrow\;\eta^{\text{\tiny T}}\;(\Varid{inl}\;\anonymous )\;\mathbin{\times^{\text{\tiny T}}}\;\eta^{\text{\tiny T}}\;(\Varid{inr}\;\Varid{n}))){}\<[E]%
 \\[\blanklineskip]%
-\>[B]{}\Conid{T}_{ScLam}\;\in\;\Conid{SPF}\;\bot\;\Conid{ℕ}{}\<[E]%
-\\
-\>[B]{}\Conid{T}_{ScLam}\;\mathrel{=}\;\mu^{\text{\tiny T}}\;{}\<[15]%
+\>[B]{}\Conid{T}_{\Conid{ScLam}}\;\in\;\Conid{SPF}\;\bot\;\Conid{ℕ}{}\<[E]%
+\\
+\>[B]{}\Conid{T}_{\Conid{ScLam}}\;\mathrel{=}\;\mu^{\text{\tiny T}}\;{}\<[15]%
 \>[15]{}({}\<[21]%
@@
 \\
-\>[15]{}\Varid{+\char94 T*}\;{}\<[21]%
-\>[21]{}(((\eta^{\text{\tiny T}}\;\ensuremath{\mbox{$\circ$}}\;\Varid{inr})\;\Varid{×\char94 T*}\;(\eta^{\text{\tiny T}}\;\ensuremath{\mbox{$\circ$}}\;\Varid{inr})){}\<[E]%
-\\
-\>[15]{}\Varid{+\char94 T*}\;{}\<[21]%
+\>[15]{}\mathbin{\uplus^{\text{\tiny T}}}\;{}\<[21]%
+\>[21]{}(((\eta^{\text{\tiny T}}\;\ensuremath{\mbox{$\circ$}}\;\Varid{inr})\;\mathbin{\times^{\text{\tiny T}}}\;(\eta^{\text{\tiny T}}\;\ensuremath{\mbox{$\circ$}}\;\Varid{inr})){}\<[E]%
+\\
+\>[15]{}\mathbin{\uplus^{\text{\tiny T}}}\;{}\<[21]%
 \>[21]{}\Delta^{\text{\tiny T}}\;\Varid{suc}\;(\eta^{\text{\tiny T}}\;\ensuremath{\mbox{$\circ$}}\;\Varid{inr}))){}\<[E]%

### 2011-05-09 journal/paper.tex
Bib

@@
 The category of containers is a full and faithful sub-category of the functor category.
-We have also shown that the category of containers is locally cartesian closed, and is closed under formation of co-products.
+We have also shown that the category of containers is cartesian closed, and is closed under formation of co-products.
 
@@
 \begin{proposition} 
-\ensuremath{(\Conid{IFunc},\eta^{\text{\tiny F}},\anonymous \bind ^{\text{\tiny F}}\anonymous )} is a \emph{relative monad}\cite{relmonads} on the 
+\ensuremath{(\Conid{IFunc},\eta^{\text{\tiny F}},\anonymous \bind ^{\text{\tiny F}}\anonymous )} is a \emph{relative monad}\cite{alti:relmonads} on the 
 lifting functor \ensuremath{\uparrow\;\in\;\Conid{Set}_{i}\;\rightarrow\;\Conid{Set}_{i+1}}.
@@
 non-indexed counterparts, it only remains to show that \ensuremath{\Conid{M}} types can be, reduced
-to \ensuremath{\Conid{W}} types. This is a result from \cite{C-CSPTs}, though in the setting of 
+to \ensuremath{\Conid{W}} types. This is a result from our previous work on containers~\cite{alti:cont-tcs}, though in the setting of 
 indexed \ensuremath{\Conid{WI}} types, we can give a better intuition.
@@
 For the moment denote this chain \ensuremath{\Conid{F}\;\!^{\omega}\;\mathrel{=}\;((\lambda\;\Varid{n}\;\rightarrow\;\Conid{F}\;\!^{\Varid{n}}\;\top),\lambda\;\Varid{n}\;\rightarrow\;\Conid{F}\;\!^{\Varid{n}}\;\mathbin{!})}.
-We know from Asperti and Longo \cite{AspertiLongo} that if \ensuremath{\Conid{F}} is 
+We know from Asperti and Longo \cite{aspertilongo} that if \ensuremath{\Conid{F}} is 
 $\omega$-continuous, \emph{i.e.} that for any chain \ensuremath{(\Conid{A},\Varid{a})}:
@@
 
-To see this we first observe that there exists an isomorphism between 
-\ensuremath{\Conid{LIM}\;(\Conid{A},\Varid{a})} and \ensuremath{\Conid{LIM}\;(\Conid{A}\;\ensuremath{\mbox{$\circ$}}\;\Varid{suc},\Varid{a}\;\ensuremath{\mbox{$\circ$}}\;\Varid{suc})}:
+To see this we first observe that we there is an isomorphism between the limit of a chain, and the limit of any of its \emph{tails}:
 
@@
 \column{E}{@{}>{\hspre}l<{\hspost}@{}}%
-\>[B]{}\Varid{tailC}\;\in\;(\Varid{c}\;\in\;\Conid{Chain})\;\rightarrow\;\Conid{LIM}\;\Varid{c}\;\rightarrow\;\Conid{LIM}\;(\pi_{0}\;\Varid{c}\;\ensuremath{\mbox{$\circ$}}\;\Varid{suc},\pi_{1}\;\Varid{c}\;\ensuremath{\mbox{$\circ$}}\;\Varid{suc}){}\<[E]%
-\\
-\>[B]{}\Varid{tailC}\;(\Conid{A},\Varid{a})\;(\Varid{f},\Varid{p})\;\mathrel{=}\;\Varid{f}\;\ensuremath{\mbox{$\circ$}}\;\Varid{suc},\Varid{p}\;\ensuremath{\mbox{$\circ$}}\;\Varid{suc}{}\<[E]%
-\\[\blanklineskip]%
-\>[B]{}\Varid{tailC⁻¹}\;\in\;(\Varid{c}\;\in\;\Conid{Chain})\;\rightarrow\;\Conid{LIM}\;(\pi_{0}\;\Varid{c}\;\ensuremath{\mbox{$\circ$}}\;\Varid{suc},\pi_{1}\;\Varid{c}\;\ensuremath{\mbox{$\circ$}}\;\Varid{suc})\;\rightarrow\;\Conid{LIM}\;\Varid{c}{}\<[E]%
-\\
-\>[B]{}\Varid{tailC⁻¹}\;(\Conid{A},\Varid{a})\;(\Varid{f},\Varid{p})\;\mathrel{=}\;\Varid{f′},\Varid{p′}{}\<[E]%
+\>[B]{}\Varid{tail}\;\in\;\Conid{Chain}\;\rightarrow\;\Conid{Chain}{}\<[E]%
+\\
+\>[B]{}\Varid{tail}\;(\Conid{A},\Varid{a})\;\mathrel{=}\;(\Conid{A}\;\ensuremath{\mbox{$\circ$}}\;\Varid{suc},\Varid{a}\;\ensuremath{\mbox{$\circ$}}\;\Varid{suc}){}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\Varid{tailLIM}\;\in\;(\Varid{c}\;\in\;\Conid{Chain})\;\rightarrow\;\Conid{LIM}\;\Varid{c}\;\rightarrow\;\Conid{LIM}\;(\Varid{tail}\;\Varid{c}){}\<[E]%
+\\
+\>[B]{}\Varid{tailLIM}\;(\Conid{A},\Varid{a})\;(\Varid{f},\Varid{p})\;\mathrel{=}\;\Varid{f}\;\ensuremath{\mbox{$\circ$}}\;\Varid{suc},\Varid{p}\;\ensuremath{\mbox{$\circ$}}\;\Varid{suc}{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\Varid{tailLIM⁻¹}\;\in\;(\Varid{c}\;\in\;\Conid{Chain})\;\rightarrow\;\Conid{LIM}\;(\Varid{tail}\;\Varid{c})\;\rightarrow\;\Conid{LIM}\;\Varid{c}{}\<[E]%
+\\
+\>[B]{}\Varid{tailLIM⁻¹}\;(\Conid{A},\Varid{a})\;(\Varid{f},\Varid{p})\;\mathrel{=}\;\Varid{f′},\Varid{p′}{}\<[E]%
 \\
@@
 \noindent 
-this allows us to construct the isomorphism between \ensuremath{\Conid{F}\;(\Conid{LIM}\;\Conid{F}\;\!^{\omega})} and 
+We also note that the tail of \ensuremath{\Conid{F}\;\!^{\omega}} is \ensuremath{((\lambda\;\Varid{n}\;\rightarrow\;\Conid{F}\;(\Conid{F}\;\!^{\Varid{n}}\;\top)),\lambda\;\Varid{n}\;\rightarrow\;\Conid{F}\;(\Conid{F}\;\!^{\Varid{n}}\;\mathbin{!}))}, which allows us to construct the isomorphism between \ensuremath{\Conid{F}\;(\Conid{LIM}\;\Conid{F}\;\!^{\omega})} and
 \ensuremath{\Conid{LIM}\;\Conid{F}\;\!^{\omega}}:
@@
 &\cong&& \ensuremath{\Conid{LIM}\;(\Conid{F}\;\ensuremath{\mbox{$\circ$}}\;(\lambda\;\Varid{n}\;\rightarrow\;\Conid{F}\;\!^{\Varid{n}}\;\top),\Conid{F}\;\ensuremath{\mbox{$\circ$}}\;(\lambda\;\Varid{n}\;\rightarrow\;\Conid{F}\;\!^{\Varid{n}}\;\mathbin{!}))} & \{\mbox{\ensuremath{\Conid{F}} is $\omega$-continuous}\} \\
-&\equiv&& \ensuremath{\Conid{LIM}\;((\lambda\;\Varid{n}\;\rightarrow\;\Conid{F}\;\!^{\Varid{suc}\Varid{n}}\;\top),(\lambda\;\Varid{n}\;\rightarrow\;\Conid{F}\;\!^{\Varid{suc}\Varid{n}}\;\mathbin{!}))} & \{\mbox{definition}\}\\
-&\cong&& \ensuremath{\Conid{LIM}\;\Conid{F}\;\!^{\omega}} & \{\mbox{ \ensuremath{\Varid{tailC}} }\} \\
+&\equiv&& \ensuremath{\Conid{LIM}\;((\lambda\;\Varid{n}\;\rightarrow\;\Conid{F}\;(\Conid{F}\;\!^{\Varid{n}}\;\top)),(\lambda\;\Varid{n}\;\rightarrow\;\Conid{F}\;(\Conid{F}\;\!^{\Varid{n}}\;\mathbin{!})))} & \{\mbox{definition}\}\\
+&\cong&& \ensuremath{\Conid{LIM}\;\Conid{F}\;\!^{\omega}} & \{\mbox{ \ensuremath{\Varid{tailLIM}} }\} \\
 \end{align*}
@@
 
+We now give a syntax for defining indexed strictly positive types and strictly positive families:
+
 \begin{hscode}\SaveRestoreHook
@@
 \column{5}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{12}{@{}>{\hspre}l<{\hspost}@{}}%
 \column{20}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{46}{@{}>{\hspre}l<{\hspost}@{}}%
 \column{47}{@{}>{\hspre}l<{\hspost}@{}}%
@@
 \>[47]{}\rightarrow\;\Conid{SPF}\;\Conid{I}\;\Conid{J}{}\<[E]%
-\\[\blanklineskip]%
-\>[B]{}\anonymous \bind ^{\text{\tiny T}}\anonymous \;\in\;\forall{}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\mskip1.5mu\}\;\rightarrow\;\Conid{ISPT}\;\Conid{I}\;\rightarrow\;\Conid{SPF}\;\Conid{J}\;\Conid{I}\;\rightarrow\;\Conid{ISPT}\;\Conid{J}{}\<[E]%
-\\
-\>[B]{}\eta^{\text{\tiny T}}\;\Varid{i}\;{}\<[12]%
-\>[12]{}\bind ^{\text{\tiny T}}\;\Conid{F}\;\mathrel{=}\;\Conid{F}\;\Varid{i}{}\<[E]%
-\\
-\>[B]{}\Delta^{\text{\tiny T}}\;\Varid{f}\;\Conid{G}\;\Varid{j}\;{}\<[12]%
-\>[12]{}\bind ^{\text{\tiny T}}\;\Conid{F}\;\mathrel{=}\;\Delta^{\text{\tiny T}}\;\Varid{f}\;(\lambda\;\Varid{k}\;\rightarrow\;\Conid{G}\;\Varid{k}\;\bind ^{\text{\tiny T}}\;\Conid{F})\;\Varid{j}{}\<[E]%
-\\
-\>[B]{}\Sigma^{\text{\tiny T}}\;\Varid{f}\;\Conid{G}\;\Varid{k}\;{}\<[12]%
-\>[12]{}\bind ^{\text{\tiny T}}\;\Conid{F}\;\mathrel{=}\;\Sigma^{\text{\tiny T}}\;\Varid{f}\;(\lambda\;\Varid{j}\;\rightarrow\;\Conid{G}\;\Varid{j}\;\bind ^{\text{\tiny T}}\;\Conid{F})\;\Varid{k}{}\<[E]%
-\\
-\>[B]{}\Pi^{\text{\tiny T}}\;\Varid{f}\;\Conid{G}\;\Varid{k}\;{}\<[12]%
-\>[12]{}\bind ^{\text{\tiny T}}\;\Conid{F}\;\mathrel{=}\;\Pi^{\text{\tiny T}}\;\Varid{f}\;(\lambda\;\Varid{j}\;\rightarrow\;\Conid{G}\;\Varid{j}\;\bind ^{\text{\tiny T}}\;\Conid{F})\;\Varid{k}{}\<[E]%
-\\
-\>[B]{}\mu^{\text{\tiny T}}\;\Conid{G}\;\Varid{j}\;{}\<[12]%
-\>[12]{}\bind ^{\text{\tiny T}}\;\Conid{F}\;\mathrel{=}\;\mu^{\text{\tiny T}}\;(\lambda\;\Varid{k}\;\rightarrow\;\Conid{G}\;\Varid{k}\;\bind ^{\text{\tiny T}}\;[\mskip1.5mu {}\<[46]%
-\>[46]{}(\lambda\;\Varid{i}\;\rightarrow\;\Conid{F}\;\Varid{i}\;\bind ^{\text{\tiny T}}\;(\eta^{\text{\tiny T}}\;\ensuremath{\mbox{$\circ$}}\;\Varid{inl})),(\eta^{\text{\tiny T}}\;\ensuremath{\mbox{$\circ$}}\;\Varid{inr})\mskip1.5mu])\;\Varid{j}{}\<[E]%
-\ColumnHook
-\end{hscode}\resethooks
+\\
+\>[3]{}\hsindent{2}{}\<[5]%
+\>[5]{}\nu^{\text{\tiny T}}\;\in\;\forall{}\;\{\mskip1.5mu \Conid{J}\mskip1.5mu\}\;{}\<[20]%
+\>[20]{}(\Conid{F}\;\in\;\Conid{SPF}\;(\Conid{I}\;\uplus\;\Conid{J})\;\Conid{J})\;{}\<[47]%
+\>[47]{}\rightarrow\;\Conid{SPF}\;\Conid{I}\;\Conid{J}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+We intend to interpret terms in this syntax as indexed functors, in order to interpret \ensuremath{\mu^{\text{\tiny T}}} and \ensuremath{\nu^{\text{\tiny T}}} we need to go first via indexed containers, which we know to be closed under ther formation of these fixed-points:
 
@@
 \>[20]{}\mathrel{=}\;\!\;\!\!\;\mu^{\text{\tiny C}}\;\Varid{⟦}\;\Conid{F}\;\Varid{⟧}^{\text{\tiny T}\star}\;\!\!\;\Varid{j}{}\<[E]%
-\ColumnHook
-\end{hscode}\resethooks
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{⟦}\;\nu^{\text{\tiny T}}\;\Conid{F}\;\Varid{j}\;\Varid{⟧}^{\text{\tiny T}}\;{}\<[20]%
+\>[20]{}\mathrel{=}\;\!\;\!\!\;\nu^{\text{\tiny C}}\;\Varid{⟦}\;\Conid{F}\;\Varid{⟧}^{\text{\tiny T}\star}\;\!\!\;\Varid{j}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+We can equip this syntax with a substitution operation, \ensuremath{\anonymous \bind ^{\text{\tiny T}}\anonymous }:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{14}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{48}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Keyword{mutual}{}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Conid{ISPT}\;\in\;\forall{}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\mskip1.5mu\}\;\rightarrow\;(\Conid{I}\;\rightarrow\;\Conid{J})\;\rightarrow\;\Conid{ISPT}\;\Conid{I}\;\rightarrow\;\Conid{ISPT}\;\Conid{J}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Conid{ISPT}\;\gamma\;\Varid{t}\;\mathrel{=}\;\Varid{t}\;\bind ^{\text{\tiny T}}\;(\eta^{\text{\tiny T}}\;\ensuremath{\mbox{$\circ$}}\;\gamma){}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\anonymous \bind ^{\text{\tiny T}}\anonymous \;\in\;\forall{}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\mskip1.5mu\}\;\rightarrow\;\Conid{ISPT}\;\Conid{I}\;\rightarrow\;\Conid{SPF}\;\Conid{J}\;\Conid{I}\;\rightarrow\;\Conid{ISPT}\;\Conid{J}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\eta^{\text{\tiny T}}\;\Varid{i}\;{}\<[14]%
+\>[14]{}\bind ^{\text{\tiny T}}\;\Conid{F}\;\mathrel{=}\;\Conid{F}\;\Varid{i}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Delta^{\text{\tiny T}}\;\Varid{f}\;\Conid{G}\;\Varid{j}\;{}\<[14]%
+\>[14]{}\bind ^{\text{\tiny T}}\;\Conid{F}\;\mathrel{=}\;\Delta^{\text{\tiny T}}\;\Varid{f}\;(\lambda\;\Varid{k}\;\rightarrow\;\Conid{G}\;\Varid{k}\;\bind ^{\text{\tiny T}}\;\Conid{F})\;\Varid{j}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Sigma^{\text{\tiny T}}\;\Varid{f}\;\Conid{G}\;\Varid{k}\;{}\<[14]%
+\>[14]{}\bind ^{\text{\tiny T}}\;\Conid{F}\;\mathrel{=}\;\Sigma^{\text{\tiny T}}\;\Varid{f}\;(\lambda\;\Varid{j}\;\rightarrow\;\Conid{G}\;\Varid{j}\;\bind ^{\text{\tiny T}}\;\Conid{F})\;\Varid{k}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Pi^{\text{\tiny T}}\;\Varid{f}\;\Conid{G}\;\Varid{k}\;{}\<[14]%
+\>[14]{}\bind ^{\text{\tiny T}}\;\Conid{F}\;\mathrel{=}\;\Pi^{\text{\tiny T}}\;\Varid{f}\;(\lambda\;\Varid{j}\;\rightarrow\;\Conid{G}\;\Varid{j}\;\bind ^{\text{\tiny T}}\;\Conid{F})\;\Varid{k}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\mu^{\text{\tiny T}}\;\Conid{G}\;\Varid{j}\;{}\<[14]%
+\>[14]{}\bind ^{\text{\tiny T}}\;\Conid{F}\;\mathrel{=}\;\mu^{\text{\tiny T}}\;(\lambda\;\Varid{k}\;\rightarrow\;\Conid{G}\;\Varid{k}\;\bind ^{\text{\tiny T}}\;[\mskip1.5mu {}\<[48]%
+\>[48]{}(\Conid{ISPT}\;\Varid{inl}\;\ensuremath{\mbox{$\circ$}}\;\Conid{F}),(\eta^{\text{\tiny T}}\;\ensuremath{\mbox{$\circ$}}\;\Varid{inr})\mskip1.5mu])\;\Varid{j}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\nu^{\text{\tiny T}}\;\Conid{G}\;\Varid{j}\;{}\<[14]%
+\>[14]{}\bind ^{\text{\tiny T}}\;\Conid{F}\;\mathrel{=}\;\nu^{\text{\tiny T}}\;(\lambda\;\Varid{k}\;\rightarrow\;\Conid{G}\;\Varid{k}\;\bind ^{\text{\tiny T}}\;[\mskip1.5mu {}\<[48]%
+\>[48]{}(\Conid{ISPT}\;\Varid{inl}\;\ensuremath{\mbox{$\circ$}}\;\Conid{F}),(\eta^{\text{\tiny T}}\;\ensuremath{\mbox{$\circ$}}\;\Varid{inr})\mskip1.5mu])\;\Varid{j}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+As defined above this doesn't pass Agda's termination check, due to deriving the \ensuremath{\Conid{ISPT}} from the monad instance.
+If we define the map of the functor directly the whole thing obviously terminates, at the expense of having to show the two definitions of the map for \ensuremath{\Conid{ISPT}} agree.
 
@@
 
-The firstst is by definition, and the others follow by induction on \ensuremath{\Conid{F}}. 
+The first is by definition, and the others follow by induction on \ensuremath{\Conid{F}}. 
 To show that the structure is preserved by \ensuremath{\Varid{⟦}\anonymous \Varid{⟧}^{\text{\tiny T}}} it is sufficient to show that for all \ensuremath{\Conid{F}\;\in\;\Conid{ISPT}\;\Conid{J}} and \ensuremath{\Conid{G}\;\in\;\Conid{SPF}\;\Conid{I}\;\Conid{J}} there exist mutually inverse container
@@
 
+We define disjoint union and cartesian product just as we did in the functor and container universes:
+
 \begin{hscode}\SaveRestoreHook
@@
 \bibliographystyle{plain}
-\bibliography{paper}
+\bibliography{ic}
 

### 2011-05-09 journal/paper.tex
first version of introduction

--- 2011-05-02 journal/paper.tex
@@
 \usepackage{stmaryrd}
+\usepackage{color}
 
 \newcommand{\note}[1]{}
+\newcommand{\todo}[1]{\textcolor{red}{\textbf{Todo:~}#1}}
 
@@
 
-Blah
+  We show that the syntactically rich notion of inductive families can
+  be reduced to a core type theory with a fixed number of type
+  constructors exploiting the novel notion of indexed containers.
+  Indexed containers generalize simple containers, capturing strictly
+  positive families instead of just strictly positive types, without
+  having to extend the core type theory. Other applications of indexed
+  containers include datatype-generic programming and reasoning about
+  polymorphic functions. The construction presented here has been
+  formalized using the Agda system.
 
@@
 
+\noindent Inductive datatypes are a central feature of modern Type Theory
+(e.g. COQ~\cite{CIC}) or functional programming (e.g. 
+Haskell\footnote{Here we shall view Haskell as an approximation of strong
+  functional programming as proposed by Turner \cite{sfp} and ignore
+non-termination.})
+
+Examples include the natural numbers al Peano:
 \begin{hscode}\SaveRestoreHook
@@
 \end{hscode}\resethooks
-
+the set of lists indexed by any given set:
 \begin{hscode}\SaveRestoreHook
@@
 \end{hscode}\resethooks
-
+and the set of  de Bruijn $\lambda$-terms:
 \begin{hscode}\SaveRestoreHook
@@
 
+\noindent An elegant way to formalize and reason about inductive types
+is to model them as the initial algebra of an endofunctor, we can
+define the siganture functors cirresponding to each of the examples above:
+
 \begin{hscode}\SaveRestoreHook
@@
 
+This perspective has been very
+successful in providing a generic approach to programming with and
+reasoning about inductive types, e.g. see the \emph{Algebra of
+Programming} \cite{BirdDeMoor:AlgProp}.
+
+While the theory of inductive types is well developed, we often want
+to have a finer, more expressive, notion of types, for example to
+ensure the absence of run time errors --- access to arrays out of
+range or access to an undefined variable in the previous example of
+$\lambda$-terms.
+
+To model this we move to the notion of an inductive
+family in Type Theory. A family is a type indexed by another already
+given type. The first example is the family of finite sets \ensuremath{\Conid{Fin}} which
+assigns to any natural number \ensuremath{\Varid{n}} a set \ensuremath{\Conid{Fin}\;\Varid{n}} which has exactly
+\ensuremath{\Varid{n}}-elements. \ensuremath{\Conid{Fin}} can be used where in conventional reasoning we
+assume any finite set, e.g. when dealing with a finite address apce or
+a finite set of variables. The inductive definition of \ensuremath{\Conid{Fin}} refines
+the type of natural numbers:
 \begin{hscode}\SaveRestoreHook
@@
 
+In the same fashion we can refine the type of lists to the type of
+vectors which are additionally indexed by a number indicating the
+length of the vector:
+
 \begin{hscode}\SaveRestoreHook
@@
 
+Using \ensuremath{\Conid{Fin}} and \ensuremath{\Conid{Vec}} instead of \ensuremath{\Conid{Nat}} and \ensuremath{\Conid{List}} enables us to write
+a total projection function projecting the nth element out of vector:
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{20}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Varid{\char95 !!\char95 }\;\in\;\{\mskip1.5mu \Conid{A}\;\in\;\Conid{Set}\mskip1.5mu\}\;\rightarrow\;\Conid{List}\;\Conid{A}\;\rightarrow\;\Conid{ℕ}\;\rightarrow\;\Conid{Maybe}\;\Conid{A}{}\<[E]%
+\\
+\>[B]{}[\mskip1.5mu \mskip1.5mu]\;\mathbin{!!}\;\Varid{n}\;{}\<[20]%
+\>[20]{}\mathrel{=}\;\Varid{nothing}{}\<[E]%
+\\
+\>[B]{}(\Varid{a}\;\Varid{∷}\;\Varid{as})\;\mathbin{!!}\;\Varid{zero}\;{}\<[20]%
+\>[20]{}\mathrel{=}\;\Varid{just}\;\Varid{a}{}\<[E]%
+\\
+\>[B]{}(\Varid{a}\;\Varid{∷}\;\Varid{as})\;\mathbin{!!}\;\Varid{suc}\;\Varid{n}\;{}\<[20]%
+\>[20]{}\mathrel{=}\;\Varid{as}\;\mathbin{!!}\;\Varid{n}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+Note, that a corresponding function \ensuremath{\Varid{\char95 !!\char95 }\;\in\;\{\mskip1.5mu \Conid{A}\;\in\;\Conid{Set}\mskip1.5mu\}\;\rightarrow\;\Conid{List}\;\Conid{A}\;\rightarrow\;\Conid{ℕ}\;\rightarrow\;\Conid{A}} is not definable in a total langauge like Agda.
+
+Finally we can define the notion of a well-scoped lambda term with
+\ensuremath{\Conid{ScLam}} which assigns to a natural number \ensuremath{\Varid{n}} the set of $\lambda$-terms
+with at most \ensuremath{\Varid{n}} free variables \ensuremath{\Conid{ScLam}\;\Varid{n}}. DeBruijn variables are now
+modelled by elements of \ensuremath{\Conid{Fin}\;\Varid{n}} replacing \ensuremath{\Conid{Nat}} in the previous,
+unindexed definition of $\lambda$-terms \ensuremath{\Conid{Lam}}.
+
 \begin{hscode}\SaveRestoreHook
@@
 
-\begin{hscode}\SaveRestoreHook
-\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
-\>[B]{}\Conid{F}_{\Conid{Fin}}\;\in\;(\Conid{ℕ}\;\rightarrow\;\Conid{Set})\;\rightarrow\;\Conid{ℕ}\;\rightarrow\;\Conid{Set}{}\<[E]%
-\\
-\>[B]{}\Conid{F}_{\Conid{Fin}}\;\Conid{X}\;\Varid{n}\;\mathrel{=}\;\Sigma\;\Conid{ℕ}\;\lambda\;\Varid{m}\;\rightarrow\;(\Varid{n}\;\equiv\;\Varid{suc}\;\Varid{m})\;\times\;(\top\;\uplus\;\Conid{X}\;\Varid{m}){}\<[E]%
-\\[\blanklineskip]%
-\>[B]{}\Conid{F}_{\Conid{Vec}}\;\in\;(\Conid{A}\;\in\;\Conid{Set})\;\rightarrow\;(\Conid{ℕ}\;\rightarrow\;\Conid{Set})\;\rightarrow\;\Conid{ℕ}\;\rightarrow\;\Conid{Set}{}\<[E]%
-\\
-\>[B]{}\Conid{F}_{\Conid{Vec}}\;\Conid{A}\;\Conid{X}\;\Varid{n}\;\mathrel{=}\;\Varid{n}\;\equiv\;\Varid{zero}\;\uplus\;\Sigma\;\Conid{ℕ}\;\lambda\;\Varid{m}\;\rightarrow\;(\Varid{n}\;\equiv\;\Varid{suc}\;\Varid{m})\;\times\;(\Conid{A}\;\times\;\Conid{X}\;\Varid{m}){}\<[E]%
-\\[\blanklineskip]%
-\>[B]{}\Conid{F}_{\Conid{ScLam}}\;\in\;(\Conid{ℕ}\;\rightarrow\;\Conid{Set})\;\rightarrow\;\Conid{ℕ}\;\rightarrow\;\Conid{Set}{}\<[E]%
-\\
-\>[B]{}\Conid{F}_{\Conid{ScLam}}\;\Conid{X}\;\Varid{n}\;\mathrel{=}\;\Conid{Fin}\;\Varid{n}\;\uplus\;(\Conid{X}\;\Varid{n}\;\times\;\Conid{X}\;\Varid{n})\;\uplus\;(\Conid{X}\;\ensuremath{\mbox{$\circ$}}\;\Varid{suc})\;\Varid{n}{}\<[E]%
-\ColumnHook
-\end{hscode}\resethooks
-
+\noindent
+Importantly, the constructor
+\ensuremath{\Varid{lam}} reduces the number of \emph{free} variables by one --- by
+binding one. 
+Inductive families may be mutually defined, for example the scoped
+versions of  $\beta$ (\ensuremath{\Conid{NfLam}})
+normal forms and neutral $\lambda$-terms (\ensuremath{\Conid{NeLam}}): 
 \begin{hscode}\SaveRestoreHook
@@
 
+The initial algebra semantics of inductive types can be extended to
+model inductive families by replacing functors on the category \ensuremath{\Conid{Set}}
+with functors on the category of families indexed by a given type - in
+the case of $\lambda$-terms this indexing type was \ensuremath{\Conid{Nat}}. The objects
+of the category of families indexed over a type \ensuremath{\Conid{I}\;\in\;\Varid{set}} are
+\ensuremath{\Conid{I}}-indexed families, i.e. functions of type \ensuremath{\Conid{I}\;\rightarrow\;\Conid{Set}}, and a
+morphism between \ensuremath{\Conid{I}}-indexed families \ensuremath{\Conid{A},\Conid{B}\;\in\;\Conid{I}\;\rightarrow\;\Conid{Set}} is given by a
+family of maps \ensuremath{\Varid{f}\;\in\;(\Varid{i}\;\in\;\Conid{I})\;\to \;\Conid{A}\;\Varid{i}\;\to \;\Conid{B}\;\Varid{i}}
+Indeed, this category
+is easily seen to be isomorphic to the slice category $\ensuremath{\Conid{Set}}/ \ensuremath{\Conid{I}}$ but
+the chosen representation is more convenient type-theoretically. Using
+$\Sigma$-types and equality types from Type Theory, we can define the
+following endofunctors \ensuremath{\Conid{F}_{\Conid{Fin}},\Conid{F}_{\Conid{Vec}}} and \ensuremath{\Conid{F}_{\Conid{Lam}}}
+on the category of families
+over \ensuremath{\Conid{Nat}} whose initial algebras are \ensuremath{\Conid{Fin}} and \ensuremath{\Conid{Lam}}, respectively:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Conid{F}_{\Conid{Fin}}\;\in\;(\Conid{ℕ}\;\rightarrow\;\Conid{Set})\;\rightarrow\;\Conid{ℕ}\;\rightarrow\;\Conid{Set}{}\<[E]%
+\\
+\>[B]{}\Conid{F}_{\Conid{Fin}}\;\Conid{X}\;\Varid{n}\;\mathrel{=}\;\Sigma\;\Conid{ℕ}\;\lambda\;\Varid{m}\;\rightarrow\;(\Varid{n}\;\equiv\;\Varid{suc}\;\Varid{m})\;\times\;(\top\;\uplus\;\Conid{X}\;\Varid{m}){}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\Conid{F}_{\Conid{Vec}}\;\in\;(\Conid{A}\;\in\;\Conid{Set})\;\rightarrow\;(\Conid{ℕ}\;\rightarrow\;\Conid{Set})\;\rightarrow\;\Conid{ℕ}\;\rightarrow\;\Conid{Set}{}\<[E]%
+\\
+\>[B]{}\Conid{F}_{\Conid{Vec}}\;\Conid{A}\;\Conid{X}\;\Varid{n}\;\mathrel{=}\;\Varid{n}\;\equiv\;\Varid{zero}\;\uplus\;\Sigma\;\Conid{ℕ}\;\lambda\;\Varid{m}\;\rightarrow\;(\Varid{n}\;\equiv\;\Varid{suc}\;\Varid{m})\;\times\;(\Conid{A}\;\times\;\Conid{X}\;\Varid{m}){}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\Conid{F}_{\Conid{ScLam}}\;\in\;(\Conid{ℕ}\;\rightarrow\;\Conid{Set})\;\rightarrow\;\Conid{ℕ}\;\rightarrow\;\Conid{Set}{}\<[E]%
+\\
+\>[B]{}\Conid{F}_{\Conid{ScLam}}\;\Conid{X}\;\Varid{n}\;\mathrel{=}\;\Conid{Fin}\;\Varid{n}\;\uplus\;(\Conid{X}\;\Varid{n}\;\times\;\Conid{X}\;\Varid{n})\;\uplus\;(\Conid{X}\;\ensuremath{\mbox{$\circ$}}\;\Varid{suc})\;\Varid{n}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+The equality type expresses the focussed character of the
+constructors for \ensuremath{\Conid{Fin}}.
+
+\todo{Discuss mutual case.}
+
+This approach extends uniformly to more complicated examples such as
+the family of typed $\lambda$-terms, using lists of types  to
+represent typing contexts:
 \begin{hscode}\SaveRestoreHook
@@
 
+\noindent
+Types like this can be used to implement a tag-free, terminating
+evaluator~\cite{bsn}. To obtain the corresponding functors
+is a laborious but straightforward exercise.
+
+\todo{Expand here?}
+
+\subsection{Overview over the paper}
+\label{sec:overview-over-paper}
+
+We develop our type theoretic and categorical background in section
+\ref{sec:background} and also summarize the basic definitions of
+non-indexed containers. In section \ref{sec:ifunc} we develop the
+concept of an indexed functor, showing that this is a relative monad
+and presenting basic constructions on indexed functors including the
+definition of a parametrized initial algebra. In section
+\ref{sec:icont} we devlop the basic theory of indexed containers and
+relate them to indexed functors. Subsequently in section
+\ref{sec:initalg} we construct initial algebras of indexed containers
+assuming the existence of indexed W-types, this can be dualized to
+showing the existence of terminal coalgebras from indexed M-types 
+\ref{sec:termcoalg}. Both requirements, indexed W-types and indexed
+M-types can be derived from ordinary W-types, this is shown in section
+\ref{sec:w-enough}. Finally, we define a syntax from strictly positive
+families and interpret this using indexed containers \ref{sec:spf}.
+
+\subsection{Related work}
+\label{sec:related-work}
+
+\noindent
+Inductive families are the backbone of
+dependently typed programming as present in Epigram or
+Agda~\cite{Agda}. Coq also supports the definition of inductive families
+but programming with them is rather hard --- a situation which has been
+improved by the new \texttt{Program} tactic~\cite{sozeau}. 
+More recently, the implementation of Generalized Algebraic Datatypes 
+(GADTs)~\cite{Hinze:GADT} 
+allows \ensuremath{\Conid{Fin}} and \ensuremath{\Conid{Lam}} to be encoded in Haskell:
+\begin{tabbing}\tt
+~data~Fin~a~where~\\
+\tt ~~~FZero~\char58{}\char58{}~Fin~\char40{}Maybe~a\char41{}\\
+\tt ~~~FSucc~\char58{}\char58{}~Fin~a~\char45{}\char62{}~Fin~\char40{}Maybe~a\char41{}\\
+\tt ~\\
+\tt ~data~Lam~a~where~\\
+\tt ~~~Var~\char58{}\char58{}~Fin~a~\char45{}\char62{}~Lam~a\\
+\tt ~~~App~\char58{}\char58{}~Lam~a~\char45{}\char62{}~Lam~a~\char45{}\char62{}~Lam~a\\
+\tt ~~~Abs~\char58{}\char58{}~Lam~\char40{}Maybe~a\char41{}~\char45{}\char62{}~Lam~a
+\end{tabbing}
+Here \texttt{Fin} and \texttt{Lam} are indexed by types instead of
+natural numbers; The type constructor \texttt{Maybe} serves as a type level
+copy of the $\succ$ constructor for natural numbers.
+Note that \texttt{Lam} is actually just a nested datatype 
+\cite{alti:csl99} while \texttt{Fin} exploits the full power of
+GADTs because the range of the constructors is constrained.
+
+\todo{Rewrite and expand}
+
+The paper is an expanded and revised version of the LICS paper by the
+first and 3rd author \cite{lics}. In the present paper we have
+integrated the Agda formalisation in the main development, which in
+many instances required extending it. We have made explicit the use of
+relative monads which was only hinted at in the conference version
+based on the recent work on relative monads \cite{relmon}. We have
+also dualized the development to terminal coalgebras which requires a
+non-trivial change in the setup (section \ref{sec:termcoalg}).  We
+have also formalized the derivation of indexed W-types from ordinary
+W-types (section \ref{wifromw}. The derivation of M-types from W-types
+(section \ref{sec:mfromw})
+was already given in \cite{C-CSPTs} is revisited here exploiting the
+indexed W-type derived previously amd the development is formalized in
+Agda.
+
+\todo{What did I miss?}
+
 \section{Background}
+\label{sec:background}
 
@@
 \section{Indexed Functors}
+\label{sec:ifunc}
 
@@
 \section{Indexed containers}
+\label{sec:icont}
 
@@
 \section{Initial Algebras of Indexed Containers}
+\label{sec:initalg}
 
@@
 \section{Terminal Co-Algebras of Indexed Containers}
+\label{sec:termcoalg}
 
@@
 \section{W is still enough}
+\label{sec:w-enough}
 
 \subsection*{\ensuremath{\Conid{WI}} from \ensuremath{\Conid{W}}}
+\label{wifromw}
 
@@
 \subsection*{\ensuremath{\Conid{M}} from \ensuremath{\Conid{W}}}
+\label{sec:mfromw}
+
 Since we have shown that both \ensuremath{\Conid{WI}} and \ensuremath{\Conid{MI}} types can be reduced to their 

### 2011-05-10 journal/paper.tex
some rejigging, added some works to bckground.

@@
 assigns to any natural number \ensuremath{\Varid{n}} a set \ensuremath{\Conid{Fin}\;\Varid{n}} which has exactly
-\ensuremath{\Varid{n}}-elements. \ensuremath{\Conid{Fin}} can be used where in conventional reasoning we
-assume any finite set, e.g. when dealing with a finite address apce or
+\ensuremath{\Varid{n}} elements. \ensuremath{\Conid{Fin}} can be used where in conventional reasoning we
+assume any finite set, e.g. when dealing with a finite address apace or
 a finite set of variables. The inductive definition of \ensuremath{\Conid{Fin}} refines
@@
 \todo{Expand here?}
-
-\subsection{Overview over the paper}
-\label{sec:overview-over-paper}
-
-We develop our type theoretic and categorical background in section
-\ref{sec:background} and also summarize the basic definitions of
-non-indexed containers. In section \ref{sec:ifunc} we develop the
-concept of an indexed functor, showing that this is a relative monad
-and presenting basic constructions on indexed functors including the
-definition of a parametrized initial algebra. In section
-\ref{sec:icont} we devlop the basic theory of indexed containers and
-relate them to indexed functors. Subsequently in section
-\ref{sec:initalg} we construct initial algebras of indexed containers
-assuming the existence of indexed W-types, this can be dualized to
-showing the existence of terminal coalgebras from indexed M-types 
-\ref{sec:termcoalg}. Both requirements, indexed W-types and indexed
-M-types can be derived from ordinary W-types, this is shown in section
-\ref{sec:w-enough}. Finally, we define a syntax from strictly positive
-families and interpret this using indexed containers \ref{sec:spf}.
-
-\subsection{Related work}
-\label{sec:related-work}
 
@@
 natural numbers; The type constructor \texttt{Maybe} serves as a type level
-copy of the $\succ$ constructor for natural numbers.
+copy of the \ensuremath{\Varid{succ}} constructor for natural numbers.
 Note that \texttt{Lam} is actually just a nested datatype 
@@
 
-\todo{Rewrite and expand}
-
-The paper is an expanded and revised version of the LICS paper by the
+\subsection{Overview over the paper}
+\label{sec:overview-over-paper}
+
+We develop our type theoretic and categorical background in section
+\ref{sec:background} and also summarize the basic definitions of
+non-indexed containers. In section \ref{sec:ifunc} we develop the
+concept of an indexed functor, showing that this is a relative monad
+and presenting basic constructions on indexed functors including the
+definition of a parametrized initial algebra. In section
+\ref{sec:icont} we devlop the basic theory of indexed containers and
+relate them to indexed functors. Subsequently in section
+\ref{sec:initalg} we construct initial algebras of indexed containers
+assuming the existence of indexed W-types, this can be dualized to
+showing the existence of terminal coalgebras from indexed M-types 
+\ref{sec:termcoalg}. Both requirements, indexed W-types and indexed
+M-types can be derived from ordinary W-types, this is shown in section
+\ref{sec:w-enough}. Finally, we define a syntax from strictly positive
+families and interpret this using indexed containers \ref{sec:spf}.
+
+\subsection{Related work}
+\label{sec:related-work}
+
+\noindent We introduce the notion of indexed container which
+generalizes containers allowing us to represent inductive
+families. This is a further step from \emph{dependent polynomial
+  functors} \cite{HylandGambino} representing endofunctors on a slice
+category. Indexed containers as introduced in the present paper allow us
+to represent functors between different slices and capture also mutual
+and nested inductive definitions.
+
+While Hyland and Gambino \cite{HylandGambino} show that dependent polynomial 
+functors always
+have initial algebras, we show that indexed containers are closed under 
+parametrized initial algebras. Hence we can apply the fixpoint
+construction several times. The flexibility of indexed
+containers allows us to also establish closure under the adjoints of
+reindexing. This leads directly to a grammar for strictly positive
+families, which itself is an instance of a strictly positive family 
+(section \ref{sec:spf}) --- see also our previous work \cite{alti:cats07,alti:jcats07}.
+
+Containers are related to Girard's normal functors \cite{GirardNormal} which
+themselves are a special case of Joyal's analytic functors
+\cite{JoyalA:fonaes} --- those that allow only finite sets of positions.
+Fiore, Gambino, Hyland and Winskel's work on generalized species
+\cite{fiore2008ccb} considers those concepts in a more generic setting ---
+th e precise relation of this work to indexed containers remains to be
+explored.
+
+Perhaps the earliest publication related to indexed containers
+occurs in Petersson and Synek's paper
+\cite{PS89} from 1989. They present rules extending Martin-L{\"o}f's
+type theory with a set constructor for `tree sets' : families of
+mutually defined inductive sets, over a fixed index set.
+
+Inspired in part by Petersson and Synek's constructor,
+Hancock, Hyvernat and Setzer \cite{hancock-apal06} applied indexed (and unindexed)
+containers, under the name `interaction structures' to the task of
+modelling imperative interfaces such as command-response interfaces in
+a number of publications.
+
+This paper is an expanded and revised version of the LICS paper by the
 first and 3rd author \cite{lics}. In the present paper we have
@@
 based on the recent work on relative monads \cite{relmon}. We have
-also dualized the development to terminal coalgebras which requires a
-non-trivial change in the setup (section \ref{sec:termcoalg}).  We
+also dualized the development to terminal coalgebras which required
+the type of paths to be defined inductively instead of recursively as
+done in the conference paper (section \ref{sec:termcoalg}).  We
 have also formalized the derivation of indexed W-types from ordinary
@@
 was already given in \cite{C-CSPTs} is revisited here exploiting the
-indexed W-type derived previously amd the development is formalized in
+indexed W-type derived previously. moreover the development is formalized in
 Agda.
@@
 
-Our contructions are all developed in Agda, and so we adopt its syntax, but we will take certain liberties with its type-theory.
+Our constructions are all developed in Agda, and so we adopt its syntax, but we will take certain liberties with its type-theory.
 
@@
 \noindent
-As a notational convenience, we will continue to define extra Agda data-types in the rest of the paper, but in the end we will show how each of these can be reduced to a theory that contains only \ensuremath{\Conid{W}}.
-For compactness, and readablity we will also define functions using Agda's pattern matching syntax, rather than encoding them using wrec, it is an unstated lemma that each of these definitions can be reduced to terms which only use \ensuremath{\Varid{wrec}}.
+As a notational convenience, we will continue to define extra Agda data-types
+in the rest of the paper, but in the end we will show how each of these can
+be reduced to a theory that contains only \ensuremath{\Conid{W}}. For compactness, and
+readability we will also define functions using Agda's pattern matching
+syntax, rather than encoding them using \ensuremath{\Varid{wrec}}, it is an unstated lemma that
+each of these definitions can be reduced to terms which only use \ensuremath{\Varid{wrec}}.
 
@@
 
-This is an intensioanl equality, but we want to work in a setting with extensional type-theory, so we extend the propositional equality with this extensionality axiom:
+This is an intensional equality, but we want to work in a setting with extensional type-theory, so we extend the propositional equality with this extensionality axiom:
 
@@
 
-This creates non-canonical elements of \ensuremath{\Varid{\char95 ≅\char95 }}, \emph{i.e.} closed terms in equality types which are not \ensuremath{\Varid{refl}}.
-In order to deal with these non-canonical elements, we also rely on axiom \ensuremath{\Conid{K}}, or the uniqueness of idenity proofs:
+This creates non-canonical elements of \ensuremath{\Varid{\char95 ≅\char95 }}, \emph{i.e.} closed terms in
+equality types which are not \ensuremath{\Varid{refl}}. In order to deal with these
+non-canonical elements, we also rely on axiom \ensuremath{\Conid{K}}, or the uniqueness of
+identity proofs:
 
@@
 
-We are going to use type theory versions of certain category theoretic concepts 
-For instance, we use ends \ensuremath{\Conid{End}} to capture natural transformations.
+With these assumptions we obtain a theory which corresponds to
+extensional Type Theory \cite{hofmann-conservativity}.
+
+We are going to use type theory versions of certain category theoretic
+concepts For instance, we use ends \ensuremath{\Conid{End}} to capture natural transformations.
 Given a bifunctor \ensuremath{\Conid{F}\;\in\;\Conid{Set}^{\Varid{op}}\;\rightarrow\;\Conid{Set}\;\rightarrow\;\Conid{Set}}, an element of \ensuremath{\prodd\;\Conid{X}\;.\;\Conid{F}\;\Conid{X}\;\Conid{X}} is
@@
 \noindent
-The natural transformations between functors \ensuremath{\Conid{F}} and \ensuremath{\Conid{G}} are
-ends \ensuremath{\prodd\;\Conid{X}\;.\;\Conid{F}\;\Conid{X}\;\rightarrow\;\Conid{G}\;\Conid{X}}. We will often ignore the presence of the proofs, and 
+The natural transformations between functors \ensuremath{\Conid{F}} and \ensuremath{\Conid{G}} are ends \ensuremath{\prodd\;\Conid{X}\;.\;\Conid{F}\;\Conid{X}\;\rightarrow\;\Conid{G}\;\Conid{X}}.
+We will often ignore the presence of the proofs, and
 use such ends directly as polymorphic functions.
@@
 
-Finally, for readability we will elide certain artifacts in Agda's syntax, for instance the quantification of implicit arguments when their types can be inferred from the context.
-The reader should be reassured that the paper is a literate agda file, available from the final author's webpage.
+Finally, for readability we will elide certain artifacts in Agda's syntax,
+for instance the quantification of implicit arguments when their types can be
+inferred from the context. The reader should be reassured that the paper is a
+literate agda file, available from the final author's webpage.
 
@@
 
+The initial algebra semantics is useful to provide a generic
+analysis of inductive types exploiting generic concepts such as
+constructors and functorial map. However, it cannot say whether such inductive
+types actually exist, and it falls short of providing a systematic
+characterisation of generic operations such as equality or the
+zipper~\cite{huet:zipper,conor:derivative}.
+
+In previous
+work, \cite{alti:cont-tcs,alti:fossacs03}, we have proposed the notion of a container
+type: A (unary) container is given by a set of shapes \ensuremath{\Conid{S}} and a
+family of positions \ensuremath{\Conid{P}} assigning, to each shape, the set
+of positions where data can be stored in a data structure of that
+shape.
+
 \begin{hscode}\SaveRestoreHook
@@
 \column{5}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Keyword{record}\;\Conid{Cont}\;\in\;\Conid{Set₁}\;\Keyword{where}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Keyword{constructor}\;\anonymous \lhd\anonymous {}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Keyword{field}{}\<[E]%
+\\
+\>[3]{}\hsindent{2}{}\<[5]%
+\>[5]{}\Conid{S}\;\in\;\Conid{Set}{}\<[E]%
+\\
+\>[3]{}\hsindent{2}{}\<[5]%
+\>[5]{}\Conid{P}\;\in\;\Conid{S}\;\rightarrow\;\Conid{Set}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+Every container \ensuremath{\Conid{S}\;\lhd\;\Conid{P}}  gives rise to a functor:
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
 \column{21}{@{}>{\hspre}l<{\hspost}@{}}%
@@
 \column{E}{@{}>{\hspre}l<{\hspost}@{}}%
-\>[B]{}\Keyword{record}\;\Conid{Cont}\;\in\;\Conid{Set₁}\;\Keyword{where}{}\<[E]%
-\\
-\>[B]{}\hsindent{3}{}\<[3]%
-\>[3]{}\Keyword{constructor}\;\anonymous \lhd\anonymous {}\<[E]%
-\\
-\>[B]{}\hsindent{3}{}\<[3]%
-\>[3]{}\Keyword{field}{}\<[E]%
-\\
-\>[3]{}\hsindent{2}{}\<[5]%
-\>[5]{}\Conid{S}\;\in\;\Conid{Set}{}\<[E]%
-\\
-\>[3]{}\hsindent{2}{}\<[5]%
-\>[5]{}\Conid{P}\;\in\;\Conid{S}\;\rightarrow\;\Conid{Set}{}\<[E]%
-\\[\blanklineskip]%
 \>[B]{}\Varid{⟦\char95 ⟧}\;\in\;\Conid{Cont}\;\rightarrow\;\Conid{Func}{}\<[E]%
@@
 
+We define morphisms of containers, this can be derived from the specification that embedding should be full and faithful using the Yoneda lemma:
+
 \begin{hscode}\SaveRestoreHook
@@
 The category of containers is a full and faithful sub-category of the functor category.
-We have also shown that the category of containers is cartesian closed, and is closed under formation of co-products.
+We have also shown that the category of containers is cartesian closed (\cite{cie}, and is closed under formation of co-products.
 
@@
 This allows us to model a broad range of nested and mutual types as containers.
-We will develop an analogous construction for indexed conatainers in section ???.
 
@@
 functor's action on objects, or on morphisms. A morphism between to such 
-indexed functors is a natural transormation:
+indexed functors is a natural transformation:
 
@@
 \noindent
-This construction is used, for instance, in building the pattern functor for \ensuremath{\Conid{ScLam}} as in the introduction; Concentranting only on the \ensuremath{\Varid{abs}} case we want to build
-\ensuremath{\Conid{ScLam′}\;\Conid{X}\;\Varid{n}\;\mathrel{=}\;(\Conid{X}\;\ensuremath{\mbox{$\circ$}}\;\Varid{suc})\;\Varid{n}}.
+This construction is used, for instance, in building the pattern functor for
+\ensuremath{\Conid{ScLam}} as in the introduction; Concentrating only on the \ensuremath{\Varid{abs}} case we want
+to build  \ensuremath{\Conid{ScLam′}\;\Conid{X}\;\Varid{n}\;\mathrel{=}\;(\Conid{X}\;\ensuremath{\mbox{$\circ$}}\;\Varid{suc})\;\Varid{n}}.
 Or simply \ensuremath{\Conid{ScLam′}\;\Conid{X}\;\mathrel{=}\;\Delta^{\text{\tiny F}}\;\Varid{suc}\;\Conid{X}}.
-In general this combinator
-restricts the functor \ensuremath{\Conid{X}} to the indicies in the image of the
-function \ensuremath{\Varid{f}}.
+In
+general this combinator restricts the functor \ensuremath{\Conid{X}} to the indices in the
+image of the function \ensuremath{\Varid{f}}.
 
@@
 \noindent
-Perhaps unsuprisingly, \ensuremath{\Sigma^{\text{\tiny F}}} turns out to be the left adjoint to re-indexing 
+Perhaps unsurprisingly, \ensuremath{\Sigma^{\text{\tiny F}}} turns out to be the left adjoint to re-indexing 
 (\ensuremath{\Delta^{\text{\tiny F}}}). Its right adjoint, we denote \ensuremath{\Pi^{\text{\tiny F}}}:
@@
 For the morphism part of an indexed-functor over a co-product we can eliminate
-the coproduct and curry the result ing definition in this way:
+the co-product and curry the resulting definition in this way:
 
@@
 Which follow from the extensionality of our propositional equality, the 
-assosciativity of \ensuremath{\Sigma} and the terminality of \ensuremath{\top}. By the full and faithful 
+associativity of \ensuremath{\Sigma} and the terminality of \ensuremath{\top}. By the full and faithful 
 nature of the embedding into \ensuremath{\Conid{IFunc}} we can then reuse the result that
@@
 
-Again we appeal to the full and faithfullness of \ensuremath{\Varid{⟦\char95 ⟧\char95 }} and show instead that
+Again we appeal to the full and faithfulness of \ensuremath{\Varid{⟦\char95 ⟧\char95 }} and show instead that
 the embedding into \ensuremath{\Conid{IFunc}} preserves these constructions. That, is we want to show that the following three statements hold:
@@
 \noindent
-The composite container has shapes given by a shape \ensuremath{\Varid{s}\;\in\;\Conid{S}} and an assigment of \ensuremath{\Conid{T}} 
-shapes to \ensuremath{\Conid{P}^{\Conid{J}}\;\Varid{s}} positions. Positions are then a choice between 
-a \ensuremath{\Conid{I}}-indexed position, or a pair of an \ensuremath{\Conid{J}}-indexed position, and a \ensuremath{\Conid{Q}} position
-\emph{underneath} the appropriate \ensuremath{\Conid{T}} shape.
+The composite container has shapes given by a shape \ensuremath{\Varid{s}\;\in\;\Conid{S}} and an assignment
+of \ensuremath{\Conid{T}} shapes to \ensuremath{\Conid{P}^{\Conid{J}}\;\Varid{s}} positions. Positions are then a choice between a
+\ensuremath{\Conid{I}}-indexed position, or a pair of an \ensuremath{\Conid{J}}-indexed position, and a \ensuremath{\Conid{Q}}
+position \emph{underneath} the appropriate \ensuremath{\Conid{T}} shape.
 
@@
 
-We will now examine how to construct the initial algebra of a container of the form \ensuremath{\Conid{F}\;\in\;\Conid{ICont}^{\star}\;(\Conid{I}\;\uplus\;\Conid{J})\;\Conid{J}}.
-The shapes of such a container are an \ensuremath{\Conid{J}}-indexed family of \ensuremath{\Conid{Set}}s and the positions are indexed by \ensuremath{\Conid{I}\;\uplus\;\Conid{J}}; we will treat these position as two separate entities, those positions indexed by \ensuremath{\Conid{I}} -- the recusive positions -- and those by \ensuremath{\Conid{J}} -- the payload positions.
-
-The shapes of initial algebra we are constructing will be trees with S shapes at the nodes and which branch over the recursive \ensuremath{\Conid{P}^{\Conid{I}}} positions.
-We call these trees \emph{indexed} \ensuremath{\Conid{W}}-types, denoted \ensuremath{\Conid{WI}} and they are the initial algebra of the functor \ensuremath{\Varid{⟦}\;\Conid{S}\;\lhd\;\Conid{P}^{\Conid{J}}\;\Varid{⟧}^{\star}}:
+We will now examine how to construct the initial algebra of a container of
+the form \ensuremath{\Conid{F}\;\in\;\Conid{ICont}^{\star}\;(\Conid{I}\;\uplus\;\Conid{J})\;\Conid{J}}. The shapes of such a container are an
+\ensuremath{\Conid{J}}-indexed family of \ensuremath{\Conid{Set}}s and the positions are indexed by \ensuremath{\Conid{I}\;\uplus\;\Conid{J}}; we
+will treat these position as two separate entities, those positions indexed
+by \ensuremath{\Conid{I}} -- the recursive positions -- and those by \ensuremath{\Conid{J}} -- the payload
+positions.
+
+The shapes of initial algebra we are constructing will be trees with S shapes
+at the nodes and which branch over the recursive \ensuremath{\Conid{P}^{\Conid{I}}} positions. We call
+these trees \emph{indexed} \ensuremath{\Conid{W}}-types, denoted \ensuremath{\Conid{WI}} and they are the initial
+algebra of the functor \ensuremath{\Varid{⟦}\;\Conid{S}\;\lhd\;\Conid{P}^{\Conid{J}}\;\Varid{⟧}^{\star}}:
 
@@
 \noindent
-This mirrors the construction for plain containers, where we can view ordinary \ensuremath{\Conid{W}} types as the initial algebra of a container functor.
-
-Positions are given by paths through such a tree, terminated by a non-recursive \ensuremath{\Conid{P}^{\Conid{I}}}:
+This mirrors the construction for plain containers, where we can view
+ordinary \ensuremath{\Conid{W}} types as the initial algebra of a container functor.
+
+Positions are given by paths through such a tree, terminated by a
+non-recursive \ensuremath{\Conid{P}^{\Conid{I}}}:
 
@@
 \noindent
-We can now give the object part of the patrametrized initial algebra of a container, given by:
+We can now give the object part of the parametrised initial algebra of a
+container, given by:
 
@@
 \noindent
-The algebra map is a container morphism from the partial aplication of \ensuremath{\Conid{F}} and its parametrised initial algebra, to the initial algebra, given by the algebra map of \ensuremath{\Conid{WI}} (\ensuremath{\Varid{sup}}) and our mediation funtion \ensuremath{\Varid{path}}:
+The algebra map is a container morphism from the partial application of \ensuremath{\Conid{F}}
+and its parametrised initial algebra, to the initial algebra, given by the
+algebra map of \ensuremath{\Conid{WI}} (\ensuremath{\Varid{sup}}) and our mediation function \ensuremath{\Varid{path}}:
 
@@
 
-Dually to the initial algebra construction out-lined above, we can also show that indexed-containers are closed under parameterized terminal co-algebras.
-We proceed in much the same way as before, by first constructing the dual of the indexed \ensuremath{\Conid{W}}-type, which we refer to as an indexed \ensuremath{\Conid{M}}-type.
-As you might expect this is in fact the plain (as opposed to parametrized) terminal co-algebra of an indexed container functor:
+Dually to the initial algebra construction out-lined above, we can also show
+that indexed-containers are closed under parameterised terminal co-algebras.
+We proceed in much the same way as before, by first constructing the dual of
+the indexed \ensuremath{\Conid{W}}-type, which we refer to as an indexed \ensuremath{\Conid{M}}-type. As you might
+expect this is in fact the plain (as opposed to parametrized) terminal
+co-algebra of an indexed container functor:
 
@@
 \>[14]{}\Varid{r}\;\Varid{t}\;\Varid{j}\;(\Varid{inr}\;(\Varid{i},\Varid{p},\Varid{runfold}\;(\pi_{1}\;(\Varid{f}\;\anonymous \;\Varid{t})\;\Varid{i}\;\Varid{p})\;\Varid{j}\;\Varid{q})){}\<[E]%
-\\[\blanklineskip]%
-\>[B]{}\Varid{-}\mskip1.5mu\}{}\<[E]%
 \ColumnHook
@@
 
+So far we have developed a theory of indexed containers using a rich Type
+Theory. We claimed in the introduction, however, that this theory required
+only the presence of \ensuremath{\Conid{W}}-types. In this section we will outline the
+translation of many of the definitions above into such a spartan theory.
+First we will show how to obtain indexed \ensuremath{\Conid{W}}-types from un-indexed ones, and
+by analogy \ensuremath{\Conid{MI}} from \ensuremath{\Conid{M}}, and then we will revisit a proof of how to derive
+\ensuremath{\Conid{M}}-types from \ensuremath{\Conid{W}}.
+
 \subsection*{\ensuremath{\Conid{WI}} from \ensuremath{\Conid{W}}}
@@
 
-How, then, can we build \ensuremath{\Conid{WI}} from \ensuremath{\Conid{W}}?
-The initial step is to create a type of \emph{pre}-\ensuremath{\Conid{WI}} trees, with nodes containing a shape \emph{and} its index, and branching over positions \emph{and their} indicies:
+How, then, can we build \ensuremath{\Conid{WI}} from \ensuremath{\Conid{W}}? The initial step is to create a type
+of \emph{pre}-\ensuremath{\Conid{WI}} trees, with nodes containing a shape \emph{and} its index,
+and branching over positions \emph{and their} indices:
 
@@
 Since we have shown that both \ensuremath{\Conid{WI}} and \ensuremath{\Conid{MI}} types can be reduced to their
-non-indexed counterparts, it only remains to show that \ensuremath{\Conid{M}} types can be, reduced
-to \ensuremath{\Conid{W}} types. This is a result from our previous work on containers~\cite{alti:cont-tcs}, though in the setting of 
-indexed \ensuremath{\Conid{WI}} types, we can give a better intuition.
+non-indexed counterparts, it only remains to show that \ensuremath{\Conid{M}} types can be,
+reduced
+to \ensuremath{\Conid{W}} types. This is a result from our previous work on
+containers~\cite{alti:cont-tcs}, though in the setting of indexed \ensuremath{\Conid{WI}} types,
+we can give a better intuition.
 
@@
 
-We 
-want to build \ensuremath{\Conid{M}}-types, which we know to be the terminal co-algebras of 
+We want to build \ensuremath{\Conid{M}}-types, which we know to be the terminal co-algebras of 
 container functors. In order to do this, we must construct 
@@
 iteration of the morphism part of the container functor applied to the unique 
-moprhism into the terminal object:
+morphism into the terminal object:
 
@@
 
-So now we can build the chain of finitie itererations of a container functor:
+So now we can build the chain of finite iterations of a container functor:
 
@@
 To prove the structure is a relative 
-monad we observe that the following equlities hold:
+monad we observe that the following equalities hold:
 

### 2011-05-10 journal/paper.tex
started conclusions (mainly copied from conference paper).

@@
 
+We have shown how inductive and coinductive families, a central
+feature in dependently typed programming, can be constructed from the
+standard infrastructure present in Type Theory, i.e. W-types together
+with $\Pi$, $\Sigma$ and equality types. Indeed, we are able to reduce
+the syntactically rich notion of families to a small collection of
+categorically inspired combinators. This is an alternative to the
+complex syntactic schemes present in the \emph{Calculus of Inductive
+  Constructions} (CIC), or in the Agda and Epigram systems. We are
+able to encode inductively defined families in a small core language
+which means that we rely only on a small trusted code base. The
+reduction to W-types requires an extensional propositional
+equality. Our current approach using an axiom \ensuremath{\Varid{ext}} is sufficent for
+proofs but isn't computationally adequate. A more satisfying approach
+would built on \emph{Observational Type Theory} (OTT)
+\cite{alti:ott-conf}.
+
+\todo{Mention Epigram 2?}
+
+The present paper is an annotated Agda script, i.e. all the proofs are
+checked by the Agda system. We have tried hard to integrate the formal
+development with the narrative. In some cases we have surpressed
+certain details present in the source of the paper to keep the
+material readable.
+
+A more serious challenge are mutual inductively (or coinductively)
+defined families where one type depends on another
+\cite{setzer-forsberg-indind}. A typical example is the syntax of Type
+Theory itself which, to simplify, can be encoded by mutually defining
+contexts containing terms, types in a given context and terms in a
+given type:
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Conid{Con}\;\in\;\Conid{Set}{}\<[E]%
+\\
+\>[B]{}\Conid{Ty}\;\in\;\Conid{Con}\;\rightarrow\;\Conid{Set}{}\<[E]%
+\\
+\>[B]{}\Conid{Tm}\;\in\;(\Gamma\;\in\;\Conid{Con})\;\rightarrow\;\Conid{Ty}\;\Gamma\;\rightarrow\;\Conid{Set}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+In recent work \cite{calco-indind} present a categorical semantics for
+this kind of definitions based on dialgebras. However, a presentation
+of strictly positive definitions in the spirit of conatienrs is not
+yet available.
+
+\todo{Discuss the relationship to inductive-recursive definitions.}
+
 \bibliographystyle{plain}

### 2011-05-10 journal/paper.tex
NeNf SPF

--- 2011-05-10 journal/paper.tex
@@
 $\Sigma$-types and equality types from Type Theory, we can define the
-following endofunctors \ensuremath{\Conid{F}_{\Conid{Fin}},\Conid{F}_{\Conid{Vec}}} and \ensuremath{\Conid{F}_{\Conid{Lam}}}
+following endofunctors \ensuremath{\Conid{F}_{\Conid{Fin}}}, \ensuremath{\Conid{F}_{\Conid{Vec}}} and \ensuremath{\Conid{F}_{\Conid{Lam}}}
 on the category of families
@@
 constructors for \ensuremath{\Conid{Fin}}.
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Conid{FNe}\;\in\;(\Conid{ℕ}\;\rightarrow\;\Conid{Set})\;\rightarrow\;(\Conid{ℕ}\;\rightarrow\;\Conid{Set})\;\rightarrow\;\Conid{ℕ}\;\rightarrow\;\Conid{Set}{}\<[E]%
+\\
+\>[B]{}\Conid{FNe}\;\Conid{X}\;\Conid{Y}\;\Varid{n}\;\mathrel{=}\;\Conid{Fin}\;\Varid{n}\;\uplus\;(\Conid{X}\;\Varid{n}\;\uplus\;\Conid{Y}\;\Varid{n}){}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\Conid{FNf}\;\in\;(\Conid{ℕ}\;\rightarrow\;\Conid{Set})\;\rightarrow\;(\Conid{ℕ}\;\rightarrow\;\Conid{Set})\;\rightarrow\;\Conid{ℕ}\;\rightarrow\;\Conid{Set}{}\<[E]%
+\\
+\>[B]{}\Conid{FNf}\;\Conid{X}\;\Conid{Y}\;\Varid{n}\;\mathrel{=}\;(\Conid{Y}\;\ensuremath{\mbox{$\circ$}}\;\Varid{suc})\;\Varid{n}\;\uplus\;\Conid{X}\;\Varid{n}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
 

### 2011-05-10 journal/paper.tex
tinkering

@@
   functional programming as proposed by Turner \cite{sfp} and ignore
-non-termination.})
-
-Examples include the natural numbers al Peano:
+non-termination.}). Examples include the natural numbers al Peano:
 \begin{hscode}\SaveRestoreHook
@@
 to have a finer, more expressive, notion of types, for example to
-ensure the absence of run time errors --- access to arrays out of
+ensure the absence of runtime errors --- access to arrays out of
 range or access to an undefined variable in the previous example of
@@
 \end{hscode}\resethooks
-Note, that a corresponding function \ensuremath{\Varid{\char95 !!\char95 }\;\in\;\{\mskip1.5mu \Conid{A}\;\in\;\Conid{Set}\mskip1.5mu\}\;\rightarrow\;\Conid{List}\;\Conid{A}\;\rightarrow\;\Conid{ℕ}\;\rightarrow\;\Conid{A}} is not definable in a total langauge like Agda.
+Note, that a corresponding function \ensuremath{\Varid{\char95 !!\char95 }\;\in\;\{\mskip1.5mu \Conid{A}\;\in\;\Conid{Set}\mskip1.5mu\}\;\rightarrow\;\Conid{List}\;\Conid{A}\;\rightarrow\;\Conid{ℕ}\;\rightarrow\;\Conid{A}} is not definable in a total language like Agda.
 
@@
 with functors on the category of families indexed by a given type - in
-the case of $\lambda$-terms this indexing type was \ensuremath{\Conid{Nat}}. The objects
+the case of all our examples so far this indexing type was \ensuremath{\Conid{Nat}}. The objects
 of the category of families indexed over a type \ensuremath{\Conid{I}\;\in\;\Varid{set}} are
@@
 
-We have $\Pi$-types, denoted \ensuremath{(\Varid{a}\;\in\;\Conid{A})\;\rightarrow\;\Conid{B}\;\Varid{a}} and $\Sigma$-types, which we denote in a non-standard way: \ensuremath{\Sigma(\!\;\Varid{a}\;\in\;\Conid{A}\;\!)\!\times\!\;\Conid{B}\;\Varid{a}}.
+We have $\Pi$-types, denoted \ensuremath{(\Varid{a}\;\in\;\Conid{A})\;\rightarrow\;\Conid{B}\;\Varid{a}} and $\Sigma$-types, which we write as: \ensuremath{\Sigma(\!\;\Varid{a}\;\in\;\Conid{A}\;\!)\!\times\!\;\Conid{B}\;\Varid{a}}.
 In fact this is sugar for the record type:
@@
 
-With these assumptions we obtain a theory which corresponds to
+With these ingredients we obtain a theory which corresponds to
 extensional Type Theory \cite{hofmann-conservativity}.
@@
 literate agda file, available from the final author's webpage.
+
+\todo{Define Func.}
 
@@
 
-\section{Terminal Co-Algebras of Indexed Containers}
+\section{Terminal Coalgebras of Indexed Containers}
 \label{sec:termcoalg}
 
-Dually to the initial algebra construction out-lined above, we can also show
-that indexed-containers are closed under parameterised terminal co-algebras.
+Dually to the initial algebra construction outlined above, we can also show
+that indexed containers are closed under parameterised terminal coalgebras.
 We proceed in much the same way as before, by first constructing the dual of
@@
 expect this is in fact the plain (as opposed to parametrized) terminal
-co-algebra of an indexed container functor:
+coalgebra of an indexed container functor:
 
@@
 
-Here we employ Agda's approach to co-programming, where we mark (possibly) infinite subtrees with \ensuremath{\infty}, \ensuremath{\sharp\;\in\;\Conid{A}\;\rightarrow\;\infty\;\Conid{A}} and \ensuremath{\flat\;\in\;\infty\;\Conid{A}\;\rightarrow\;\Conid{A}} pack and unpack infinite objects respectively.
+Here we employ Agda's approach to coprogramming (e.g.
+see \cite{txa:mpc2010g}), where we mark (possibly) infinite subtrees with \ensuremath{\infty}, \ensuremath{\sharp\;\in\;\Conid{A}\;\rightarrow\;\infty\;\Conid{A}} and \ensuremath{\flat\;\in\;\infty\;\Conid{A}\;\rightarrow\;\Conid{A}} pack and unpack infinite objects respectively.
 
@@
 
+\todo{Derive MI from M or at least say so and hide the proof.}
+
 \subsection*{\ensuremath{\Conid{M}} from \ensuremath{\Conid{W}}}
@@
 containers~\cite{alti:cont-tcs}, though in the setting of indexed \ensuremath{\Conid{WI}} types,
-we can give a better intuition.
+we can give a better expalnation.
 
@@
 \section{Strictly Positive Families}
+\label{sec:spf}
 
@@
 \>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Conid{SPF}\;\in\;\forall{}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\;\Conid{K}\mskip1.5mu\}\;\rightarrow\;(\Conid{I}\;\rightarrow\;\Conid{J})\;\rightarrow\;\Conid{SPF}\;\Conid{I}\;\Conid{K}\;\rightarrow\;\Conid{SPF}\;\Conid{J}\;\Conid{K}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Conid{SPF}\;\gamma\;\Varid{t}\;\Varid{k}\;\mathrel{=}\;\Conid{ISPT}\;\gamma\;(\Varid{t}\;\Varid{k}){}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\hsindent{3}{}\<[3]%
 \>[3]{}\anonymous \bind ^{\text{\tiny T}}\anonymous \;\in\;\forall{}\;\{\mskip1.5mu \Conid{I}\;\Conid{J}\mskip1.5mu\}\;\rightarrow\;\Conid{ISPT}\;\Conid{I}\;\rightarrow\;\Conid{SPF}\;\Conid{J}\;\Conid{I}\;\rightarrow\;\Conid{ISPT}\;\Conid{J}{}\<[E]%
@@
 \>[14]{}\bind ^{\text{\tiny T}}\;\Conid{F}\;\mathrel{=}\;\mu^{\text{\tiny T}}\;(\lambda\;\Varid{k}\;\rightarrow\;\Conid{G}\;\Varid{k}\;\bind ^{\text{\tiny T}}\;[\mskip1.5mu {}\<[48]%
-\>[48]{}(\Conid{ISPT}\;\Varid{inl}\;\ensuremath{\mbox{$\circ$}}\;\Conid{F}),(\eta^{\text{\tiny T}}\;\ensuremath{\mbox{$\circ$}}\;\Varid{inr})\mskip1.5mu])\;\Varid{j}{}\<[E]%
+\>[48]{}(\Conid{SPF}\;\Varid{inl}\;\Conid{F}),(\eta^{\text{\tiny T}}\;\ensuremath{\mbox{$\circ$}}\;\Varid{inr})\mskip1.5mu])\;\Varid{j}{}\<[E]%
 \\
@@
 \>[14]{}\bind ^{\text{\tiny T}}\;\Conid{F}\;\mathrel{=}\;\nu^{\text{\tiny T}}\;(\lambda\;\Varid{k}\;\rightarrow\;\Conid{G}\;\Varid{k}\;\bind ^{\text{\tiny T}}\;[\mskip1.5mu {}\<[48]%
-\>[48]{}(\Conid{ISPT}\;\Varid{inl}\;\ensuremath{\mbox{$\circ$}}\;\Conid{F}),(\eta^{\text{\tiny T}}\;\ensuremath{\mbox{$\circ$}}\;\Varid{inr})\mskip1.5mu])\;\Varid{j}{}\<[E]%
+\>[48]{}(\Conid{SPF}\;\Varid{inl}\;\Conid{F}),(\eta^{\text{\tiny T}}\;\ensuremath{\mbox{$\circ$}}\;\Varid{inr})\mskip1.5mu])\;\Varid{j}{}\<[E]%
 \ColumnHook
@@
 \>[15]{}({}\<[21]%
-\>[21]{}(\eta^{\text{\tiny T}}\;\ensuremath{\mbox{$\circ$}}\;\Varid{inr}){}\<[E]%
+\>[21]{}\Conid{SPF}\;(\lambda\;())\;\Conid{T}_{\Conid{Fin}}{}\<[E]%
 \\
@@
 \>[21]{}\Delta^{\text{\tiny T}}\;\Varid{suc}\;(\eta^{\text{\tiny T}}\;\ensuremath{\mbox{$\circ$}}\;\Varid{inr}))){}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+Note that we have to weaken the reference to \ensuremath{\Conid{T}_{\Conid{Fin}}} in the definition of 
+\ensuremath{\Conid{T}_{\Conid{ScLam}}}, since under the \ensuremath{\mu^{\text{\tiny T}}} we can refer to the recursive \ensuremath{\Conid{TSCLam}} trees, 
+but \ensuremath{\Conid{T}_{\Conid{Fin}}} itself can refer to no variables.
+
+We can also define the mutual types, \ensuremath{\Conid{Ne}} and \ensuremath{\Conid{Nf}}. Here, a copy of the normal 
+forms is defined \emph{inside} the definition of the neutral terms, and vice
+versa:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{10}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{11}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{12}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{17}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{18}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{23}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{29}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Conid{T}_{\Conid{Ne}}\;\in\;\Conid{SPF}\;\bot\;\Conid{ℕ}{}\<[E]%
+\\
+\>[B]{}\Conid{T}_{\Conid{Ne}}\;\mathrel{=}\;\mu^{\text{\tiny T}}\;({}\<[17]%
+\>[17]{}\Conid{SPF}\;(\lambda\;())\;\Conid{T}_{\Conid{Fin}}{}\<[E]%
+\\
+\>[B]{}\hsindent{11}{}\<[11]%
+\>[11]{}\mathbin{\uplus^{\text{\tiny T}}}\;{}\<[17]%
+\>[17]{}((\eta^{\text{\tiny T}}\;\ensuremath{\mbox{$\circ$}}\;\Varid{inr})\;\mathbin{\times^{\text{\tiny T}}}\;\Conid{TNeNf})){}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Keyword{where}\;{}\<[10]%
+\>[10]{}\Conid{TNeNf}\;\in\;\Conid{SPF}\;(\bot\;\uplus\;\Conid{ℕ})\;\Conid{ℕ}{}\<[E]%
+\\
+\>[10]{}\Conid{TNeNf}\;\mathrel{=}\;\mu^{\text{\tiny T}}\;{}\<[23]%
+\>[23]{}({}\<[29]%
+\>[29]{}(\Delta^{\text{\tiny T}}\;\Varid{suc}\;(\eta^{\text{\tiny T}}\;\ensuremath{\mbox{$\circ$}}\;\Varid{inr})){}\<[E]%
+\\
+\>[23]{}\mathbin{\uplus^{\text{\tiny T}}}\;{}\<[29]%
+\>[29]{}(\eta^{\text{\tiny T}}\;\ensuremath{\mbox{$\circ$}}\;(\Varid{inl}\;\ensuremath{\mbox{$\circ$}}\;\Varid{inr}))){}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\Conid{T}_{\Conid{Nf}}\;\in\;\Conid{SPF}\;\bot\;\Conid{ℕ}{}\<[E]%
+\\
+\>[B]{}\Conid{T}_{\Conid{Nf}}\;\mathrel{=}\;\mu^{\text{\tiny T}}\;{}\<[12]%
+\>[12]{}({}\<[18]%
+\>[18]{}\Delta^{\text{\tiny T}}\;\Varid{suc}\;(\eta^{\text{\tiny T}}\;\ensuremath{\mbox{$\circ$}}\;\Varid{inr}){}\<[E]%
+\\
+\>[12]{}\mathbin{\uplus^{\text{\tiny T}}}\;{}\<[18]%
+\>[18]{}\Conid{TNfNe}){}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Keyword{where}\;{}\<[10]%
+\>[10]{}\Conid{TNfNe}\;\in\;\Conid{SPF}\;(\bot\;\uplus\;\Conid{ℕ})\;\Conid{ℕ}{}\<[E]%
+\\
+\>[10]{}\Conid{TNfNe}\;\mathrel{=}\;\mu^{\text{\tiny T}}\;{}\<[23]%
+\>[23]{}({}\<[29]%
+\>[29]{}\Conid{SPF}\;(\lambda\;())\;\Conid{T}_{\Conid{Fin}}{}\<[E]%
+\\
+\>[23]{}\mathbin{\uplus^{\text{\tiny T}}}\;{}\<[29]%
+\>[29]{}((\eta^{\text{\tiny T}}\;\ensuremath{\mbox{$\circ$}}\;\Varid{inr})\;\mathbin{\times^{\text{\tiny T}}}\;(\eta^{\text{\tiny T}}\;\ensuremath{\mbox{$\circ$}}\;(\Varid{inl}\;\ensuremath{\mbox{$\circ$}}\;\Varid{inr})))){}\<[E]%
 \ColumnHook
@@
 this kind of definitions based on dialgebras. However, a presentation
-of strictly positive definitions in the spirit of conatienrs is not
+of strictly positive definitions in the spirit of contaienrs is not
 yet available.

### 2011-05-10 journal/paper.tex
Various changes

@@
 
-We'll also require a notion of propositional equality, in Agda this is defined via a data-type:
+We'll also require a notion of propositional equality. To simplyfy the presentation of some definitions later on, we will employ a heterogeneous equality.
+This can be defined in Agda via a data-type:
 
@@
 \end{hscode}\resethooks
+
+Most of the time our equalities will be homogeneous, however, so we introduce a short hand for this:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Varid{\char95 ≡\char95 }\;\in\;\{\mskip1.5mu \Conid{A}\;\in\;\Conid{Set}\mskip1.5mu\}\;\rightarrow\;\Conid{A}\;\rightarrow\;\Conid{A}\;\rightarrow\;\Conid{Set}{}\<[E]%
+\\
+\>[B]{}\Varid{a}\;\equiv\;\Varid{b}\;\mathrel{=}\;\Varid{a}\;\cong\;\Varid{b}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+It is also known that homogeneous and heterogeneous equality have the same 
+strength, so all the definitions employing our equality could also be encoded in
+a theory with only homogeneous equality.
 

### 2011-05-10 journal/paper.tex
approx

@@
 is to model them as the initial algebra of an endofunctor, we can
-define the siganture functors cirresponding to each of the examples above:
+define the siganture functors corresponding to each of the examples above:
 
@@
 \column{E}{@{}>{\hspre}l<{\hspost}@{}}%
-\>[B]{}\Conid{FNe}\;\in\;(\Conid{ℕ}\;\rightarrow\;\Conid{Set})\;\rightarrow\;(\Conid{ℕ}\;\rightarrow\;\Conid{Set})\;\rightarrow\;\Conid{ℕ}\;\rightarrow\;\Conid{Set}{}\<[E]%
-\\
-\>[B]{}\Conid{FNe}\;\Conid{X}\;\Conid{Y}\;\Varid{n}\;\mathrel{=}\;\Conid{Fin}\;\Varid{n}\;\uplus\;(\Conid{X}\;\Varid{n}\;\uplus\;\Conid{Y}\;\Varid{n}){}\<[E]%
-\\[\blanklineskip]%
-\>[B]{}\Conid{FNf}\;\in\;(\Conid{ℕ}\;\rightarrow\;\Conid{Set})\;\rightarrow\;(\Conid{ℕ}\;\rightarrow\;\Conid{Set})\;\rightarrow\;\Conid{ℕ}\;\rightarrow\;\Conid{Set}{}\<[E]%
-\\
-\>[B]{}\Conid{FNf}\;\Conid{X}\;\Conid{Y}\;\Varid{n}\;\mathrel{=}\;(\Conid{Y}\;\ensuremath{\mbox{$\circ$}}\;\Varid{suc})\;\Varid{n}\;\uplus\;\Conid{X}\;\Varid{n}{}\<[E]%
+\>[B]{}\Conid{F}_{\Conid{NeLam}}\;\in\;(\Conid{ℕ}\;\rightarrow\;\Conid{Set})\;\rightarrow\;(\Conid{ℕ}\;\rightarrow\;\Conid{Set})\;\rightarrow\;\Conid{ℕ}\;\rightarrow\;\Conid{Set}{}\<[E]%
+\\
+\>[B]{}\Conid{F}_{\Conid{NeLam}}\;\Conid{X}\;\Conid{Y}\;\Varid{n}\;\mathrel{=}\;\Conid{Fin}\;\Varid{n}\;\uplus\;(\Conid{X}\;\Varid{n}\;\uplus\;\Conid{Y}\;\Varid{n}){}\<[E]%
+\\[\blanklineskip]%
+\>[B]{}\Conid{F}_{\Conid{NfLam}}\;\in\;(\Conid{ℕ}\;\rightarrow\;\Conid{Set})\;\rightarrow\;(\Conid{ℕ}\;\rightarrow\;\Conid{Set})\;\rightarrow\;\Conid{ℕ}\;\rightarrow\;\Conid{Set}{}\<[E]%
+\\
+\>[B]{}\Conid{F}_{\Conid{NfLam}}\;\Conid{X}\;\Conid{Y}\;\Varid{n}\;\mathrel{=}\;(\Conid{Y}\;\ensuremath{\mbox{$\circ$}}\;\Varid{suc})\;\Varid{n}\;\uplus\;\Conid{X}\;\Varid{n}{}\<[E]%
 \ColumnHook
@@
 
-We have $\Pi$-types, denoted \ensuremath{(\Varid{a}\;\in\;\Conid{A})\;\rightarrow\;\Conid{B}\;\Varid{a}} and $\Sigma$-types, which we write as: \ensuremath{\Sigma(\!\;\Varid{a}\;\in\;\Conid{A}\;\!)\!\times\!\;\Conid{B}\;\Varid{a}}.
+We have $\Pi$-types, denoted \ensuremath{(\Varid{a}\;\in\;\Conid{A})\;\rightarrow\;\Conid{B}\;\Varid{a}} and $\Sigma$-types, which we write as: \ensuremath{(\!\;\Varid{a}\;\in\;\Conid{A}\;\!)\times\;\Conid{B}\;\Varid{a}}.
 In fact this is sugar for the record type:
@@
 \>[B]{}\hsindent{3}{}\<[3]%
-\>[3]{}\Varid{sup}\;\in\;\Sigma(\!\;\Varid{s}\;\in\;\Conid{S}\;\!)\!\times\!\;(\Conid{P}\;\Varid{s}\;\rightarrow\;\Conid{W}\;\Conid{S}\;\Conid{P})\;\rightarrow\;\Conid{W}\;\Conid{S}\;\Conid{P}{}\<[E]%
+\>[3]{}\Varid{sup}\;\in\;(\!\;\Varid{s}\;\in\;\Conid{S}\;\!)\times\;(\Conid{P}\;\Varid{s}\;\rightarrow\;\Conid{W}\;\Conid{S}\;\Conid{P})\;\rightarrow\;\Conid{W}\;\Conid{S}\;\Conid{P}{}\<[E]%
 \\[\blanklineskip]%
@@
 readability we will also define functions using Agda's pattern matching
-syntax, rather than encoding them using \ensuremath{\Varid{wrec}}, it is an unstated lemma that
-each of these definitions can be reduced to terms which only use \ensuremath{\Varid{wrec}}.
+syntax, rather than encoding them using \ensuremath{\Varid{wrec}}, all of these definitions can 
+be reduced to terms which only use \ensuremath{\Varid{wrec}}.
 
@@
 
-We are going to use type theory versions of certain category theoretic
-concepts For instance, we use ends \ensuremath{\Conid{End}} to capture natural transformations.
+We are going to use type theoretic versions of certain category theoretic
+concepts. For example we represent functors by packing up their definitions in Agda's records. An endo functor on set, is given by:
+
+\begin{hscode}\SaveRestoreHook
+\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{3}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{8}{@{}>{\hspre}l<{\hspost}@{}}%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Keyword{record}\;\Conid{Func}\;\in\;\Conid{Set₁}\;\Keyword{where}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{obj}\;{}\<[8]%
+\>[8]{}\in\;\Conid{Set}\;\rightarrow\;\Conid{Set}{}\<[E]%
+\\
+\>[B]{}\hsindent{3}{}\<[3]%
+\>[3]{}\Varid{mor}\;{}\<[8]%
+\>[8]{}\in\;\forall{}\;\{\mskip1.5mu \Conid{A}\;\Conid{B}\mskip1.5mu\}\;\rightarrow\;(\Conid{A}\;\rightarrow\;\Conid{B})\;\rightarrow\;\Varid{obj}\;\Conid{A}\;\rightarrow\;\Varid{obj}\;\Conid{B}{}\<[E]%
+\ColumnHook
+\end{hscode}\resethooks
+
+It would also be possible to pack up the functor laws as extra fields in these 
+records.
+
+We use ends \ensuremath{\Conid{End}} to capture natural transformations.
 Given a bifunctor \ensuremath{\Conid{F}\;\in\;\Conid{Set}^{\Varid{op}}\;\rightarrow\;\Conid{Set}\;\rightarrow\;\Conid{Set}}, an element of \ensuremath{\prodd\;\Conid{X}\;.\;\Conid{F}\;\Conid{X}\;\Conid{X}} is
@@
 
-In this setting, the Yoneda lemma can be stated as follows, for any functor \ensuremath{\Conid{F}\;\in\;\Conid{Set}\;\rightarrow\;\Conid{Set}}:
+In this setting, the Yoneda lemma can be stated as follows, for any functor \ensuremath{\Conid{F}}:
 
@@
 for instance the quantification of implicit arguments when their types can be
-inferred from the context. The reader should be reassured that the paper is a
+inferred from the context. We will often leave out record projections 
+from notions such as \ensuremath{\Conid{Func}}, allowing the functor to stand for both its action 
+on object and morphism, just as would happen in the category theory 
+literature. The reader should be reassured that the paper is a
 literate agda file, available from the final author's webpage.
-
-\todo{Define Func.}
 
@@
 \>[21]{}\{\mskip1.5mu \Varid{obj}\;{}\<[28]%
-\>[28]{}\mathrel{=}\;\lambda\;\Conid{A}\;\rightarrow\;\Sigma(\!\;\Varid{s}\;\in\;\Conid{S}\;\!)\!\times\!\;(\Conid{P}\;\Varid{s}\;\rightarrow\;\Conid{A}){}\<[E]%
+\>[28]{}\mathrel{=}\;\lambda\;\Conid{A}\;\rightarrow\;(\!\;\Varid{s}\;\in\;\Conid{S}\;\!)\times\;(\Conid{P}\;\Varid{s}\;\rightarrow\;\Conid{A}){}\<[E]%
 \\
@@
 \>[20]{}\mathrel{=}\;{}\<[23]%
-\>[23]{}\lambda\;\Conid{A}\;\rightarrow\;\Sigma(\!\;\Varid{j}\;\in\;\Conid{J}\;\!)\!\times\!\;(\Varid{f}\;\Varid{j}\;\equiv\;\Varid{k}\;\times\;\;\Conid{F}\;\Conid{A}\;\Varid{j}){}\<[E]%
+\>[23]{}\lambda\;\Conid{A}\;\rightarrow\;(\!\;\Varid{j}\;\in\;\Conid{J}\;\!)\times\;(\Varid{f}\;\Varid{j}\;\equiv\;\Varid{k}\;\times\;\;\Conid{F}\;\Conid{A}\;\Varid{j}){}\<[E]%
 \\
@@
 \noindent
-A parametrized \ensuremath{\Conid{F}}-algebra for \ensuremath{\Conid{F}\;\in\;\Conid{IFunc}^{\star}\;(\Conid{I}\;\uplus\;\Conid{J})\;\Conid{I}} is a pair of an 
+A parametrised \ensuremath{\Conid{F}}-algebra for \ensuremath{\Conid{F}\;\in\;\Conid{IFunc}^{\star}\;(\Conid{I}\;\uplus\;\Conid{J})\;\Conid{I}} is a pair of an 
 indexed-functor \ensuremath{\Conid{G}\;\in\;\Conid{IFunc}\;\Conid{J}\;\Conid{I}} and a natural transformation
@@
 \noindent
-As you might expect, a parametrized initial algebra for \ensuremath{\Conid{F}}, if it is exists, 
-will be the initial object in the category of parametrized \ensuremath{\Conid{F}}-algebras.
-
-The fact that the parametrized initial algebra construction can be iterated, 
+As you might expect, a parametrised initial algebra for \ensuremath{\Conid{F}}, if it is exists, 
+will be the initial object in the category of parametrised \ensuremath{\Conid{F}}-algebras.
+
+The fact that the parametrised initial algebra construction can be iterated, 
 means that we can define nested and mutual families of data-types, such as the
@@
 \>[19]{}\mathrel{=}\;\lambda\;\Conid{A}\;{}\<[26]%
-\>[26]{}\rightarrow\;\Sigma(\!\;\Varid{s}\;\in\;\Conid{S}\;\!)\!\times\!\;(\Conid{P}\;\Varid{s}\;\rightarrow^{\star}\;\Conid{A}){}\<[E]%
+\>[26]{}\rightarrow\;(\!\;\Varid{s}\;\in\;\Conid{S}\;\!)\times\;(\Conid{P}\;\Varid{s}\;\rightarrow^{\star}\;\Conid{A}){}\<[E]%
 \\
@@
                 & \ensuremath{\Varid{⟦}\;\Conid{S}\;\lhd\;\Conid{P}\;\Varid{⟧}\;\Rightarrow^{\text{\tiny F}}\;\Conid{F}} & \\
-  \equiv  \;    & \ensuremath{\prodd\;\Conid{X}\;.\;\Sigma(\!\;\Varid{s}\;\in\;\Conid{S}\;(\Conid{P}\;\Varid{s}\;\rightarrow^{\star}\;\Conid{X})\;\rightarrow\;\Conid{F}\;\Conid{X}} & \{\mbox{by definition}\} \\
+  \equiv  \;    & \ensuremath{\prodd\;\Conid{X}\;.\;(\!\;\Varid{s}\;\in\;\Conid{S}\;(\Conid{P}\;\Varid{s}\;\rightarrow^{\star}\;\Conid{X})\;\rightarrow\;\Conid{F}\;\Conid{X}} & \{\mbox{by definition}\} \\
   \equiv  \;    & \ensuremath{\prodd\;\Conid{X}\;.\;(\Varid{s}\;\in\;\Varid{s})\;\rightarrow\;(\Conid{P}\;\Varid{s}\;\rightarrow^{\star}\;\Conid{X})\;\rightarrow\;\Conid{F}\;\Conid{X}} & \{\mbox{currying}\} \\
@@
            & \ensuremath{\Varid{⟦}\;\Conid{S}\;\lhd\;\Conid{P}\;\Varid{⟧}\;\Rightarrow^{\text{\tiny F}}\;\Varid{⟦}\;\Conid{T}\;\lhd\;\Conid{Q}\;\Varid{⟧}} \\
- \cong \;  & \ensuremath{(\Varid{s}\;\in\;\Conid{S})\;\rightarrow\;\Sigma(\!\;\Varid{t}\;\in\;\Conid{T}\;^{\star}\;\!)\!\times\!\;(\Conid{Q}\;\Varid{t}\;\rightarrow^{\star}\;\Conid{P}\;\Varid{s})} \\
- \cong \;  & \ensuremath{\Sigma(\!\;\Varid{f}\;\in\;\Conid{S}\;\rightarrow\;\Conid{T}\;\!)\!\times\!\;((\Varid{s}\;\in\;\Conid{S})\;\rightarrow\;\Conid{Q}\;(\Varid{f}\;\Varid{s})\;\rightarrow^{\star}\;\Conid{P}\;\Varid{s})}
+ \cong \;  & \ensuremath{(\Varid{s}\;\in\;\Conid{S})\;\rightarrow\;(\!\;\Varid{t}\;\in\;\Conid{T}\;^{\star}\;\!)\times\;(\Conid{Q}\;\Varid{t}\;\rightarrow^{\star}\;\Conid{P}\;\Varid{s})} \\
+ \cong \;  & \ensuremath{(\!\;\Varid{f}\;\in\;\Conid{S}\;\rightarrow\;\Conid{T}\;\!)\times\;((\Varid{s}\;\in\;\Conid{S})\;\rightarrow\;\Conid{Q}\;(\Varid{f}\;\Varid{s})\;\rightarrow^{\star}\;\Conid{P}\;\Varid{s})}
 \end{align*}
@@
 \>[6]{}\lambda (\!\;\Varid{s}\;\!,\!\;\Varid{f}\;\!\!)\;\Varid{j}\;\!\;\rightarrow\;\Sigma\;{}\<[34]%
-\>[34]{}(\Sigma(\!\;\Varid{i}\;\in\;\Conid{I}\;\!)\!\times\!\;\Conid{P}\;\Varid{s}\;\Varid{i})\;(\lambda (\!\;\Varid{i}\;\!,\!\;\Varid{p}\;\!\!)\;\rightarrow\;\Conid{Q}\;\Varid{i}\;(\Varid{f}\;\Varid{i}\;\Varid{p})\;\Varid{j}\;\!\;\!)\;\!\;\!{}\<[E]%
+\>[34]{}((\!\;\Varid{i}\;\in\;\Conid{I}\;\!)\times\;\Conid{P}\;\Varid{s}\;\Varid{i})\;(\lambda (\!\;\Varid{i}\;\!,\!\;\Varid{p}\;\!\!)\;\rightarrow\;\Conid{Q}\;\Varid{i}\;(\Varid{f}\;\Varid{i}\;\Varid{p})\;\Varid{j}\;\!\;\!)\;\!\;\!{}\<[E]%
 \ColumnHook
@@
 \>[3]{}\hsindent{5}{}\<[8]%
-\>[8]{}(\Sigma(\!\;\Varid{j}\;\in\;\Conid{J}\;\!)\!\times\!\;(\Varid{f}\;\Varid{j}\;\equiv\;\Varid{k}\;\times\;\Conid{S}\;\Varid{j}))\;{}\<[E]%
+\>[8]{}((\!\;\Varid{j}\;\in\;\Conid{J}\;\!)\times\;(\Varid{f}\;\Varid{j}\;\equiv\;\Varid{k}\;\times\;\Conid{S}\;\Varid{j}))\;{}\<[E]%
 \\
@@
 \>[5]{}\lhd\;{}\<[8]%
-\>[8]{}\lambda\;\Varid{s}\;\Varid{i}\;\rightarrow\;\Sigma(\!\;\Varid{j}\;\in\;\Conid{J}\;\!)\!\times\!\;(\Sigma(\!\;\Varid{eq}\;\in\;\Varid{f}\;\Varid{j}\;\equiv\;\Varid{k}\;\!)\!\times\!\;\Conid{P}\;\Varid{j}\;(\Varid{s}\;\Varid{j}\;\Varid{eq})\;\Varid{i}){}\<[E]%
+\>[8]{}\lambda\;\Varid{s}\;\Varid{i}\;\rightarrow\;(\!\;\Varid{j}\;\in\;\Conid{J}\;\!)\times\;((\!\;\Varid{eq}\;\in\;\Varid{f}\;\Varid{j}\;\equiv\;\Varid{k}\;\!)\times\;\Conid{P}\;\Varid{j}\;(\Varid{s}\;\Varid{j}\;\Varid{eq})\;\Varid{i}){}\<[E]%
 \ColumnHook
@@
 \>[10]{}\uplus\;{}\<[13]%
-\>[13]{}(\Sigma(\!\;\Varid{j}\;\in\;\Conid{J}\;\!)\!\times\!\;(\Sigma(\!\;\Varid{p}\;\in\;\Conid{P}^{\Conid{J}}\;\Varid{s}\;\Varid{j}\;\!)\!\times\!\;\Conid{Q}\;\Varid{j}\;(\Varid{f}\;\Varid{j}\;\Varid{p})\;\Varid{i}))\;\!\;\!){}\<[E]%
+\>[13]{}((\!\;\Varid{j}\;\in\;\Conid{J}\;\!)\times\;((\!\;\Varid{p}\;\in\;\Conid{P}^{\Conid{J}}\;\Varid{s}\;\Varid{j}\;\!)\times\;\Conid{Q}\;\Varid{j}\;(\Varid{f}\;\Varid{j}\;\Varid{p})\;\Varid{i}))\;\!\;\!){}\<[E]%
 \ColumnHook
@@
 \>[13]{}\uplus\;{}\<[16]%
-\>[16]{}(\Sigma(\!\;\Varid{j′}\;\in\;\Conid{J}\;\!)\!\times\!\;(\Sigma(\!\;\Varid{p}\;\in\;\Conid{P}^{\Conid{J}}\;\Varid{j}\;\Varid{s}\;\Varid{j′}\;\!)\!\times\!\;\Conid{Path}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\;\Conid{P}^{\Conid{J}}\;\Varid{j′}\;(\Varid{f}\;\Varid{j′}\;\Varid{p})\;\Varid{i}))\;{}\<[E]%
+\>[16]{}((\!\;\Varid{j′}\;\in\;\Conid{J}\;\!)\times\;((\!\;\Varid{p}\;\in\;\Conid{P}^{\Conid{J}}\;\Varid{j}\;\Varid{s}\;\Varid{j′}\;\!)\times\;\Conid{Path}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\;\Conid{P}^{\Conid{J}}\;\Varid{j′}\;(\Varid{f}\;\Varid{j′}\;\Varid{p})\;\Varid{i}))\;{}\<[E]%
 \\
@@
 \>[13]{}\uplus\;{}\<[16]%
-\>[16]{}(\Sigma(\!\;\Varid{j′}\;\in\;\Conid{J}\;\!)\!\times\!\;(\Sigma(\!\;\Varid{p}\;\in\;\Conid{P}^{\Conid{J}}\;\Varid{j}\;\Varid{s}\;\Varid{j′}\;\!)\!\times\!\;\Conid{Path}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\;\Conid{P}^{\Conid{J}}\;\Varid{j′}\;(\flat\;(\Varid{f}\;\Varid{j′}\;\Varid{p}))\;\Varid{i}))\;{}\<[E]%
+\>[16]{}((\!\;\Varid{j′}\;\in\;\Conid{J}\;\!)\times\;((\!\;\Varid{p}\;\in\;\Conid{P}^{\Conid{J}}\;\Varid{j}\;\Varid{s}\;\Varid{j′}\;\!)\times\;\Conid{Path}\;\Conid{S}\;\Conid{P}^{\Conid{I}}\;\Conid{P}^{\Conid{J}}\;\Varid{j′}\;(\flat\;(\Varid{f}\;\Varid{j′}\;\Varid{p}))\;\Varid{i}))\;{}\<[E]%
 \\
@@
 \\
-\>[B]{}\Conid{WI′}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\Conid{S}\;\Conid{P}\;\mathrel{=}\;\Conid{W}\;(\Sigma(\!\;\Varid{i}\;\in\;\Conid{I}\;\!)\!\times\!\;\Conid{S}\;\Varid{i})\;(\lambda (\!\;\Varid{i}\;\!,\!\;\Varid{s}\;\!\!)\;\rightarrow\;\Sigma(\!\;\Varid{i′}\;\in\;\Conid{I}\;\!)\!\times\!\;\Conid{P}\;\Varid{i}\;\Varid{s}\;\Varid{i′}\;\!\;\!){}\<[E]%
+\>[B]{}\Conid{WI′}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\Conid{S}\;\Conid{P}\;\mathrel{=}\;\Conid{W}\;((\!\;\Varid{i}\;\in\;\Conid{I}\;\!)\times\;\Conid{S}\;\Varid{i})\;(\lambda (\!\;\Varid{i}\;\!,\!\;\Varid{s}\;\!\!)\;\rightarrow\;(\!\;\Varid{i′}\;\in\;\Conid{I}\;\!)\times\;\Conid{P}\;\Varid{i}\;\Varid{s}\;\Varid{i′}\;\!\;\!){}\<[E]%
 \ColumnHook
@@
 \\
-\>[B]{}\Conid{WIl}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\Conid{S}\;\Conid{P}\;\mathrel{=}\;\Conid{W}\;(\Conid{I}\;\times\;(\Sigma(\!\;\Varid{i}\;\in\;\Conid{I}\;\!)\!\times\!\;\Conid{S}\;\Varid{i}))\;(\lambda (\!\;\Varid{i′}\;\!,\!\;\Varid{i}\;\!,\!\;\Varid{s}\;\!\!)\;\rightarrow\;\Sigma(\!\;\Varid{i′}\;\in\;\Conid{I}\;\!)\!\times\!\;\Conid{P}\;\Varid{i}\;\Varid{s}\;\Varid{i′}\;\!\;\!){}\<[E]%
+\>[B]{}\Conid{WIl}\;\{\mskip1.5mu \Conid{I}\mskip1.5mu\}\;\Conid{S}\;\Conid{P}\;\mathrel{=}\;\Conid{W}\;(\Conid{I}\;\times\;((\!\;\Varid{i}\;\in\;\Conid{I}\;\!)\times\;\Conid{S}\;\Varid{i}))\;(\lambda (\!\;\Varid{i′}\;\!,\!\;\Varid{i}\;\!,\!\;\Varid{s}\;\!\!)\;\rightarrow\;(\!\;\Varid{i′}\;\in\;\Conid{I}\;\!)\times\;\Conid{P}\;\Varid{i}\;\Varid{s}\;\Varid{i′}\;\!\;\!){}\<[E]%
 \ColumnHook
@@
 \>[B]{}\hsindent{3}{}\<[3]%
-\>[3]{}\Keyword{where}\;\Conid{PathS}\;\in\;\Sigma(\!\;\Varid{j}\;\in\;\Conid{J}\;\!)\!\times\!\;\Conid{WI}\;\Conid{S}\;\Conid{P}^{\Conid{J}}\;\Varid{j}\;\rightarrow\;\Conid{Set}{}\<[E]%
+\>[3]{}\Keyword{where}\;\Conid{PathS}\;\in\;(\!\;\Varid{j}\;\in\;\Conid{J}\;\!)\times\;\Conid{WI}\;\Conid{S}\;\Conid{P}^{\Conid{J}}\;\Varid{j}\;\rightarrow\;\Conid{Set}{}\<[E]%
 \\
@@
 \>[3]{}\hsindent{6}{}\<[9]%
-\>[9]{}\Conid{PathP}\;\in\;(\Varid{jw}\;\in\;\Sigma(\!\;\Varid{j}\;\in\;\Conid{J}\;\!)\!\times\!\;\Conid{WI}\;\Conid{S}\;\Conid{P}^{\Conid{J}}\;\Varid{j})\;(\Varid{s}\;\in\;\Conid{PathS}\;\Varid{jw})\;\rightarrow\;\Sigma(\!\;\Varid{j}\;\in\;\Conid{J}\;\!)\!\times\!\;\Conid{WI}\;\Conid{S}\;\Conid{P}^{\Conid{J}}\;\Varid{j}\;\rightarrow\;\Conid{Set}{}\<[E]%
+\>[9]{}\Conid{PathP}\;\in\;(\Varid{jw}\;\in\;(\!\;\Varid{j}\;\in\;\Conid{J}\;\!)\times\;\Conid{WI}\;\Conid{S}\;\Conid{P}^{\Conid{J}}\;\Varid{j})\;(\Varid{s}\;\in\;\Conid{PathS}\;\Varid{jw})\;\rightarrow\;(\!\;\Varid{j}\;\in\;\Conid{J}\;\!)\times\;\Conid{WI}\;\Conid{S}\;\Conid{P}^{\Conid{J}}\;\Varid{j}\;\rightarrow\;\Conid{Set}{}\<[E]%
 \\
@@
 \\
-\>[B]{}\Conid{Chain}\;\mathrel{=}\;\Sigma(\!\;\Conid{A}\;\in\;(\Conid{ℕ}\;\rightarrow\;\Conid{Set})\;\!)\!\times\!\;((\Varid{n}\;\in\;\Conid{ℕ})\;\rightarrow\;\Conid{A}\;(\Varid{suc}\;\Varid{n})\;\rightarrow\;\Conid{A}\;\Varid{n}){}\<[E]%
+\>[B]{}\Conid{Chain}\;\mathrel{=}\;(\!\;\Conid{A}\;\in\;(\Conid{ℕ}\;\rightarrow\;\Conid{Set})\;\!)\times\;((\Varid{n}\;\in\;\Conid{ℕ})\;\rightarrow\;\Conid{A}\;(\Varid{suc}\;\Varid{n})\;\rightarrow\;\Conid{A}\;\Varid{n}){}\<[E]%
 \ColumnHook
@@
 \\
-\>[B]{}\Conid{LIM}\;(\Conid{A},\Varid{a})\;\mathrel{=}\;\Sigma(\!\;\Varid{f}\;\in\;((\Varid{n}\;\in\;\Conid{ℕ})\;\rightarrow\;\Conid{A}\;\Varid{n})\;\!)\!\times\!\;((\Varid{n}\;\in\;\Conid{ℕ})\;\rightarrow\;\Varid{a}\;\Varid{n}\;(\Varid{f}\;(\Varid{suc}\;\Varid{n}))\;\equiv\;\Varid{f}\;\Varid{n}){}\<[E]%
+\>[B]{}\Conid{LIM}\;(\Conid{A},\Varid{a})\;\mathrel{=}\;(\!\;\Varid{f}\;\in\;((\Varid{n}\;\in\;\Conid{ℕ})\;\rightarrow\;\Conid{A}\;\Varid{n})\;\!)\times\;((\Varid{n}\;\in\;\Conid{ℕ})\;\rightarrow\;\Varid{a}\;\Varid{n}\;(\Varid{f}\;(\Varid{suc}\;\Varid{n}))\;\equiv\;\Varid{f}\;\Varid{n}){}\<[E]%
 \\[\blanklineskip]%
@@
 \>[21]{}({}\<[21E]%
-\>[24]{}\lambda\;\Varid{n}\;\rightarrow\;\Sigma(\!\;\Varid{s}\;\in\;\Conid{S}\;\!)\!\times\!\;(\Conid{P}\;\Varid{s}\;\rightarrow\;\Conid{A}\;\Varid{n})){}\<[E]%
+\>[24]{}\lambda\;\Varid{n}\;\rightarrow\;(\!\;\Varid{s}\;\in\;\Conid{S}\;\!)\times\;(\Conid{P}\;\Varid{s}\;\rightarrow\;\Conid{A}\;\Varid{n})){}\<[E]%
 \\
@@
 \>[3]{}\hsindent{8}{}\<[11]%
-\>[11]{}\rightarrow\;\Sigma(\!\;\Varid{s}\;\in\;\Conid{S}\;\!)\!\times\!\;(\Conid{P}\;\Varid{s}\;\rightarrow\;(\Conid{LIM}\;(\Conid{A},\Varid{a}))){}\<[E]%
+\>[11]{}\rightarrow\;(\!\;\Varid{s}\;\in\;\Conid{S}\;\!)\times\;(\Conid{P}\;\Varid{s}\;\rightarrow\;(\Conid{LIM}\;(\Conid{A},\Varid{a}))){}\<[E]%
 \ColumnHook
@@
 \column{E}{@{}>{\hspre}l<{\hspost}@{}}%
-\>[B]{}\Conid{T}_{\Conid{Ne}}\;\in\;\Conid{SPF}\;\bot\;\Conid{ℕ}{}\<[E]%
-\\
-\>[B]{}\Conid{T}_{\Conid{Ne}}\;\mathrel{=}\;\mu^{\text{\tiny T}}\;({}\<[17]%
+\>[B]{}\Conid{T}_{\Conid{NeLam}}\;\in\;\Conid{SPF}\;\bot\;\Conid{ℕ}{}\<[E]%
+\\
+\>[B]{}\Conid{T}_{\Conid{NeLam}}\;\mathrel{=}\;\mu^{\text{\tiny T}}\;({}\<[17]%
 \>[17]{}\Conid{SPF}\;(\lambda\;())\;\Conid{T}_{\Conid{Fin}}{}\<[E]%
@@
 \>[11]{}\mathbin{\uplus^{\text{\tiny T}}}\;{}\<[17]%
-\>[17]{}((\eta^{\text{\tiny T}}\;\ensuremath{\mbox{$\circ$}}\;\Varid{inr})\;\mathbin{\times^{\text{\tiny T}}}\;\Conid{TNeNf})){}\<[E]%
+\>[17]{}((\eta^{\text{\tiny T}}\;\ensuremath{\mbox{$\circ$}}\;\Varid{inr})\;\mathbin{\times^{\text{\tiny T}}}\;\Conid{T}_{\Conid{NeNf}})){}\<[E]%
 \\
@@
 \>[3]{}\Keyword{where}\;{}\<[10]%
-\>[10]{}\Conid{TNeNf}\;\in\;\Conid{SPF}\;(\bot\;\uplus\;\Conid{ℕ})\;\Conid{ℕ}{}\<[E]%
-\\
-\>[10]{}\Conid{TNeNf}\;\mathrel{=}\;\mu^{\text{\tiny T}}\;{}\<[23]%
+\>[10]{}\Conid{T}_{\Conid{NeNf}}\;\in\;\Conid{SPF}\;(\bot\;\uplus\;\Conid{ℕ})\;\Conid{ℕ}{}\<[E]%
+\\
+\>[10]{}\Conid{T}_{\Conid{NeNf}}\;\mathrel{=}\;\mu^{\text{\tiny T}}\;{}\<[23]%
 \>[23]{}({}\<[29]%
@@
 \\[\blanklineskip]%
-\>[B]{}\Conid{T}_{\Conid{Nf}}\;\in\;\Conid{SPF}\;\bot\;\Conid{ℕ}{}\<[E]%
-\\
-\>[B]{}\Conid{T}_{\Conid{Nf}}\;\mathrel{=}\;\mu^{\text{\tiny T}}\;{}\<[12]%
+\>[B]{}\Conid{T}_{\Conid{NfLam}}\;\in\;\Conid{SPF}\;\bot\;\Conid{ℕ}{}\<[E]%
+\\
+\>[B]{}\Conid{T}_{\Conid{NfLam}}\;\mathrel{=}\;\mu^{\text{\tiny T}}\;{}\<[12]%
 \>[12]{}({}\<[18]%
@@
 \>[12]{}\mathbin{\uplus^{\text{\tiny T}}}\;{}\<[18]%
-\>[18]{}\Conid{TNfNe}){}\<[E]%
+\>[18]{}\Conid{T}_{\Conid{NfNe}}){}\<[E]%
 \\
@@
 \>[3]{}\Keyword{where}\;{}\<[10]%
-\>[10]{}\Conid{TNfNe}\;\in\;\Conid{SPF}\;(\bot\;\uplus\;\Conid{ℕ})\;\Conid{ℕ}{}\<[E]%
-\\
-\>[10]{}\Conid{TNfNe}\;\mathrel{=}\;\mu^{\text{\tiny T}}\;{}\<[23]%
+\>[10]{}\Conid{T}_{\Conid{NfNe}}\;\in\;\Conid{SPF}\;(\bot\;\uplus\;\Conid{ℕ})\;\Conid{ℕ}{}\<[E]%
+\\
+\>[10]{}\Conid{T}_{\Conid{NfNe}}\;\mathrel{=}\;\mu^{\text{\tiny T}}\;{}\<[23]%
 \>[23]{}({}\<[29]%

### 2011-05-10 journal/paper.tex
bibs

--- 2011-05-10 journal/paper.tex
@@
 \column{B}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{20}{@{}>{\hspre}l<{\hspost}@{}}%
-\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
-\>[B]{}\Varid{\char95 !!\char95 }\;\in\;\{\mskip1.5mu \Conid{A}\;\in\;\Conid{Set}\mskip1.5mu\}\;\rightarrow\;\Conid{List}\;\Conid{A}\;\rightarrow\;\Conid{ℕ}\;\rightarrow\;\Conid{Maybe}\;\Conid{A}{}\<[E]%
-\\
-\>[B]{}[\mskip1.5mu \mskip1.5mu]\;\mathbin{!!}\;\Varid{n}\;{}\<[20]%
-\>[20]{}\mathrel{=}\;\Varid{nothing}{}\<[E]%
-\\
-\>[B]{}(\Varid{a}\;\Varid{∷}\;\Varid{as})\;\mathbin{!!}\;\Varid{zero}\;{}\<[20]%
-\>[20]{}\mathrel{=}\;\Varid{just}\;\Varid{a}{}\<[E]%
-\\
-\>[B]{}(\Varid{a}\;\Varid{∷}\;\Varid{as})\;\mathbin{!!}\;\Varid{suc}\;\Varid{n}\;{}\<[20]%
-\>[20]{}\mathrel{=}\;\Varid{as}\;\mathbin{!!}\;\Varid{n}{}\<[E]%
+\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
+\>[B]{}\Varid{\char95 !!\char95 }\;\in\;\{\mskip1.5mu \Conid{A}\;\in\;\Conid{Set}\mskip1.5mu\}\;\rightarrow\;\{\mskip1.5mu \Varid{n}\;\in\;\Conid{ℕ}\mskip1.5mu\}\;\rightarrow\;\Conid{Vec}\;\Conid{A}\;\Varid{n}\;\rightarrow\;\Conid{Fin}\;\Varid{n}\;\rightarrow\;\Conid{A}{}\<[E]%
+\\
+\>[B]{}[\mskip1.5mu \mskip1.5mu]\;\mathbin{!!}\;(){}\<[E]%
+\\
+\>[B]{}(\Varid{a}\;\Varid{∷}\;\Varid{as})\;\mathbin{!!}\;\Varid{zero}\;\mathrel{=}\;\Varid{a}{}\<[E]%
+\\
+\>[B]{}(\Varid{a}\;\Varid{∷}\;\Varid{as})\;\mathbin{!!}\;\Varid{suc}\;\Varid{n}\;\mathrel{=}\;\Varid{as}\;\mathbin{!!}\;\Varid{n}{}\<[E]%
 \ColumnHook
@@
 
-The equality type expresses the focussed character of the
-constructors for \ensuremath{\Conid{Fin}}.
+The equality type expresses the focussed character of the constructors
+for \ensuremath{\Conid{Fin}}. The mutual definition of \ensuremath{\Conid{NeLam}} and \ensuremath{\Conid{NfLam}} can be
+represented by two binary functors:
 
@@
 \\
-\>[B]{}\Conid{FNe}\;\Conid{X}\;\Conid{Y}\;\Varid{n}\;\mathrel{=}\;\Conid{Fin}\;\Varid{n}\;\uplus\;(\Conid{X}\;\Varid{n}\;\uplus\;\Conid{Y}\;\Varid{n}){}\<[E]%
+\>[B]{}\Conid{FNe}\;\Conid{X}\;\Conid{Y}\;\Varid{n}\;\mathrel{=}\;\Conid{Fin}\;\Varid{n}\;\uplus\;(\Conid{X}\;\Varid{n}\;\times\;\Conid{Y}\;\Varid{n}){}\<[E]%
 \\[\blanklineskip]%
@@
 
-\todo{Discuss mutual case.}
+We can construct \ensuremath{\Conid{NeLam}} and \ensuremath{\Conid{NfLam}} by an elimination procedure:
+first we define a parametrized initial algebra \ensuremath{\Conid{NeLam'}\;\in\;(\Conid{ℕ}\;\rightarrow\;\Conid{Set})\;\rightarrow\;\Conid{ℕ}\;\rightarrow\;\Conid{Set}} so that \ensuremath{\Conid{NeLam'}\;\Conid{Y}} is the initial algebra of \ensuremath{\lambda\;\Conid{X}\;\rightarrow\;\Conid{FNe}\;\Conid{X}\;\Conid{Y}}
+and then \ensuremath{\Conid{NfLam}} is the initial algebra of \ensuremath{\lambda\;\Conid{Y}\;\rightarrow\;\Conid{FNf}\;(\Conid{NeLam'}\;\Conid{Y})\;\Conid{Y}}.
+Symmetrically we derive \ensuremath{\Conid{NeLam}} --- compare this with the encoding in
+section \ref{sec:spf}.
 
@@
 This paper is an expanded and revised version of the LICS paper by the
-first and 3rd author \cite{lics}. In the present paper we have
+first and 3rd author \cite{alti:lics09}. In the present paper we have
 integrated the Agda formalisation in the main development, which in
@@
 relative monads which was only hinted at in the conference version
-based on the recent work on relative monads \cite{relmon}. We have
+based on the recent work on relative monads \cite{alti:fossacs10}. We have
 also dualized the development to terminal coalgebras which required
@@
 (section \ref{sec:mfromw})
-was already given in \cite{C-CSPTs} is revisited here exploiting the
+was already given in \cite{alti:cont-tcs} is revisited here exploiting the
 indexed W-type derived previously. moreover the development is formalized in
@@
 With these ingredients we obtain a theory which corresponds to
-extensional Type Theory \cite{hofmann-conservativity}.
+extensional Type Theory \cite{hofmann1996conservativity}.
 
@@
 The category of containers is a full and faithful sub-category of the functor category.
-We have also shown that the category of containers is cartesian closed (\cite{cie}, and is closed under formation of co-products.
+We have also shown that the category of containers is cartesian closed (\cite{txa:cie10}, and is closed under formation of co-products.
 
@@
 defined families where one type depends on another
-\cite{setzer-forsberg-indind}. A typical example is the syntax of Type
+\cite{forsberg2010inductive}. A typical example is the syntax of Type
 Theory itself which, to simplify, can be encoded by mutually defining
@@
 \end{hscode}\resethooks
-In recent work \cite{calco-indind} present a categorical semantics for
+In recent work \cite{txa:catind2} present a categorical semantics for
 this kind of definitions based on dialgebras. However, a presentation
